### 2019-05-09 bmc_article.tex
Update on Overleaf.

%% BioMed_Central_Tex_Template_v1.06
%%                                      %
%  bmc_article.tex            ver: 1.06 %
%                                       %

%%IMPORTANT: do not delete the first line of this template
%%It must be present to enable the BMC Submission system to
%%recognise this template!!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                     %%
%%  LaTeX template for BioMed Central  %%
%%     journal article submissions     %%
%%                                     %%
%%          <8 June 2012>              %%
%%                                     %%
%%                                     %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% For instructions on how to fill out this Tex template           %%
%% document please refer to Readme.html and the instructions for   %%
%% authors page on the biomed central website                      %%
%% http://www.biomedcentral.com/info/authors/                      %%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%% BioMed Central currently use the MikTex distribution of         %%
%% TeX for Windows) of TeX and LaTeX.  This is available from      %%
%% http://www.miktex.org                                           %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% additional documentclass options:
%  [doublespacing]
%  [linenumbers]   - put the line numbers on margins

%%% loading packages, author definitions

%\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
\documentclass{bmcart}

%%% Load packages
%\usepackage{amsthm,amsmath}
%\RequirePackage{natbib}
%\RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
\RequirePackage{hyperref}
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                             %%
%%  If you wish to display your graphics for   %%
%%  your own use using includegraphic or       %%
%%  includegraphics, then comment out the      %%
%%  following two lines of code.               %%
%%  NB: These line *must* be included when     %%
%%  submitting to BMC.                         %%
%%  All figure files must be submitted as      %%
%%  separate graphics through the BMC          %%
%%  submission process, not included in the    %%
%%  submitted article.                         %%
%%                                             %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\includegraphic{}
\def\includegraphics{}

%%% Put your definitions there:
\startlocaldefs
\endlocaldefs

%%% Begin ...
\begin{document}

%%% Start of article front matter
\begin{frontmatter}

\begin{fmbox}
\dochead{Research}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter the title of your article here     %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{The landscape of chloroplast genome assembly tools}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter the authors here                   %%
%%                                          %%
%% Specify information, if available,       %%
%% in the form:                             %%
%%   <key>={<id1>,<id2>}                    %%
%%   <key>=                                 %%
%% Comment or delete the keys which are     %%
%% not used. Repeat \author command as much %%
%% as required.                             %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
   corref={aff1},                       % id of corresponding address, if any
   noteref={n1},                        % id's of article notes, if any
   email={jane.e.doe@cambridge.co.uk}   % email address
]{\inits{JE}\fnm{Jane E} \snm{Doe}}

\author[
   addressref={aff1,aff2},
   email={markus.ankenbrand@uni-wuerzubrg.de}
]{\inits{MJA}\fnm{Markus J} \snm{Ankenbrand}}

\author[
    addressref={aff2},
    email={jan.freudenthal@uni-wuerzburg.de}
    ]{\inits{JAF}\fnm{Jan A} \snm{Freudenthal}}

\author[
   addressref={aff1,aff2},
   email={niklas.terhoeven@uni-wuerzubrg.de}
]{\inits{NT}\fnm{Niklas} \snm{Terhoeven}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter the authors' addresses here        %%
%%                                          %%
%% Repeat \address commands as much as      %%
%% required.                                %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\address[id=aff1]{%                           % unique id
  \orgname{Department of Bioinformatics, University of W\"{u}rzburg}, % university, etc
  \street{Biozentrum, Am Hubland},                     %
  \postcode{97074},                                % post or zip code
  \city{W\"{u}rzburg},                              % city
  \cny{Germany}                                    % country
}
\address[id=aff2]{%
  \orgname{Center for Computational and Theoretical Biology, University of W\"{u}rzburg},
  \street{Biozentrum, Am Hubland},
  \postcode{97074}
  \city{W\"{u}rzburg},
  \cny{Germany}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter short notes here                   %%
%%                                          %%
%% Short notes will be after addresses      %%
%% on first page.                           %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{artnotes}
%\note{Sample of title note}     % note to the article
\note[id=n1]{Equal contributor} % note, connected to author
\end{artnotes}

\end{fmbox}% comment this for two column layout

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% The Abstract begins here                 %%
%%                                          %%
%% Please refer to the Instructions for     %%
%% authors on http://www.biomedcentral.com  %%
%% and include the section headings         %%
%% accordingly for your article type.       %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstractbox}

\begin{abstract} % abstract
The special issue will accept manuscripts presenting:

- in-depth analyses of advantages

-limitations of state-of-the-art methods

-demonstration on a variety of representative datasets and simulations

-clear guidelines/recommendations for the end-user

-insight into future directions for methods
\parttitle{First part title} %if any
Text for this section.

\parttitle{Second part title} %if any
Text for this section.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% The keywords begin here                  %%
%%                                          %%
%% Put each keyword in separate \kwd{}.     %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{keyword}
\kwd{Chloroplast}
\kwd{Genome assembly}
\kwd{author}
\end{keyword}

% MSC classifications codes, if any
%\begin{keyword}[class=AMS]
%\kwd[Primary ]{}
%\kwd{}
%\kwd[; secondary ]{}
%\end{keyword}

\end{abstractbox}
%
%\end{fmbox}% uncomment this for twcolumn layout

\end{frontmatter}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% The Main Body begins here                %%
%%                                          %%
%% Please refer to the instructions for     %%
%% authors on:                              %%
%% http://www.biomedcentral.com/info/authors%%
%% and include the section headings         %%
%% accordingly for your article type.       %%
%%                                          %%
%% See the Results and Discussion section   %%
%% for details on how to create sub-sections%%
%%                                          %%
%% use \cite{...} to cite references        %%
%%  \cite{koon} and                         %%
%%  \cite{oreg,khar,zvai,xjon,schn,pond}    %%
%%  \nocite{smith,marg,hunn,advi,koha,mouse}%%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% start of article main body
% <put your article body there>

%%%%%%%%%%%%%%%%
%% Background %%
%%
\section*{Introduction}
\subsection*{General introduction and motivation}
Genome sequencing - important bilogical insights.
Eukaryotes have organelles with separate genomes.
Particularly plants have chloroplasts beside mitochondria (generally chloroplast or plastid? plastid bit more general, I think also chromoplasts etc).
Chloroplast genomes are widely used for evolutionary analyses.
Comparative genomics even more informative.
Complete chloro genome much easier to get than complete core genome.
But specific genome structure (esp. inverted repeat) makes automated resolution with short reads hard.
Many genome sequencing project contain chloroplast reads as a by-product even though that was not the aim of the study.
Resolved chloroplast helps to remove these reads which can improve assembly of the core.
Databases contain short read data for species where no reference chloroplast is available in the databases.
Resolving these would allow for more and larger scale comparative studies on whole chloroplasts.
Open question (?) structural variation across taxonomic groups.
Some researchers (e.g. Coissac et al.) use shallow genome sequencing to reconstruct full chloroplast genomes for use as super barcodes.

\subsection*{Chloroplast genome architecture}
Maybe separate section describing a prototypical chloroplast: LSC, IRa, SSC, IRb. Gene number and content. Size ranges. Evolutionary history incl. endosymbiontic gene transfer. Reduced genomes in parasitic plants. Loss of ndh gene family (maybe too specific). Preliminary SNP analysis in A. thaliana to estimate intraspecific variability? Is there anything known about intra-organismic variability (do some plants have multiple populations of chloroplasts? probably off topic).

\subsection*{Approaches to extracting chloroplasts from whole genome data}
1. Getting chloroplast reads out of mixed files
Mapping (potentially iterative), k-mer coverage analysis, seeded assembly
2. Assembly of chloroplast (incl special structure with IRs)
normal assembly - then blast, assembly then graph resolution, might be combined with step 1.

\subsection*{Purpose and scope of this study}
Clearly state criteria. Work with mixed data. Full automation. De novo - no manual selection of appropriate reference. No manual finishing. The step we are interested in is: from raw paired Illumina (!) reads to a fasta file containing the assembly (optimally full, circularized and on one contig). We are not interested in annotation or any additional contigs (genomic, mitochondrion, rRNA, etc.).
%\cite{koon,oreg,khar,zvai,xjon,schn,pond,smith,marg,hunn,advi,koha,mouse}

\section*{Methods}
Source code for all methods at \url{https://github.com/chloroExtractorTeam/benchmark} (zenodo doi), docker containers at ..., datasets at (zenodo links for simulated and real).

\subsection*{Inclusion Criteria}
List criteria that tools had to fulfill to be included in this study (maybe redundant with purpose and scope section).
List all programs that met the criteria with reference and very brief description:
org-asm, chloroExtractor, fast-plast, IOGA, NovoPlasty, GetOrganelle, chloroplast assembly protocol.
Name other relevant methods that were excluded (short description, reference, reason for exclusion).

\subsection*{Our Setup}
Defined interface, forward.fq and reverse.fq as only input. output.fa as only relevant output.
Docker container, all derived from main container, wrapper script makes all tools work conforming to the defined interface. Run docker containers for performance measurement and singularity containers on real datasets.
Singularity container were built from docker containers for usage on Julia-HPC of JMU using Singularity v.2.5.2 \cite{kurtzer2017singularity}
All singularity containers were run on the Julia-HPC on Intel® Xeon® Gold 6140 Processors using slurm workload manager version 17.11.8 \cite{Jette02slurm}. Assemblies run on 4 threads using 10 GB RAM with a timelimit of 48 hours

\subsection*{Data}
\subsubsection*{Simulated}
A. thaliana (TAIR10). Perfect data, sliding window with seqkit (circular for chloro and mito). No errors, no insert size variation, perfect quality, equal coverage.

\subsubsection*{Real}
Datasets in SRA with reference chloroplast in cp database.
Total of 380 SRA samples selected (see supplementary table?).

\subsection*{Evaluation Criteria}
\subsubsection*{Computational Resources}
Description of our performance measurement with docker. List metrics that are monitored, I/O, CPU, memory, ...
On simulated dataset with different read counts and different number of threads given.

\subsubsection*{Qualitative}
List evaluation criteria, cite JOSS reviewer guidelines.

The qualitative evaluation is mainly based on the reviewer guidelines for the Journal of Open Source
Software (JOSS). \textbf{TODO:CITE}
To create a standard environment, all tools were tested in a fresh default installation of Ubuntu 18.04.2 running in a virtual machine. The tools were installed according to their installation 
instructions and a tutorial was followed, if one existed. During the evaluation, the following
questions were asked:

\begin{itemize}
    \item Is the tool easy to install? 
    \item Is there a way to test the installation? 
    \item Is there a tutorial on how to use the tool? 
    \item Is there a good documentation on the parameter settings? 
    \item Is the tool maintained (issues answered, implementation of new features)? 
    \item Is the tool Open Source?
\end{itemize}

These questions were answered with "GOOD", "OK" or "BAD", depending on the quality of the result. 
For example, a "GOOD" installation utilizes a automated package or dependency management like apt,
CRAN, docker, etc. An "OK" installation procedure provides a custom script to install everything
or at least lists all dependencies. A "BAD" installation procedure fails to list important dependencies
or produces errors, that prevent a successful installation.

After an initial evaluation, we contacted all authors via their github or gitlab issue tracking to
report any flaws we found.

\subsubsection*{Quantitative}
We want to quantify continuity, completeness, correctness, repeat resolution.
We use continuity: number of contigs.
Completeness: Number of covered bases on reference (when aligning assembly).
Correctness: Number of covered bases in assembly (when aligning reference).
Repeat resolution: Difference between above two measures (indicates collapsed or expanded repeats)
%
%\nocite{oreg,schn,pond,smith,marg,hunn,advi,koha,mouse}

Foreach dataset and assembler the proposed chloroplast was compared to the respective reference chloroplast using minimap2 v2.16 for pairwise alignment \cite{li2018minimap2}.

\[ score = 1 - ( |1- cov_{ref}| +  |1- cov_{qry}| + |1- \frac{cov_{qry}}{cov_{ref}}| ) \]

%% score = 1 - (abs(1-ref_cov_frac) + abs(1-qry_cov_frac) + abs(1-rep_res) + abs(1-(1/contig_num))))

\section*{Results}
\subsection*{Computational Resources}
Table and figure of performance evaluation. Including RAM, I/O, runtime, parallelization ability, CPU usage. Free text description of results, range, mean/median, effect of input size, threads parameter, ...
\subsection*{Quantitative}

\includegraphics{Violin.png}

\subsection*{Qualitative}

\begin{table}[]
    \centering
\begin{tabular}{lcccccc}   
Tool & Installation & Test & Tutorial & Documentation & Maintenance & FLOSS\\                           \hline 
GetOrganelle & OK & BAD & OK & GOOD & GOOD & GOOD\\  
fast-plast & BAD & OK & OK & GOOD & GOOD & GOOD\\ 
org.ASM & BAD & OK & GOOD & OK & GOOD & GOOD\\ 
NOVOPlasty & GOOD & OK & OK & GOOD & GOOD & OK\\
ChloroExtractor & GOOD & OK & OK & GOOD & GOOD & GOOD\\
IOGA & BAD & BAD & BAD & OK & OK  & BAD\\
Chl Asm Prot & OK & OK & GOOD & OK & GOOD & GOOD\\ 
\end{tabular}      
    \caption{Overview of the results of the qualitative usability evaluation. Each tool 
    could score "GOOD", "OK" or "BAD" in each of the categories.}
    \label{tab:resultsQual}
\end{table}

Most of the tools were evaluated as mainly "GOOD" (see table \ref{tab:resultsQual}). However, a few critique points remained.
Two minor dependencies were missing in the GetOrganelle installation instructions. This was fixed by the authors after we opened an issue. There was also no test data available and an issue occurred when running it on a \textit{A. thaliana} dataset. We are currently in the process of resolving this with the authors.

Also the fast-plast installation instruction were missing some dependencies. Like GetOrganelle, fast-plast does not offer a test dataset or a tutorial, except from some example commands.

The org.ASM installation instructions did not work. We found some issues, which are probably related to the requirement of python3.7. Instead of a test, there is a tutorial with sample data available. However following this resulted in a segmentation fault.

The main critique points of NOVOPlasty was the lack of a test dataset with instructions. This was fixed by the authors after we contacted them. NOVOPlasty uses a custom license. An OSI approved license would be preferred here.

ChloroExtractor does come with a test dataset and a short tutorial. However, a way to evaluate the results of the test run would be nice.

The IOGA installation instructions were missing many dependencies. Also, there was no test data or tutorial available and there is no license assigned to it. Since there was no update to the github repository for the last three years, the project can be seen as inactive. After contact, the authors promised to resolve the mentioned issues.

As many of the other tools, the installation instructions for the Chloroplast Assembly Protocol were missing some dependencies. The list was updated after we contacted the authors. This tool does come with a test dataset, however a note about the expected outcome would be nice. A more extensive tutorial is provided. The description about the parameter is short, but seems to be sufficient.

\section*{Discussion}
Discuss Computational Resources. Implications of very long running. Also state minimum requirements on the hardware (RAM, CPUs, storage). Importance of this depends on use case (if goal is one single chloroplast

We evaluated all tools under the assumption that they are used in the most basic form (default parameters, no hand selected reference, no pre-processing of the data or post-processing of the result, restricted runtime). It is important to note that any tool might perform significantly different if parameters and references are fine-tuned for each dataset.

\subsection*{Clear guidelines for the end-user}
Which program (or combination of programs) to use? Does the decision depend on some parameter of the data (read length, amount, taxonomic group, ...)?

\subsection*{Ideas for future development}
Combining components from different tools might be a promising approach. E.g. read scaling from ChloroExtractor, assembly from GetOrganelle and structural resolution with fast-plast.
Mitigate installation issues e.g. by containerization.
Improve documentation and usability.
Maybe better integrated guessing of parameters (?) at least for automatization (but also because users tend to run a tool with default settings and look on what they get, only powerusers tweak parameters - and if it is possible to get a full chloroplast by guessing the best parameters there is no need for specific knowledge of parameters and their effects by the end user).
Other (more) data types, PacBio, nanopore.

\section*{Conclusion}
Short summary of clear guidelines and future development (might not be necessary as these are the last two sections of the Discussion anyway, so we might elect to skip this).

Put results back in context: the multitude of available tools shows importance to solve the challenge of chloro extraction. Presented benchmarking shows that all tools sometimes struggle even with ``perfect'' data. Although no program works everytime, most chloroplasts are resolved by at least one tool (is that so?). So programs are complementary, more effort to combine strengths of different methods (or automatic parameter selection - if failure is due to suboptimal parameters for the specific dataset).

Outlook: next step in the pipeline is annotation. There is a similar problem: many tools, which one to use? 
A large scale study reconstructing chloroplasts throughout SRA (or 1001 genome project) is feasible and promising using the existing tools (estimated runtime, number of novel chloroplasts).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Backmatter begins here                   %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{backmatter}

\section*{Competing interests}
  The authors disclose that SP, NT, FF, and MJA are developers of ChloroExtractor, one of the tools benchmarked in this article. The authors exercised caution not to let this fact unfairly influence their judgement.

\section*{Author's contributions}
    Text for this section \ldots

\section*{Acknowledgements}
  Text for this section \ldots
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                  The Bibliography                       %%
%%                                                         %%
%%  Bmc_mathpys.bst  will be used to                       %%
%%  create a .BBL file for submission.                     %%
%%  After submission of the .TEX file,                     %%
%%  you will be prompted to submit your .BBL file.         %%
%%                                                         %%
%%                                                         %%
%%  Note that the displayed Bibliography will not          %%
%%  necessarily be rendered by Latex exactly as specified  %%
%%  in the online Instructions for Authors.                %%
%%                                                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% if your bibliography is in bibtex format, use those commands:
\bibliographystyle{bmc-mathphys} % Style BST file (bmc-mathphys, vancouver, spbasic).
\bibliography{bmc_article}      % Bibliography file (usually '*.bib' )
% for author-year bibliography (bmc-mathphys or spbasic)
% a) write to bib file (bmc-mathphys only)
% @settings{label, options="nameyear"}
% b) uncomment next line
%\nocite{label}

% or include bibliography directly:
% \begin{thebibliography}
% \bibitem{b1}
% \end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                               %%
%% Figures                       %%
%%                               %%
%% NB: this is for captions and  %%
%% Titles. All graphics must be  %%
%% submitted separately and NOT  %%
%% included in the Tex document  %%
%%                               %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%
%% Do not use \listoffigures as most will included as separate files

\section*{Figures}
  \begin{figure}[h!]
  \caption{\csentence{Sample figure title.}
      A short description of the figure content
      should go here.}
      \end{figure}

\begin{figure}[h!]
  \caption{\csentence{Sample figure title.}
      Figure legend text.}
      \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                               %%
%% Tables                        %%
%%                               %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
\begin{table}[h!]
\caption{Sample table title. This is where the description of the table should go.}
      \begin{tabular}{cccc}
        \hline
           & B1  &B2   & B3\\ \hline
        A1 & 0.1 & 0.2 & 0.3\\
        A2 & ... & ..  & .\\
        A3 & ..  & .   & .\\ \hline
      \end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                               %%
%% Additional Files              %%
%%                               %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Additional Files}
  \subsection*{Additional file 1 --- Sample additional file title}
    Additional file descriptions text (including details of how to
    view the file, if it is in a non-standard format or the file extension).  This might
    refer to a multi-page table or a figure.

  \subsection*{Additional file 2 --- Sample additional file title}
    Additional file descriptions text.

\end{backmatter}
\end{document}

### 2019-05-13 code/evaluate_completeness.sh
Fixed contig name length issue

@@ -3,9 +3,10 @@
 REF=$1
 QRY=$2
 NAME=$3
-
-minimap2 -a -N 5 -x asm5 --cs -c $REF $QRY | samtools view -Sb | samtools sort >${NAME}_vs_ref.bam
-minimap2 -a -N 5 -x asm5 --cs -c $QRY $REF | samtools view -Sb | samtools sort >ref_vs_${NAME}.bam
+QRYF=$(tempfile)  
+cat $QRY | sed 's/>.*/>c/g' | seqkit rename  > $QRYF
+minimap2 -a -N 5 -x asm5 --cs -c $REF $QRYF | samtools view -Sb | samtools sort >${NAME}_vs_ref.bam
+minimap2 -a -N 5 -x asm5 --cs -c $QRYF $REF | samtools view -Sb | samtools sort >ref_vs_${NAME}.bam
 
 echo -ne "$NAME\t"
 bedtools genomecov -ibam ${NAME}_vs_ref.bam -bga | perl -ane '$l=$F[2]-$F[1];$t+=$l;$c+=$l if($F[3]>0);END{print "$t\t$c\t".($c/$t)}'

### 2019-05-13 code/eval_cov.r
Add plots

@@ -1,7 +1,31 @@
-require(tidyverse)
+dps = c("tidyverse","dabestr","UpSetR")                   
+sapply(dps,function(x){if(!require(x,character.only = T)){install.packages(x);library(x,character.only = T)}else{library(x,character.only = T)}})
+
+
+
 
 res <- read_tsv("res.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
 
 out_tibble <- res %>% mutate(rep_res =  qry_cov/ref_cov ) %>% mutate(score =  1 - (abs(1-ref_cov_frac) + abs(1-qry_cov_frac) + abs(1-rep_res) + abs(1-(1/contig_num))))
 
 out_tibble %>% ggplot(aes(x=assembler,y=dataset,fill=score)) + geom_tile() ;  ggsave("Plot.pdf")
+
+out_tibble %>% ggplot(aes(y=score,x=assembler)) + geom_violin(adjuts=1000) + coord_cartesian(ylim = c(-2.5, 1.25)) + geom_boxplot(alpha=0.25,width=0.25) + geom_jitter() ; ggsave("Violin.pdf")
+
+
+upssetlist  = out_tibble %>% filter(score>0.99)  %>% select(dataset,assembler) %>% split(.$assembler) %>% lapply("[[",1)
+
+
+pdf("UpSet.pdf")
+upset(fromList(upssetlist), order.by = "freq")
+dev.off()
+
+
+
+unpaired_mean_diff <- dabest(out_tibble %>% drop_na, y= score ,x= assembler,
+                             idx = unique(out_tibble$assembler),
+                             paired = F)
+
+plot("Swarm.pdf")
+plot(unpaired_mean_diff)
+dev.off()

### 2019-05-14 performance/parse_log_files.pl
Script to parse the logfile output

@@ -1,0 +1,214 @@
+#!/usr/bin/env perl
+
+use strict;
+use warnings;
+
+use JSON;
+use DateTime::Format::DateParse;
+
+use Bio::SeqIO;
+use Digest::MD5;
+
+my $inputdir = shift;
+my $prog     = shift;
+my $threads  = shift;
+my $seq_len  = shift;
+my $ratio    = shift;
+my $amount   = shift;
+my $replica  = shift;
+
+# build basename
+my $basename  = ( length($inputdir) > 0 ) ? $inputdir."/" : "";
+$basename    .= join("_", ($prog, $threads, $seq_len, $ratio, $amount, $replica));
+
+print STDERR "Searching for following basename: '$basename'\n";
+
+my ($start_time, 
+    $end_time, 
+    $overall_runtime, 
+    $cpu_time, 
+    $peak_cpu_usage, 
+    $peak_memory, 
+    $peak_disk_usage, 
+    $exit_code,
+    $num_contigs,
+    $total_seq_length,
+    $md5
+    )=(
+    "", 
+    "", 
+    "",
+    0,
+    0,
+    0,
+    0, 
+    "",
+    0,
+    0,
+    "-");
+
+# get the overall runtime from .json file
+my $filename = $basename.".json";
+if (-e $filename)
+{
+    my $json = get_json($filename);
+
+    $start_time      = DateTime::Format::DateParse->parse_datetime( $json->[0]{State}{StartedAt} );
+    $end_time        = DateTime::Format::DateParse->parse_datetime( $json->[0]{State}{FinishedAt} );
+    $overall_runtime = $end_time->epoch() - $start_time->epoch();
+    $exit_code       = $json->[0]{State}{ExitCode};
+}
+
+# get the CPU-usage and Memory from .stats.json file
+$filename = $basename.".stats.json";
+if (-e $filename)
+{
+    my $json = get_json($filename, 1);
+
+    foreach (@$json)
+    {
+	if (exists $_->{cpu_stats}{cpu_usage}{total_usage} && $_->{cpu_stats}{cpu_usage}{total_usage} > $cpu_time)
+	{
+	    $cpu_time = $_->{cpu_stats}{cpu_usage}{total_usage};
+	}
+
+	if (exists $_->{memory_stats}{max_usage} && $_->{memory_stats}{max_usage} > $peak_memory)
+	{
[…]

### 2019-05-14 code/eval_cov.r
Update score

@@ -1,31 +1,47 @@
-dps = c("tidyverse","dabestr","UpSetR")                   
+dps = c("tidyverse","dabestr","UpSetR","RColorBrewer","ggbeeswarm")                   
 sapply(dps,function(x){if(!require(x,character.only = T)){install.packages(x);library(x,character.only = T)}else{library(x,character.only = T)}})
 
 
 
 
-res <- read_tsv("res.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
+## load output file from alignment analyis
 
-out_tibble <- res %>% mutate(rep_res =  qry_cov/ref_cov ) %>% mutate(score =  1 - (abs(1-ref_cov_frac) + abs(1-qry_cov_frac) + abs(1-rep_res) + abs(1-(1/contig_num))))
+res <- read_tsv("res2.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
 
-out_tibble %>% ggplot(aes(x=assembler,y=dataset,fill=score)) + geom_tile() ;  ggsave("Plot.pdf")
+res_sim  <- read_tsv("res.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
 
-out_tibble %>% ggplot(aes(y=score,x=assembler)) + geom_violin(adjuts=1000) + coord_cartesian(ylim = c(-2.5, 1.25)) + geom_boxplot(alpha=0.25,width=0.25) + geom_jitter() ; ggsave("Violin.pdf")
+out_tibble <- res %>% mutate(rep_res = exp(-abs(log(qry_cov/ref_cov)))) %>%
+    mutate(score =  1 - (abs(1-ref_cov_frac) + abs(1-qry_cov_frac) + abs(1-rep_res) + abs(1-(1/contig_num))))
+
+head(out_tibble)
+
+## tile plot for simulated data 
+out_tibble_sim %>% ggplot(aes(x=assembler,y=dataset,fill=score)) + geom_tile() 
 
 
-upssetlist  = out_tibble %>% filter(score>0.99)  %>% select(dataset,assembler) %>% split(.$assembler) %>% lapply("[[",1)
+## swarm plot for 
+
[…]

### 2019-05-15 performance/run_benchmark_for_setting.sh
Avoiding race conditions for run which only differ in thread number

@@ -5,7 +5,9 @@ THREADS=$2
 LENGTH_READS=$3
 READ_RATIO=$4
 AMOUNT=$5
-REPLICATE=$6
+ITERATION=$6
+
+REPLICATE="${ITERATION}"_"${THREADS}"_"${RANDOM}"
 
 VERSION=v1.0
 
@@ -49,7 +51,7 @@ Parameters:
    Read length:              ${LENGTH_READS}
    Genome-chloroplast ratio: ${READ_RATIO}
    Input read number:        ${AMOUNT}
-   Replicate number:         ${REPLICATE}
+   Replicate number:         ${ITERATION}
 
 Output:
    Docker image to use:      ${DOCKERIMAGE}
@@ -57,6 +59,7 @@ Output:
    Assembler output folder:  ${OUTFOLDER}
    Name of output file:      ${NAME}
    Basename of logfolder:    ${LOGBASE}
+   Folder for calulations:   ${REPLICATE}
 
 EOF
 
@@ -142,6 +145,6 @@ docker rm ${DOCKERID}
 
 date +"[%Y-%m-%d %H:%M:%S] Removing output folder"
 cp "${REPLICATE}"/"${OUTFOLDER}"/output.fa ${LOGBASE}.output.fa
-rm -rf "${REPLICATE}"/"${OUTFOLDER}"
+rm -rf "${REPLICATE}"
 
 date +"[%Y-%m-%d %H:%M:%S] Finished benchmark"

### 2019-05-15 code/eval_cov.r
Update eval_cov.r

@@ -4,6 +4,7 @@ sapply(dps,function(x){if(!require(x,character.only = T)){install.packages(x);li
 
 
 
+
 ## load output file from alignment analyis
 
 res <- read_tsv("res2.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
@@ -11,37 +12,62 @@ res <- read_tsv("res2.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov"
 res_sim  <- read_tsv("res.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
 
 out_tibble <- res %>% mutate(rep_res = exp(-abs(log(qry_cov/ref_cov)))) %>%
-    mutate(score =  1 - (abs(1-ref_cov_frac) + abs(1-qry_cov_frac) + abs(1-rep_res) + abs(1-(1/contig_num))))
-
-head(out_tibble)
-
-## tile plot for simulated data 
-out_tibble_sim %>% ggplot(aes(x=assembler,y=dataset,fill=score)) + geom_tile() 
+    mutate(score =  (1 - ((abs(1-ref_cov_frac)/4) + (abs(1-qry_cov_frac)/4) + (abs(1-rep_res)/4) + (abs(1-(1/contig_num))/4)))*100)
 
 
-## swarm plot for 
 
-out_tibble %>% ggplot(aes(y=score,x=assembler,col=assembler)) + geom_boxplot(notch=F,alpha=0.3,width=0.2,color="black",fill="#c0c0c0")+ geom_quasirandom() + theme_bw()
+out_tibble_sim <- res_sim %>% mutate(rep_res = exp(-abs(log(qry_cov/ref_cov)))) %>%
+    mutate(score =  (1 - ((abs(1-ref_cov_frac)/4) + (abs(1-qry_cov_frac)/4) + (abs(1-rep_res)/4) + (abs(1-(1/contig_num))/4)))*100)
 
 
+my_col=brewer.pal(7,"Set2")
+
+## tile plot for simulated data
+
+out_tibble_sim %>% ggplot(aes(x=assembler,y=dataset,fill=score)) + geom_tile() + theme_bw()+
+    scale_fill_continuous(low = my_col[2] ,high = my_col[1]) +
[…]

### 2019-05-15 code/eval_cov.r
Update eval_cov.r

@@ -2,36 +2,41 @@ dps = c("tidyverse","dabestr","UpSetR","RColorBrewer","ggbeeswarm")
 sapply(dps,function(x){if(!require(x,character.only = T)){install.packages(x);library(x,character.only = T)}else{library(x,character.only = T)}})
 
 
-
-
-
 ## load output file from alignment analyis
+### order assemblers for ggplot
+res <- read_tsv("res2_clean.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
 
-res <- read_tsv("res2.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
+## simulated data 
+res_sim  <- read_tsv("res_clean.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
 
-res_sim  <- read_tsv("res.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
-
+## calculate the score for each assembly for real data
 out_tibble <- res %>% mutate(rep_res = exp(-abs(log(qry_cov/ref_cov)))) %>%
     mutate(score =  (1 - ((abs(1-ref_cov_frac)/4) + (abs(1-qry_cov_frac)/4) + (abs(1-rep_res)/4) + (abs(1-(1/contig_num))/4)))*100)
 
+## order the assemblers for ggplot
+out_tibble$assembler_f <- factor(out_tibble$assembler, levels=c("CAP","CE","Fast-Plast","GetOrganelle","IOGA","NOVOPlasty","org.ASM"))
 
 
+## calculate the score for each assembly for simulated  data 
 out_tibble_sim <- res_sim %>% mutate(rep_res = exp(-abs(log(qry_cov/ref_cov)))) %>%
     mutate(score =  (1 - ((abs(1-ref_cov_frac)/4) + (abs(1-qry_cov_frac)/4) + (abs(1-rep_res)/4) + (abs(1-(1/contig_num))/4)))*100)
 
+## order the assemblers for ggplot
+out_tibble_sim$assembler_f <- factor(out_tibble_sim$assembler,
[…]

### 2019-05-15 code/eval_cov.r
Add plot for reproducability estimate

@@ -96,14 +96,48 @@ run_log_mem$amount_f <- factor(run_log_mem$amount, levels=c("25K","250K","2.5M")
 run_log_mem %>% ggplot(aes(y=mag,x=as.factor(threads), fill=program)) + geom_boxplot()  + theme_bw() +
     scale_fill_manual(values=my_col) + facet_grid(usage~. ,scales = "free_y")  + scale_color_manual(values=my_col) +
     theme(text = element_text(size=15), legend.title=element_blank(),axis.title.y=element_blank()) +
-    xlab("Number of threads")
+    xlab("Number of threads") + scale_y_log10()
 ggsave("cpu_mem_disk_usage.pdf")
 
 
 
 ## plot disk usage and memory vs input size and number of threads 
 run_log_mem %>%   ggplot(aes(y=mag,x=as.factor(threads), fill=program)) + geom_boxplot()  +
-    theme_bw() +scale_fill_manual(values=my_col) + facet_grid(usage~amount_f ,scales = "free_y")  + scale_color_manual(values=my_col) +
+    theme_bw() +scale_fill_manual(values=my_col) + facet_grid(usage~amount_f ,scales = "free_y")  +
+    scale_color_manual(values=my_col) + 
     theme(text = element_text(size=15), legend.title=element_blank(),axis.title.y=element_blank()) +
     xlab("Number of threads") + scale_y_log10()
 ggsave("usage_amount_threads.pdf")
+
+
+
+### Analyze re runs
+
+
+res_re  <- read_tsv("res_re_clean.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
+
+
+out_tibble_re <- res_re %>% mutate(rep_res = exp(-abs(log(qry_cov/ref_cov)))) %>%
+    mutate(score =  (1 - ((abs(1-ref_cov_frac)/4) + (abs(1-qry_cov_frac)/4) + (abs(1-rep_res)/4) + (abs(1-(1/contig_num))/4)))*100)
+
+## order the assemblers for ggplot
+out_tibble_re$assembler_f <- factor(out_tibble_re$assembler, levels=c("CAP","CE","Fast-Plast","GetOrganelle","IOGA","NOVOPlasty","org.ASM"))
+
+
+##filter out_tibble with re run datasets
+
[…]

### 2019-05-15 code/eval_cov.r
Update eval_cov.r

@@ -1,4 +1,4 @@
-dps = c("tidyverse","dabestr","UpSetR","RColorBrewer","ggbeeswarm")                   
+dps = c("tidyverse","dabestr","UpSetR","RColorBrewer","ggbeeswarm","ggpmisc")                   
 sapply(dps,function(x){if(!require(x,character.only = T)){install.packages(x);library(x,character.only = T)}else{library(x,character.only = T)}})
 
 
@@ -132,12 +132,10 @@ out_re2 <- out_tibble_re[paste0(unlist(out_tibble_re[,1]),unlist(out_tibble_re[,
 
 out_j <- out_re %>% add_column(score_rerun = out_re2$score)
 out_j %>% ggplot(aes(x=score,y=score_rerun,col=assembler)) + geom_point()  + theme_bw() +
-    facet_wrap(~assembler,ncol=3,scales="free") +
+    facet_wrap(~assembler,ncol=3,scales="free") + geom_smooth(method="lm", se = T) +
+    stat_poly_eq(formula = x ~ y,parse=T) +
     guides(col=guide_legend(ncol=2)) +
     theme(legend.title = element_blank(),legend.position = c(0.5,0.2), text=element_text(size=15)) +
     xlab("Score run 1") + ylab("Score run 2")
 
 ggsave("repro.pdf")
-
-
-

### 2019-05-16 code/eval_cov.r
Update eval_cov.r

@@ -7,7 +7,7 @@ sapply(dps,function(x){if(!require(x,character.only = T)){install.packages(x);li
 res <- read_tsv("res2_clean.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
 
 ## simulated data 
-res_sim  <- read_tsv("res_clean.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
+res_sim  <- read_tsv("res_sim_clean.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
 
 ## calculate the score for each assembly for real data
 out_tibble <- res %>% mutate(rep_res = exp(-abs(log(qry_cov/ref_cov)))) %>%
@@ -45,7 +45,7 @@ ggsave("swarm.pdf")
 
 ### count the number of runs with output 
 n_obs = paste0("n=", out_tibble %>% drop_na %>% group_by(assembler) %>%  tally() %>% select(n) %>% unlist)
-
+n_obs
 
 ## create upsetplot 
 pdf("upset.pdf")
@@ -65,14 +65,14 @@ run_log <- read_tsv("log_clean.tsv")
 run_log[,14:15] <- run_log[,14:15]  / 10^9
 
 ## plot boxplots for computataion times 
-run_log %>% filter(exit_code==0) %>% ggplot(aes(y=run_time_sec,x=as.factor(threads), fill=program)) +
+run_log_mem %>% filter(exit_code==0) %>% ggplot(aes(y=run_time_sec,x=as.factor(program), fill=as.factor(threads))) +
     geom_boxplot() + 
     theme_bw() + scale_fill_manual(values=my_col) +
-    theme(text = element_text(size=15), legend.title=element_blank()) +
-    xlab("Number of threads") + ylab("Run time (s)") +
+    theme(text = element_text(size=15),legend.position = c(0.65,0.3)) +
+    guides(fill=guide_legend(title="Number of threads")) +
+    xlab("Assembler") + ylab("Run time (s)") + facet_wrap(amount_f~.,ncol=2) +
     scale_y_log10()
 
-coord_cartesian (ylim=c(0,3500))
[…]

### 2019-05-16 bmc_article.tex
Update on Overleaf.

@@
 %\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
+\usepackage{graphicx}
 
@@
     addressref={aff2},
+    email={simon-pfaff@gmx.de}
+    ]{\inits{SP}\fnm{Simon} \snm{Pfaff}}
+
+\author[
+    addressref={aff2},
     email={jan.freudenthal@uni-wuerzburg.de}
@@
 \author[
-   addressref={aff1,aff2},
+   addressref={aff2,aff3},
    email={niklas.terhoeven@uni-wuerzubrg.de}
@@
   \orgname{Center for Computational and Theoretical Biology, University of W\"{u}rzburg},
-  \street{Biozentrum, Am Hubland},
+  \street{Campus Hubland Nord},
   \postcode{97074}
+  \city{W\"{u}rzburg},
+  \cny{Germany}
+}
+\address[id=aff3]{%
+  \orgname{AnaLife Data Science},
+  \street{Friedrich-Bergius-Ring 15},
+  \postcode{97076}
   \city{W\"{u}rzburg},
@@
 \subsubsection*{Qualitative}
-List evaluation criteria, cite JOSS reviewer guidelines.
 
-The qualitative evaluation is mainly based on the reviewer guidelines for the Journal of Open Source
-Software (JOSS). \textbf{TODO:CITE}
-To create a standard environment, all tools were tested in a fresh default installation of Ubuntu 18.04.2 running in a virtual machine. The tools were installed according to their installation 
-instructions and a tutorial was followed, if one existed. During the evaluation, the following
+The qualitative evaluation is mainly based on the reviewer guidelines for the Journal of Open Source Software (JOSS) \cite{joss}.
+To create a standard environment, all tools were tested in a fresh default installation of Ubuntu 18.04.2 running in a virtual machine.
+The tools were installed according to their installation instructions and
+the provided tutorial or example usage was executed. During the evaluation, the following
 questions were asked:
@@
     \item Is the tool easy to install? 
-    \item Is there a way to test the installation? 
-    \item Is there a tutorial on how to use the tool? 
+    \item Is there a way to test the installation or a tutorial on how to use the tool? 
     \item Is there a good documentation on the parameter settings? 
@@
 
-\[ score = 1 - ( |1- cov_{ref}| +  |1- cov_{qry}| + |1- \frac{cov_{qry}}{cov_{ref}}| ) \]
+\[ score = 1 - ( |1- cov_{ref}| +  |1- cov_{qry}| + |1- e^{ \ln{\frac{cov_{qry}}{cov_{ref}}| }}) \]
 
 %% score = 1 - (abs(1-ref_cov_frac) + abs(1-qry_cov_frac) + abs(1-rep_res) + abs(1-(1/contig_num))))
+
+\subsubsection{reproducibility}
+For reproducibility testing we randomly choose 100 data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
+The resulting assemblies were scored again as described above and the scores of the 1.
+and the 2.
+run were compared to each other.
 
@@
 \begin{tabular}{lcccccc}   
-Tool & Installation & Test & Tutorial & Documentation & Maintenance & FLOSS\\                           \hline 
-GetOrganelle & OK & BAD & OK & GOOD & GOOD & GOOD\\  
-fast-plast & BAD & OK & OK & GOOD & GOOD & GOOD\\ 
-org.ASM & BAD & OK & GOOD & OK & GOOD & GOOD\\ 
-NOVOPlasty & GOOD & OK & OK & GOOD & GOOD & OK\\
-ChloroExtractor & GOOD & OK & OK & GOOD & GOOD & GOOD\\
-IOGA & BAD & BAD & BAD & OK & OK  & BAD\\
-Chl Asm Prot & OK & OK & GOOD & OK & GOOD & GOOD\\ 
+Tool & Installation & Test/Tutorial & Documentation & Maintenance & FLOSS\\                           \hline 
+GetOrganelle    & OK   & OK   & GOOD & GOOD & GOOD\\  
+Fast-Plast      & BAD  & OK   & GOOD & GOOD & GOOD\\ 
+org.ASM         & BAD  & BAD  & OK   & GOOD & GOOD\\ 
+NOVOPlasty      & GOOD & GOOD & GOOD & GOOD & OK\\
+CE & GOOD & GOOD & GOOD & GOOD & GOOD\\
+IOGA            & BAD  & BAD  & OK   & OK   & BAD\\
+CAP    & OK   & GOOD & OK   & GOOD & GOOD\\ 
 \end{tabular}      
@@
 Two minor dependencies were missing in the GetOrganelle installation instructions.
-This was fixed by the authors after we opened an issue.
-There was also no test data available and an issue occurred when running it on a \textit{A.
-thaliana} dataset.
+There was also no test data available and an issue occurred when running it on a \textit{A.~thaliana} dataset.
 We are currently in the process of resolving this with the authors.
 
-Also the fast-plast installation instruction were missing some dependencies. Like GetOrganelle, fast-plast does not offer a test dataset or a tutorial, except from some example commands.
+The fast-plast installation instructions were missing some dependencies. Like GetOrganelle, fast-plast does not offer a test dataset or a tutorial, except from some example commands.
 
@@
 We found some issues, which are probably related to the requirement of python3.7.
-Instead of a test, there is a tutorial with sample data available.
-However following this resulted in a segmentation fault.
+There is a tutorial with sample data available.
+However following the instructions resulted in a segmentation fault.
+We found a workaround for this bug and contacted the authors.
 
-The main critique points of NOVOPlasty was the lack of a test dataset with instructions.
+The main critique point of NOVOPlasty was the lack of a test dataset with instructions.
 This was fixed by the authors after we contacted them.
@@
 The description about the parameter is short, but seems to be sufficient.
+
+\subsection*{Quantitative}
+\subsubsection*{Simulated data}
+\textit{tile plot for simulated data goes here}
+The only assembler obtaining perfect results according to our score for the simulated datasets is getOrganelle.
+IOGA and CAP showed the worst performance being unable to fully assemble a single chloroplast out of 14.
+NOVOPlasty performed second best with scores above 80 for all datasets, only failing to resolve the chloroplast contig into one single circular assembly.
+As could have been expected the overall performance is best, when the input data data consists purely of chloroplast reads.
+Only IOGA and CAP failed to deliver any results once each.
+Besides that no clear causality between length of the input reads, ratio of core vs chloroplast reads and the performance can be clearly observed.
+
+\subsubsection*{real data sets}
+\textit{swarm plot goes here }
+%% Den upset plot eventuell erst in die Discussion reinbringen ? Da wir davon ableiten welche tools wir empfehlen?
+
+\subsubsection{Reproducability}
+\textit{plot repro.pdf goes here}
+
+\subsection*{Performance metrics}
+
+\subsubsection*{Time requirements}
+
+\textit{plot comp_time_log.pdf goes here}
+
+\subsubsection*{Memory and CPU Usage }
+\textit{plot usage_amout_threads.pdf goes here}
+
+\[ CAP_n=221 , CE_n=205 , Fast-Plast_n=352 , GetOrganelle_n=356" IOGA_n=296, NOVOPlasty_n=270 org.ASM_n=228 \]
 
@@
 \section*{Author's contributions}
-    Text for this section \ldots
+    MJA and FF conceived of the presented idea and supervised the findings of this manuscript.
+SP and FF created the docker images.
+NT performed the qualitative analysis for all assemblers.
+MJA prepared the simulated and real data sets.
+JAF assembled the real data sets.
+FF ran the performance assemblies on the simulated data sets.
+All authors developed the score model.
+JAF and MJA implemented the score model and prepared the figures.
+All authors discussed the results and contributed to the final manuscript.
 

### 2019-05-17 bmc_article.tex
Update on Overleaf.

@@
 
-\def\includegraphic{}
-\def\includegraphics{}
+%\def\includegraphic{}
+%\def\includegraphics{}
 
@@
 \startlocaldefs
+\newcommand{\formatprogramnames}[1]{\texttt{#1}}
+\newcommand{\ce}{\formatprogramnames{chloroExtractor}}
+\newcommand{\oa}{\formatprogramnames{ORG.Asm}}
+\newcommand{\fp}{\formatprogramnames{Fast-Plast}}
+\newcommand{\ioga}{\formatprogramnames{IOGA}}
+\newcommand{\np}{\formatprogramnames{NOVOPlasty}}
+\newcommand{\go}{\formatprogramnames{GetOrganelle}}
+\newcommand{\cassp}{\formatprogramnames{Chloroplast assembly protocol}}
+\newcommand{\docker}[2]{\href{https://cloud.docker.com/u/chloroextractorteam/repository/docker/chloroextractorteam/#1}{chloroextracteam/#1:#2}}
+\newcommand{\dockerce}{\docker{benchmark\_chloroextractor}{v2.0.0}}
+\newcommand{\dockercesha}{sha256:8f49e03424b37e699c5fea9391f79dbb9f2d0dc550ce86c4c700f39deec2dacd}
 \endlocaldefs
@@
 \author[
-   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
-   corref={aff1},                       % id of corresponding address, if any
-   noteref={n1},                        % id's of article notes, if any
-   email={jane.e.doe@cambridge.co.uk}   % email address
-]{\inits{JE}\fnm{Jane E} \snm{Doe}}
-
-\author[
-   addressref={aff1,aff2},
-   email={markus.ankenbrand@uni-wuerzubrg.de}
-]{\inits{MJA}\fnm{Markus J} \snm{Ankenbrand}}
-
+    addressref={aff2},
+    noteref={n1},
+    email={jan.freudenthal@uni-wuerzburg.de}
+    ]{\inits{JAF}\fnm{Jan A} \snm{Freudenthal}}
 \author[
     addressref={aff2},
+    noteref={n1},
     email={simon-pfaff@gmx.de}
     ]{\inits{SP}\fnm{Simon} \snm{Pfaff}}
-
-\author[
-    addressref={aff2},
-    email={jan.freudenthal@uni-wuerzburg.de}
-    ]{\inits{JAF}\fnm{Jan A} \snm{Freudenthal}}
-
 \author[
@@
 ]{\inits{NT}\fnm{Niklas} \snm{Terhoeven}}
+\author[
+   addressref={aff1,aff2},
+   noteref={n2},
+   email={markus.ankenbrand@uni-wuerzubrg.de}
+]{\inits{MJA}\fnm{Markus J} \snm{Ankenbrand}}
+\author[
+   addressref={aff1,aff4},                   % id's of addresses, e.g. {aff1,aff2}
+   corref={aff1},                       % id of corresponding address, if any
+   noteref={n2},                        % id's of article notes, if any
+   email={frank.foerster@uni-wuerzburg.de}   % email address
+]{\inits{FF}\fnm{Frank} \snm{Förster}}
 
@@
 
-\address[id=aff1]{%                           % unique id
+\address[id=aff2]{%                           % unique id
   \orgname{Department of Bioinformatics, University of W\"{u}rzburg}, % university, etc
@@
 }
-\address[id=aff2]{%
+\address[id=aff1]{%
   \orgname{Center for Computational and Theoretical Biology, University of W\"{u}rzburg},
@@
   \city{W\"{u}rzburg},
+  \cny{Germany}
+}
+\address[id=aff4]{%
+  \orgname{Fraunhofer IME-BR},
+  \street{Winchester Str.\ 2},
+  \postcode{97076}
+  \city{Gie\ss{}en},
   \cny{Germany}
@@
 \note[id=n1]{Equal contributor} % note, connected to author
+\note[id=n2]{Corresponding author} % note, connected to author
 \end{artnotes}
@@
 Eukaryotes have organelles with separate genomes.
-Particularly plants have chloroplasts beside mitochondria (generally chloroplast or plastid? plastid bit more general, I think also chromoplasts etc).
+Particularly, plants have chloroplasts beside mitochondria (generally chloroplast or plastid? plastid bit more general, I think also chromoplasts etc).
+Chloroplast genome content and structure reviewed elsewhere \cite{wicke_evolution_2011,green_chloroplast_2011}.
 Chloroplast genomes are widely used for evolutionary analyses.
 Comparative genomics even more informative.
-Complete chloro genome much easier to get than complete core genome.
+Complete chloroplast genome much easier to get than complete core genome.
 But specific genome structure (esp. inverted repeat) makes automated resolution with short reads hard.
@@
 Databases contain short read data for species where no reference chloroplast is available in the databases.
+There is a lot of potential use cases for chloroplast genomes \cite{tonti-filippini_what_2017}
 Resolving these would allow for more and larger scale comparative studies on whole chloroplasts.
 Open question (?) structural variation across taxonomic groups.
-Some researchers (e.g. Coissac et al.) use shallow genome sequencing to reconstruct full chloroplast genomes for use as super barcodes.
+Some researchers use shallow genome sequencing to reconstruct full chloroplast genomes for use as super-barcodes \cite{coissac_barcodes_2016}.
 
@@
 Source code for all methods at \url{https://github.com/chloroExtractorTeam/benchmark} (zenodo doi), docker containers at ..., datasets at (zenodo links for simulated and real).
+This study adheres to the guidelines for computational method benchmarking \cite{weber_essential_2018}.
 
@@
 List all programs that met the criteria with reference and very brief description:
-org-asm, chloroExtractor, fast-plast, IOGA, NovoPlasty, GetOrganelle, chloroplast assembly protocol.
+\oa{}, \ce{}, \fp{}, \ioga{}, \np{}, \go{}, \cassp{}.
 Name other relevant methods that were excluded (short description, reference, reason for exclusion).
@@
 \subsection*{Our Setup}
+\dockerce{}
+
 Defined interface, forward.fq and reverse.fq as only input. output.fa as only relevant output.
@@
 
-\[ score = 1 - ( |1- cov_{ref}| +  |1- cov_{qry}| + |1- e^{ \ln{\frac{cov_{qry}}{cov_{ref}}| }}) \]
+\[ score = 1 - \frac{1}{4} \cdot \left( |1- cov_{ref}| +  |1- cov_{qry}| + \left|1- e^{-\left| \ln{\frac{cov_{qry}}{cov_{ref}}}\right|}\right| + \left| 1 - \frac{1}{n_{contigs}} \right| \right) \]
+
+Ich glaube diese Formel lässt sich vereinfachen zu:
+\[ score = \frac{1}{4} \cdot \left( cov_{ref} +  cov_{qry} + e^{-\left| \ln{\frac{cov_{qry}}{cov_{ref}}}\right|} + \frac{1}{n_{contigs} }\right) \]
 
@@
 
-\subsubsection{reproducibility}
+\subsubsection*{reproducibility}
 For reproducibility testing we randomly choose 100 data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
@@
 
-\includegraphics{Violin.png}
-
 \subsection*{Qualitative}
@@
     \centering
-\begin{tabular}{lcccccc}   
-Tool & Installation & Test/Tutorial & Documentation & Maintenance & FLOSS\\                           \hline 
-GetOrganelle    & OK   & OK   & GOOD & GOOD & GOOD\\  
-Fast-Plast      & BAD  & OK   & GOOD & GOOD & GOOD\\ 
-org.ASM         & BAD  & BAD  & OK   & GOOD & GOOD\\ 
-NOVOPlasty      & GOOD & GOOD & GOOD & GOOD & OK\\
-CE & GOOD & GOOD & GOOD & GOOD & GOOD\\
-IOGA            & BAD  & BAD  & OK   & OK   & BAD\\
-CAP    & OK   & GOOD & OK   & GOOD & GOOD\\ 
-\end{tabular}      
     \caption{Overview of the results of the qualitative usability evaluation. Each tool 
@@
     \label{tab:resultsQual}
+\begin{tabular}{lcccccc}   
+Tool & Installation & Test/Tutorial & Documentation & Maintenance & FLOSS\\                           \hline 
+\go{}    & OK   & OK   & GOOD & GOOD & GOOD\\  
+\fp{}      & BAD  & OK   & GOOD & GOOD & GOOD\\ 
+\oa{}         & BAD  & BAD  & OK   & GOOD & GOOD\\ 
+\np{}      & GOOD & GOOD & GOOD & GOOD & OK\\
+\ce{} & GOOD & GOOD & GOOD & GOOD & GOOD\\
+\ioga{}            & BAD  & BAD  & OK   & OK   & BAD\\
+\cassp{}    & OK   & GOOD & OK   & GOOD & GOOD\\ 
+\end{tabular}      
 \end{table}
@@
 Most of the tools were evaluated as mainly "GOOD" (see table \ref{tab:resultsQual}). However, a few critique points remained.
-Two minor dependencies were missing in the GetOrganelle installation instructions.
+Two minor dependencies were missing in the \go{} installation instructions.
 There was also no test data available and an issue occurred when running it on a \textit{A.~thaliana} dataset.
@@
 
-The fast-plast installation instructions were missing some dependencies. Like GetOrganelle, fast-plast does not offer a test dataset or a tutorial, except from some example commands.
+The \fp{ installation instructions were missing some dependencies. Like \go{}, \fp{} does not offer a test dataset or a tutorial, except from some example commands.
 
-The org.ASM installation instructions did not work.
+The \oa{} installation instructions did not work.
 We found some issues, which are probably related to the requirement of python3.7.
@@
 
-The main critique point of NOVOPlasty was the lack of a test dataset with instructions.
+The main critique point of \np{} was the lack of a test dataset with instructions.
 This was fixed by the authors after we contacted them.
-NOVOPlasty uses a custom license.
+\np{} uses a custom license.
 An OSI approved license would be preferred here.
 
-ChloroExtractor does come with a test dataset and a short tutorial. However, a way to evaluate the results of the test run would be nice.
+The \ce{} does come with a test dataset and a short tutorial. However, a way to evaluate the results of the test run would be nice.
 
-The IOGA installation instructions were missing many dependencies.
+The \ioga{} installation instructions were missing many dependencies.
 Also, there was no test data or tutorial available and there is no license assigned to it.
@@
 
-As many of the other tools, the installation instructions for the Chloroplast Assembly Protocol were missing some dependencies.
+As many of the other tools, the installation instructions for the \cassp{} were missing some dependencies.
 The list was updated after we contacted the authors.
@@
 \textit{tile plot for simulated data goes here}
-The only assembler obtaining perfect results according to our score for the simulated datasets is getOrganelle.
-IOGA and CAP showed the worst performance being unable to fully assemble a single chloroplast out of 14.
-NOVOPlasty performed second best with scores above 80 for all datasets, only failing to resolve the chloroplast contig into one single circular assembly.
+The only assembler obtaining perfect results according to our score for the simulated datasets is \go{}.
+\ioga{} and CAP showed the worst performance being unable to fully assemble a single chloroplast out of 14.
+\np{} performed second best with scores above 80 for all datasets, only failing to resolve the chloroplast contig into one single circular assembly.
 As could have been expected the overall performance is best, when the input data data consists purely of chloroplast reads.
-Only IOGA and CAP failed to deliver any results once each.
+Only \ioga{} and CAP failed to deliver any results once each.
 Besides that no clear causality between length of the input reads, ratio of core vs chloroplast reads and the performance can be clearly observed.
@@
 \subsubsection*{real data sets}
-\textit{swarm plot goes here }
+\textit{swarm plot goes here}
 %% Den upset plot eventuell erst in die Discussion reinbringen ? Da wir davon ableiten welche tools wir empfehlen?
@@
 
-\textit{plot comp_time_log.pdf goes here}
+\textit{plot comp\_time\_log.pdf goes here}
 
 \subsubsection*{Memory and CPU Usage }
-\textit{plot usage_amout_threads.pdf goes here}
+\textit{plot usage\_amout\_threads.pdf goes here}
 
-\[ CAP_n=221 , CE_n=205 , Fast-Plast_n=352 , GetOrganelle_n=356" IOGA_n=296, NOVOPlasty_n=270 org.ASM_n=228 \]
+\[ CAP_n=221 , CE_n=205 , Fast-Plast_n=352 , GetOrganelle_n=356 IOGA_n=296, NOVOPlasty_n=270 org.ASM_n=228 \]
 
@@
 \subsection*{Ideas for future development}
-Combining components from different tools might be a promising approach. E.g. read scaling from ChloroExtractor, assembly from GetOrganelle and structural resolution with fast-plast.
+Combining components from different tools might be a promising approach. E.g. read scaling from \ce{}, assembly from \go{} and structural resolution with fast-plast.
 Mitigate installation issues e.g. by containerization.
@@
 \section*{Competing interests}
-  The authors disclose that SP, NT, FF, and MJA are developers of ChloroExtractor, one of the tools benchmarked in this article.
+  The authors disclose that SP, NT, FF, and MJA are developers of \ce{}, one of the tools benchmarked in this article.
 The authors exercised caution not to let this fact unfairly influence their judgement.
@@
   \begin{figure}[h!]
+  \includegraphics[width=\textwidth]{plots/swarm.pdf}
   \caption{\csentence{Sample figure title.}
@@
 \begin{figure}[h!]
+  \includegraphics[width=\textwidth]{plots/usage_amount_threads.pdf}
+  \caption{\csentence{Sample figure title.}
+      Figure legend text.}
+      \end{figure}
+
+\begin{figure}[h!]
+  \includegraphics[width=\textwidth]{plots/sim_tiles.pdf}
+  \caption{\csentence{Sample figure title.}
+      Figure legend text.}
+      \end{figure}
+
+\begin{figure}[h!]
+  \includegraphics[width=\textwidth]{plots/repro.pdf}
+  \caption{\csentence{Sample figure title.}
+      Figure legend text.}
+      \end{figure}
+
+\begin{figure}[h!]
+  \includegraphics[width=\textwidth]{plots/comp_time_log.pdf}
+  \caption{\csentence{Sample figure title.}
+      Figure legend text.}
+      \end{figure}
+
+\begin{figure}[h!]
+  \includegraphics[width=\textwidth,page=2]{plots/upset.pdf}
   \caption{\csentence{Sample figure title.}

### 2019-05-17 bmc_article.tex
Update on Overleaf.

@@
 
+\usepackage{cleveref}
+
+\usepackage{biocon}
+\newplant{At}{genus=Arabidopsis,epithet=thaliana}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \newcommand{\cassp}{\formatprogramnames{Chloroplast assembly protocol}}
+
+% Niklas table
+%\newcommand{\ok}{\textcolor[rgb]{0.7,0.7,0}{\textsc{\bfseries{}OKAY}}}
+%\newcommand{\bad}{\textcolor{red}{\textsc{\bfseries{}BAD}}}
+%\newcommand{\good}{\textcolor[rgb]{0,0.6,0}{\textsc{\bfseries{}GOOD}}}
+\newcommand{\ok}{\textsc{Okay}}
+\newcommand{\bad}{\textsc{Bad}}
+\newcommand{\good}{\textsc{Good}}
+
+% List of docker images
 \newcommand{\docker}[2]{\href{https://cloud.docker.com/u/chloroextractorteam/repository/docker/chloroextractorteam/#1}{chloroextracteam/#1:#2}}
 \newcommand{\dockerce}{\docker{benchmark\_chloroextractor}{v2.0.0}}
-\newcommand{\dockercesha}{sha256:8f49e03424b37e699c5fea9391f79dbb9f2d0dc550ce86c4c700f39deec2dacd}
+\newcommand{\dockercesha}{\texttt{8f49e03424b37e699c5fea9391f79dbb9f2d0dc550ce86c4c700f39deec2dacd}}
+\newcommand{\dockeroa}{\docker{benchmark\_org-asm}{v2.0.0}}
+\newcommand{\dockeroasha}{\texttt{ff83677c97b7c4e346191b9e04a5162eeea2a8dfd9e60ff84067d33747868f60}}
+\newcommand{\dockerfp}{\docker{benchmark\_fastplast}{v2.0.0}}
+\newcommand{\dockerfpsha}{\texttt{a3d06a610f8340ba49c3ff3b27342534e2a5348b17caa4fd3c3f3d327243a272}}
+\newcommand{\dockerioga}{\docker{benchmark\_ioga}{v2.0.0}}
+\newcommand{\dockeriogasha}{\texttt{4698a21c343c60290bbf16811165a654ff01e8fddeb41cd75d0771b7f45968c0}}
+\newcommand{\dockernp}{\docker{benchmark\_novoplasty}{v2.0.0}}
+\newcommand{\dockernpsha}{\texttt{106387bad4e8e5c53fb9d4c3bdd60cdddf05a47b52a38697369eeabb947c547c}}
+\newcommand{\dockergo}{\docker{benchmark\_getorganelle}{v2.0.0}}
+\newcommand{\dockergosha}{\texttt{2ed3a464a82025a196ea56c649d0b0a3472cef76994bb065d56054d93298d956}}
+\newcommand{\dockercassp}{\docker{benchmark\_chloroplast\_assembly\_protocol}{v2.0.0}}
+\newcommand{\dockercasspsha}{\texttt{d10d2317103d91fadec4cb1d5466ac109f23176ad74b6f44f0179175f050155d}}
 \endlocaldefs
@@
 \subsection*{General introduction and motivation}
-Genome sequencing - important bilogical insights.
+Genome sequencing - important biological insights.
 Eukaryotes have organelles with separate genomes.
@@
 Loss of ndh gene family (maybe too specific).
-Preliminary SNP analysis in A.
-thaliana to estimate intraspecific variability?
+Preliminary SNP analysis in \plant{At} to estimate intraspecific variability?
 Is there anything known about intra-organismic variability (do some plants have multiple populations of chloroplasts?
@@
 \section*{Methods}
-Source code for all methods at \url{https://github.com/chloroExtractorTeam/benchmark} (zenodo doi), docker containers at ..., datasets at (zenodo links for simulated and real).
+Source code for all methods is available at \url{https://github.com/chloroExtractorTeam/benchmark} and archived under (zenodo doi).
+All docker images are published on \url{https://cloud.docker.com/u/chloroextractorteam/} and are named with a leading \texttt{benchmark\_} (\cref{tab:dockerimages}).
+datasets at (zenodo links for simulated and real).
 This study adheres to the guidelines for computational method benchmarking \cite{weber_essential_2018}.
@@
 \subsubsection*{Simulated}
-A. thaliana (TAIR10). Perfect data, sliding window with seqkit (circular for chloro and mito). No errors, no insert size variation, perfect quality, equal coverage.
+\plant{At} (TAIR10). Perfect data, sliding window with seqkit (circular for chloro and mito). No errors, no insert size variation, perfect quality, equal coverage.
 
@@
 
-These questions were answered with "GOOD", "OK" or "BAD", depending on the quality of the result. 
-For example, a "GOOD" installation utilizes a automated package or dependency management like apt,
-CRAN, docker, etc. An "OK" installation procedure provides a custom script to install everything
-or at least lists all dependencies. A "BAD" installation procedure fails to list important dependencies
+These questions were answered with \good{}, \ok{} or \bad{}, depending on the quality of the result. 
+For example, a \good{} installation utilizes a automated package or dependency management like apt,
+CRAN, docker, etc. An \ok{} installation procedure provides a custom script to install everything
+or at least lists all dependencies. A \bad{} installation procedure fails to list important dependencies
 or produces errors, that prevent a successful installation.
@@
 Free text description of results, range, mean/median, effect of input size, threads parameter, ...
-\subsection*{Quantitative}
 
 \subsection*{Qualitative}
-
-\begin{table}[]
-    \centering
-    \caption{Overview of the results of the qualitative usability evaluation. Each tool 
-    could score "GOOD", "OK" or "BAD" in each of the categories.}
-    \label{tab:resultsQual}
-\begin{tabular}{lcccccc}   
-Tool & Installation & Test/Tutorial & Documentation & Maintenance & FLOSS\\                           \hline 
-\go{}    & OK   & OK   & GOOD & GOOD & GOOD\\  
-\fp{}      & BAD  & OK   & GOOD & GOOD & GOOD\\ 
-\oa{}         & BAD  & BAD  & OK   & GOOD & GOOD\\ 
-\np{}      & GOOD & GOOD & GOOD & GOOD & OK\\
-\ce{} & GOOD & GOOD & GOOD & GOOD & GOOD\\
-\ioga{}            & BAD  & BAD  & OK   & OK   & BAD\\
-\cassp{}    & OK   & GOOD & OK   & GOOD & GOOD\\ 
-\end{tabular}      
-\end{table}
-
-Most of the tools were evaluated as mainly "GOOD" (see table \ref{tab:resultsQual}). However, a few critique points remained.
+Most of the tools were evaluated as mainly \good{} (see table \ref{tab:resultsQual}). However, a few critique points remained.
 Two minor dependencies were missing in the \go{} installation instructions.
-There was also no test data available and an issue occurred when running it on a \textit{A.~thaliana} dataset.
+There was also no test data available and an issue occurred when running it on a \plant{At} dataset.
 We are currently in the process of resolving this with the authors.
 
-The \fp{ installation instructions were missing some dependencies. Like \go{}, \fp{} does not offer a test dataset or a tutorial, except from some example commands.
+The \fp{} installation instructions were missing some dependencies. Like \go{}, \fp{} does not offer a test dataset or a tutorial, except from some example commands.
 
@@
 The only assembler obtaining perfect results according to our score for the simulated datasets is \go{}.
-\ioga{} and CAP showed the worst performance being unable to fully assemble a single chloroplast out of 14.
+\ioga{} and \cassp{} showed the worst performance being unable to fully assemble a single chloroplast out of 14.
 \np{} performed second best with scores above 80 for all datasets, only failing to resolve the chloroplast contig into one single circular assembly.
-As could have been expected the overall performance is best, when the input data data consists purely of chloroplast reads.
-Only \ioga{} and CAP failed to deliver any results once each.
+(As could have been expected -> discussion) the overall performance is best, when the input data consists purely of chloroplast reads.
+Only \ioga{} and \cassp{} failed to deliver any results once each.
 Besides that no clear causality between length of the input reads, ratio of core vs chloroplast reads and the performance can be clearly observed.
@@
 \subsubsection*{real data sets}
+Highest scoring is \go{} next is \fp{} while \ioga{} and \cassp{} perform poorly, never reaching a score of 1 (figure 1). TODO: median/mean score, mad/sd Tabelle
+
 \textit{swarm plot goes here}
@@
 
+\begin{figure}[h!]
+  \includegraphics[width=\textwidth]{plots/real_datasets_tree.pdf}
+  \caption{\csentence{Sample figure title.}
+      Figure legend text.}
+      \end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section*{Tables}
+\begin{table}[]
+    \centering
+    \caption{Overview of the results of the qualitative usability evaluation. Each tool 
+    could score \good{}, \ok{} or \bad{} in each of the categories.}
+    \label{tab:resultsQual}
+\begin{tabular}{p{3cm}cccccc}   
+Tool & Installation & Test/Tutorial & Documentation & Maintenance & FLOSS\\                           \hline \ce{}     &  \good{}  &  \good{}  &  \good{}  &  \good{}  &  \good{} \\
+\cassp{}  &  \ok{}    &  \good{}  &  \ok{}    &  \good{}  &  \good{} \\
+\fp{}     &  \bad{}   &  \ok{}    &  \good{}  &  \good{}  &  \good{} \\
+\go{}     &  \ok{}    &  \ok{}    &  \good{}  &  \good{}  &  \good{} \\
+\ioga{}   &  \bad{}   &  \bad{}   &  \ok{}    &  \ok{}    &  \bad{}  \\
+\np{}     &  \good{}  &  \good{}  &  \good{}  &  \good{}  &  \ok{}   \\
+\oa{}     &  \bad{}   &  \bad{}   &  \ok{}    &  \good{}  &  \good{} \\ \hline
+\end{tabular}      
+\end{table}
+
+\begin{table}[h!]
+\caption{Docker images used in our benchmark setup.}
+\label{tab:dockerimages}
+\centering
+      \resizebox{\textwidth}{!}{\begin{tabular}{ccc}
+        \hline
+          Tool & Image name and tag & SHA256 Checksum   \\ \hline
+          \ce & \dockerce & \dockercesha \\
+          \cassp & \dockercassp & \dockercasspsha \\
+          \fp & \dockerfp & \dockerfpsha \\
+          \go & \dockergo & \dockergosha \\
+          \ioga & \dockerioga & \dockeriogasha \\
+          \np & \dockernp & \dockernpsha \\
+          \oa & \dockeroa & \dockeroasha \\ \hline
+      \end{tabular}}
+\end{table}
+
 \begin{table}[h!]

### 2019-05-20 code/eval_cov.r
Update eval_cov.r

@@ -51,8 +51,8 @@ n_obs
 pdf("upset.pdf")
 UL  = out_tibble %>% filter(score>99)  %>% select(dataset,assembler) %>% split(.$assembler) %>% lapply("[[",1)
 upset(fromList(UL), order.by = "freq",sets.bar.color=my_col[c(4,3,6,7,2)],
-      point.size=5,matrix.color = my_col[3],shade.color = my_col[c(1,5,4)],
-      shade.alpha = 0.5, main.bar.color = colorRamps::green2red(20),text.scale = 1.5)
+      point.size=5,matrix.color = my_col[3],
+      shade.alpha = 0.5, text.scale = 1.5)
 dev.off()
 
 
@@ -64,8 +64,13 @@ run_log <- read_tsv("log_clean.tsv")
 ## convert bytes to GB in log file 
 run_log[,14:15] <- run_log[,14:15]  / 10^9
 
+run_log_mem <- run_log %>%  filter(exit_code==0) %>%
+    gather(key="usage",value="mag", cpu_usage_percent, peak_cpu_usage_percent, peak_memory_bytes,peak_disk_usage_bytes)
+run_log_mem$amount_f <- factor(run_log_mem$amount, levels=c("25K","250K","2.5M"))
+
 ## plot boxplots for computataion times 
-run_log_mem %>% filter(exit_code==0) %>% ggplot(aes(y=run_time_sec,x=as.factor(program), fill=as.factor(threads))) +
+run_log_mem %>% filter(exit_code==0) %>%
+    ggplot(aes(y=run_time_sec,x=as.factor(program), fill=as.factor(threads))) +
     geom_boxplot() + 
     theme_bw() + scale_fill_manual(values=my_col) +
     theme(text = element_text(size=15),legend.position = c(0.65,0.3)) +
@@ -78,8 +83,7 @@ ggsave("comp_time_log.pdf")
 
 ##plot memory and cpu usage
 ## convert tibble to long format for ggplot
-run_log_mem <- run_log %>%  filter(exit_code==0) %>%
-    gather(key="usage",value="mag", cpu_usage_percent, peak_cpu_usage_percent, peak_memory_bytes,peak_disk_usage_bytes)
+
 
 ##rename usage parameters in tibble for ggplot
 new_usages = c("CPU usage (%)" , "Peak CPU usage (%)"," Peak memory (GB)", "Peak disk usage (GB)")
[…]

### 2019-05-20 bmc_article.tex
Update on Overleaf.

@@
 \subsection*{General introduction and motivation}
-Genome sequencing - important biological insights.
-Eukaryotes have organelles with separate genomes.
-Particularly, plants have chloroplasts beside mitochondria (generally chloroplast or plastid? plastid bit more general, I think also chromoplasts etc).
+The chloroplast as the photosynthetic organelle harboring its own genome has been an early target for sequencing.
+The first chloroplast genome sequences were obtained as early as 1986 \cite{ohyama_chloroplast_1986,shinozaki_complete_1986}.
+These efforts elucidated the general genome organization and structure of chloroplasts, expanded by many more studies over the years.
 Chloroplast genome content and structure reviewed elsewhere \cite{wicke_evolution_2011,green_chloroplast_2011}.
-Chloroplast genomes are widely used for evolutionary analyses.
-Comparative genomics even more informative.
-Complete chloroplast genome much easier to get than complete core genome.
-But specific genome structure (esp. inverted repeat) makes automated resolution with short reads hard.
-Many genome sequencing project contain chloroplast reads as a by-product even though that was not the aim of the study.
-Resolved chloroplast helps to remove these reads which can improve assembly of the core.
-Databases contain short read data for species where no reference chloroplast is available in the databases.
+Chloroplast genomes are widely used for evolutionary analyses (TODO cite), barcoding (TODO cite), and meta-barcoding (TODO cite).
+Interesting aspect of chloroplast genomes are their reduced size through endosymbiotic gene transfer \cite{martin_evolutionary_2002,timmis_endosymbiotic_2004} and the strong conservation of the remaining genes (cite).
+Despite the overall high conservation there are striking differences between groups (e.g.
+loss of whole gene families like ndh genes in /textit{Droseraceae} \cite{nevill_plastome-wide_2019} and extreme evolutionary cases with very low GC content and a modified genetic code \cite{su_novel_2019}).
+These differences call for comparative genomic approaches.
+
+It is much easier to decipher the complete chloroplast genome than the complete core genome (cite?).
+However, the specific genome structure (esp. the large inverted repeat) complicates automated resolution with short read technologies (cite?).
+Many genome sequencing projects contain chloroplast reads as by-product.
+In some cases the chloroplast data is even considered contamination so experimental protocols for reducing their content have been developed \cite{lutz_isolation_2011}.
+The resolved chloroplast genome helps to remove these reads, which can improve assembly of the core genome.
+Databases exist, containing short read data for species where no reference chloroplast is publicly available.
 There is a lot of potential use cases for chloroplast genomes \cite{tonti-filippini_what_2017}
-Resolving these would allow for more and larger scale comparative studies on whole chloroplasts.
-Open question (?) structural variation across taxonomic groups.
-Some researchers use shallow genome sequencing to reconstruct full chloroplast genomes for use as super-barcodes \cite{coissac_barcodes_2016}.
+Resolving these (hidden treasures) would allow for more and larger scale comparative studies on whole chloroplasts.
+In a different application researchers use shallow genome sequencing to reconstruct full chloroplast genomes for use as super-barcodes \cite{coissac_barcodes_2016}.
+There are also applications in biotechnology and genetic engineering \cite{daniell_chloroplast_2016}.
 
@@
 normal assembly - then blast, assembly then graph resolution, might be combined with step 1.
+\cite{twyford_strategies_2017}
 
@@
 
-\subsubsection*{reproducibility}
+\subsubsection*{Reproducibility}
 For reproducibility  testing we randomly choose 100 data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
@@
 
-\subsubsection{Reproducability}
+\subsubsection*{Reproducibility}
 \textit{plot repro.pdf goes here}
+
+Reproducibility was tested as described above, by re-unning assemblies and comparison of the scores of the two assemblies.
+Figure N shows the scores of the 1.
+runs versus the scores of the 2.
+scores.
+Runs that did not produce an output were manually scored with 0.
+\go{}  was the only tool that succeeded in obtaining similar scores for all the assemblies, without having and completely unsuccessful assemblies for this subset of data.
+Except for \fp{} all the other tools had at least one assembly that was unsuccessful in either runs, but produced on output in the other.
+Notably \ioga{} appears to have a tendency of being able to perform differently in independent runs.
+More that 10 \% of the assemblies failed once, but were successful in the other run.
+
+Both \fp{} and \np{} tend to have minor changes in the assembly when the overall performance is comparably well, leading to the arrow-shaped scatter plots.
+\ce{} and \cassp{} only have few deviations between the two runs, besides a few one-time non-performing datasets, the other all scored the same.
+1
 
@@
 \textit{plot comp\_time\_log.pdf goes here}
+
+In terms of time efficiency there was a great difference between input datasets, number of threads and the tool in use ranging from a few minutes to several hours.
+Some assemblies failed to finsih within the time-limit we set at 48 hours.
+On average the longest time to complete assemblies was taken by \ioga{} and \fb{} followed by \oa{} and \go{} the most time efficient overall was \ce{} with on average is a little faster than \np{} and \cassp{}
+%% multithreading
+Not all the tools were able to benefit from having access to multiple threads.
+Both \no and \oa take about the same time independent of being able to utilize 1,2,4 or 8 threads.
+\cassp{}, \ce{} , \go and \fb{} all profit from multi-threading
 
@@
   \includegraphics[width=\textwidth]{plots/repro.pdf}
-  \caption{\csentence{Sample figure title.}
+  \caption{\csentence{Scatterplot of scores between two independent runs for reproducibility testing}
       Figure legend text.}

### 2019-05-20 bmc_article.tex
Update on Overleaf.

@@
 
-\[ score = 1 - \frac{1}{4} \cdot \left( |1- cov_{ref}| +  |1- cov_{qry}| + \left|1- e^{-\left| \ln{\frac{cov_{qry}}{cov_{ref}}}\right|}\right| + \left| 1 - \frac{1}{n_{contigs}} \right| \right) \]
+\[ score = \frac{1}{4} \cdot \left( cov_{ref} +  cov_{qry} + e^{-\left| \ln{\frac{cov_{qry}}{cov_{ref}}}\right|} + \frac{1}{n_{contigs} }\right) \]
 
-Ich glaube diese Formel lässt sich vereinfachen zu:
-\[ score = \frac{1}{4} \cdot \left( cov_{ref} +  cov_{qry} + e^{-\left| \ln{\frac{cov_{qry}}{cov_{ref}}}\right|} + \frac{1}{n_{contigs} }\right) \]
+% equivalenter Vorschlag mit min anstatt e^ln
+
+\[ score = \frac{1}{4} \cdot \left( cov_{ref} +  cov_{qry} + min\left\{ \frac{cov_{qry}}{cov_{ref}}, \frac{cov_{ref}}{cov_{qry}}\right\} + \frac{1}{n_{contigs} }\right) \cdot 100  \]
 
@@
   \includegraphics[width=\textwidth]{plots/usage_amount_threads.pdf}
-  \caption{\csentence{Sample figure title.}
-      Figure legend text.}
+  \caption{\csentence{Performance metrics}
+      Boxplots depictiing the demand of CPU and RAM and disk space needed depending on the assembler, input data size and number of threads}
       \end{figure}
@@
   \includegraphics[width=\textwidth]{plots/sim_tiles.pdf}
-  \caption{\csentence{Sample figure title.}
+  \caption{\csentence{Score of assemblies on simulated data}
       Figure legend text.}
@@
   \includegraphics[width=\textwidth]{plots/repro.pdf}
-  \caption{\csentence{Scatterplot of scores between two independent runs for reproducibility testing}
-      Figure legend text.}
+  \caption{\csentence{Scores between two independent runs for reproducibility testing}
+      }
       \end{figure}
@@
   \includegraphics[width=\textwidth]{plots/comp_time_log.pdf}
-  \caption{\csentence{Sample figure title.}
-      Figure legend text.}
+  \caption{\csentence{Computation time depending on number of threads and size of input data}
+  }
       \end{figure}
@@
   \includegraphics[width=\textwidth,page=2]{plots/upset.pdf}
-  \caption{\csentence{Sample figure title.}
-      Figure legend text.}
+  \caption{\csentence{Upset plot \cite{lex2014upset} comparing success of assemblers on the real data sets}
+      The plot shows the intersection of success ($score > 99$) between assemblers.
+For 69 datasets only \go{} was able to obtain a complete chloroplast.
+43 were successful with both \go{} and \fp{} and so on}
       \end{figure}
@@
   \includegraphics[width=\textwidth]{plots/real_datasets_tree.pdf}
-  \caption{\csentence{Sample figure title.}
+  \caption{\csentence{Sucess of assemblers on real data sets on tree derived from ncbi taxonomy \cite{ncbi2011}}
       Figure legend text.}

### 2019-05-21 bmc_article.tex
Update on Overleaf.

@@
 Chloroplast genome content and structure reviewed elsewhere \cite{wicke_evolution_2011,green_chloroplast_2011}.
-Chloroplast genomes are widely used for evolutionary analyses (TODO cite), barcoding (TODO cite), and meta-barcoding (TODO cite).
+Chloroplast genomes are widely used for evolutionary analyses \cite{martin_plastid_2010,xiao-ming_inferring_2017}, barcoding \cite{kress_use_2005,hollingsworth_dna_2009,de_vere_dna_2015}, and meta-barcoding \cite{bell_review_2016,deiner_environmental_2017}.
 Interesting aspect of chloroplast genomes are their reduced size through endosymbiotic gene transfer \cite{martin_evolutionary_2002,timmis_endosymbiotic_2004} and the strong conservation of the remaining genes (cite).
@@
 \subsection*{Purpose and scope of this study}
-Clearly state criteria.
+The goal of this study is to compare the effectiveness and efficiency of existing tools to de-novo assemble whole chloroplast genomes from raw mixed genomic datasets with minimal configuration.
+This means: no data prep, no specific reference (but \plant{At} if required), default parameters, no manual finishing.
+We further restricted our benchmark to paired Illumina datasets as these are the most common (cite?) and most (all?) tools in this study can not handle any other types.
+
+In our opinion this reflects the most common use cases: (1) a user trying a tool quickly without digging into options for fine tuning and (2) large scale automatic applications.
+Still, we acknowledge that the performance of the tools might be significantly improved by optimizing parameters (and references if applicable) for each dataset specifically.
+(However, this was outside the scope of this study.)
+
+%Clearly state criteria.
 Work with mixed data.
@@
 List all programs that met the criteria with reference and very brief description:
-\oa{}, \ce{}, \fp{}, \ioga{}, \np{}, \go{}, \cassp{}.
+\oa{}, \ce{}, \fp{}, \ioga{}, \np{} \cite{dierckxsens_novoplasty:_2017}, \go{}, \cassp{}.
 Name other relevant methods that were excluded (short description, reference, reason for exclusion).
@@
 A large scale study reconstructing chloroplasts throughout SRA (or 1001 genome project) is feasible and promising using the existing tools (estimated runtime, number of novel chloroplasts).
+A meta-tool that automatically combines the different programs could be developed.
+The benchmarking study could be augmented to automatically select the closest reference from the database and provide that to any tool that can take advantage of references.
 
@@
   The authors disclose that SP, NT, FF, and MJA are developers of \ce{}, one of the tools benchmarked in this article.
-The authors exercised caution not to let this fact unfairly influence their judgement.
+The authors exercised caution not to let this fact unfairly influence their judgment.
 

### 2019-05-22 docker/wrapper.sh
Fix change of CPUTHREADS for CAP by rewriting the original perl script

@@ -242,8 +242,6 @@ then
 
     0_get_cp_reads.pl input cp_noref $REFERENCE
 
-    # set threads
-    sed -i 's/\(CPUTHREADS[[:space:]]*=[[:space:]]*\)[0-9]*/\1'${NUMCPUS}'/g' $(which 1_cleanreads.pl)
     1_cleanreads.pl -folder cp_noref
 
     if [ -e cp_noref/cleanreads.txt ]

### 2019-05-22 docker/wrapper.sh
Fix the creation of empty output.fa files if CAP finishes, but did not create a sspace.final.scaffolds.fasta

@@ -249,8 +249,12 @@ then
 	sed 's/[[:space:]]*nd[[:space:]]*nd[[:space:]]*/ FR 250 /g' cp_noref/cleanreads.txt >cp_noref/assembly_pe
 	2_assemble_reads.pl cp_noref assembly_pe -threads ${NUMCPUS}
 
-	find -name "sspace.final.scaffolds.fasta" | sort | head -1 | xargs -I{} cp {} output.fa
-    else
+	find -name "sspace.final.scaffolds.fasta" | sort | head -1 | xargs --no-run-if-empty -I{} cp {} output.fa
+    fi
+
+    # finally check if an output file exists, if not, create an empty one
+    if [ ! -e output.fa ]
+    then
 	touch output.fa
     fi
 fi

### 2019-05-22 docker/wrapper.sh
Change env var for CAP

@@ -195,7 +195,7 @@ EOF
 
 fi
 
-if [ -n "$CHLOROPLASTASSEMBLYPROTOCOL" ]
+if [ -n "$CHLOROPLASTASSEMBLYPROTOCOLVERSION" ]
 then
     date +"[%Y-%m-%d %H:%M:%S] Starting chloroplast-assembly-protocol"
 

### 2019-05-27 bmc_article.tex
Update on Overleaf.

@@
 
-\usepackage{cleveref}
+\usepackage[noabbrev]{cleveref}
+\usepackage{siunitx}
+\DeclareSIUnit \basepair{bp}
+\DeclareSIUnit \byte{B}
+\DeclareSIPrefix\mebi{Mi}{10}
+\DeclareSIPrefix\gibi{Gi}{10}
 
@@
 %\def\includegraphics{}
+
+\usepackage{todonotes}
 
@@
 \author[
-    addressref={aff2},
+    addressref={aff2,aff3},
     noteref={n1},
@@
 \author[
-   addressref={aff1,aff2},
+   addressref={aff1,aff2,aff3 },
    noteref={n2},
@@
 Despite the overall high conservation there are striking differences between groups (e.g.
-loss of whole gene families like ndh genes in /textit{Droseraceae} \cite{nevill_plastome-wide_2019} and extreme evolutionary cases with very low GC content and a modified genetic code \cite{su_novel_2019}).
+loss of whole gene families like ndh genes in \textit{Droseraceae} \cite{nevill_plastome-wide_2019} and extreme evolutionary cases with very low GC content and a modified genetic code \cite{su_novel_2019}).
 These differences call for comparative genomic approaches.
@@
 \subsection*{Approaches to extracting chloroplasts from whole genome data}
+\todo{ausbauen}
 1. Getting chloroplast reads out of mixed files
@@
 This means: no data prep, no specific reference (but \plant{At} if required), default parameters, no manual finishing.
-We further restricted our benchmark to paired Illumina datasets as these are the most common (cite?) and most (all?) tools in this study can not handle any other types.
+We further restricted our benchmark to paired Illumina datasets as these are the most common \todo{cite?} and most \todo{(all?)} tools in this study can not handle any other types.
 
@@
 \section*{Methods}
-Source code for all methods is available at \url{https://github.com/chloroExtractorTeam/benchmark} and archived under (zenodo doi).
+Source code for all methods is available at \url{https://github.com/chloroExtractorTeam/benchmark} and archived under \todo{(zenodo doi)}.
 All docker images are published on \url{https://cloud.docker.com/u/chloroextractorteam/} and are named with a leading \texttt{benchmark\_} (\cref{tab:dockerimages}).
-datasets at (zenodo links for simulated and real).
+datasets at \todo{(zenodo links for simulated and real)}.
 This study adheres to the guidelines for computational method benchmarking \cite{weber_essential_2018}.
 
-\subsection*{Inclusion Criteria}
-List criteria that tools had to fulfill to be included in this study (maybe redundant with purpose and scope section).
-List all programs that met the criteria with reference and very brief description:
-\oa{}, \ce{}, \fp{}, \ioga{}, \np{} \cite{dierckxsens_novoplasty:_2017}, \go{}, \cassp{}.
-Name other relevant methods that were excluded (short description, reference, reason for exclusion).
+\subsection*{Tool Selection}
+
+We included tools designed for assembling chloroplasts from whole genome paired end Illumina sequencing data.
+The tools must be available as open source software and allow execution via a command line interface \todo{das noch oben in der scope section erwähnen}.
+A graphical user interface is not suitable for
+running automated comparisons. The following tools were determined to be within the scope of this study:
+
+\oa{} \cite{coissac_barcodes_2016}, 
+\ce{} \cite{j_ankenbrand_chloroextractor:_2018}, 
+\fp{} \cite{mckain__fast-plast_2017}, 
+\ioga{} \cite{bakker_herbarium_2016}, 
+\np{} \cite{dierckxsens_novoplasty:_2017}, 
+\go{} \cite{jin_getorganelle:_2018}, 
+\cassp{} \cite{sancho_comparative_2018}.
+
+Other related tools for assembling chloroplasts but outside the scope of this study are \texttt{Organelle PBA} \cite{Soorni2017}, a protocol for \texttt{Genious}, \texttt{sestaton/Chloro}, \texttt{Norgal} and \texttt{MitoBim}.
+\texttt{Organelle PBA} is designed for PacBio data and does not work with paired Illumina data only.
+\texttt{Genious} software \todo{cite - die empfohlene Ref passt nicht da wir Geneious ja gar nicht verwenden, wir bräuchten eine ref die sagt, dass es das protocol gibt @niklas.
+\url{https://support.geneious.com/hc/en-us/articles/227534768-How-do-I-cite-Geneious-in-a-paper-}} is closed source and GUI based.
+\texttt{sestaton/Chloro} (\url{https://github.com/sestaton/Chloro}) fits all criteria but is flagged as a work in progress and development seems to have ended two years ago.
+\texttt{Norgal} \cite{Al-Nakeeb2017} is a tool to extract organellar DNA from whole genome data based on a k-mer frequency approach.
+However the final output is a set of contigs of mixed mitochondrial and plastid origin.
+The suggested approach to get a finished chloroplast genome is to run \np{} on the ten longest contigs.
+\texttt{MitoBim} is specifically designed for mitochondrial genomes.
+Even though there is a claim by the author that it can be used for chloroplasts as well (\url{https://github.com/chrishah/MITObim/issues/16}, accessed: 2019-05-27), there is no further description on how to do that.
+\todo{haben wir es versucht?}
+\todo{method description paper - war das method description paper nicht das chloroplast assembly protocol? @niklas}
 
 \subsection*{Our Setup}
-\dockerce{}
-
+\todo{ausformulieren}
 Defined interface, forward.fq and reverse.fq as only input. output.fa as only relevant output.
@@
 Singularity container were built from docker containers for usage on Julia-HPC of JMU using Singularity v.2.5.2 \cite{kurtzer2017singularity}
-All singularity containers were run on the Julia-HPC on Intel® Xeon® Gold 6140 Processors using slurm workload manager version 17.11.8 \cite{Jette02slurm}.
-Assemblies run on 4 threads using 10 GB RAM with a timelimit of 48 hours
-
+All singularity containers were run on the Julia-HPC on Intel® Xeon® Gold \num{6140} Processors using slurm workload manager version 17.11.8 \cite{Jette02slurm}.
+Assemblies run on \num{4} threads using \SI{10}{\gibi\byte} RAM with a timelimit of \SI{48}{\hour}.
 \subsection*{Data}
 \subsubsection*{Simulated}
-\plant{At} (TAIR10). Perfect data, sliding window with seqkit (circular for chloro and mito). No errors, no insert size variation, perfect quality, equal coverage.
+To avoid suffering from sequencing errors and biological variances, we simulated perfect reads based on the \plant{At} (TAIR10) chloroplast assembly \cite{tair10}.
+Therefore we used a sliding window approach with seqkit \cite{seqkit} \todo{seqkit parameter - würde ich hier nicht erwähnen, seqkit wurde mehrfach mit verschiedenen sub commands und parametern aufgerufen, die genaue Doku ist hier: \url{https://github.com/chloroExtractorTeam/benchmark/blob/master/03_representative_datasets.md}}.
+For the final simulated data sets reads based on pseudo mixtures of TAIR10's core and chloroplast genome:  \num{0}:\num{1}, \num{1}:\num{10}, \num{1}:\num{100}, and \num{1}:\num{1000}.
+Additionally, we generated different read lengths (\SIlist{150;250}{\basepair}).
+
+%(circular for chloro and mito). No errors, no insert size variation, perfect quality, equal coverage.
 
 \subsubsection*{Real}
-Datasets in SRA with reference chloroplast in cp database.
-Total of 380 SRA samples selected (see supplementary table?).
+We downloaded sequencing data from SRA \cite{sra2010} of all organisms with a reference
+chloroplast in CpBase \cite{cpbase}.
+In total, this accumulated to \num{380} datasets, including \num{6} without data and \num{5} with malformatted data.
+This leads to a total set of \num{369} datasets \todo{see supplementary table?}.
 
@@
 \subsubsection*{Computational Resources}
-Description of our performance measurement with docker. List metrics that are monitored, I/O, CPU, memory, ...
-On simulated dataset with different read counts and different number of threads given.
+Due to computational resources are limited, we evaluated the effect of different input parameters.
+To monitor the influence, we recorded the mean and the peak CPU usage, the peak memory consumption, and the size of the assembly folder. 
+As input data, we used different data sets comprising \numlist{25000;250000;2500000} read pairs based on our simulated perfect reads.
+Therefore, the simulated perfect read files have been read repeatedly to achieve the required number of read pairs.
+We used our docker image setup (\cref{tab:dockerimages}) to run all assembly programs three times on a given parameter setting.
+The setting combined the different input data and different number of threads to use (\numlist{1;2;4;8}).
+Some programs used more CPU threads than specified, therefore, the number of CPUs available have been fixed using the CPUs option while running the docker run command.
+For each assembly setting, we recorded the peak memory consumption, the CPU usage for calculation of mean and peak CPU usage, and the size of the folder where the assembly was calculated.
+The values of CPU and memory usage have been obtained by docker.
+The disk usage was estimated using the GNU tool du.
+We used GNU parallel for queuing of the different settings \cite{Tange2011a}.
 
@@
 To create a standard environment, all tools were tested in a fresh default installation of Ubuntu 18.04.2 running in a virtual machine.
+We chose this setup instead of the docker container, because it resembles a typical user environment better than the minimal docker installation.
 The tools were installed according to their installation instructions and
@@
 
-Foreach dataset and assembler the proposed chloroplast was compared to the respective reference chloroplast using minimap2 v2.16 for pairwise alignment \cite{li2018minimap2}.
+Foreach dataset and assembler the proposed chloroplast was compared to the respective reference chloroplast using \texttt{minimap2} v2.16 for pairwise alignment \cite{li2018minimap2}.
 
-\[ score = \frac{1}{4} \cdot \left( cov_{ref} +  cov_{qry} + e^{-\left| \ln{\frac{cov_{qry}}{cov_{ref}}}\right|} + \frac{1}{n_{contigs} }\right) \]
+\begin{equation}
+   score = \frac{1}{4} \cdot \left( cov_{ref} +  cov_{qry} + min\left\{ \frac{cov_{qry}}{cov_{ref}}, \frac{cov_{ref}}{cov_{qry}}\right\} + \frac{1}{n_{contigs} }\right) \cdot 100 
+   \label{eq:quantitative}
+\end{equation}
 
-% equivalenter Vorschlag mit min anstatt e^ln
-
-\[ score = \frac{1}{4} \cdot \left( cov_{ref} +  cov_{qry} + min\left\{ \frac{cov_{qry}}{cov_{ref}}, \frac{cov_{ref}}{cov_{qry}}\right\} + \frac{1}{n_{contigs} }\right) \cdot 100  \]
-
-%% score = 1 - (abs(1-ref_cov_frac) + abs(1-qry_cov_frac) + abs(1-rep_res) + abs(1-(1/contig_num))))
+Formula 1 shows the quantitative measurements taken to score the assemblies from 0 to 100, with 100 being the best possible and 0 the worst score.
+Four different metrics were Incorporated: The coverage of the assembled chloroplast genome versus the reference genome $cov_{ref}$, to evaluate how many bases of the query genome can be mapped to its respective reference genome.
+Secondly we mapped the reference genome against the query to asses the coverage of the reference genome $cov_{qry}$.
+To penalize differences in the size of the assembly and the reference genome we used the term  $min\left\{ \frac{cov_{qry}}{cov_{ref}}, \frac{cov_{ref}}{cov_{qry}}\right\}$ the $min$ was applied to ensure, that always values between 0 and 1 were obtained.
+The fourth metric used is the number of contigs, with a perfect score being achieved if once circular chromosome was assembled.
+All four metrics contribute equally with $\frac{1}{4}$ to the final score.
 
 \subsubsection*{Reproducibility}
-For reproducibility  testing we randomly choose 100 data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
+For reproducibility  testing we randomly choose  \num{100} data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
 The resulting assemblies were scored again as described above and the scores of the 1.
@@
 \section*{Results}
-\subsection*{Computational Resources}
-Table and figure of performance evaluation.
+\subsection*{Performance metrics}
+%\subsection*{Computational Resources}
+%Table and figure of performance evaluation.
 Including RAM, I/O, runtime, parallelization ability, CPU usage.
 Free text description of results, range, mean/median, effect of input size, threads parameter, ...
+
+\subsubsection*{Time requirements}
+
+\textit{plot comp\_time\_log.pdf goes here}
+
+In terms of time efficiency there was a great difference between input datasets, number of threads and the tool in use ranging from a few minutes to several hours.
+Some assemblies failed to finish within the time-limit we set at \SI{48}{\hour}.
+On average the longest time to complete assemblies was taken by \ioga{} and \fp{} followed by \oa{} and \go{} the most time efficient overall was \ce{} with on average is a little faster than \np{} and \cassp{}
+%% multithreading
+Not all the tools were able to benefit from having access to multiple threads.
+Both \np{} and \oa{} take about the same time independent of being able to utilize \numlist[list-final-separator={, or }]{1;2;4;8} threads.
+\cassp{}, \ce{} , \go and \fp{} all profit from multi-threading.
+
+\subsubsection*{Memory and CPU Usage }
+\textit{plot usage\_amout\_threads.pdf goes here}
+
+\[ CAP_n=221 , CE_n=205 , Fast-Plast_n=352 , GetOrganelle_n=356 IOGA_n=296, NOVOPlasty_n=270 org.ASM_n=228 \]
 
@@
 The only assembler obtaining perfect results according to our score for the simulated datasets is \go{}.
-\ioga{} and \cassp{} showed the worst performance being unable to fully assemble a single chloroplast out of 14.
-\np{} performed second best with scores above 80 for all datasets, only failing to resolve the chloroplast contig into one single circular assembly.
+\ioga{} and \cassp{} showed the worst performance being unable to fully assemble a single chloroplast out of \num{14}.
+\np{} performed second best with scores above \num{80} for all datasets, only failing to resolve the chloroplast contig into one single circular assembly.
 (As could have been expected -> discussion) the overall performance is best, when the input data consists purely of chloroplast reads.
@@
 \subsubsection*{real data sets}
-Highest scoring is \go{} next is \fp{} while \ioga{} and \cassp{} perform poorly, never reaching a score of 1 (figure 1). TODO: median/mean score, mad/sd Tabelle
+Highest scoring is \go{} next is \fp{} while \ioga{} and \cassp{} perform poorly, never reaching a score of  \num{1} (\cref{fig:swarmplot}). TODO: median/mean score, mad/sd Tabelle
 
@@
 \subsubsection*{Reproducibility}
-\textit{plot repro.pdf goes here}
-
-Reproducibility was tested as described above, by re-unning assemblies and comparison of the scores of the two assemblies.
-Figure N shows the scores of the 1.
-runs versus the scores of the 2.
-scores.
-Runs that did not produce an output were manually scored with 0.
+Reproducibility was tested as described above, by re-unning assemblies and comparison of the scores of the two assemblies (\cref{fig:reproducibility}).
+Replicates that did not produce an output were manually scored with \num{0}. 
 \go{} was the only tool that succeeded in obtaining similar scores for all the assemblies, without having and completely unsuccessful assemblies for this subset of data.
-Except for \fp{} all the other tools had at least one assembly that was unsuccessful in either runs, but produced on output in the other.
+Except for \fp{} all the other tools had at least one assembly that was unsuccessful in either runs, but produced an output in the other.
 Notably \ioga{} appears to have a tendency of being able to perform differently in independent runs.
-More that 10 \% of the assemblies failed once, but were successful in the other run.
+More that \SI{10}{\percent} of the assemblies failed once, but were successful in the other run.
 
@@
 \ce{} and \cassp{} only have few deviations between the two runs, besides a few one-time non-performing datasets, the other all scored the same.
-1
-
-\subsection*{Performance metrics}
-
-\subsubsection*{Time requirements}
-
-\textit{plot comp\_time\_log.pdf goes here}
-
-In terms of time efficiency there was a great difference between input datasets, number of threads and the tool in use ranging from a few minutes to several hours.
-Some assemblies failed to finsih within the time-limit we set at 48 hours.
-On average the longest time to complete assemblies was taken by \ioga{} and \fb{} followed by \oa{} and \go{} the most time efficient overall was \ce{} with on average is a little faster than \np{} and \cassp{}
-%% multithreading
-Not all the tools were able to benefit from having access to multiple threads.
-Both \no and \oa take about the same time independent of being able to utilize 1,2,4 or 8 threads.
-\cassp{}, \ce{} , \go and \fb{} all profit from multi-threading
-
-\subsubsection*{Memory and CPU Usage }
-\textit{plot usage\_amout\_threads.pdf goes here}
-
-\[ CAP_n=221 , CE_n=205 , Fast-Plast_n=352 , GetOrganelle_n=356 IOGA_n=296, NOVOPlasty_n=270 org.ASM_n=228 \]
 
@@
 \subsection*{Ideas for future development}
-Combining components from different tools might be a promising approach. E.g. read scaling from \ce{}, assembly from \go{} and structural resolution with fast-plast.
+Combining components from different tools might be a promising approach. E.g. read scaling from \ce{}, assembly from \go{} and structural resolution with \fp{}.
 Mitigate installation issues e.g. by containerization.
@@
 \section*{Conclusion}
-Short summary of clear guidelines and future development (might not be necessary as these are the last two sections of the Discussion anyway, so we might elect to skip this).
+%Short summary of clear guidelines and future development (might not be necessary as these are the last two sections of the Discussion anyway, so we might elect to skip this).
+\todo{sollten wir lobend erwähnen, dass alle auf github/gitlab sind?}
 
@@
 Outlook: next step in the pipeline is annotation. There is a similar problem: many tools, which one to use? 
-A large scale study reconstructing chloroplasts throughout SRA (or 1001 genome project) is feasible and promising using the existing tools (estimated runtime, number of novel chloroplasts).
+A large scale study reconstructing chloroplasts throughout SRA (or \num{1001} genome project) is feasible and promising using the existing tools (estimated runtime, number of novel chloroplasts).
 A meta-tool that automatically combines the different programs could be developed.
@@
       should go here.}
+      \label{fig:swarmplot}
       \end{figure}
@@
       Boxplots depictiing the demand of CPU and RAM and disk space needed depending on the assembler, input data size and number of threads}
+      \label{fig:performance_memory_cpu}
       \end{figure}
@@
       Figure legend text.}
+      \label{fig:simulated}
       \end{figure}
@@
       }
+      \label{fig:reproducibility}
       \end{figure}
@@
   }
+        \label{fig:performance_runtime}
       \end{figure}
@@
       The plot shows the intersection of success ($score > 99$) between assemblers.
-For 69 datasets only \go{} was able to obtain a complete chloroplast.
-43 were successful with both \go{} and \fp{} and so on}
+For \num{69} datasets only \go{} was able to obtain a complete chloroplast.
+\num{43} were successful with both \go{} and \fp{} and so on}
+            \label{fig:upset}
       \end{figure}
@@
       Figure legend text.}
+      \label{fig:tree}
       \end{figure}

### 2019-05-28 code/eval_cov.r
Update eval_cov.r

@@ -1,13 +1,13 @@
-dps = c("tidyverse","dabestr","UpSetR","RColorBrewer","ggbeeswarm","ggpmisc")                   
+dps = c("tidyverse","dabestr","UpSetR","RColorBrewer","ggbeeswarm","ggpmisc","xtable")                   
 sapply(dps,function(x){if(!require(x,character.only = T)){install.packages(x);library(x,character.only = T)}else{library(x,character.only = T)}})
 
 
 ## load output file from alignment analyis
 ### order assemblers for ggplot
-res <- read_tsv("res2_clean.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
+res <- read_tsv("results/res2_clean.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
 
 ## simulated data 
-res_sim  <- read_tsv("res_sim_clean.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
+res_sim  <- read_tsv("results/res_sim_clean.tsv",col_names=c("dataset","assembler","ref_tot","ref_cov","ref_cov_frac","qry_tot","qry_cov","qry_cov_frac","contig_num"))
 
 ## calculate the score for each assembly for real data
 out_tibble <- res %>% mutate(rep_res = exp(-abs(log(qry_cov/ref_cov)))) %>%
@@ -32,7 +32,7 @@ my_col=brewer.pal(7,"Set2")
 out_tibble_sim %>% ggplot(aes(x=assembler,y=dataset,fill=score)) + geom_tile() + theme_bw()+
     scale_fill_continuous(low = my_col[2] ,high = my_col[1]) +
     theme(axis.title.y = element_blank(),axis.title.x=element_blank(),text = element_text(size=15))
-ggsave("sim_tiles.pdf")
+ggsave("plots/sim_tiles.pdf")
 
 
 ## swarm plot for real datasets
@@ -40,7 +40,7 @@ out_tibble %>% drop_na %>%  ggplot(aes(y=score,x=assembler_f,color=assembler_f))
     geom_boxplot(notch=F,alpha=0.3,width=0.2,color="black",fill="#c0c0c0") +
[…]

### 2019-05-28 bmc_article.tex
Update on Overleaf.

@@
 \usepackage{todonotes}
+\setlength{\marginparwidth}{3cm}
+
+\newcounter{todocounter}
+\newcommand{\ak}[1]
+{\stepcounter{todocounter}
+ \todo[color=green!40,author=Arthur]{\thetodocounter: #1}
+ }
 
@@
 \newcommand{\cassp}{\formatprogramnames{Chloroplast assembly protocol}}
+
+\newcommand{\zenododataset}{\cite{zenododataset}}
+\newcommand{\zenodorepo}{\cite{zenodorepo}}
 
@@
 \author[
-   addressref={aff2,aff3},
+   addressref={aff1,aff3},
    email={niklas.terhoeven@uni-wuerzubrg.de}
@@
 %%
+\newpage
 \section*{Introduction}
 \subsection*{General introduction and motivation}
-The chloroplast as the photosynthetic organelle harboring its own genome has been an early target for sequencing.
+The chloroplast as the photosynthetic organelle harboring its own genome has been an early target for sequencing.\ak{maybe even 1-2 sentences about general chloroplast importance}
 The first chloroplast genome sequences were obtained as early as 1986 \cite{ohyama_chloroplast_1986,shinozaki_complete_1986}.
 These efforts elucidated the general genome organization and structure of chloroplasts, expanded by many more studies over the years.
-Chloroplast genome content and structure reviewed elsewhere \cite{wicke_evolution_2011,green_chloroplast_2011}.
+Chloroplast genome content and structure \textcolor{red} {are}  reviewed elsewhere \cite{wicke_evolution_2011,green_chloroplast_2011}.
 Chloroplast genomes are widely used for evolutionary analyses \cite{martin_plastid_2010,xiao-ming_inferring_2017}, barcoding \cite{kress_use_2005,hollingsworth_dna_2009,de_vere_dna_2015}, and meta-barcoding \cite{bell_review_2016,deiner_environmental_2017}.
@@
 
-It is much easier to decipher the complete chloroplast genome than the complete core genome (cite?).
+It is much easier to decipher the complete chloroplast genome than the complete core genome, due its comparably smaller size.
+For example \textit{Arabidopsis thaliana} core genome is approximately \SI{125}{\mega\basepair} in length \cite{schmuths2004,cao2011} while the size of the chloroplast genome with \SI{154}{\kilo\basepair} is more than \SI{800}{\times} smaller than the core genome \cite{sato1999}.
 However, the specific genome structure (esp. the large inverted repeat) complicates automated resolution with short read technologies (cite?).
@@
 Is there anything known about intra-organismic variability (do some plants have multiple populations of chloroplasts?
-probably off topic).
+\ak{Yes, they do , Heteroplasmy} probably off topic).\ak{nope, I think this is important}
 
@@
 \subsection*{Purpose and scope of this study}
-The goal of this study is to compare the effectiveness and efficiency of existing tools to de-novo assemble whole chloroplast genomes from raw mixed genomic datasets with minimal configuration.
-This means: no data prep, no specific reference (but \plant{At} if required), default parameters, no manual finishing.
-We further restricted our benchmark to paired Illumina datasets as these are the most common \todo{cite?} and most \todo{(all?)} tools in this study can not handle any other types.
+The goal of this study is to compare the effectiveness and efficiency of existing open source command-line tools to de-novo assemble whole chloroplast genomes from raw mixed genomic data sets with minimal configuration.
+This means: no data preparation, no specific reference (but \plant{At} if required), default parameters, no manual finishing.
+We further restricted our benchmark to paired Illumina data sets as these are the most common \todo{cite?} and the %\todo{(all?) - habs gecheckt}
+tools in this study can not handle any other types.
 
 In our opinion this reflects the most common use cases: (1) a user trying a tool quickly without digging into options for fine tuning and (2) large scale automatic applications.
-Still, we acknowledge that the performance of the tools might be significantly improved by optimizing parameters (and references if applicable) for each dataset specifically.
+Still, we acknowledge that the performance of the tools might be significantly improved by optimizing parameters (and references if applicable) for each data set specifically.
 (However, this was outside the scope of this study.)
@@
 \section*{Methods}
-Source code for all methods is available at \url{https://github.com/chloroExtractorTeam/benchmark} and archived under \todo{(zenodo doi)}.
+Source code for all methods is available at \url{https://github.com/chloroExtractorTeam/benchmark} and archived under \zenodorepo{}.
 All docker images are published on \url{https://cloud.docker.com/u/chloroextractorteam/} and are named with a leading \texttt{benchmark\_} (\cref{tab:dockerimages}).
-datasets at \todo{(zenodo links for simulated and real)}.
+Our simulated data sets are stored at \zenododataset{}.
 This study adheres to the guidelines for computational method benchmarking \cite{weber_essential_2018}.
@@
 We included tools designed for assembling chloroplasts from whole genome paired end Illumina sequencing data.
-The tools must be available as open source software and allow execution via a command line interface \todo{das noch oben in der scope section erwähnen}.
+The tools must be available as open source software and allow execution via a command line interface.
 A graphical user interface is not suitable for
@@
 
-Other related tools for assembling chloroplasts but outside the scope of this study are \texttt{Organelle PBA} \cite{Soorni2017}, a protocol for \texttt{Genious}, \texttt{sestaton/Chloro}, \texttt{Norgal} and \texttt{MitoBim}.
+Other related tools for assembling chloroplasts but outside the scope of this study are \texttt{Organelle PBA} \cite{Soorni2017}, \texttt{sestaton/Chloro} \cite{sestaton}, \texttt{Norgal}  \cite{Al-Nakeeb2017} and \texttt{MitoBim} \cite{mitobim2013}.
+
 \texttt{Organelle PBA} is designed for PacBio data and does not work with paired Illumina data only.
-\texttt{Genious} software \todo{cite - die empfohlene Ref passt nicht da wir Geneious ja gar nicht verwenden, wir bräuchten eine ref die sagt, dass es das protocol gibt @niklas.
-\url{https://support.geneious.com/hc/en-us/articles/227534768-How-do-I-cite-Geneious-in-a-paper-}} is closed source and GUI based.
-\texttt{sestaton/Chloro} (\url{https://github.com/sestaton/Chloro}) fits all criteria but is flagged as a work in progress and development seems to have ended two years ago.
-\texttt{Norgal} \cite{Al-Nakeeb2017} is a tool to extract organellar DNA from whole genome data based on a k-mer frequency approach.
+\texttt{sestaton/Chloro} fits all criteria but is flagged as a work in progress and development seems to have ended two years ago.
+\texttt{Norgal} is a tool to extract organellar DNA from whole genome data based on a k-mer frequency approach.
 However the final output is a set of contigs of mixed mitochondrial and plastid origin.
@@
 Even though there is a claim by the author that it can be used for chloroplasts as well (\url{https://github.com/chrishah/MITObim/issues/16}, accessed: 2019-05-27), there is no further description on how to do that.
-\todo{haben wir es versucht?}
-\todo{method description paper - war das method description paper nicht das chloroplast assembly protocol? @niklas}
+\todo{haben wir es versucht?
+- nein}
+Additionally, there is a protocol for the \texttt{Geneious} \cite{geneious} software available \cite{geneious-protocol}.
+However, \texttt{Geneious} is closed source and GUI based, which is not in the scope of this study.
+There is also another publication describing a method for assembling chloroplasts \cite{method-description-paper}. However, the link to the software is not active anymore.
 
@@
 To avoid suffering from sequencing errors and biological variances, we simulated perfect reads based on the \plant{At} (TAIR10) chloroplast assembly \cite{tair10}.
-Therefore we used a sliding window approach with seqkit \cite{seqkit} \todo{seqkit parameter - würde ich hier nicht erwähnen, seqkit wurde mehrfach mit verschiedenen sub commands und parametern aufgerufen, die genaue Doku ist hier: \url{https://github.com/chloroExtractorTeam/benchmark/blob/master/03_representative_datasets.md}}.
+Therefore we used a sliding window approach with seqkit \cite{seqkit}.
+The exact commands can be found inside \href{https://github.com/chloroExtractorTeam/benchmark/blob/master/03_representative_datasets.md}{\texttt{03\_representative\_datasets.md}} in \zenododataset{}.
 For the final simulated data sets reads based on pseudo mixtures of TAIR10's core and chloroplast genome:  \num{0}:\num{1}, \num{1}:\num{10}, \num{1}:\num{100}, and \num{1}:\num{1000}.
@@
 The values of CPU and memory usage have been obtained by docker.
-The disk usage was estimated using the GNU tool du.
-We used GNU parallel for queuing of the different settings \cite{Tange2011a}.
+The disk usage was estimated using the GNU tool \texttt{du}.
+We used \texttt{GNU parallel} for queuing of the different settings \cite{Tange2011a}.
 
@@
 The qualitative evaluation is mainly based on the reviewer guidelines for the Journal of Open Source Software (JOSS) \cite{joss}.
-To create a standard environment, all tools were tested in a fresh default installation of Ubuntu 18.04.2 running in a virtual machine.
+To create a standard environment, all tools were tested in a fresh default installation of Ubuntu 18.04.2 running in a virtual machine (VirtualBox Version 5.2.18\_Ubuntu r123745).
 We chose this setup instead of the docker container, because it resembles a typical user environment better than the minimal docker installation.
@@
 
-After an initial evaluation, we contacted all authors via their github or gitlab issue tracking to
+After an initial evaluation, we contacted all authors via their GitHub or GitLab issue tracking to
 report any flaws we found.
@@
 \subsubsection*{Quantitative}
-We want to quantify continuity, completeness, correctness, repeat resolution.
-We use continuity: number of contigs.
-Completeness: Number of covered bases on reference (when aligning assembly).
-Correctness: Number of covered bases in assembly (when aligning reference).
-Repeat resolution: Difference between above two measures (indicates collapsed or expanded repeats)
+
+%We use continuity: number of contigs.
+%Completeness: Number of covered bases on reference (when aligning assembly).
+%Correctness: Number of covered bases in assembly (when aligning reference).
+%Repeat resolution: Difference between above two measures (indicates collapsed or expanded repeats)
 %
@@
 
-Foreach dataset and assembler the proposed chloroplast was compared to the respective reference chloroplast using \texttt{minimap2} v2.16 for pairwise alignment \cite{li2018minimap2}.
+%We want to quantify continuity, completeness, correctness and repeat resolution.
+
+Foreach dataset and assembler the proposed chloroplast was compared to the respective reference chloroplast using a pairwise alignment obtained with \texttt{minimap2} v2.16 \cite{li2018minimap2}.
+Based on theses alignments the score is calculated as shown in \cref{eq:quantitative}
+The assemblies were scored on a scale from 0 to 100, with 100 being the best and 0 the worst possible score.
+Four different metrics were Incorporated, each contributing  $\frac{1}{4}$ to the total score: Completeness, correctness, repeat resolution and continuity.
+
+The completeness is estimated as the coverage of the assembled chloroplast genome versus the reference genome ($cov_{ref}$).
+It resembles how many bases of the query genome can be mapped to its respective reference genome.
+Secondly, we mapped the reference genome against the query.
+The coverage of the reference genome ($cov_{qry}$) is used as measurment for the correctness of the assembly.
+The repeat resolution is estimated from the size difference of the assembly and the reference genome ($min\left\{ \frac{cov_{qry}}{cov_{ref}}, \frac{cov_{ref}}{cov_{qry}}\right\}$).The $min$ was applied to ensure, that only values between 0 and 1 were obtained.
+The fourth metric used is the continuity, represented by the number of contigs.
+A perfect score is achieved if one circular chromosome was assembled.
 
@@
 \end{equation}
-
-Formula 1 shows the quantitative measurements taken to score the assemblies from 0 to 100, with 100 being the best possible and 0 the worst score.
-Four different metrics were Incorporated: The coverage of the assembled chloroplast genome versus the reference genome $cov_{ref}$, to evaluate how many bases of the query genome can be mapped to its respective reference genome.
-Secondly we mapped the reference genome against the query to asses the coverage of the reference genome $cov_{qry}$.
-To penalize differences in the size of the assembly and the reference genome we used the term  $min\left\{ \frac{cov_{qry}}{cov_{ref}}, \frac{cov_{ref}}{cov_{qry}}\right\}$ the $min$ was applied to ensure, that always values between 0 and 1 were obtained.
-The fourth metric used is the number of contigs, with a perfect score being achieved if once circular chromosome was assembled.
-All four metrics contribute equally with $\frac{1}{4}$ to the final score.
 
@@
 \subsubsection*{Time requirements}
-
-\textit{plot comp\_time\_log.pdf goes here}
-
-In terms of time efficiency there was a great difference between input datasets, number of threads and the tool in use ranging from a few minutes to several hours.
+In terms of time efficiency there was a great difference between input datasets, number of threads and the tool in use ranging from a few minutes to several hours (\cref{fig:performance_runtime}).
 Some assemblies failed to finish within the time-limit we set at \SI{48}{\hour}. 
-On average the longest time to complete assemblies was taken by \ioga{} and \fp{} followed by \oa{} and \go{} the most time efficient overall was \ce{} with on average is a little faster than \np{} and \cassp{}
+On average the longest time to complete assemblies was taken by \ioga{} and \fp{} followed by \oa{} and \go{} the most time efficient overall was \ce{} with on average is a little faster than \np{} and \cassp{}.
 %% multithreading
@@
 Both \np{} and \oa{} take about the same time independent of being able to utilize \numlist[list-final-separator={, or }]{1;2;4;8} threads.
-\cassp{}, \ce{} , \go and \fp{} all profit from multi-threading.
+\cassp{}, \ce{} , \go and \fp{} all profit from multi-threading (\cref{fig:performance_runtime}, \cref{fig:performance_memory_cpu}).
 
 \subsubsection*{Memory and CPU Usage }
-\textit{plot usage\_amout\_threads.pdf goes here}
-
-\[ CAP_n=221 , CE_n=205 , Fast-Plast_n=352 , GetOrganelle_n=356 IOGA_n=296, NOVOPlasty_n=270 org.ASM_n=228 \]
+The peak and mean CPU usage, as well as peak memory and disk usage have been recorded for all assemblers based on a input data set size and a number of threads to use (\cref{fig:performance_memory_cpu}).
+Mainly, the size of the input set influenced the peak memory usage with an exception for \ce{} and \ioga{}.
+Those two assemblers seems to have a memory usage pattern, which is less influenced by data set size.
+The number of allowed threads have only no or a limited impact on the peak memory usage.
+Nevertheless, all programs profit by a higher number of threads, even more if the input size increases.
+In contrast, the disk usage is independent from input size and number of threads for all assemblers, but the factor between the programs exceeds a factor of \num{100}.
 
@@
 Two minor dependencies were missing in the \go{} installation instructions.
-There was also no test data available and an issue occurred when running it on a \plant{At} dataset.
+There was also no test data available and an issue occurred when running it on a \plant{At} data set.
 We are currently in the process of resolving this with the authors.
 
-The \fp{} installation instructions were missing some dependencies. Like \go{}, \fp{} does not offer a test dataset or a tutorial, except from some example commands.
+The \fp{} installation instructions were missing some dependencies. Like \go{}, \fp{} does not offer a test data set or a tutorial, except from some example commands.
 
 The \oa{} installation instructions did not work.
-We found some issues, which are probably related to the requirement of python3.7.
+We found some issues, which are probably related to the requirement of \texttt{Python~3.7}.
 There is a tutorial with sample data available.
@@
 
-The main critique point of \np{} was the lack of a test dataset with instructions.
+The main critique point of \np{} was the lack of a test data set with instructions.
 This was fixed by the authors after we contacted them.
@@
 
-The \ce{} does come with a test dataset and a short tutorial. However, a way to evaluate the results of the test run would be nice.
+The \ce{} does come with a test data set and a short tutorial. However, a way to evaluate the results of the test run would be nice.
 
@@
 Also, there was no test data or tutorial available and there is no license assigned to it.
-Since there was no update to the github repository for the last three years, the project can be seen as inactive.
+Since there was no update to the GitHub repository for the last three years, the project can be seen as inactive.
 After contact, the authors promised to resolve the mentioned issues.
@@
 The list was updated after we contacted the authors.
-This tool does come with a test dataset, however a note about the expected outcome would be nice.
+This tool does come with a test data set, however a note about the expected outcome would be nice.
 A more extensive tutorial is provided.
@@
 \subsubsection*{Simulated data}
-\textit{tile plot for simulated data goes here}
-The only assembler obtaining perfect results according to our score for the simulated datasets is \go{}.
+The only assembler obtaining perfect results according to our score for the simulated data sets is \go{} (\cref{fig:simulated}).
 \ioga{} and \cassp{} showed the worst performance being unable to fully assemble a single chloroplast out of \num{14}.
-\np{} performed second best with scores above \num{80} for all datasets, only failing to resolve the chloroplast contig into one single circular assembly.
+\np{} performed second best with scores above \num{80} for all data sets, only failing to resolve the chloroplast contig into one single circular assembly.
 (As could have been expected -> discussion) the overall performance is best, when the input data consists purely of chloroplast reads.
@@
 \subsubsection*{real data sets}
-Highest scoring is \go{} next is \fp{} while \ioga{} and \cassp{} perform poorly, never reaching a score of  \num{1} (\cref{fig:swarmplot}). TODO: median/mean score, mad/sd Tabelle
+Concerning the performance of the assemblers on evaluated on the real data sets from SRA database we were able to observe considerable differences in the median score (\cref{fig:swarmplot}).
+The highest scores were achieved by \go{} with a median of 99.7 and 199 circular assemblies out of a total of 356 assemblies that resulted in an output  \cref{tab:scores}.
+The performance of \go{} is seconded by \fb{} \np{} \oa{}, with \fb{} outperforming the latter two slightly in terms of score, however \fb{} as almost or more than twice as much \num{114} perfectly assembled chloroplast genomes as \np{} with \num{66} or \num{55} circular genomes for \oa{}.
+\ioga{} and \cassp{} were both not able to assemble a single circular, single-contig genome \cref{tab:scores}, consequently resulting in the lowest mean and median scores.
+
+%% Ich werde die Namen in der Tabelle anpassen, sobald ich die finale Version habe
+
+\cref{fig:upset}
 
@@
 \subsubsection*{Reproducibility}
-Reproducibility was tested as described above, by re-unning assemblies and comparison of the scores of the two assemblies (\cref{fig:reproducibility}).
+Reproducibility was tested as described above, by re-running assemblies and comparison of the scores of the two assemblies (\cref{fig:reproducibility}).
 Replicates that did not produce an output were manually scored with \num{0}. 
@@
 Both \fp{} and \np{} tend to have minor changes in the assembly when the overall performance is comparably well, leading to the arrow-shaped scatter plots.
-\ce{} and \cassp{} only have few deviations between the two runs, besides a few one-time non-performing datasets, the other all scored the same.
+\ce{} and \cassp{} only have few deviations between the two runs, besides a few one-time non-performing data sets, the other all scored the same.
 
@@
 We evaluated all tools under the assumption that they are used in the most basic form (default parameters, no hand selected reference, no pre-processing of the data or post-processing of the result, restricted runtime).
-It is important to note that any tool might perform significantly different if parameters and references are fine-tuned for each dataset.
+It is important to note that any tool might perform significantly different if parameters and references are fine-tuned for each data set.
 
@@
 Although no program works everytime, most chloroplasts are resolved by at least one tool (is that so?).
-So programs are complementary, more effort to combine strengths of different methods (or automatic parameter selection - if failure is due to suboptimal parameters for the specific dataset).
+So programs are complementary, more effort to combine strengths of different methods (or automatic parameter selection - if failure is due to suboptimal parameters for the specific data set).
 
@@
 \begin{figure}[h!]
+  \includegraphics[width=\textwidth]{plots/comp_time_log.pdf}
+  \caption{\csentence{Computation time depending on number of threads and size of input data}
+  }
+        \label{fig:performance_runtime}
+      \end{figure}
+
+\begin{figure}[h!]
   \includegraphics[width=\textwidth]{plots/usage_amount_threads.pdf}
@@
       \label{fig:reproducibility}
-      \end{figure}
-
-\begin{figure}[h!]
-  \includegraphics[width=\textwidth]{plots/comp_time_log.pdf}
-  \caption{\csentence{Computation time depending on number of threads and size of input data}
-  }
-        \label{fig:performance_runtime}
       \end{figure}
@@
 
-\begin{table}[h!]
-\caption{Sample table title. This is where the description of the table should go.}
-      \begin{tabular}{cccc}
+\begin{table}[ht]
+\caption{Mean scores of chloroplast genome assemblers}
+\label{tab:scores}
+\centering
+\begin{tabular}{rlrrrr}
   \hline
-           & B1  &B2   & B3\\ \hline
-        A1 & 0.1 & 0.2 & 0.3\\
-        A2 & ... & ..  & .\\
-        A3 & ..  & .   & .\\ \hline
+ & assembler & Mean & SD & N\_perfect & N\_tot \\ 
+  \hline
+  1 & CAP & 51.26 & 8.42 &   0 & 221 \\ 
+  2 & CE & 69.99 & 12.33 &  14 & 205 \\ 
+  3 & Fast-Plast & 86.96 & 15.33 & 114 & 352 \\ 
+  4 & GetOrganelle & 89.13 & 15.30 & 199 & 356 \\ 
+  5 & IOGA & 68.74 & 11.69 &   0 & 296 \\ 
+  6 & NOVOPlasty & 82.78 & 16.55 &  66 & 270 \\ 
+  7 & org.ASM & 82.77 & 16.38 &  55 & 228 \\ 
+   \hline
 \end{tabular}
 \end{table}
+
+\begin{table}[ht]
+\caption{Performance metrics input size 25K}
+\label{tab:perform25K}
+\centering
+\begin{tabular}{rlrrrr}
+  \hline
+ & program & threads & Peak CPU usage & Peak memeory & Peak disk usage (GB) \\ 
+  \hline
+1 & CAP &   1 & 113.32 & 0.31 & 0.06 \\ 
+  2 & CAP &   2 & 166.60 & 0.26 & 0.05 \\ 
+  3 & CAP &   4 & 305.99 & 0.26 & 0.05 \\ 
+  4 & CAP &   8 & 569.12 & 0.37 & 0.06 \\ 
+  5 & CE &   1 & 111.49 & 3.41 & 0.07 \\ 
+  6 & CE &   2 & 199.12 & 3.41 & 0.07 \\ 
+  7 & CE &   4 & 343.22 & 3.41 & 0.07 \\ 
+  8 & CE &   8 & 509.51 & 3.41 & 0.07 \\ 
+  9 & Fast-Plast &   1 & 118.31 & 0.77 & 0.30 \\ 
+  10 & Fast-Plast &   2 & 213.57 & 0.77 & 0.31 \\ 
+  11 & Fast-Plast &   4 & 379.27 & 0.77 & 0.32 \\ 
+  12 & Fast-Plast &   8 & 657.20 & 0.77 & 0.35 \\ 
+  13 & GetOrganelle &   1 & 111.39 & 0.38 & 0.05 \\ 
+  14 & GetOrganelle &   2 & 170.30 & 0.32 & 0.05 \\ 
+  15 & GetOrganelle &   4 & 242.27 & 0.31 & 0.06 \\ 
+  16 & GetOrganelle &   8 & 346.98 & 0.31 & 0.07 \\ 
+  17 & IOGA &   1 & 118.12 & 18.61 & 6.25 \\ 
+  18 & IOGA &   2 & 224.74 & 17.88 & 6.26 \\ 
+  19 & IOGA &   4 & 394.98 & 16.62 & 5.60 \\ 
+  20 & IOGA &   8 & 733.11 & 21.76 & 11.13 \\ 
+  21 & NOVOPlasty &   1 & 78.38 & 0.04 & 0.00 \\ 
+  22 & NOVOPlasty &   2 & 86.64 & 0.04 & 0.00 \\ 
+  23 & NOVOPlasty &   4 & 86.50 & 0.04 & 0.00 \\ 
+  24 & NOVOPlasty &   8 & 87.32 & 0.04 & 0.00 \\ 
+  25 & org.ASM &   1 & 112.08 & 0.79 & 0.03 \\ 
+  26 & org.ASM &   2 & 115.44 & 0.79 & 0.03 \\ 
+  27 & org.ASM &   4 & 105.09 & 0.79 & 0.03 \\ 
+  28 & org.ASM &   8 & 105.78 & 0.79 & 0.03 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[ht]
+\caption{Performance metrics input size 250K}
+\label{tab:perform250K}
+\centering
+\begin{tabular}{rlrrrr}
+  \hline
+ & program & threads & Peak CPU usage & Peak memeory & Peak disk usage (GB) \\ 
+  \hline
+1 & CAP &   1 & 114.38 & 0.90 & 0.65 \\ 
+  2 & CAP &   2 & 204.39 & 0.93 & 0.65 \\ 
+  3 & CAP &   4 & 337.09 & 0.97 & 0.65 \\ 
+  4 & CAP &   8 & 652.75 & 1.08 & 0.65 \\ 
+  5 & CE &   1 & 117.57 & 3.96 & 0.63 \\ 
+  6 & CE &   2 & 230.35 & 3.96 & 0.63 \\ 
+  7 & CE &   4 & 414.25 & 3.96 & 0.63 \\ 
+  8 & CE &   8 & 755.76 & 3.97 & 0.63 \\ 
+  9 & Fast-Plast &   1 & 118.81 & 1.40 & 0.78 \\ 
+  10 & Fast-Plast &   2 & 234.12 & 2.25 & 0.78 \\ 
+  11 & Fast-Plast &   4 & 425.89 & 2.32 & 0.79 \\ 
+  12 & Fast-Plast &   8 & 845.94 & 2.52 & 0.79 \\ 
+  13 & GetOrganelle &   1 & 117.94 & 1.07 & 0.40 \\ 
+  14 & GetOrganelle &   2 & 227.05 & 1.13 & 0.40 \\ 
+  15 & GetOrganelle &   4 & 403.35 & 1.08 & 0.40 \\ 
+  16 & GetOrganelle &   8 & 747.20 & 1.03 & 0.39 \\ 
+  17 & IOGA &   1 & 118.62 & 12.03 & 4.01 \\ 
+  18 & IOGA &   2 & 234.09 & 9.71 & 4.01 \\ 
+  19 & IOGA &   4 & 420.77 & 10.09 & 3.48 \\ 
+  20 & IOGA &   8 & 842.57 & 19.21 & 9.45 \\ 
+  21 & NOVOPlasty &   1 & 111.97 & 0.32 & 0.00 \\ 
+  22 & NOVOPlasty &   2 & 115.07 & 0.32 & 0.00 \\ 
+  23 & NOVOPlasty &   4 & 116.42 & 0.31 & 0.00 \\ 
+  24 & NOVOPlasty &   8 & 115.86 & 0.31 & 0.00 \\ 
+  25 & org.ASM &   1 & 118.10 & 0.93 & 0.06 \\ 
+  26 & org.ASM &   2 & 161.76 & 0.93 & 0.06 \\ 
+  27 & org.ASM &   4 & 163.01 & 0.93 & 0.06 \\ 
+  28 & org.ASM &   8 & 160.74 & 0.93 & 0.06 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[ht]
+\caption{Performance metrics input size 2.5M}
+\label{tab:perform2.5M  }
+\centering
+\begin{tabular}{rlrrrr}
+  \hline
+ & program & threads & Peak CPU usage & Peak memeory & Peak disk usage (GB) \\ 
+ \hline
+1 & CAP &   1 & 118.80 & 6.83 & 6.59 \\ 
+  2 & CAP &   2 & 209.22 & 7.58 & 6.59 \\ 
+  3 & CAP &   4 & 357.36 & 7.25 & 6.59 \\ 
+  4 & CAP &   8 & 683.71 & 6.99 & 6.59 \\ 
+  5 & CE &   1 & 118.78 & 5.34 & 2.01 \\ 
+  6 & CE &   2 & 234.82 & 5.34 & 2.01 \\ 
+  7 & CE &   4 & 415.74 & 5.28 & 2.09 \\ 
+  8 & CE &   8 & 844.95 & 5.34 & 2.01 \\ 
+  9 & Fast-Plast &   1 & 119.24 & 6.80 & 5.80 \\ 
+  10 & Fast-Plast &   2 & 237.34 & 6.98 & 5.82 \\ 
+  11 & Fast-Plast &   4 & 443.27 & 8.02 & 5.69 \\ 
+  12 & Fast-Plast &   8 & 872.07 & 8.87 & 5.69 \\ 
+  13 & GetOrganelle &   1 & 118.91 & 5.25 & 3.31 \\ 
+  14 & GetOrganelle &   2 & 235.18 & 5.26 & 3.31 \\ 
+  15 & GetOrganelle &   4 & 420.10 & 5.44 & 3.31 \\ 
+  16 & GetOrganelle &   8 & 845.13 & 6.07 & 3.31 \\ 
+  17 & IOGA &   1 & 119.46 & 18.64 & 8.83 \\ 
+  18 & IOGA &   2 & 237.22 & 21.24 & 10.19 \\ 
+  19 & IOGA &   4 & 425.50 & 18.71 & 10.56 \\ 
+  20 & IOGA &   8 & 857.29 & 25.23 & 16.51 \\ 
+  21 & NOVOPlasty &   1 & 112.67 & 2.69 & 0.00 \\ 
+  22 & NOVOPlasty &   2 & 117.77 & 2.58 & 0.00 \\ 
+  23 & NOVOPlasty &   4 & 117.40 & 2.74 & 0.00 \\ 
+  24 & NOVOPlasty &   8 & 117.28 & 2.74 & 0.00 \\ 
+  25 & org.ASM &   1 & 118.73 & 2.63 & 0.37 \\ 
+  26 & org.ASM &   2 & 184.53 & 2.63 & 0.37 \\ 
+  27 & org.ASM &   4 & 177.03 & 2.63 & 0.37 \\ 
+  28 & org.ASM &   8 & 176.25 & 2.63 & 0.37 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+% \begin{table}[h!]
+% \caption{Sample table title. This is where the description of the table should go.}
+%       \begin{tabular}{cccc}
+%         \hline
+%           & B1  &B2   & B3\\ \hline
+%         A1 & 0.1 & 0.2 & 0.3\\
+%         A2 & ... & ..  & .\\
+%         A3 & ..  & .   & .\\ \hline
+%       \end{tabular}
+% \end{table}
 

### 2019-05-28 bmc_article.tex
Update on Overleaf.

@@
 \author[
-   addressref={aff1,aff2,aff3 },
+   addressref={aff1},
+   email={arthur.korte@uni-wuerzubrg.de}
+]{\inits{AK}\fnm{Arthur} \snm{Korte}}
+\author[
+   addressref={aff2,aff1,aff3 },
    noteref={n2},
@@
 tools in this study can not handle any other types.
+\todo{tools can not handle passt hier finde ich nicht als Begründung.
+Wir geben gerade vor was uns interessiert und wählen später Tools aus die dazu passen.
+Sonst gibt es einen Ringschluss zwischen Scope und Tool Selection.}
 
@@
 Even though there is a claim by the author that it can be used for chloroplasts as well (\url{https://github.com/chrishah/MITObim/issues/16}, accessed: 2019-05-27), there is no further description on how to do that.
-\todo{haben wir es versucht?
+%\todo{haben wir es versucht?
 - nein}
@@
 For reproducibility  testing we randomly choose  \num{100} data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
-The resulting assemblies were scored again as described above and the scores of the 1.
-and the 2.
-run were compared to each other.
+The resulting assemblies were scored again as described above and the scores of the first and the second run were compared to each other.
 
@@
 \section*{Discussion}
-Discuss Computational Resources.
-Implications of very long running.
-Also state minimum requirements on the hardware (RAM, CPUs, storage).
-Importance of this depends on use case (if goal is one single chloroplast
+Depending on the use case the different criteria assessed in this work need to be weighted differently.
+For example ease of installation and use might not be a big concern if the tool is installed once and integrated in an automated pipeline.
+On the other hand this factor alone might prevent other users from being able to use the tool at all.
+Similarly computational requirements or run time is less relevant if the goal is to assemble a single chloroplast for further analysis, but it is essential if hundreds or thousands of samples should be processed in parallel for a large scale study.
+Eventually, both ease of use and runtime are irrelevant if the tool is not able to successfully accomplish it's task.
+Also the scope of this study needs to be considered when interpreting the guidelines below.
+In particular, we evaluated all tools under the assumption that they are used in the most basic form (default parameters, no hand selected reference, no pre-processing of the data or post-processing of the result, restricted runtime).
+It is important to note that any tool might perform significantly different if parameters and references are fine-tuned for the specific data set.
 
-We evaluated all tools under the assumption that they are used in the most basic form (default parameters, no hand selected reference, no pre-processing of the data or post-processing of the result, restricted runtime).
-It is important to note that any tool might perform significantly different if parameters and references are fine-tuned for each data set.
+The overall best success rate both on simulated and real data was achieved by \go{} followed by \fp{}.
+Both tools complement each other as each is able to successfully reconstruct a full chloroplasts in cases where the other tool fails.
+In rare cases \np{} or \oa{} are the only tool to succeed.
+For \fp{}, \np{} and \oa{} do not perform 100\% reproducibly so re-running the tool after a failed attempt might be successful.
+\ce{} yields few complete chloroplast assemblies but requires few resources and is easy to install and use (so it can be considered as a quick first try).
+Both \ioga{} and \cassp{} fail to return any success.
 
 \subsection*{Clear guidelines for the end-user}
-Which program (or combination of programs) to use? Does the decision depend on some parameter of the data (read length, amount, taxonomic group, ...)?
+Given these results our recommendation to users is to run \go{} and in case of failure \fp{}.
+If both programs fail it is sensible to re-run \fp{} and try \np{} and \oa{}.
+This procedure maximizes the chance to effectively and efficiently recover the circular chloroplast genome from mixed genome data.
+If this procedure fails a next step could be a reference guided approach (or tweaking parameters).
+For an automated approach running \go{} and \fp{} in parallel appears to be a good trade-off between chance of success and resources.
+
+\todo{Does the decision depend on some parameter of the data (read length, amount, taxonomic group, ...)?}
 
@@
   \caption{\csentence{Sucess of assemblers on real data sets on tree derived from ncbi taxonomy \cite{ncbi2011}}
-      Figure legend text.}
+      Figure legend text. }
       \label{fig:tree}
-      \end{figure}
+      \end{figure}\todo{cite itol}
 

### 2019-05-29 bmc_article.tex
Update on Overleaf.

@@
 \newcommand{\zenodorepo}{\cite{zenodorepo}}
+
+\newcommand{\genename}[1]{\textit{#1}}
 
@@
 These efforts elucidated the general genome organization and structure of chloroplasts, expanded by many more studies over the years.
-Chloroplast genome content and structure \textcolor{red} {are}  reviewed elsewhere \cite{wicke_evolution_2011,green_chloroplast_2011}.
+Chloroplast genome content and structure are reviewed elsewhere \cite{wicke_evolution_2011,green_chloroplast_2011}.
 Chloroplast genomes are widely used for evolutionary analyses \cite{martin_plastid_2010,xiao-ming_inferring_2017}, barcoding \cite{kress_use_2005,hollingsworth_dna_2009,de_vere_dna_2015}, and meta-barcoding \cite{bell_review_2016,deiner_environmental_2017}.
@@
 Despite the overall high conservation there are striking differences between groups (e.g.
-loss of whole gene families like ndh genes in \textit{Droseraceae} \cite{nevill_plastome-wide_2019} and extreme evolutionary cases with very low GC content and a modified genetic code \cite{su_novel_2019}).
+loss of whole gene families like \genename{ndh} genes in Droseraceae \cite{nevill_plastome-wide_2019} and extreme evolutionary cases with very low GC content and a modified genetic code \cite{su_novel_2019}).
 These differences call for comparative genomic approaches.
@@
 Reduced genomes in parasitic plants.
-Loss of ndh gene family (maybe too specific).
+Loss of \genename{ndh} gene family (maybe too specific).
 Preliminary SNP analysis in \plant{At} to estimate intraspecific variability?
@@
 \subsection*{Approaches to extracting chloroplasts from whole genome data}
-\todo{ausbauen}
-1. Getting chloroplast reads out of mixed files
-Mapping (potentially iterative), k-mer coverage analysis, seeded assembly
-2. Assembly of chloroplast (incl special structure with IRs)
-normal assembly - then blast, assembly then graph resolution, might be combined with step 1.
-\cite{twyford_strategies_2017}
+
+In general, obtaining a chloroplast genome from WGS data requires two steps. First, the chloroplast reads have to be extracted from the mixed sequencing data. 
+The second step is the assembly and resolving the special circular structure including the inverted repeat.
+The extraction of the reads can be achieved by mapping the reads to a reference chloroplast. \todo{example}
+This can also be done iteratively, as done by \todo{\ioga{}?}.
+A different approach relies on the higher coverage of chloroplast data in the whole genome sequencing data set.
+A kmer analysis can be used here to extract the most frequent reads.
+An example for this is implemented in \ce{}.
+A third method, solving both steps simultaneously, uses a reference chloroplast as seed and then assembles the reads based on that. \todo{example}
+
+Once the chloroplast reads are extracted from the data set, they need to be assembled.
+To resolve the special structure, it is possible to analyze the assembly graph and infer the circular structure and the inverted repeat from that.
+This approach is used in \ce{}.
+A second method uses local alignments to the assembly to find the correct order of the contigs.
+\todo{example}
+
+\todo{cite twyford strategies 2017}
+
+%\todo{ausbauen}
+%1. Getting chloroplast reads out of mixed files
+%Mapping (potentially iterative), k-mer coverage analysis, seeded assembly
+%2. Assembly of chloroplast (incl special structure with IRs)
+%normal assembly - then blast, assembly then graph resolution, might be combined with step 1.
 
@@
 This means: no data preparation, no specific reference (but \plant{At} if required), default parameters, no manual finishing.
-We further restricted our benchmark to paired Illumina data sets as these are the most common \todo{cite?} and the %\todo{(all?) - habs gecheckt}
-tools in this study can not handle any other types.
-\todo{tools can not handle passt hier finde ich nicht als Begründung.
+We further restricted our benchmark to paired end Illumina data sets as these are the most common sequencing platform \cite{Goodwin2016}.
+% done by Frank \todo{tools can not handle passt hier finde ich nicht als Begründung.
 Wir geben gerade vor was uns interessiert und wählen später Tools aus die dazu passen.
@@
 \subsection*{Our Setup}
-\todo{ausformulieren}
-Defined interface, forward.fq and reverse.fq as only input. output.fa as only relevant output.
-Docker container, all derived from main container, wrapper script makes all tools work conforming to the defined interface.
-Run docker containers for performance measurement and singularity containers on real datasets.
-Singularity container were built from docker containers for usage on Julia-HPC of JMU using Singularity v.2.5.2 \cite{kurtzer2017singularity}
+% done by Frank \todo{ausformulieren}
+We want to use accomplish a minimum of different parameter settings for all assembly programs.
+Therefore, we decided to specify that all programs have to work based on two input files, representing a data set's forward (\texttt{forward.fq}) and reverse input (\texttt{reverse.fq}).
+Moreover, depending on the assembler, files with different names and locations are generated as final output.
+Those different files are copied and renamed to ensure \texttt{output.fa} as exclusive output of an assembly approach.
+Additionally, we want to an environment variable to control the number of allowed threads.
+All three requirements (defined input file names, defined output file name, thread number control via environment variable) are ensured by a simple wrapper script (\texttt{wrapper.sh}).
+Finally, for a maximum of reproducibility all programs are bundled into individual docker images based on a central base image which provides all the required software.
+That docker images were used for the recording of the consumption of computational resources.
+Furthermore, all our docker images are converted into singularity containers for the quantitative measurement on simulated and real data sets .
+%
+Singularity container were built from docker images for usage on Julia-HPC of JMU using Singularity v.2.5.2 \cite{kurtzer2017singularity}
 All singularity containers were run on the Julia-HPC on Intel® Xeon® Gold \num{6140} Processors using slurm workload manager version 17.11.8 \cite{Jette02slurm}.
@@
 To avoid suffering from sequencing errors and biological variances, we simulated perfect reads based on the \plant{At} (TAIR10) chloroplast assembly \cite{tair10}.
-Therefore we used a sliding window approach with seqkit \cite{seqkit}.
-The exact commands can be found inside \href{https://github.com/chloroExtractorTeam/benchmark/blob/master/03_representative_datasets.md}{\texttt{03\_representative\_datasets.md}} in \zenododataset{}.
+We used a sliding window approach with \texttt{seqkit} \cite{seqkit}.
+The exact commands are documented in \href{https://github.com/chloroExtractorTeam/benchmark/blob/master/03_representative_datasets.md}{\texttt{03\_representative\_datasets.md}} in \zenododataset{}.
 For the final simulated data sets reads based on pseudo mixtures of TAIR10's core and chloroplast genome:  \num{0}:\num{1}, \num{1}:\num{10}, \num{1}:\num{100}, and \num{1}:\num{1000}.
-Additionally, we generated different read lengths (\SIlist{150;250}{\basepair}).
+Additionally, we generated different read lengths (\SIlist{150;250}{\basepair}) and subsets with exactly 2 million read pairs.
 
@@
 \subsubsection*{Real}
-We downloaded sequencing data from SRA \cite{sra2010} of all organisms with a reference
-chloroplast in CpBase \cite{cpbase}.
-In total, this accumulated to \num{380} datasets, including \num{6} without data and \num{5} with malformatted data.
-This leads to a total set of \num{369} datasets \todo{see supplementary table?}.
+Additionally, we selected real datasets deposited at SRA \cite{sra2010}.
+Among all datasets that matched this search \texttt{((((((("green plants"[orgn]) AND "wgs"[Strategy]) AND "illumina"[Platform]) AND "biomol dna"[Properties]) AND "paired"[Layout]) AND "random"[Selection])) AND "public"[Access]} (on 2019-03-28) we selected one dataset per species with a reference chloroplast in CpBase \cite{cpbase}.
+In total, this accumulated to \num{380} datasets, including \num{6} without data and \num{5} with malformatted data \todo{soll ich da die genauen accessions nochmal raussuchen?
+bzw.
+im supp table flaggen?}.
+This leads to a total set of \num{369} datasets \todo{see supplementary table - da die real\_datasets.tsv, die sraruninfo oder eine custom table?}.
 
@@
 
-\subsubsection*{real data sets}
+\subsubsection*{Real data sets}
 Concerning the performance of the assemblers on evaluated on the real data sets from SRA database we were able to observe considerable differences in the median score (\cref{fig:swarmplot}).
 The highest scores were achieved by \go{} with a median of 99.7 and 199 circular assemblies out of a total of 356 assemblies that resulted in an output  \cref{tab:scores}.
-The performance of \go{} is seconded by \fb{} \np{} \oa{}, with \fb{} outperforming the latter two slightly in terms of score, however \fb{} as almost or more than twice as much \num{114} perfectly assembled chloroplast genomes as \np{} with \num{66} or \num{55} circular genomes for \oa{}.
+The performance of \go{} is seconded by \fp{} \np{} \oa{}, with \fp{} outperforming the latter two slightly in terms of score, however \fp{} as almost or more than twice as much \num{114} perfectly assembled chloroplast genomes as \np{} with \num{66} or \num{55} circular genomes for \oa{}.
 \ioga{} and \cassp{} were both not able to assemble a single circular, single-contig genome \cref{tab:scores}, consequently resulting in the lowest mean and median scores.
-
-%% Ich werde die Namen in der Tabelle anpassen, sobald ich die finale Version habe
 
@@
 Similarly computational requirements or run time is less relevant if the goal is to assemble a single chloroplast for further analysis, but it is essential if hundreds or thousands of samples should be processed in parallel for a large scale study.
-Eventually, both ease of use and runtime are irrelevant if the tool is not able to successfully accomplish it's task.
+Eventually, both ease of use and runtime are irrelevant if the tool is not able to successfully accomplish its task.
 Also the scope of this study needs to be considered when interpreting the guidelines below.
@@
 In rare cases \np{} or \oa{} are the only tool to succeed.
-For \fp{}, \np{} and \oa{} do not perform 100\% reproducibly so re-running the tool after a failed attempt might be successful.
+The tools \fp{}, \np{}, and \oa{} seem to be not \SI{100}{\percent} reproducible, thus re-running the tool after a failed attempt might be successful.
 \ce{} yields few complete chloroplast assemblies but requires few resources and is easy to install and use (so it can be considered as a quick first try).
@@
 \begin{table}[ht]
+\caption{Scores of assemblies of simulated data}
+\centering
+\begin{tabular}{rlrrrrrrr}
+  \hline
+ & dataset & CAP & CE & Fast-Plast & GetOrganelle & IOGA & NOVOPlasty & org.ASM \\ 
+  \hline
+1 & sim\_150bp.0-1 & 79.10 & 100.00 & 99.72 & 100.00 &  & 91.52 & 100.00 \\ 
+  2 & sim\_150bp.1-10 &  & 56.44 &  & 100.00 &  & 91.52 & 78.00 \\ 
+  3 & sim\_150bp.1-10.2M &  &  & 99.97 & 100.00 &  & 100.00 & 82.72 \\ 
+  4 & sim\_150bp.1-100 &  & 100.00 &  & 100.00 &  & 91.52 & 91.50 \\ 
+  5 & sim\_150bp.1-100.2M &  & 100.00 & 99.47 & 100.00 & 74.82 & 100.00 & 100.00 \\ 
+  6 & sim\_150bp.1-1000 & 79.10 &  &  & 100.00 &  & 91.52 & 91.50 \\ 
+  7 & sim\_150bp.1-1000.2M & 79.10 & 100.00 & 99.72 & 100.00 &  & 91.52 & 100.00 \\ 
+  8 & sim\_250bp.0-1 & 79.10 & 100.00 & 93.83 & 100.00 &  & 91.52 & 100.00 \\ 
+  9 & sim\_250bp.1-10 &  & 54.98 & 68.45 & 100.00 &  & 91.52 & 40.20 \\ 
+  10 & sim\_250bp.1-10.2M &  &  & 93.00 & 100.00 &  & 87.40 & 40.20 \\ 
+  11 & sim\_250bp.1-100 &  & 100.00 & 93.83 & 100.00 & 65.81 & 91.52 & 100.00 \\ 
+  12 & sim\_250bp.1-100.2M &  & 100.00 & 93.83 & 100.00 & 75.73 & 87.40 & 100.00 \\ 
+  13 & sim\_250bp.1-1000 & 79.10 & 21.30 &  & 100.00 &  & 91.52 & 91.50 \\ 
+  14 & sim\_250bp.1-1000.2M & 79.10 & 100.00 & 93.83 & 100.00 &  & 87.40 & 100.00 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+\begin{table}[ht]
 \caption{Mean scores of chloroplast genome assemblers}
@@
 \end{table}
+
+\include{sets_re_runs.tex}
 

### 2019-05-30 bmc_article.tex
Update on Overleaf.

@@
 \newcounter{todocounter}
+\newcommand{\ff}[1]
+{\stepcounter{todocounter}
+ \todo[color=blue!40,author=For Frank]{\thetodocounter: #1}
+ }
 \newcommand{\ak}[1]
@@
 \begin{abstract} % abstract
+\ff{Abstract}
+Useful as always: \url{https://cbs.umn.edu/sites/cbs.umn.edu/files/public/downloads/Annotated_Nature_abstract.pdf}
 The special issue will accept manuscripts presenting:
@@
 \kwd{Chloroplast}
-\kwd{Genome assembly}
-\kwd{author}
+\kwd{Genome}
+\kwd{Assembly}
+\kwd{Software}
+\kwd{Benchmark}
 \end{keyword}
@@
 For example \textit{Arabidopsis thaliana} core genome is approximately \SI{125}{\mega\basepair} in length \cite{schmuths2004,cao2011} while the size of the chloroplast genome with \SI{154}{\kilo\basepair} is more than \SI{800}{\times} smaller than the core genome \cite{sato1999}.
-However, the specific genome structure (esp. the large inverted repeat) complicates automated resolution with short read technologies (cite?).
+However, the specific genome structure (esp. the large inverted repeat) complicates automated resolution with short read technologies\todo{cite}.
 Many genome sequencing projects contain chloroplast reads as by-product.
@@
 
-\subsection*{Chloroplast genome architecture}
+\subsection*{Chloroplast genome architecture}\ff{Chloroplast genome architecture section}
 Maybe separate section describing a prototypical chloroplast: LSC, IRa, SSC, IRb.
@@
 
+Defferent strategies have been developed to assemble chloroplast genomes \cite{twyford_strategies_2017}.
 In general, obtaining a chloroplast genome from WGS data requires two steps. First, the chloroplast reads have to be extracted from the mixed sequencing data. 
@@
 \todo{example}
-
-\todo{cite twyford strategies 2017}
 
@@
 Four different metrics were Incorporated, each contributing  $\frac{1}{4}$ to the total score: Completeness, correctness, repeat resolution and continuity.
+These metrics are similar in concept by those used in the Assemblathon 2 project: coverage, validity, multiplicity, and parsimony \cite{assemblathon2}.
 
@@
 The resulting assemblies were scored again as described above and the scores of the first and the second run were compared to each other.
+This information is important to decide whether it is worth it to re-try a program in case of failure.
 
@@
 \subsection*{Ideas for future development}
+\ff{this section (lower priority)}
 Combining components from different tools might be a promising approach. E.g. read scaling from \ce{}, assembly from \go{} and structural resolution with \fp{}.
@@
 \section*{Conclusion}
+\ff{Conclusion}
 %Short summary of clear guidelines and future development (might not be necessary as these are the last two sections of the Discussion anyway, so we might elect to skip this).

### 2019-06-03 code/eval_cov.r
Update eval_cov.r

@@ -1,4 +1,4 @@
-dps = c("tidyverse","dabestr","UpSetR","RColorBrewer","ggbeeswarm","ggpmisc","xtable")                   
+dps = c("tidyverse","dabestr","UpSetR","RColorBrewer","ggbeeswarm","ggpmisc","xtable","foreach")           
 sapply(dps,function(x){if(!require(x,character.only = T)){install.packages(x);library(x,character.only = T)}else{library(x,character.only = T)}})
 
 
@@ -62,6 +62,7 @@ dev.off()
 run_log <- read_tsv("results/log_clean.tsv")
 
 ## convert bytes to GB in log file 
+
 run_log[,14:15] <- run_log[,14:15]  / 10^9
 
 run_log_mem <- run_log %>%  filter(exit_code==0) %>%
@@ -150,10 +151,26 @@ out_j %>% ggplot(aes(x=score,y=score_rerun,col=assembler)) + geom_point()  + the
 ggsave("plots/repro.pdf")
 
 
-out_tibble %>% drop_na %>% select(assembler, score) %>% group_by(assembler) %>%
-    summarize(Mean=mean(score),
-              Median=median(score),
-              SD = sqrt(var(score)),
-              N_perfect = length(which(score > 99)),
-              N_tot = length(score)) %>%
-    xtable
+
+
+score_summary <- out_tibble %>% drop_na %>% select(assembler, score) %>% group_by(assembler) %>%
+    summarize(Mean=mean(score), SD = sqrt(var(score)), N_perfect = length(which(score > 99)), N_tot = length(score))
+
+xtable(score_summary)
+
+out_tibble_sim %>% select(assembler,score,dataset) %>% spread(assembler,score)  %>% xtable
+
+
+sra <- read.delim("SRA/my_accs",header =F )
+re_run <- read.delim("re_runs.txt",header =F )
+
+sra_re <- sra %>% add_column("Re-eval" = 
+            foreach(i = 1:nrow(sra),.combine = "c") %do%
+            ifelse(sra[i,1] %in% re_run[,1], "Yes","NO"))
+
+print.xtable(sra_re %>% xtable,file="sets_re_runs.tex",type="latex")
+
+colnames(sra_re)[1] <- "data set"
+
+write.csv(sra_re,"sets_re_runs.csv")
+

### 2019-06-05 bmc_article.tex
Update on Overleaf.

--- 2019-05-29 bmc_article.tex
@@
 \author[
-    addressref={aff2,aff3},
+    addressref={aff1,aff3},
     noteref={n1},
@@
 \author[
-    addressref={aff2},
+    addressref={aff1,aff2},
     noteref={n1},
@@
 \author[
-   addressref={aff2,aff1,aff3 },
+   addressref={aff1,aff3,aff2 },
    noteref={n2},
@@
 \author[
-   addressref={aff1,aff4},                   % id's of addresses, e.g. {aff1,aff2}
+   addressref={aff2,aff4},                   % id's of addresses, e.g. {aff1,aff2}
    corref={aff1},                       % id of corresponding address, if any
@@
 
+\address[id=aff1]{%
+  \orgname{Center for Computational and Theoretical Biology, University of W\"{u}rzburg},
+  \street{Campus Hubland Nord},
+  \postcode{97074}
+  \city{W\"{u}rzburg},
+  \cny{Germany}
+}
+
+\address[id=aff3]{%
+  \orgname{AnaLife Data Science},
+  \street{Friedrich-Bergius-Ring 15},
+  \postcode{97076}
+  \city{W\"{u}rzburg},
+  \cny{Germany}
+}
 \address[id=aff2]{%                           % unique id
@@
 }
-\address[id=aff1]{%
-  \orgname{Center for Computational and Theoretical Biology, University of W\"{u}rzburg},
-  \street{Campus Hubland Nord},
-  \postcode{97074}
-  \city{W\"{u}rzburg},
-  \cny{Germany}
-}
-\address[id=aff3]{%
-  \orgname{AnaLife Data Science},
-  \street{Friedrich-Bergius-Ring 15},
-  \postcode{97076}
-  \city{W\"{u}rzburg},
-  \cny{Germany}
-}
+
 \address[id=aff4]{%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{abstractbox}
-
 \begin{abstract} % abstract
-The special issue will accept manuscripts presenting:
-
-- in-depth analyses of advantages
-
--limitations of state-of-the-art methods
-
--demonstration on a variety of representative datasets and simulations
-
--clear guidelines/recommendations for the end-user
-
--insight into future directions for methods
-\parttitle{First part title} %if any
-Text for this section.
-
-\parttitle{Second part title} %if any
-Text for this section.
+%One or two sentences providing a basic introduction to the field, comprehensible to a scientist in any discipline.
+Chloroplasts are photosynthetic active organelles in plant cells and contain their own genomic information.
+That genome can be utilized in different scientific fields like phylogenetics or biotechnology.
+%Two to three sentences ofmore detailed background, comprehensible to scientists in related disciplines.
+Thus, different assemblers have been developed specialized in chloroplast assemblies.
+Those assemblers often use the output of whole genome sequencing experiments as input.
+Such sequencing data contain usually the complete chloroplast genome information, even if the sequencing aims for the core genome.
+%One sentence clearly stating the general problem being addressed by this particular study.
+The Different assembly tools have never been systematically compared. %to each other concerning success rate or computational requirements.
+%One sentence summarising the main result (with the words “here we show” or their equivalent).
+Here we present a benchmark of seven chloroplast assembly tools, which are under active\todo{Niklas: da kann man bei IOGA drüber streiten} development and are capable to succeed in more than \SI{60}{\percent} of real data sets.
+%Two or three sentences explaining what the main result reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
+Our results show significant differences between the tested assemblers in terms of generating whole chloroplast genome sequences and computational requirements.
+Moreover, we suggest further development to improve user experience and success rate.
+%One or two sentences to put the results into a more general context. 
+In terms of reproducibility, we created docker images for each tested tool, which are available for the scientific community.
+Following the presented guidelines, users are able to analyse and screen data sets for chloroplast genomes using only standard computer infrastructure.
+%Two or three sentences to provide a broader perspective, readily comprehensible to a scientist in any discipline, may be included in the first paragraph if the editor considers that the accessibility of the paper is significantly enhanced by their inclusion.
+Thus large scale screening for chloroplasts as hidden treasures within genomic sequencing data is feasible.
+
+%\ff{Abstract}
+%Useful as always: \url{https://cbs.umn.edu/sites/cbs.umn.edu/files/public/downloads/Annotated_Nature_abstract.pdf}
+%The special issue will accept manuscripts presenting:
+%
+%- in-depth analyses of advantages
+%
+%-limitations of state-of-the-art methods
+%
+%-demonstration on a variety of representative datasets and simulations
+%
+%-clear guidelines/recommendations for the end-user
+%
+%-insight into future directions for methods
+%\parttitle{First part title} %if any
+%Text for this section.
+%
+%\parttitle{Second part title} %if any
+%Text for this section.
 \end{abstract}
@@
 %%
-\newpage
 \section*{Introduction}
 \subsection*{General introduction and motivation}
-The chloroplast as the photosynthetic organelle harboring its own genome has been an early target for sequencing.\ak{maybe even 1-2 sentences about general chloroplast importance}
+Chloroplasts are essential organelles present in plant cells and the cells of some protists.
+Chloroplasts enable the conversion of light energy into chemical energy via photosyntesis.
+They harbor their own ribosomes and a circular DNA genome with a size between \SIrange{120}{160}{\kilo\basepair} \cite{palmer_1985}.
+Because of this small size, the chloroplast genome has been an early target for sequencing.
 The first chloroplast genome sequences were obtained as early as 1986 \cite{ohyama_chloroplast_1986,shinozaki_complete_1986}.
-These efforts elucidated the general genome organization and structure of chloroplasts, expanded by many more studies over the years.
-Chloroplast genome content and structure are reviewed elsewhere \cite{wicke_evolution_2011,green_chloroplast_2011}.
+These early efforts elucidated the general genome organization and structure of the chloroplast DNA. 
+Chloroplast genome content and structure are reviewed for example in \cite{wicke_evolution_2011,green_chloroplast_2011}.
 Chloroplast genomes are widely used for evolutionary analyses \cite{martin_plastid_2010,xiao-ming_inferring_2017}, barcoding \cite{kress_use_2005,hollingsworth_dna_2009,de_vere_dna_2015}, and meta-barcoding \cite{bell_review_2016,deiner_environmental_2017}.
-Interesting aspect of chloroplast genomes are their reduced size through endosymbiotic gene transfer \cite{martin_evolutionary_2002,timmis_endosymbiotic_2004} and the strong conservation of the remaining genes (cite).
-Despite the overall high conservation there are striking differences between groups (e.g.
-loss of whole gene families like \genename{ndh} genes in Droseraceae \cite{nevill_plastome-wide_2019} and extreme evolutionary cases with very low GC content and a modified genetic code \cite{su_novel_2019}).
+Interesting aspects of chloroplast genomes are their small size (\SIrange{120}{160}{\kilo\basepair},\cite{palmer_1985}), caused through endosymbiotic gene transfer \cite{martin_evolutionary_2002,timmis_endosymbiotic_2004} and the low number of \numrange{100}{120} genes that are still encoded on the chloroplast genome \cite{wicke_evolution_2011}.
+Despite the overall high conservation of the genome sequence, there are striking differences in the gene content between different groups (e.g.
+the loss of the whole \genename{ndh} gene family in Droseraceae \cite{nevill_plastome-wide_2019}).
+Even more extreme evolutionary cases, where chloroplasts show a very low GC content and a modified genetic code are described \cite{su_novel_2019}.
+
 These differences call for comparative genomic approaches.
-
-It is much easier to decipher the complete chloroplast genome than the complete core genome, due its comparably smaller size.
-For example \textit{Arabidopsis thaliana} core genome is approximately \SI{125}{\mega\basepair} in length \cite{schmuths2004,cao2011} while the size of the chloroplast genome with \SI{154}{\kilo\basepair} is more than \SI{800}{\times} smaller than the core genome \cite{sato1999}.
-However, the specific genome structure (esp. the large inverted repeat) complicates automated resolution with short read technologies (cite?).
-Many genome sequencing projects contain chloroplast reads as by-product.
-In some cases the chloroplast data is even considered contamination so experimental protocols for reducing their content have been developed \cite{lutz_isolation_2011}.
-The resolved chloroplast genome helps to remove these reads, which can improve assembly of the core genome.
-Databases exist, containing short read data for species where no reference chloroplast is publicly available.
-There is a lot of potential use cases for chloroplast genomes \cite{tonti-filippini_what_2017}
-Resolving these (hidden treasures) would allow for more and larger scale comparative studies on whole chloroplasts.
-In a different application researchers use shallow genome sequencing to reconstruct full chloroplast genomes for use as super-barcodes \cite{coissac_barcodes_2016}.
-There are also applications in biotechnology and genetic engineering \cite{daniell_chloroplast_2016}.
-
-\subsection*{Chloroplast genome architecture}
-Maybe separate section describing a prototypical chloroplast: LSC, IRa, SSC, IRb.
-Gene number and content.
-Size ranges.
-Evolutionary history incl.
-endosymbiontic gene transfer.
-Reduced genomes in parasitic plants.
-Loss of \genename{ndh} gene family (maybe too specific).
-Preliminary SNP analysis in \plant{At} to estimate intraspecific variability?
+Given the small size, it is much easier to decipher the complete chloroplast genome than the complete core genome.
+For example the \plant{At} core genome is approximately \SI{125}{\mega\basepair} in length \cite{schmuths2004,cao2011} while the size of the \plant{At} chloroplast genome with \SI{154}{\kilo\basepair} is more than \SI{800}{\times} smaller \cite{sato1999}.
+
+Even if only a single chloroplast is located inside a plant cell, several hundreds copies of the chloroplast genome exists in each cell \cite{kumar_2014,bendich_1987}.
+Therefore, many genome sequencing projects contain chloroplast reads as by-product.
+In some cases the chloroplast data is even considered contamination and experimental protocols for reducing their content have been developed \cite{lutz_isolation_2011}.
+An alternative approach to improve the assembly of the core genome would be to first resolve the chloroplast genome and afterwards use this information to remove those reads that map to the chloroplast genome.
+
+Structurally, two inverted repeats (IR\textsubscript{A} and IR\textsubscript{B}) of \SIrange{10}{76}{\kilo\basepair} divide the chloroplast genome into a large (LSC) and a small single copy (SSC) region \cite{palmer_1985}.
+Those large inverted repeats complicates automated resolution with short read technologies\cite{Wang2018}.
+Moreover, the existence of different chloroplasts within a single individual, and thus multiple different chloroplast genomes, have been described for different plants \cite{corriveau_1988,Chat2002,Scar2016}.
+Although the origin and evolutionary importance of this phenomena, - called heteroplasmy - are only poorly understood, the assembly of whole chloroplast genomes might be hindered.
+
+Databases containing short read data for species where no reference chloroplast sequence is publicly available, exist.
+The availability of whole chloroplast genomes would enable large scale comparative studies \cite{tonti-filippini_what_2017}.
+Additionally, reconstructed full chloroplast genomes have been used as super-barcodes \cite{coissac_barcodes_2016}, for biotechnology applications and genetic engineering \cite{daniell_chloroplast_2016}.
+
+%\subsection*{Chloroplast genome architecture}\ff{Chloroplast genome architecture section}
+%
+%Maybe separate section describing a prototypical chloroplast: LSC, IRa, SSC, IRb. Gene number and content. 
+%Size ranges. 
+%Evolutionary history incl. endosymbiontic gene transfer. 
+%Reduced genomes in parasitic plants. Loss of \genename{ndh} gene family (maybe too specific).
+%Preliminary SNP analysis in \plant{At} to estimate intraspecific variability?
 Is there anything known about intra-organismic variability (do some plants have multiple populations of chloroplasts?
@@
 
+Different strategies have been developed to assemble chloroplast genomes \cite{twyford_strategies_2017}.
 In general, obtaining a chloroplast genome from WGS data requires two steps. First, the chloroplast reads have to be extracted from the mixed sequencing data. 
-The second step is the assembly and resolving the special circular structure including the inverted repeat.
-The extraction of the reads can be achieved by mapping the reads to a reference chloroplast. \todo{example}
-This can also be done iteratively, as done by \todo{\ioga{}?}.
-A different approach relies on the higher coverage of chloroplast data in the whole genome sequencing data set.
-A kmer analysis can be used here to extract the most frequent reads.
+The second step is the assembly and resolving the special circular structure including the inverted repeats.
+The extraction of the reads can be achieved by mapping the reads to a reference chloroplast. \cite{Vinga2012}.
+A different approach that does not perform alignments, relies on the higher coverage of chloroplast data in the whole genome sequencing data set\cite{Chan2013}.
+Here, a $k$-mer analysis can be used to extract the most frequent reads.
 An example for this is implemented in \ce{}.
-A third method, solving both steps simultaneously, uses a reference chloroplast as seed and then assembles the reads based on that. \todo{example}
-
-Once the chloroplast reads are extracted from the data set, they need to be assembled.
-To resolve the special structure, it is possible to analyze the assembly graph and infer the circular structure and the inverted repeat from that.
-This approach is used in \ce{}.
-A second method uses local alignments to the assembly to find the correct order of the contigs.
-\todo{example}
-
-\todo{cite twyford strategies 2017}
-
-%\todo{ausbauen}
-%1. Getting chloroplast reads out of mixed files
-%Mapping (potentially iterative), k-mer coverage analysis, seeded assembly
-%2. Assembly of chloroplast (incl special structure with IRs)
-%normal assembly - then blast, assembly then graph resolution, might be combined with step 1.
+A third method combines both approaches by useing a reference chloroplast as seed and simultaneously assembling the reads based on $k$-mers \cite{dierckxsens_novoplasty:_2017}.
+
+%\todo{Niklas: wir nennen hier immer nur \ce{} als beispiel - wir sollten auch andere nennen}
+%\todo{example}
+%\ak{e.g.
+HomBlocks: A multiple-alignment construction pipeline for organelle phylogenomics based on locally collinear block searching, aber ist nicht inkluded, also können wir zitieren, müssen aber nicht}
 
 \subsection*{Purpose and scope of this study}
-The goal of this study is to compare the effectiveness and efficiency of existing open source command-line tools to de-novo assemble whole chloroplast genomes from raw mixed genomic data sets with minimal configuration.
-This means: no data preparation, no specific reference (but \plant{At} if required), default parameters, no manual finishing.
-We further restricted our benchmark to paired end Illumina data sets as these are the most common sequencing platform \cite{Goodwin2016}.
-% done by Frank \todo{tools can not handle passt hier finde ich nicht als Begründung.
-Wir geben gerade vor was uns interessiert und wählen später Tools aus die dazu passen.
-Sonst gibt es einen Ringschluss zwischen Scope und Tool Selection.}
+The goal of this study is to compare the effectiveness and efficiency of existing open source command-line tools to de-novo assemble whole chloroplast genomes from raw genomic data sets with minimal configuration.
+This includes no need for extensive data preparation, no need for a specific reference (apart from \plant{At}), no need to change default parameters, no manual finishing.
+We further restricted our benchmark to paired end Illumina data sets as these are routinely generated by modern sequencing platforms \cite{Goodwin2016}.
 
@@
 Still, we acknowledge that the performance of the tools might be significantly improved by optimizing parameters (and references if applicable) for each data set specifically.
-(However, this was outside the scope of this study.)
-
-%Clearly state criteria.
-Work with mixed data.
-Full automation.
-De novo - no manual selection of appropriate reference.
-No manual finishing.
-The step we are interested in is: from raw paired Illumina (!) reads to a fasta file containing the assembly (optimally full, circularized and on one contig).
-We are not interested in annotation or any additional contigs (genomic, mitochondrion, rRNA, etc.).
-%\cite{koon,oreg,khar,zvai,xjon,schn,pond,smith,marg,hunn,advi,koha,mouse}
+However an exhaustive comparison - including tuning of all different possible parameters for each tool- would not been possible within the scope of this study.
+
+Our results will enable the discovery of novel chloroplast genomes as well as an assembly of inter/intra-individual differences in the respective chloroplast genomes.
 
 \section*{Methods}
-Source code for all methods is available at \url{https://github.com/chloroExtractorTeam/benchmark} and archived under \zenodorepo{}.
+\subsection*{Data availability}
+Source code for all methods used is available at \url{https://github.com/chloroExtractorTeam/benchmark} and archived in zenodo under \zenodorepo{}.
 All docker images are published on \url{https://cloud.docker.com/u/chloroextractorteam/} and are named with a leading \texttt{benchmark\_} (\cref{tab:dockerimages}).
-Our simulated data sets are stored at \zenododataset{}.
+
+To enable a fair comparison of all tools, we generated simulated sequencing data.
+Those simulated data sets are stored at \zenododataset{}.
 This study adheres to the guidelines for computational method benchmarking \cite{weber_essential_2018}.
@@
 \subsection*{Tool Selection}
-
 We included tools designed for assembling chloroplasts from whole genome paired end Illumina sequencing data.
-The tools must be available as open source software and allow execution via a command line interface.
-A graphical user interface is not suitable for
-running automated comparisons. The following tools were determined to be within the scope of this study:
-
+As a requirement, all tools must be available as open source software and allow execution via a command line interface.
+As a graphical user interface is not suitable for
+running automated comparisons, tools only providing a graphical interface have not been included. The following tools were determined to be within the scope of this study:
 \oa{} \cite{coissac_barcodes_2016}, 
@@
 \np{} \cite{dierckxsens_novoplasty:_2017}, 
-\go{} \cite{jin_getorganelle:_2018}, 
+\go{} \cite{jin_getorganelle:_2018}, and
 \cassp{} \cite{sancho_comparative_2018}.
 
-Other related tools for assembling chloroplasts but outside the scope of this study are \texttt{Organelle PBA} \cite{Soorni2017}, \texttt{sestaton/Chloro} \cite{sestaton}, \texttt{Norgal}  \cite{Al-Nakeeb2017} and \texttt{MitoBim} \cite{mitobim2013}.
-
-\texttt{Organelle PBA} is designed for PacBio data and does not work with paired Illumina data only.
-\texttt{sestaton/Chloro} fits all criteria but is flagged as a work in progress and development seems to have ended two years ago.
-\texttt{Norgal} is a tool to extract organellar DNA from whole genome data based on a k-mer frequency approach.
+Other related tools for assembling chloroplasts that did not meet our criteria and are therefore outside the scope of this study are for example:
+\texttt{Organelle PBA} \cite{Soorni2017}, \texttt{sestaton/Chloro} \cite{sestaton}, \texttt{Norgal}  \cite{Al-Nakeeb2017}, and \texttt{MitoBim} \cite{mitobim2013}.
+
+\texttt{Organelle PBA} is designed for PacBio data and does not work with paired Illumina data alone.
+\texttt{sestaton/Chloro} fits our criteria, but it is flagged as work in progress and development and support seem to have ended two years ago.
+\texttt{Norgal} is a tool to extract organellar DNA from whole genome data based on a \textit{k}-mer frequency approach.
 However the final output is a set of contigs of mixed mitochondrial and plastid origin.
 The suggested approach to get a finished chloroplast genome is to run \np{} on the ten longest contigs.
+Therefore we only included \np{} with the default settings and excluded \texttt{Norgal}.
 \texttt{MitoBim} is specifically designed for mitochondrial genomes.
-Even though there is a claim by the author that it can be used for chloroplasts as well (\url{https://github.com/chrishah/MITObim/issues/16}, accessed: 2019-05-27), there is no further description on how to do that.
-%\todo{haben wir es versucht?
-- nein}
+Even though there is a claim by the author that it can be used for chloroplasts as well, there is no further description on how to do that \cite{mitobim_issue16}.
+
 Additionally, there is a protocol for the \texttt{Geneious} \cite{geneious} software available \cite{geneious-protocol}.
@@
 % done by Frank \todo{ausformulieren}
-We want to use accomplish a minimum of different parameter settings for all assembly programs.
-Therefore, we decided to specify that all programs have to work based on two input files, representing a data set's forward (\texttt{forward.fq}) and reverse input (\texttt{reverse.fq}).
-Moreover, depending on the assembler, files with different names and locations are generated as final output.
-Those different files are copied and renamed to ensure \texttt{output.fa} as exclusive output of an assembly approach.
-Additionally, we want to an environment variable to control the number of allowed threads.
+We want to use accomplish a minimum of different parameter settings for all assembly programs to enable a fair comparison. 
+Therefore, we decided to specify that all programs have to work based on two input files, representing a data set's forward (\texttt{forward.fq}) and reverse  (\texttt{reverse.fq}) sequence file in FASTQ format.
+Depending on the assembler, output files with different names and locations are generated.
+Those different files are copied and renamed to ensure that each assembly approach produces the same output file (\texttt{output.fa}). 
+Additionally, we set an environment variable for all programs to control the number of allowed threads.
 All three requirements (defined input file names, defined output file name, thread number control via environment variable) are ensured by a simple wrapper script (\texttt{wrapper.sh}).
-Finally, for a maximum of reproducibility all programs are bundled into individual docker images based on a central base image which provides all the required software.
-That docker images were used for the recording of the consumption of computational resources.
-Furthermore, all our docker images are converted into singularity containers for the quantitative measurement on simulated and real data sets .
-%
-Singularity container were built from docker images for usage on Julia-HPC of JMU using Singularity v.2.5.2 \cite{kurtzer2017singularity}
-All singularity containers were run on the Julia-HPC on Intel® Xeon® Gold \num{6140} Processors using slurm workload manager version 17.11.8 \cite{Jette02slurm}.
-Assemblies run on \num{4} threads using \SI{10}{\gibi\byte} RAM with a timelimit of \SI{48}{\hour}.
+Finally, for a maximum of reproducibility all programs have been bundled into individual docker images based on a central base image which provides all the required software.
+Those docker images were used for the recording of the consumption of computational resources.
+Furthermore, all our docker images have been converted into singularity containers for the quantitative measurement on simulated and real data sets.
+Singularity container were built from docker images for usage on a HPC-environment using Singularity v.2.5.2 \cite{kurtzer2017singularity}
+All singularity containers were run on %the Julia-HPC 
+\ak{I would note refer to Julia in the ms, maybe we could add it as a link}
+Intel® Xeon® Gold \num{6140}  Processors using a Slurm workload manager version 17.11.8 \cite{Jette02slurm}.
+Assemblies were run on \num{4} threads using \SI{10}{\gibi\byte} RAM with a time limit of \SI{48}{\hour}.
 \subsection*{Data}
@@
 The exact commands are documented in \href{https://github.com/chloroExtractorTeam/benchmark/blob/master/03_representative_datasets.md}{\texttt{03\_representative\_datasets.md}} in \zenododataset{}.
-For the final simulated data sets reads based on pseudo mixtures of TAIR10's core and chloroplast genome:  \num{0}:\num{1}, \num{1}:\num{10}, \num{1}:\num{100}, and \num{1}:\num{1000}.
-Additionally, we generated different read lengths (\SIlist{150;250}{\basepair}) and subsets with exactly 2 million read pairs.
+For the final simulated data sets reads based on mixtures of the \plant{At} (TAIR10) core and chloroplast genome were generated with different ratios ( \num{0}:\num{1}, \num{1}:\num{10}, \num{1}:\num{100}, and \num{1}:\num{1000}).
+Additionally, we generated data with different read lengths (\SIlist{150;250}{\basepair}). All data simulated contain exactly 2 million read pairs.
 
@@
 \subsubsection*{Real}
-Additionally, we selected real datasets deposited at SRA \cite{sra2010}.
-Among all datasets that matched this search \texttt{((((((("green plants"[orgn]) AND "wgs"[Strategy]) AND "illumina"[Platform]) AND "biomol dna"[Properties]) AND "paired"[Layout]) AND "random"[Selection])) AND "public"[Access]} (on 2019-03-28) we selected one dataset per species with a reference chloroplast in CpBase \cite{cpbase}.
-In total, this accumulated to \num{380} datasets, including \num{6} without data and \num{5} with malformatted data \todo{soll ich da die genauen accessions nochmal raussuchen?
-bzw.
-im supp table flaggen?}.
-This leads to a total set of \num{369} datasets \todo{see supplementary table - da die real\_datasets.tsv, die sraruninfo oder eine custom table?}.
+We selected real data deposited at SRA \cite{sra2010}.
+We searched all data that matched  \texttt{((((((("green plants"[orgn]) AND "wgs"[Strategy]) AND "illumina"[Platform]) AND "biomol dna"[Properties]) AND "paired"[Layout]) AND "random"[Selection])) AND "public"[Access]} \cite{sra_search_term}.
+For each species with a reference chloroplast in CpBase \cite{cpbase}, we selected one data set of those.
+In total, this accumulated to \num{369} data sets (see supplement for details).
 
@@
 \subsubsection*{Computational Resources}
-Due to computational resources are limited, we evaluated the effect of different input parameters.
-To monitor the influence, we recorded the mean and the peak CPU usage, the peak memory consumption, and the size of the assembly folder. 
-As input data, we used different data sets comprising \numlist{25000;250000;2500000} read pairs based on our simulated perfect reads.
-Therefore, the simulated perfect read files have been read repeatedly to achieve the required number of read pairs.
-We used our docker image setup (\cref{tab:dockerimages}) to run all assembly programs three times on a given parameter setting.
-The setting combined the different input data and different number of threads to use (\numlist{1;2;4;8}).
-Some programs used more CPU threads than specified, therefore, the number of CPUs available have been fixed using the CPUs option while running the docker run command.
-For each assembly setting, we recorded the peak memory consumption, the CPU usage for calculation of mean and peak CPU usage, and the size of the folder where the assembly was calculated.
+%Due to computational resources are limited, we evaluated the effect of different input parameters.
+We recorded the mean and the peak CPU usage, the peak memory consumption, and the size of the assembly folder for each program. 
+As input data, we used different data sets comprising \numlist{25000;250000;2500000} read pairs sampled from  our simulated reads.
+%Therefore, the simulated perfect read files have been read repeatedly to achieve the required number of read pairs.
+%\ak{etwas umständlich formuliert, hoffe ich hab es jetzt richtig formuliert und verstanden}
+We used our docker image setup (\cref{tab:dockerimages}) \ak{check NUmmerierung tables, oben war auch schon table 2} to run all assembly programs three times for each parameter setting.
+The different settings combined different input data and different number of threads to use (\numlist{1;2;4;8}).
+%\ak{in 'Our Setup' before, schreiben wir 10GiB und 4 threads, müsste dann vielleicht geändert werden}
+Some programs will use more CPU threads than specified, therefore, the number of CPUs available have been fixed using the CPU option while running the docker run command.
+For each assembly setting, we recorded the peak memory consumption, the CPU usage (mean and peak CPU usage) and the size of the folder where the assembly was calculated.
 The values of CPU and memory usage have been obtained by docker.
@@
 \subsubsection*{Qualitative}
-
 The qualitative evaluation is mainly based on the reviewer guidelines for the Journal of Open Source Software (JOSS) \cite{joss}.
@@
 The tools were installed according to their installation instructions and
-the provided tutorial or example usage was executed. During the evaluation, the following
-questions were asked:
+the provided tutorial or example usage was executed. During the evaluation, the following questions were asked:
 
@@
 \end{itemize}
-
+\newline
 These questions were answered with \good{}, \ok{} or \bad{}, depending on the quality of the result. 
-For example, a \good{} installation utilizes a automated package or dependency management like apt,
-CRAN, docker, etc. An \ok{} installation procedure provides a custom script to install everything
-or at least lists all dependencies. A \bad{} installation procedure fails to list important dependencies
-or produces errors, that prevent a successful installation.
-
-After an initial evaluation, we contacted all authors via their GitHub or GitLab issue tracking to
-report any flaws we found.
+For example, a \good{} installation utilizes a automated package or dependency management like \texttt{apt},
+CRAN, docker, etc.
+An \ok{} installation procedure provides a custom script to install everything or at least lists all dependencies.
+A \bad{} installation procedure fails to list important dependencies or produces errors, that prevent a successful installation without exhaustive debugging.
+
+After an initial evaluation, we contacted all authors via their GitHub or GitLab issue tracking to communicate potential flaws we found.
 
@@
 
-Foreach dataset and assembler the proposed chloroplast was compared to the respective reference chloroplast using a pairwise alignment obtained with \texttt{minimap2} v2.16 \cite{li2018minimap2}.
-Based on theses alignments the score is calculated as shown in \cref{eq:quantitative}
+For each data set and assembler the generated chloroplast genome was compared to the respective reference genome using a pairwise alignment obtained with \texttt{minimap2} v2.16 \cite{li2018minimap2}.
+Based on theses alignments a score is calculated as shown in \cref{eq:quantitative}
 The assemblies were scored on a scale from 0 to 100, with 100 being the best and 0 the worst possible score.
 Four different metrics were Incorporated, each contributing  $\frac{1}{4}$ to the total score: Completeness, correctness, repeat resolution and continuity.
+These metrics are similar in concept by those used in the Assemblathon 2 project: Coverage, validity, multiplicity, and parsimony \cite{assemblathon2}.
 
@@
 Secondly, we mapped the reference genome against the query.
-The coverage of the reference genome ($cov_{qry}$) is used as measurment for the correctness of the assembly.
-The repeat resolution is estimated from the size difference of the assembly and the reference genome ($min\left\{ \frac{cov_{qry}}{cov_{ref}}, \frac{cov_{ref}}{cov_{qry}}\right\}$).The $min$ was applied to ensure, that only values between 0 and 1 were obtained.
+The coverage of the reference genome ($cov_{qry}$) is used as measurement for the correctness of the assembly.
+The repeat resolution is estimated from the size difference of the assembly and the reference genome ($min\left\{ \frac{cov_{qry}}{cov_{ref}}, \frac{cov_{ref}}{cov_{qry}}\right\}$), leading to values between 0 and 1.
 The fourth metric used is the continuity, represented by the number of contigs.
-A perfect score is achieved if one circular chromosome was assembled.
+A perfect score is achieved if one circular chromosome was assembled, while the score gets worse with the amount of contigs.
 
@@
 \subsubsection*{Reproducibility}
-For reproducibility  testing we randomly choose  \num{100} data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
-The resulting assemblies were scored again as described above and the scores of the first and the second run were compared to each other.
+To ensure reproducibility of the obtained results, we randomly choose  \num{100} data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
+The resulting assemblies were scored again as described and the scores of the first and the second run were compared to each other.
+This information is important to assess the robustness of the different programs.
 
@@
 \subsubsection*{Time requirements}
-In terms of time efficiency there was a great difference between input datasets, number of threads and the tool in use ranging from a few minutes to several hours (\cref{fig:performance_runtime}).
-Some assemblies failed to finish within the time-limit we set at \SI{48}{\hour}. 
-On average the longest time to complete assemblies was taken by \ioga{} and \fp{} followed by \oa{} and \go{} the most time efficient overall was \ce{} with on average is a little faster than \np{} and \cassp{}.
+In terms of run time, massive differences between the different tools have been observed.
+Apart from tool-specific differences, input data and number of threads had huge impact.
+The observed run times varied from a few minutes to several hours (\cref{fig:performance_runtime}).
+%\ak{did I miss Figure 1 ?, need to check figure numbering in the end}
+Some assemblies failed to finish within the time-limit we set (\SI{48}{\hour}). 
+On average the longest time to generate the assemblies was taken by \ioga{} and \fp{} followed by \oa{} and \go{} the most time efficient tool was \ce{}, which on average is a little faster than \np{} and \cassp{}.
 %% multithreading
+
 Not all the tools were able to benefit from having access to multiple threads.
 Both \np{} and \oa{} take about the same time independent of being able to utilize \numlist[list-final-separator={, or }]{1;2;4;8} threads.
-\cassp{}, \ce{} , \go and \fp{} all profit from multi-threading (\cref{fig:performance_runtime}, \cref{fig:performance_memory_cpu}).
+\cassp{}, \ce{}, \go  and \fp{} all profit from multi-threading (\cref{fig:performance_runtime}, \cref{fig:performance_memory_cpu}).
 
 \subsubsection*{Memory and CPU Usage }
-The peak and mean CPU usage, as well as peak memory and disk usage have been recorded for all assemblers based on a input data set size and a number of threads to use (\cref{fig:performance_memory_cpu}).
-Mainly, the size of the input set influenced the peak memory usage with an exception for \ce{} and \ioga{}.
-Those two assemblers seems to have a memory usage pattern, which is less influenced by data set size.
-The number of allowed threads have only no or a limited impact on the peak memory usage.
-Nevertheless, all programs profit by a higher number of threads, even more if the input size increases.
-In contrast, the disk usage is independent from input size and number of threads for all assemblers, but the factor between the programs exceeds a factor of \num{100}.
+The peak and mean CPU usage, as well as peak memory and disk usage have been recorded for all assemblers based on the same input data set and number of threads to use (\cref{fig:performance_memory_cpu}).
+Mainly, the size of the input data influenced the peak memory usage with the exception of \ce{} and \ioga{}.
+Those two assemblers seems to have a memory usage pattern, which is less influenced by the size of the data.
+The number of allowed threads had only a limited impact on the peak memory usage.
+Nevertheless, all programs profit by a higher number of threads, if the size of the input data was increased.
+In contrast, the disk usage is independent from input size and number of threads for all assemblers.
+%but the factor between the programs exceeds a factor of \num{100}.
 
 \subsection*{Qualitative}
-Most of the tools were evaluated as mainly \good{} (see table \ref{tab:resultsQual}). However, a few critique points remained.
-Two minor dependencies were missing in the \go{} installation instructions.
-There was also no test data available and an issue occurred when running it on a \plant{At} data set.
+The user experience of most tools was evaluated as mainly \good{} (see table \ref{tab:resultsQual}). However, a few critique points remained.
+Two minor dependencies were missing in the \go{} installation instructions and there was no test data available.
+Additionally, an issue occurred when running it on a \plant{At} data set.
 We are currently in the process of resolving this with the authors.
@@
 We found some issues, which are probably related to the requirement of \texttt{Python~3.7}.
-There is a tutorial with sample data available.
-However following the instructions resulted in a segmentation fault.
+There is a tutorial where sample data is available.
+However, following the instructions resulted in a segmentation fault.
 We found a workaround for this bug and contacted the authors.
@@
 This was fixed by the authors after we contacted them.
-\np{} uses a custom license.
-An OSI approved license would be preferred here.
-
-The \ce{} does come with a test data set and a short tutorial. However, a way to evaluate the results of the test run would be nice.
+Additionally, \np{} uses a custom license, where an OSI approved license would be preferred.
+
+The \ce{} does come with a test data set and a short tutorial. However, it is currently not possible to evaluate the results of the test run.
 
@@
 Since there was no update to the GitHub repository for the last three years, the project can be seen as inactive.
-After contact, the authors promised to resolve the mentioned issues.
+After contacting the authors, they promised to resolve the mentioned issues.
 
@@
 The list was updated after we contacted the authors.
-This tool does come with a test data set, however a note about the expected outcome would be nice.
+This tool does come with a test data set, however a note about the expected outcome is missing.
 A more extensive tutorial is provided.
-The description about the parameter is short, but seems to be sufficient.
+The description about the parameter is short, but sufficient.
 
@@
 The only assembler obtaining perfect results according to our score for the simulated data sets is \go{} (\cref{fig:simulated}).
-\ioga{} and \cassp{} showed the worst performance being unable to fully assemble a single chloroplast out of \num{14}.
-\np{} performed second best with scores above \num{80} for all data sets, only failing to resolve the chloroplast contig into one single circular assembly.
-(As could have been expected -> discussion) the overall performance is best, when the input data consists purely of chloroplast reads.
-Only \ioga{} and \cassp{} failed to deliver any results once each.
-Besides that no clear causality between length of the input reads, ratio of core vs chloroplast reads and the performance can be clearly observed.
+\ioga{} and \cassp{} showed the worst performance, being unable to fully assemble a single chloroplast out of \num{14} runs.
+\np{} performed second best with scores above \num{80} for all data sets, only failing to resolve the contigs into one single circular chloroplast assembly.
+The overall performance \ak{of all assemblers ?} is best, when the input data consists purely of chloroplast reads.
+Only \ioga{} and \cassp{} failed to deliver any results under this scenario once.
+In general, no clear correlation between either length of the input reads or the ratio of core vs chloroplast reads and the performance of the different assemblers can be observed.
 
 \subsubsection*{Real data sets}
-Concerning the performance of the assemblers on evaluated on the real data sets from SRA database we were able to observe considerable differences in the median score (\cref{fig:swarmplot}).
-The highest scores were achieved by \go{} with a median of 99.7 and 199 circular assemblies out of a total of 356 assemblies that resulted in an output  \cref{tab:scores}.
-The performance of \go{} is seconded by \fp{} \np{} \oa{}, with \fp{} outperforming the latter two slightly in terms of score, however \fp{} as almost or more than twice as much \num{114} perfectly assembled chloroplast genomes as \np{} with \num{66} or \num{55} circular genomes for \oa{}.
-\ioga{} and \cassp{} were both not able to assemble a single circular, single-contig genome \cref{tab:scores}, consequently resulting in the lowest mean and median scores.
-
-\cref{fig:upset}
-
-\textit{swarm plot goes here}
+Concerning the performance of the assemblers on the real data sets, we were able to observe considerable differences in the median score (\cref{fig:swarmplot}).
+The highest scores were achieved by \go{} with a median of \num{99.7} and \num{199} circular assemblies out of a total of 356 assemblies that resulted in an output (\cref{tab:scores}).
+The performance of \go{} is followed by \fp{}, \np{}, \oa{}, and \ce{}.
+\fp{} is outperforming the latter two slightly in terms of score, with twice as much \num{114} perfectly assembled chloroplast genomes (\np{} produced \num{66} and \oa{} \num{55} circular genomes).
+\ioga{} and \cassp{} were both not able to assemble a single circular, single-contig genome (\cref{tab:scores}), consequently resulting in the lowest mean and median scores (\cref{fig:upset}).
+
+%\textit{swarm plot goes here}
 %% Den upset plot eventuell erst in die Discussion reinbringen ? Da wir davon ableiten welche tools wir empfehlen?
@@
 \subsubsection*{Reproducibility}
-Reproducibility was tested as described above, by re-running assemblies and comparison of the scores of the two assemblies (\cref{fig:reproducibility}).
-Replicates that did not produce an output were manually scored with \num{0}. 
-\go{} was the only tool that succeeded in obtaining similar scores for all the assemblies, without having and completely unsuccessful assemblies for this subset of data.
-Except for \fp{} all the other tools had at least one assembly that was unsuccessful in either runs, but produced an output in the other.
-Notably \ioga{} appears to have a tendency of being able to perform differently in independent runs.
-More that \SI{10}{\percent} of the assemblies failed once, but were successful in the other run.
-
-Both \fp{} and \np{} tend to have minor changes in the assembly when the overall performance is comparably well, leading to the arrow-shaped scatter plots.
-\ce{} and \cassp{} only have few deviations between the two runs, besides a few one-time non-performing data sets, the other all scored the same.
+Reproducibility was tested as described above, by re-running assemblies and comparison of the scores of two assemblies (\cref{fig:reproducibility}).
+Replicates that did not produce an output were manually scored as \num{0}. 
+\go{} was the only tool that succeeded in obtaining similar scores for all assemblies, without producing and completely unsuccessful assemblies for this subset of data.
+Except for \fp{} all the other tools had at least one assembly that was unsuccessful in one run, but produced an output in the other.\ak{oben steht \go{} war als einziges immer gut, dann kommt except for \fp{} ??
+does not seem to be consistent}  Notably \ioga{} appears to have a tendency to perform differently in independent runs.
+Here, more than \SI{10}{\percent} of the assemblies failed in one run only.
+
+Both \fp{} and \np{} tend to have minor changes in the assembly when the overall performance is comparably well, leading to the arrow-shaped scatter plots.\ak{link to figure scatter plots is issing} \ce{} and \cassp{} appear to be the most robust assemblers, having only few deviations between the two runs.
 
 \section*{Discussion}
-Depending on the use case the different criteria assessed in this work need to be weighted differently.
-For example ease of installation and use might not be a big concern if the tool is installed once and integrated in an automated pipeline.
-On the other hand this factor alone might prevent other users from being able to use the tool at all.
-Similarly computational requirements or run time is less relevant if the goal is to assemble a single chloroplast for further analysis, but it is essential if hundreds or thousands of samples should be processed in parallel for a large scale study.
-Eventually, both ease of use and runtime are irrelevant if the tool is not able to successfully accomplish its task.
+We aimed to generate an overall performance score for the different chloroplast assemblers, but depending on distinct downstream applications, the different criteria assessed in this work need to be weighted differently.
+For example, ease of installation and use might not be a big concern if the tool is installed once and integrated in an automated pipeline.
+On the other hand this factor alone might prevent other users from being able to use the tool in the first place.
+Similarly, computational requirements or run time might be less relevant, if the goal is to assemble a single chloroplast for further analysis, but it is essential if hundreds or thousands of samples should be processed in parallel for a large scale study.
+Eventually, both ease of use and run time are irrelevant if the tool is not able to successfully accomplish its task.
 Also the scope of this study needs to be considered when interpreting the guidelines below.
-In particular, we evaluated all tools under the assumption that they are used in the most basic form (default parameters, no hand selected reference, no pre-processing of the data or post-processing of the result, restricted runtime).
-It is important to note that any tool might perform significantly different if parameters and references are fine-tuned for the specific data set.
-
-The overall best success rate both on simulated and real data was achieved by \go{} followed by \fp{}.
-Both tools complement each other as each is able to successfully reconstruct a full chloroplasts in cases where the other tool fails. 
+In particular, we evaluated all tools under the assumption that they are used in the most basic form (default parameters, no hand selected reference, no pre-processing of the data or post-processing of the result, restricted run time).
+It is important to note that any tool might perform significantly different, if the above mentioned parameters  are fine-tuned for a specific data set.
+
+The overall best success rate, both on simulated and real data, was achieved by \go{} followed by \fp{}.
+Both tools complement each other, as each is able to successfully reconstruct a full chloroplasts in cases where the other tool fails. 
 In rare cases \np{} or \oa{} are the only tool to succeed.
-The tools \fp{}, \np{}, and \oa{} seem to be not \SI{100}{\percent} reproducible, thus re-running the tool after a failed attempt might be successful.
-\ce{} yields few complete chloroplast assemblies but requires few resources and is easy to install and use (so it can be considered as a quick first try).
-Both \ioga{} and \cassp{} fail to return any success.
-
-\subsection*{Clear guidelines for the end-user}
-Given these results our recommendation to users is to run \go{} and in case of failure \fp{}.
-If both programs fail it is sensible to re-run \fp{} and try \np{} and \oa{}.
-This procedure maximizes the chance to effectively and efficiently recover the circular chloroplast genome from mixed genome data.
-If this procedure fails a next step could be a reference guided approach (or tweaking parameters).
-For an automated approach running \go{} and \fp{} in parallel appears to be a good trade-off between chance of success and resources.
-
-\todo{Does the decision depend on some parameter of the data (read length, amount, taxonomic group, ...)?}
+The tools \fp{}, \np{}, and \oa{} produce the most variable results, thus re-running the tool after a failed attempt might be successful.
+\ce{} yields only few complete chloroplast assemblies, but requires also only few resources. It is easy to install and use and thus could be considered as a good option for a quick first try.
+Both \ioga{} and \cassp{} have the worst performance of all tools tested and fail to return reliable chloroplast assemblies.
+
+\subsection*{Guidelines for the end-user}
+Given these results, our recommendation is to use \go{} as default option, and in case of failure \fp{} as backup solution.\ak{what if both lead to qualitative different results?, always trust \go{} , or could one compute a high-confidence assembly by combining different results ?, might be a point for future directions.}
+If both programs fail, it is sensible to re-run \fp{} and additionally try \np{} and \oa{}.
+This procedure maximizes the chance to effectively and efficiently recover the circular chloroplast genome from mixed genomic data.
+If none of these four assemblers produce sensible results, a reference guided approach and tweaking of the default parameters, might be the solution.
+Here, it is not possible to provide general guidelines, as the procedure will differ for different data sets.
+For an automated approach, running \go{} and \fp{} in parallel appears to be a good trade-off between success rate and use of resources.
+%\todo{Does the decision depend on some parameter of the data (read length, amount, taxonomic group, ...)?}
 
 \subsection*{Ideas for future development}
-Combining components from different tools might be a promising approach. E.g. read scaling from \ce{}, assembly from \go{} and structural resolution with \fp{}.
-Mitigate installation issues e.g. by containerization.
-Improve documentation and usability.
-Maybe better integrated guessing of parameters (?) at least for automatization (but also because users tend to run a tool with default settings and look on what they get, only powerusers tweak parameters - and if it is possible to get a full chloroplast by guessing the best parameters there is no need for specific knowledge of parameters and their effects by the end user).
-Other (more) data types, PacBio, nanopore.
+%\ff{this section (lower priority)}
+For further experiments, combining different components from different tools might be a promising approach.
+For example, read scaling from \ce{} followed by an assembly by \go{} and finally the structural resolution with \fp{} could be a promising approach, combing the respective strength of the different tools.
+
+Moreover, the installation issues need to be mitigated by modern software.
+Therefore, either containerization (docker, singularity, etc.) or install workflows (eg. bioconda \cite{gruening2018}) should be established by all software packages.
+Otherwise, the burden of the software installation might result in scientists ignoring good tools.
+
+Another important feature of software is a comprehensive documentation, which needs to be up-to-date and maintained.
+Software authors should constantly improve the usability, and be open to suggestions from the users.
+
+Finally, all tools should improve their integrated guessing of default parameters, as many users avoid fine tuning of those, especially, for larger screening approaches.
+Last, as sequencing technology is developing fast ( eg.\ PacBio or nanopore), tools need to be updated to not become obsolete.
+But the hope would be that with ongoing software development and improved sequencing technologies, the generation of whole chloroplast assemblies from any species will become a routine technique.
 
 \section*{Conclusion}
+%\ff{Conclusion}
 %Short summary of clear guidelines and future development (might not be necessary as these are the last two sections of the Discussion anyway, so we might elect to skip this).
-\todo{sollten wir lobend erwähnen, dass alle auf github/gitlab sind?}
-
-Put results back in context: the multitude of available tools shows importance to solve the challenge of chloro extraction.
-Presented benchmarking shows that all tools sometimes struggle even with ``perfect'' data.
-Although no program works everytime, most chloroplasts are resolved by at least one tool (is that so?).
-So programs are complementary, more effort to combine strengths of different methods (or automatic parameter selection - if failure is due to suboptimal parameters for the specific data set).
-
-Outlook: next step in the pipeline is annotation. There is a similar problem: many tools, which one to use? 
-A large scale study reconstructing chloroplasts throughout SRA (or \num{1001} genome project) is feasible and promising using the existing tools (estimated runtime, number of novel chloroplasts).
-A meta-tool that automatically combines the different programs could be developed.
-The benchmarking study could be augmented to automatically select the closest reference from the database and provide that to any tool that can take advantage of references.
+%\todo{sollten wir lobend erwähnen, dass alle auf github/gitlab sind?}
+The main assumption for our study to benchmark different chloroplast assembly tools, is that whole genome sequencing data are also a promising source for chlorplast assemblies.
+Our benchmark shows that ~\SI{60}{\percent} of the available chloroplasts genomes, have been assembled by at least one of the tools we analysed.
+Still, even with simulated (aka``perfect'') data, not all tools succeeded in generating complete chloroplast assemblies.
+Therefore, it is important to know the strengths and weaknesses of the specific tools and provide guidelines for the users.
+Moreover, it might be necessary, to combine different methods or manually explore the parameter space, to obtain reliable results if a single run seems not sufficient.
+Ultimately, large scale studies reconstructing hundreds or thousands of chloroplast genomes are now feasible using the currently available tools. 
+%Outlook: next step in the pipeline is annotation. There is a similar problem: many tools, which one to use? 
+%A large scale study reconstructing chloroplasts throughout SRA (or \num{1001} genome project) is feasible and promising using the existing tools (estimated runtime, number of novel chloroplasts).
+%A meta-tool that automatically combines the different programs could be developed.
+%The benchmarking study could be augmented to automatically select the closest reference from the database and provide that to any tool that can take advantage of references.
 
@@
   The authors disclose that SP, NT, FF, and MJA are developers of \ce{}, one of the tools benchmarked in this article.
-The authors exercised caution not to let this fact unfairly influence their judgment.
+The authors exercised caution not to let this fact unfairly influence their judgment and recommendations.
+\ak{and I think we should mention Analife as competing interest, normally people list all non-academic shareholder whatever stuff, just to be sure }
 
@@
 %% Do not use \listoffigures as most will included as separate files
-
+\ak{figures und tables gehen noch etwas durcheinander}
+\ak{teilweise fehlen noch figure legends}
 \section*{Figures}
@@
 \caption{Scores of assemblies of simulated data}
+\label{tab:scores}
 \centering

### 2019-06-05 bmc_article.tex
Update on Overleaf.

@@
 %One or two sentences providing a basic introduction to the field, comprehensible to a scientist in any discipline.
-Chloroplasts are photosynthetic active organelles in plant cells and contain their own genomic information.
+Chloroplasts are photosynthetic organelles in plant cells and contain their own genomic information.
 That genome can be utilized in different scientific fields like phylogenetics or biotechnology.
-%Two to three sentences ofmore detailed background, comprehensible to scientists in related disciplines.
+%Two to three sentences of more detailed background, comprehensible to scientists in related disciplines.
 Thus, different assemblers have been developed specialized in chloroplast assemblies.
 Those assemblers often use the output of whole genome sequencing experiments as input.
-Such sequencing data contain usually the complete chloroplast genome information, even if the sequencing aims for the core genome.
+Such sequencing data usually contain the complete chloroplast genome information, even if the sequencing aims for the core genome.
 %One sentence clearly stating the general problem being addressed by this particular study.
-The Different assembly tools have never been systematically compared. %to each other concerning success rate or computational requirements.
+Different assembly tools have never been systematically compared. %to each other concerning success rate or computational requirements.
 %One sentence summarising the main result (with the words “here we show” or their equivalent).
-Here we present a benchmark of seven chloroplast assembly tools, which are under active\todo{Niklas: da kann man bei IOGA drüber streiten} development and are capable to succeed in more than \SI{60}{\percent} of real data sets.
+Here we present a benchmark of seven chloroplast assembly tools, capable to succeed in more than \SI{60}{\percent} of real data sets.
 %Two or three sentences explaining what the main result reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
@@
 Chloroplasts are essential organelles present in plant cells and the cells of some protists.
-Chloroplasts enable the conversion of light energy into chemical energy via photosyntesis.
-They harbor their own ribosomes and a circular DNA genome with a size between \SIrange{120}{160}{\kilo\basepair} \cite{palmer_1985}.
+Chloroplasts enable the conversion of light energy into chemical energy via photosynthesis.
+They harbor their own ribosomes and a circular DNA genome with a size between \SIrange{120}{160}{\kilo\basepair} \cite{palmer_1985}\todo{diese range umfasst die meisten aber nicht alle Chloroplasten}.
 Because of this small size, the chloroplast genome has been an early target for sequencing.
@@
 Structurally, two inverted repeats (IR\textsubscript{A} and IR\textsubscript{B}) of \SIrange{10}{76}{\kilo\basepair} divide the chloroplast genome into a large (LSC) and a small single copy (SSC) region \cite{palmer_1985}.
-Those large inverted repeats complicates automated resolution with short read technologies\cite{Wang2018}.
+Those large inverted repeats complicate automated resolution with short read technologies\cite{Wang2018}.
 Moreover, the existence of different chloroplasts within a single individual, and thus multiple different chloroplast genomes, have been described for different plants \cite{corriveau_1988,Chat2002,Scar2016}.
@@
 
-Databases containing short read data for species where no reference chloroplast sequence is publicly available, exist.
+Databases containing short read data for species where no reference chloroplast sequence is publicly available, exist. \todo{cite? SRA?}
 The availability of whole chloroplast genomes would enable large scale comparative studies \cite{tonti-filippini_what_2017}.
@@
 In general, obtaining a chloroplast genome from WGS data requires two steps. First, the chloroplast reads have to be extracted from the mixed sequencing data. 
-The second step is the assembly and resolving the special circular structure including the inverted repeats.
+The second step is the assembly and resolution of the special circular structure including the inverted repeats.
 The extraction of the reads can be achieved by mapping the reads to a reference chloroplast. \cite{Vinga2012}.
@@
 Here, a $k$-mer analysis can be used to extract the most frequent reads.
-An example for this is implemented in \ce{}.
+An example for this is implemented in \ce{} \cite{j_ankenbrand_chloroextractor:_2018}.
+\todo{ce ist hier der einzig explizit genannte Assembler, das wirkt wie bias :) entfernen?}
 A third method combines both approaches by useing a reference chloroplast as seed and simultaneously assembling the reads based on $k$-mers \cite{dierckxsens_novoplasty:_2017}.
@@
 Still, we acknowledge that the performance of the tools might be significantly improved by optimizing parameters (and references if applicable) for each data set specifically.
-However an exhaustive comparison - including tuning of all different possible parameters for each tool- would not been possible within the scope of this study.
+However, an exhaustive comparison - including tuning of all different possible parameters for each tool- was out of scope for this study.
 
@@
 As a requirement, all tools must be available as open source software and allow execution via a command line interface.
-As a graphical user interface is not suitable for
-running automated comparisons, tools only providing a graphical interface have not been included. The following tools were determined to be within the scope of this study:
+As a graphical user interface is not suitable for automated comparisons, tools only providing a graphical interface have not been included.
+The following tools were determined to be within the scope of this study:
 \oa{} \cite{coissac_barcodes_2016}, 

### 2019-06-05 bmc_article.tex
Update on Overleaf.

@@
 However, \texttt{Geneious} is closed source and GUI based, which is not in the scope of this study.
-There is also another publication describing a method for assembling chloroplasts \cite{method-description-paper}. However, the link to the software is not active anymore.
+There is also another publication describing a method for assembling chloroplasts \cite{method-description-paper}.
+However, the link to the software is not active anymore.
 
@@
 % done by Frank \todo{ausformulieren}
-We want to use accomplish a minimum of different parameter settings for all assembly programs to enable a fair comparison. 
+We want to use a minimum of different parameter settings for all assembly programs to enable a fair comparison. 
 Therefore, we decided to specify that all programs have to work based on two input files, representing a data set's forward (\texttt{forward.fq}) and reverse  (\texttt{reverse.fq}) sequence file in FASTQ format.
@@
 %\ak{etwas umständlich formuliert, hoffe ich hab es jetzt richtig formuliert und verstanden}
-We used our docker image setup (\cref{tab:dockerimages}) \ak{check NUmmerierung tables, oben war auch schon table 2} to run all assembly programs three times for each parameter setting.
+We used our docker image setup (\cref{tab:dockerimages}) \ak{check Nummerierung tables, oben war auch schon table 2} to run all assembly programs three times for each parameter setting.
 The different settings combined different input data and different number of threads to use (\numlist{1;2;4;8}).
@@
 We chose this setup instead of the docker container, because it resembles a typical user environment better than the minimal docker installation.
-The tools were installed according to their installation instructions and
-the provided tutorial or example usage was executed. During the evaluation, the following questions were asked:
+The tools were installed according to their installation instructions and the provided tutorial or example usage was executed.
+During the evaluation, the following questions were asked:
 
@@
 These questions were answered with \good{}, \ok{} or \bad{}, depending on the quality of the result. 
-For example, a \good{} installation utilizes a automated package or dependency management like \texttt{apt},
-CRAN, docker, etc.
+For example, a \good{} installation utilizes an automated package or dependency management like \texttt{apt}, CRAN, docker, etc.
 An \ok{} installation procedure provides a custom script to install everything or at least lists all dependencies.
@@
 Four different metrics were Incorporated, each contributing  $\frac{1}{4}$ to the total score: Completeness, correctness, repeat resolution and continuity.
-These metrics are similar in concept by those used in the Assemblathon 2 project: Coverage, validity, multiplicity, and parsimony \cite{assemblathon2}.
-
-The completeness is estimated as the coverage of the assembled chloroplast genome versus the reference genome ($cov_{ref}$).
+These metrics are similar in concept by those used in the Assemblathon 2 project: coverage, validity, multiplicity, and parsimony \cite{assemblathon2}.
+
+The completeness is estimated as the coverage of the assembled chloroplast genome versus the reference genome ($cov_{ref}$)
 It resembles how many bases of the query genome can be mapped to its respective reference genome.
@@
 \subsubsection*{Reproducibility}
-To ensure reproducibility of the obtained results, we randomly choose  \num{100} data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
-The resulting assemblies were scored again as described and the scores of the first and the second run were compared to each other.
+\todo{lieber Consistency?}To ensure reproducibility of the obtained results, we randomly chose  \num{100} data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
+The resulting assemblies were scored again as described and the scores of the first and the second run were compared to each other
 This information is important to assess the robustness of the different programs.
@@
 
-The \fp{} installation instructions were missing some dependencies. Like \go{}, \fp{} does not offer a test data set or a tutorial, except from some example commands.
+The \fp{} installation instructions were missing some dependencies.
+Like \go{}, \fp{} does not offer a test data set or a tutorial, except for some example commands.
 
@@
 
-The \ce{} does come with a test data set and a short tutorial. However, it is currently not possible to evaluate the results of the test run.
+The \ce{} does come with a test data set and a short tutorial.
+However, it is currently not possible to evaluate the results of the test run.
 
@@
 \fp{} is outperforming the latter two slightly in terms of score, with twice as much \num{114} perfectly assembled chloroplast genomes (\np{} produced \num{66} and \oa{} \num{55} circular genomes).
-\ioga{} and \cassp{} were both not able to assemble a single circular, single-contig genome (\cref{tab:scores}), consequently resulting in the lowest mean and median scores (\cref{fig:upset}).
+\ioga{} and \cassp{} were both not able to assemble a circular, single-contig genome (\cref{tab:scores}), consequently resulting in the lowest mean and median scores (\cref{fig:upset}).
 
@@
 Except for \fp{} all the other tools had at least one assembly that was unsuccessful in one run, but produced an output in the other.\ak{oben steht \go{} war als einziges immer gut, dann kommt except for \fp{} ??
-does not seem to be consistent}  Notably \ioga{} appears to have a tendency to perform differently in independent runs.
+does not seem to be consistent}
+Notably \ioga{} appears to have a tendency to perform differently in independent runs.
 Here, more than \SI{10}{\percent} of the assemblies failed in one run only.
 
-Both \fp{} and \np{} tend to have minor changes in the assembly when the overall performance is comparably well, leading to the arrow-shaped scatter plots.\ak{link to figure scatter plots is issing} \ce{} and \cassp{} appear to be the most robust assemblers, having only few deviations between the two runs.
+Both \fp{} and \np{} tend to have minor changes in the assembly when the overall performance is comparably well, leading to the arrow-shaped scatter plots.\ak{link to figure scatter plots is missing}
+\ce{} and \cassp{} appear to be the most robust assemblers, having only few deviations between the two runs.
 
@@
 The tools \fp{}, \np{}, and \oa{} produce the most variable results, thus re-running the tool after a failed attempt might be successful.
-\ce{} yields only few complete chloroplast assemblies, but requires also only few resources. It is easy to install and use and thus could be considered as a good option for a quick first try.
+\ce{} yields only few complete chloroplast assemblies, but requires also only few resources.
+It is easy to install and use and thus could be considered as a good option for a quick first try.
 Both \ioga{} and \cassp{} have the worst performance of all tools tested and fail to return reliable chloroplast assemblies.
@@
 Another important feature of software is a comprehensive documentation, which needs to be up-to-date and maintained.
-Software authors should constantly improve the usability, and be open to suggestions from the users.
+Software authors should constantly improve the usability\todo{ich bin nicht sicher ob ich das so hart sagen würde}, and be open to suggestions from the users.
 
@@
 The main assumption for our study to benchmark different chloroplast assembly tools, is that whole genome sequencing data are also a promising source for chlorplast assemblies.
-Our benchmark shows that ~\SI{60}{\percent} of the available chloroplasts genomes, have been assembled by at least one of the tools we analysed.
+Our benchmark shows that ~\SI{60}{\percent} of the data sets without available chloroplast genome, have been assembled by at least one of the tools we analysed.
 Still, even with simulated (aka``perfect'') data, not all tools succeeded in generating complete chloroplast assemblies.
-Therefore, it is important to know the strengths and weaknesses of the specific tools and provide guidelines for the users.
-Moreover, it might be necessary, to combine different methods or manually explore the parameter space, to obtain reliable results if a single run seems not sufficient.
+Therefore, we determined the strengths and weaknesses of the specific tools and provided guidelines for the users.
+However, it might be necessary, to combine different methods or manually explore the parameter space, to obtain reliable results if a single run seems not sufficient.
 Ultimately, large scale studies reconstructing hundreds or thousands of chloroplast genomes are now feasible using the currently available tools. 
@@
 The authors exercised caution not to let this fact unfairly influence their judgment and recommendations.
-\ak{and I think we should mention Analife as competing interest, normally people list all non-academic shareholder whatever stuff, just to be sure }
+JF, NT, and MJA are affiliated with the for-profit organization AnaLife Data Science.
+\ak{and I think we should mention Analife as competing interest, normally people list all non-academic shareholder whatever stuff, just to be sure}\todo{Ich weiß nicht ob das so passt}
 
@@
 \section*{Acknowledgements}
-Text for this section \ldots
+Text for this section\todo{haben wir da jemanden oder etwas? funding?} \ldots
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \includegraphics[width=\textwidth]{plots/swarm.pdf}
-  \caption{\csentence{Sample figure title.}
-      A short description of the figure content
-      should go here.}
+  \caption{\csentence{Results of scoring of the seven assemblers}
+  The box- and swarplots depict the results of the scoring algorithm we used. For the different assemblers. The whiskers of boxplots indicate the 1.5 x interquartile range. 
+    }
       \label{fig:swarmplot}
@@
   \caption{\csentence{Computation time depending on number of threads and size of input data}
+  The boxplots show the differences in demand of CPU time for different number of threads and input data size for the seven different assemblers
   }
@@
   \caption{\csentence{Performance metrics}
-      Boxplots depictiing the demand of CPU and RAM and disk space needed depending on the assembler, input data size and number of threads}
+      Boxplots depicting the demand of CPU and RAM and disk space needed depending on the assembler, input data size and number of threads}
       \label{fig:performance_memory_cpu}
@@
   \caption{\csentence{Score of assemblies on simulated data}
-      Figure legend text.}
+      Results of assemblies from simulated data sets. Color scale of the tiles represents the score }
       \label{fig:simulated}
@@
   \includegraphics[width=\textwidth]{plots/repro.pdf}
-  \caption{\csentence{Scores between two independent runs for reproducibility testing}
+  \caption{\csentence{Scores between two repeated runs for reproducibility testing}
+  The scatter plots depicts the scores of the 1. runs x-axis versus the scores of the 2. run y-axis of the data sets that were selected for re-evaluation. 
       }
@@
       The plot shows the intersection of success ($score > 99$) between assemblers.
-For \num{69} datasets only \go{} was able to obtain a complete chloroplast.
+For \num{69} data sets only \go{} was able to obtain a complete chloroplast.
 \num{43} were successful with both \go{} and \fp{} and so on}
@@
   \includegraphics[width=\textwidth]{plots/real_datasets_tree.pdf}
-  \caption{\csentence{Sucess of assemblers on real data sets on tree derived from ncbi taxonomy \cite{ncbi2011}}
-      Figure legend text. }
+  \caption{\csentence{Success of assemblers on real data sets on tree derived from NCBI taxonomy \cite{ncbi2011}}
+       }
       \label{fig:tree}
@@
   \hline
- & dataset & CAP & CE & Fast-Plast & GetOrganelle & IOGA & NOVOPlasty & org.ASM \\ 
+ & data set & CAP & CE & Fast-Plast & GetOrganelle & IOGA & NOVOPlasty & org.ASM \\ 
   \hline
@@
   \subsection*{Additional file 1 --- Sample additional file title}
+\todo{Supplement description}
     Additional file descriptions text (including details of how to

### 2019-06-05 manuscript/bmc_article.tex
Moving everything into a subfolder

--- 2019-06-05 bmc_article.tex
@@
 
-\usepackage{biocon}
-\newplant{At}{genus=Arabidopsis,epithet=thaliana}
+\input{biocon-stuff.tex}
+\input{docker-stuff.tex}
 
@@
 % List of docker images
-\newcommand{\docker}[2]{\href{https://cloud.docker.com/u/chloroextractorteam/repository/docker/chloroextractorteam/#1}{chloroextracteam/#1:#2}}
-\newcommand{\dockerce}{\docker{benchmark\_chloroextractor}{v2.0.0}}
-\newcommand{\dockercesha}{\texttt{8f49e03424b37e699c5fea9391f79dbb9f2d0dc550ce86c4c700f39deec2dacd}}
-\newcommand{\dockeroa}{\docker{benchmark\_org-asm}{v2.0.0}}
-\newcommand{\dockeroasha}{\texttt{ff83677c97b7c4e346191b9e04a5162eeea2a8dfd9e60ff84067d33747868f60}}
-\newcommand{\dockerfp}{\docker{benchmark\_fastplast}{v2.0.0}}
-\newcommand{\dockerfpsha}{\texttt{a3d06a610f8340ba49c3ff3b27342534e2a5348b17caa4fd3c3f3d327243a272}}
-\newcommand{\dockerioga}{\docker{benchmark\_ioga}{v2.0.0}}
-\newcommand{\dockeriogasha}{\texttt{4698a21c343c60290bbf16811165a654ff01e8fddeb41cd75d0771b7f45968c0}}
-\newcommand{\dockernp}{\docker{benchmark\_novoplasty}{v2.0.0}}
-\newcommand{\dockernpsha}{\texttt{106387bad4e8e5c53fb9d4c3bdd60cdddf05a47b52a38697369eeabb947c547c}}
-\newcommand{\dockergo}{\docker{benchmark\_getorganelle}{v2.0.0}}
-\newcommand{\dockergosha}{\texttt{2ed3a464a82025a196ea56c649d0b0a3472cef76994bb065d56054d93298d956}}
-\newcommand{\dockercassp}{\docker{benchmark\_chloroplast\_assembly\_protocol}{v2.0.0}}
-\newcommand{\dockercasspsha}{\texttt{d10d2317103d91fadec4cb1d5466ac109f23176ad74b6f44f0179175f050155d}}
 \endlocaldefs
@@
 \author[
-   addressref={aff2,aff4},                   % id's of addresses, e.g. {aff1,aff2}
+   addressref={aff1,aff2,aff4},                   % id's of addresses, e.g. {aff1,aff2}
    corref={aff1},                       % id of corresponding address, if any
@@
 In terms of reproducibility, we created docker images for each tested tool, which are available for the scientific community.
-Following the presented guidelines, users are able to analyse and screen data sets for chloroplast genomes using only standard computer infrastructure.
+Following the presented guidelines, users are able to analyze and screen data sets for chloroplast genomes using only standard computer infrastructure.
 %Two or three sentences to provide a broader perspective, readily comprehensible to a scientist in any discipline, may be included in the first paragraph if the editor considers that the accessibility of the paper is significantly enhanced by their inclusion.
@@
 Chloroplasts enable the conversion of light energy into chemical energy via photosynthesis.
-They harbor their own ribosomes and a circular DNA genome with a size between \SIrange{120}{160}{\kilo\basepair} \cite{palmer_1985}\todo{diese range umfasst die meisten aber nicht alle Chloroplasten}.
+They harbor their own ribosomes and a circular DNA genome usually with a size between \SIrange{120}{160}{\kilo\basepair} \cite{palmer_1985}.
 Because of this small size, the chloroplast genome has been an early target for sequencing.
@@
 Moreover, the existence of different chloroplasts within a single individual, and thus multiple different chloroplast genomes, have been described for different plants \cite{corriveau_1988,Chat2002,Scar2016}.
-Although the origin and evolutionary importance of this phenomena, - called heteroplasmy - are only poorly understood, the assembly of whole chloroplast genomes might be hindered.
-
-Databases containing short read data for species where no reference chloroplast sequence is publicly available, exist. \todo{cite? SRA?}
+Although the origin and evolutionary importance of this phenomena ---called heteroplasmy--- are only poorly understood, the assembly of whole chloroplast genomes might be hindered.
+
+Databases exist containing short read data for species where no reference chloroplast sequence is publicly available, eg.\ the Sequence Read Archive at NCBI \cite{sra2010}.
 The availability of whole chloroplast genomes would enable large scale comparative studies \cite{tonti-filippini_what_2017}.
 Additionally, reconstructed full chloroplast genomes have been used as super-barcodes \cite{coissac_barcodes_2016}, for biotechnology applications and genetic engineering \cite{daniell_chloroplast_2016}.
-
-%\subsection*{Chloroplast genome architecture}\ff{Chloroplast genome architecture section}
-%
-%Maybe separate section describing a prototypical chloroplast: LSC, IRa, SSC, IRb. Gene number and content. 
-%Size ranges. 
-%Evolutionary history incl. endosymbiontic gene transfer. 
-%Reduced genomes in parasitic plants. Loss of \genename{ndh} gene family (maybe too specific).
-%Preliminary SNP analysis in \plant{At} to estimate intraspecific variability?
-Is there anything known about intra-organismic variability (do some plants have multiple populations of chloroplasts?
-\ak{Yes, they do , Heteroplasmy} probably off topic).\ak{nope, I think this is important}
 
@@
 An example for this is implemented in \ce{} \cite{j_ankenbrand_chloroextractor:_2018}.
-\todo{ce ist hier der einzig explizit genannte Assembler, das wirkt wie bias :) entfernen?}
-A third method combines both approaches by useing a reference chloroplast as seed and simultaneously assembling the reads based on $k$-mers \cite{dierckxsens_novoplasty:_2017}.
-
-%\todo{Niklas: wir nennen hier immer nur \ce{} als beispiel - wir sollten auch andere nennen}
-%\todo{example}
+%\todo{ce ist hier der einzig explizit genannte Assembler, das wirkt wie bias :) entfernen?
+Nope...
+Steht klar ein Beispiel und wir haben nun mal den angesehen...
+Würde ich jetzt einmal so drin lassen.
+Alternativ nehmen wir noch einen dazu}
+A third method combines both approaches by using a reference chloroplast as seed and simultaneously assembling the reads based on $k$-mers \cite{dierckxsens_novoplasty:_2017}.
+
 %\ak{e.g.
@@
 
+\section*{Results}
+\subsection*{Performance metrics}
+%\subsection*{Computational Resources}
+%Table and figure of performance evaluation.
+Including RAM, I/O, runtime, parallelization ability, CPU usage.
+Free text description of results, range, mean/median, effect of input size, threads parameter, ...
+
+\subsubsection*{Time requirements}
+In terms of run time, massive differences between the different tools have been observed.
+Apart from tool-specific differences, input data and number of threads had huge impact.
+The observed run times varied from a few minutes to several hours (\cref{fig:performance_runtime}).
+
+Some assemblies failed to finish within the time-limit we set (\SI{48}{\hour}). 
+On average the longest time to generate the assemblies was taken by \ioga{} and \fp{} followed by \oa{} and \go{} the most time efficient tool was \ce{}, which on average is a little faster than \np{} and \cassp{}.
+%% multithreading
+
+Not all the tools were able to benefit from having access to multiple threads.
+Both \np{} and \oa{} take about the same time independent of being able to utilize \numlist[list-final-separator={, or }]{1;2;4;8} threads.
+\cassp{}, \ce{}, \go  and \fp{} all profit from multi-threading (\cref{fig:performance_runtime,fig:performance_memory_cpu}).
+
+\subsubsection*{Memory and CPU Usage }
+The peak and mean CPU usage, as well as peak memory and disk usage have been recorded for all assemblers based on the same input data set and number of threads to use (\cref{fig:performance_memory_cpu}).
+Mainly, the size of the input data influenced the peak memory usage with the exception of \ce{} and \ioga{}.
+Those two assemblers seems to have a memory usage pattern, which is less influenced by the size of the data.
+The number of allowed threads had only a limited impact on the peak memory usage.
+Nevertheless, all programs profit by a higher number of threads, if the size of the input data was increased.
+In contrast, the disk usage is independent from input size and number of threads for all assemblers.
+%but the factor between the programs exceeds a factor of \num{100}.
+
+\subsection*{Qualitative}
+The user experience of most tools was evaluated as mainly \good{} (\cref{tab:resultsQual}). However, a few critique points remained.
+Two minor dependencies were missing in the \go{} installation instructions and there was no test data available.
+Additionally, an issue occurred when running it on a \plant{At} data set.
+We are currently in the process of resolving this with the authors.
+
+The \fp{} installation instructions were missing some dependencies.
+Like \go{}, \fp{} does not offer a test data set or a tutorial, except for some example commands.
+
+The \oa{} installation instructions did not work.
+We found some issues, which are probably related to the requirement of \texttt{Python~3.7}.
+There is a tutorial where sample data is available.
+However, following the instructions resulted in a segmentation fault.
+We found a workaround for this bug and contacted the authors.
+
+The main critique point of \np{} was the lack of a test data set with instructions.
+This was fixed by the authors after we contacted them.
+Additionally, \np{} uses a custom license, where an OSI approved license would be preferred.
+
+The \ce{} does come with a test data set and a short tutorial.
+However, it is currently not possible to evaluate the results of the test run.
+
+The \ioga{} installation instructions were missing many dependencies.
+Also, there was no test data or tutorial available and there is no license assigned to it.
+Since there was no update to the GitHub repository for the last three years, the project can be seen as inactive.
+After contacting the authors, they promised to resolve the mentioned issues.
+
+As many of the other tools, the installation instructions for the \cassp{} were missing some dependencies.
+The list was updated after we contacted the authors.
+This tool does come with a test data set, however a note about the expected outcome is missing.
+A more extensive tutorial is provided.
+The description about the parameter is short, but sufficient.
+
+\subsection*{Quantitative}
+\subsubsection*{Simulated data}
+The only assembler obtaining perfect results according to our score for the simulated data sets is \go{} (\cref{fig:simulated,tab:scores_simulated}).
+\ioga{} and \cassp{} showed the worst performance, being unable to fully assemble a single chloroplast out of \num{14} runs.
+\np{} performed second best with scores above \num{80} for all data sets, only failing to resolve the contigs into one single circular chloroplast assembly.
+The overall performance is best, when the input data consists purely of chloroplast reads.
+Only \ioga{} and \cassp{} failed to deliver any results under this scenario once.
+In general, no clear correlation between either length of the input reads or the ratio of core vs chloroplast reads and the performance of the different assemblers can be observed.
+
+\subsubsection*{Real data sets}
+Concerning the performance of the assemblers on the real data sets, we were able to observe considerable differences in the median score (\cref{fig:swarmplot}).
+The highest scores were achieved by \go{} with a median of \num{99.7} and \num{199} circular assemblies out of a total of 356 assemblies that resulted in an output (\cref{tab:scores_real}).
+The performance of \go{} is followed by \fp{}, \np{}, \oa{}, and \ce{}.
+\fp{} is outperforming the latter two slightly in terms of score, with twice as much \num{114} perfectly assembled chloroplast genomes (\np{} produced \num{66} and \oa{} \num{55} circular genomes).
+\ioga{} and \cassp{} were both not able to assemble a circular, single-contig genome (\cref{tab:scores}), consequently resulting in the lowest mean and median scores (\cref{fig:upset}).
+
+%\textit{swarm plot goes here}
+%% Den upset plot eventuell erst in die Discussion reinbringen ? Da wir davon ableiten welche tools wir empfehlen?
+
+\subsubsection*{Consistency}
+Consistency was tested by re-running assemblies and comparison of the scores of two assemblies (\cref{fig:consistency}).
+Replicates that did not produce an output were manually scored as \num{0}. 
+\go{} was the only tool that succeeded in obtaining similar scores for all assemblies, without producing and completely unsuccessful assemblies for this subset of data.
+Except for \fp{} all the other tools had at least one assembly that was unsuccessful in one run, but produced an output in the other.
+%\ak{oben steht \go{} war als einziges immer gut, dann kommt except for \fp{} ?? does not seem to be consistent}
+Notably \ioga{} appears to have a tendency to perform differently in independent runs.
+Here, more than \SI{10}{\percent} of the assemblies failed in one run only.
+
+Both \fp{} and \np{} tend to have minor changes in the assembly when the overall performance is comparably well, leading to the arrow-shaped scatter plots.
+%\ak{link to figure scatter plots is missing}
+\ce{} and \cassp{} appear to be the most robust assemblers, having only few deviations between the two runs.
+
+\section*{Discussion}
+We aimed to generate an overall performance score for the different chloroplast assemblers, but depending on distinct downstream applications, the different criteria assessed in this work need to be weighted differently.
+For example, ease of installation and use might not be a big concern if the tool is installed once and integrated in an automated pipeline.
+On the other hand this factor alone might prevent other users from being able to use the tool in the first place.
+Similarly, computational requirements or run time might be less relevant, if the goal is to assemble a single chloroplast for further analysis, but it is essential if hundreds or thousands of samples should be processed in parallel for a large scale study.
+Eventually, both ease of use and run time are irrelevant if the tool is not able to successfully accomplish its task.
+Also the scope of this study needs to be considered when interpreting the guidelines below.
+In particular, we evaluated all tools under the assumption that they are used in the most basic form (default parameters, no hand selected reference, no pre-processing of the data or post-processing of the result, restricted run time).
+It is important to note that any tool might perform significantly different, if the above mentioned parameters are fine-tuned for a specific data set.
+
+The overall best success rate, both on simulated and real data, was achieved by \go{} followed by \fp{}.
+Both tools complement each other, as each is able to successfully reconstruct a full chloroplasts in cases where the other tool fails. 
+In rare cases \np{} or \oa{} are the only tool to succeed.
+The tools \fp{}, \np{}, and \oa{} produce the most variable results, thus re-running the tool after a failed attempt might be successful.
+\ce{} yields only few complete chloroplast assemblies, but requires also only few resources.
+It is easy to install and use and thus could be considered as a good option for a quick first try.
+Both \ioga{} and \cassp{} have the worst performance of all tools tested and fail to return reliable chloroplast assemblies.
+
+\subsection*{Guidelines for the end-user}
+Given these results, our recommendation is to use \go{} as default option, and in case of failure \fp{} as backup solution.
+%\ak{what if both lead to qualitative different results?, always trust \go{} , or could one compute a high-confidence assembly by combining different results ?, might be a point for future directions.}
+If both programs fail, it is sensible to re-run \fp{} and additionally try \np{} and \oa{}.
+This procedure maximizes the chance to effectively and efficiently recover the circular chloroplast genome from mixed genomic data.
+If none of these four assemblers produce sensible results, a reference guided approach and tweaking of the default parameters, might be the solution.
+Here, it is not possible to provide general guidelines, as the procedure will differ for different data sets.
+For an automated approach, running \go{} and \fp{} in parallel appears to be a good trade-off between success rate and use of resources.
+
+\subsection*{Ideas for future development}
+For further experiments, combining different components from different tools might be a promising approach.
+For example, read scaling from \ce{} followed by an assembly by \go{} and finally the structural resolution with \fp{} could be a promising approach, combing the respective strength of the different tools.
+
+Moreover, the installation issues need to be mitigated by modern software.
+Therefore, either containerization (docker, singularity, etc.) or install workflows (eg. bioconda \cite{gruening2018}) should be established by all software packages.
+Otherwise, the burden of the software installation might result in scientists ignoring good tools.
+
+Another important feature of software is a comprehensive documentation, which needs to be up-to-date and maintained.
+Additionally, software authors could improve the usability based on suggestions from their users.
+
+Finally, all tools should improve their integrated guessing of default parameters, as many users avoid fine tuning of those, especially, for larger screening approaches.
+Last, as sequencing technology is developing fast (eg.\ PacBio or nanopore), tools need to be updated to not become obsolete.
+But the hope would be that with ongoing software development and improved sequencing technologies, the generation of whole chloroplast assemblies from any species will become a routine technique.
+
+\section*{Conclusion}
+The main assumption for our study to benchmark different chloroplast assembly tools, is that whole genome sequencing data are also a promising source for chlorplast assemblies.
+Our benchmark shows that ~\SI{60}{\percent} of the data sets without available chloroplast genome, have been assembled by at least one of the tools we analysed.
+Still, even with simulated (aka``perfect'') data, not all tools succeeded in generating complete chloroplast assemblies.
+Therefore, we determined the strengths and weaknesses of the specific tools and provided guidelines for the users.
+However, it might be necessary, to combine different methods or manually explore the parameter space, to obtain reliable results if a single run seems not sufficient.
+Ultimately, large scale studies reconstructing hundreds or thousands of chloroplast genomes are now feasible using the currently available tools. 
+%Outlook: next step in the pipeline is annotation. There is a similar problem: many tools, which one to use? 
+%A large scale study reconstructing chloroplasts throughout SRA (or \num{1001} genome project) is feasible and promising using the existing tools (estimated runtime, number of novel chloroplasts).
+%A meta-tool that automatically combines the different programs could be developed.
+%The benchmarking study could be augmented to automatically select the closest reference from the database and provide that to any tool that can take advantage of references.
+
 \section*{Methods}
 \subsection*{Data availability}
-Source code for all methods used is available at \url{https://github.com/chloroExtractorTeam/benchmark} and archived in zenodo under \zenodorepo{}.
-All docker images are published on \url{https://cloud.docker.com/u/chloroextractorteam/} and are named with a leading \texttt{benchmark\_} (\cref{tab:dockerimages}).
+Source code for all methods used is available at \cite{github-benchmark-repo} and archived in zenodo under \zenodorepo{}.
+All docker images are published on \cite{dockerhub-benchmark} and are named with a leading \texttt{benchmark\_} (\cref{tab:dockerimages}).
 
@@
 \subsection*{Our Setup}
-% done by Frank \todo{ausformulieren}
 We want to use a minimum of different parameter settings for all assembly programs to enable a fair comparison. 
@@
 All singularity containers were run on %the Julia-HPC 
-\ak{I would note refer to Julia in the ms, maybe we could add it as a link}
 Intel® Xeon® Gold \num{6140} Processors using a Slurm workload manager version 17.11.8 \cite{Jette02slurm}.
@@
 %Therefore, the simulated perfect read files have been read repeatedly to achieve the required number of read pairs.
-%\ak{etwas umständlich formuliert, hoffe ich hab es jetzt richtig formuliert und verstanden}
-We used our docker image setup (\cref{tab:dockerimages}) \ak{check Nummerierung tables, oben war auch schon table 2} to run all assembly programs three times for each parameter setting.
+We used our docker image setup (\cref{tab:dockerimages}) to run all assembly programs three times for each parameter setting.
 The different settings combined different input data and different number of threads to use (\numlist{1;2;4;8}).
-%\ak{in 'Our Setup' before, schreiben wir 10GiB und 4 threads, müsste dann vielleicht geändert werden}
+
 Some programs will use more CPU threads than specified, therefore, the number of CPUs available have been fixed using the CPU option while running the docker run command.
@@
 \end{itemize}
-\newline
+
 These questions were answered with \good{}, \ok{} or \bad{}, depending on the quality of the result. 
@@
 
-\subsubsection*{Reproducibility}
-\todo{lieber Consistency?}To ensure reproducibility of the obtained results, we randomly chose  \num{100} data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
+\subsubsection*{Consistency}
+To ensure consistency of the obtained results, we randomly chose  \num{100} data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
 The resulting assemblies were scored again as described and the scores of the first and the second run were compared to each other
 This information is important to assess the robustness of the different programs.
-
-\section*{Results}
-\subsection*{Performance metrics}
-%\subsection*{Computational Resources}
-%Table and figure of performance evaluation.
-Including RAM, I/O, runtime, parallelization ability, CPU usage.
-Free text description of results, range, mean/median, effect of input size, threads parameter, ...
-
-\subsubsection*{Time requirements}
-In terms of run time, massive differences between the different tools have been observed.
-Apart from tool-specific differences, input data and number of threads had huge impact.
-The observed run times varied from a few minutes to several hours (\cref{fig:performance_runtime}).
-%\ak{did I miss Figure 1 ?, need to check figure numbering in the end}
-Some assemblies failed to finish within the time-limit we set (\SI{48}{\hour}). 
-On average the longest time to generate the assemblies was taken by \ioga{} and \fp{} followed by \oa{} and \go{} the most time efficient tool was \ce{}, which on average is a little faster than \np{} and \cassp{}.
-%% multithreading
-
-Not all the tools were able to benefit from having access to multiple threads.
-Both \np{} and \oa{} take about the same time independent of being able to utilize \numlist[list-final-separator={, or }]{1;2;4;8} threads.
-\cassp{}, \ce{}, \go  and \fp{} all profit from multi-threading (\cref{fig:performance_runtime}, \cref{fig:performance_memory_cpu}).
-
-\subsubsection*{Memory and CPU Usage }
-The peak and mean CPU usage, as well as peak memory and disk usage have been recorded for all assemblers based on the same input data set and number of threads to use (\cref{fig:performance_memory_cpu}).
-Mainly, the size of the input data influenced the peak memory usage with the exception of \ce{} and \ioga{}.
-Those two assemblers seems to have a memory usage pattern, which is less influenced by the size of the data.
-The number of allowed threads had only a limited impact on the peak memory usage.
-Nevertheless, all programs profit by a higher number of threads, if the size of the input data was increased.
-In contrast, the disk usage is independent from input size and number of threads for all assemblers.
-%but the factor between the programs exceeds a factor of \num{100}.
-
-\subsection*{Qualitative}
-The user experience of most tools was evaluated as mainly \good{} (see table \ref{tab:resultsQual}). However, a few critique points remained.
-Two minor dependencies were missing in the \go{} installation instructions and there was no test data available.
-Additionally, an issue occurred when running it on a \plant{At} data set.
-We are currently in the process of resolving this with the authors.
-
-The \fp{} installation instructions were missing some dependencies.
-Like \go{}, \fp{} does not offer a test data set or a tutorial, except for some example commands.
-
-The \oa{} installation instructions did not work.
-We found some issues, which are probably related to the requirement of \texttt{Python~3.7}.
-There is a tutorial where sample data is available.
-However, following the instructions resulted in a segmentation fault.
-We found a workaround for this bug and contacted the authors.
-
-The main critique point of \np{} was the lack of a test data set with instructions.
-This was fixed by the authors after we contacted them.
-Additionally, \np{} uses a custom license, where an OSI approved license would be preferred.
-
-The \ce{} does come with a test data set and a short tutorial.
-However, it is currently not possible to evaluate the results of the test run.
-
-The \ioga{} installation instructions were missing many dependencies.
-Also, there was no test data or tutorial available and there is no license assigned to it.
-Since there was no update to the GitHub repository for the last three years, the project can be seen as inactive.
-After contacting the authors, they promised to resolve the mentioned issues.
-
-As many of the other tools, the installation instructions for the \cassp{} were missing some dependencies.
-The list was updated after we contacted the authors.
-This tool does come with a test data set, however a note about the expected outcome is missing.
-A more extensive tutorial is provided.
-The description about the parameter is short, but sufficient.
-
-\subsection*{Quantitative}
-\subsubsection*{Simulated data}
-The only assembler obtaining perfect results according to our score for the simulated data sets is \go{} (\cref{fig:simulated}).
-\ioga{} and \cassp{} showed the worst performance, being unable to fully assemble a single chloroplast out of \num{14} runs.
-\np{} performed second best with scores above \num{80} for all data sets, only failing to resolve the contigs into one single circular chloroplast assembly.
-The overall performance \ak{of all assemblers ?} is best, when the input data consists purely of chloroplast reads.
-Only \ioga{} and \cassp{} failed to deliver any results under this scenario once.
-In general, no clear correlation between either length of the input reads or the ratio of core vs chloroplast reads and the performance of the different assemblers can be observed.
-
-\subsubsection*{Real data sets}
-Concerning the performance of the assemblers on the real data sets, we were able to observe considerable differences in the median score (\cref{fig:swarmplot}).
-The highest scores were achieved by \go{} with a median of \num{99.7} and \num{199} circular assemblies out of a total of 356 assemblies that resulted in an output (\cref{tab:scores}).
-The performance of \go{} is followed by \fp{}, \np{}, \oa{}, and \ce{}.
-\fp{} is outperforming the latter two slightly in terms of score, with twice as much \num{114} perfectly assembled chloroplast genomes (\np{} produced \num{66} and \oa{} \num{55} circular genomes).
-\ioga{} and \cassp{} were both not able to assemble a circular, single-contig genome (\cref{tab:scores}), consequently resulting in the lowest mean and median scores (\cref{fig:upset}).
-
-%\textit{swarm plot goes here}
-%% Den upset plot eventuell erst in die Discussion reinbringen ? Da wir davon ableiten welche tools wir empfehlen?
-
-\subsubsection*{Reproducibility}
-Reproducibility was tested as described above, by re-running assemblies and comparison of the scores of two assemblies (\cref{fig:reproducibility}).
-Replicates that did not produce an output were manually scored as \num{0}. 
-\go{} was the only tool that succeeded in obtaining similar scores for all assemblies, without producing and completely unsuccessful assemblies for this subset of data.
-Except for \fp{} all the other tools had at least one assembly that was unsuccessful in one run, but produced an output in the other.\ak{oben steht \go{} war als einziges immer gut, dann kommt except for \fp{} ??
-does not seem to be consistent}
-Notably \ioga{} appears to have a tendency to perform differently in independent runs.
-Here, more than \SI{10}{\percent} of the assemblies failed in one run only.
-
-Both \fp{} and \np{} tend to have minor changes in the assembly when the overall performance is comparably well, leading to the arrow-shaped scatter plots.\ak{link to figure scatter plots is missing}
-\ce{} and \cassp{} appear to be the most robust assemblers, having only few deviations between the two runs.
-
-\section*{Discussion}
-We aimed to generate an overall performance score for the different chloroplast assemblers, but depending on distinct downstream applications, the different criteria assessed in this work need to be weighted differently.
-For example, ease of installation and use might not be a big concern if the tool is installed once and integrated in an automated pipeline.
-On the other hand this factor alone might prevent other users from being able to use the tool in the first place.
-Similarly, computational requirements or run time might be less relevant, if the goal is to assemble a single chloroplast for further analysis, but it is essential if hundreds or thousands of samples should be processed in parallel for a large scale study.
-Eventually, both ease of use and run time are irrelevant if the tool is not able to successfully accomplish its task.
-Also the scope of this study needs to be considered when interpreting the guidelines below.
-In particular, we evaluated all tools under the assumption that they are used in the most basic form (default parameters, no hand selected reference, no pre-processing of the data or post-processing of the result, restricted run time).
-It is important to note that any tool might perform significantly different, if the above mentioned parameters are fine-tuned for a specific data set.
-
-The overall best success rate, both on simulated and real data, was achieved by \go{} followed by \fp{}.
-Both tools complement each other, as each is able to successfully reconstruct a full chloroplasts in cases where the other tool fails. 
-In rare cases \np{} or \oa{} are the only tool to succeed.
-The tools \fp{}, \np{}, and \oa{} produce the most variable results, thus re-running the tool after a failed attempt might be successful.
-\ce{} yields only few complete chloroplast assemblies, but requires also only few resources.
-It is easy to install and use and thus could be considered as a good option for a quick first try.
-Both \ioga{} and \cassp{} have the worst performance of all tools tested and fail to return reliable chloroplast assemblies.
-
-\subsection*{Guidelines for the end-user}
-Given these results, our recommendation is to use \go{} as default option, and in case of failure \fp{} as backup solution.\ak{what if both lead to qualitative different results?, always trust \go{} , or could one compute a high-confidence assembly by combining different results ?, might be a point for future directions.}
-If both programs fail, it is sensible to re-run \fp{} and additionally try \np{} and \oa{}.
-This procedure maximizes the chance to effectively and efficiently recover the circular chloroplast genome from mixed genomic data.
-If none of these four assemblers produce sensible results, a reference guided approach and tweaking of the default parameters, might be the solution.
-Here, it is not possible to provide general guidelines, as the procedure will differ for different data sets.
-For an automated approach, running \go{} and \fp{} in parallel appears to be a good trade-off between success rate and use of resources.
-%\todo{Does the decision depend on some parameter of the data (read length, amount, taxonomic group, ...)?}
-
-\subsection*{Ideas for future development}
-%\ff{this section (lower priority)}
-For further experiments, combining different components from different tools might be a promising approach.
-For example, read scaling from \ce{} followed by an assembly by \go{} and finally the structural resolution with \fp{} could be a promising approach, combing the respective strength of the different tools.
-
-Moreover, the installation issues need to be mitigated by modern software.
-Therefore, either containerization (docker, singularity, etc.) or install workflows (eg. bioconda \cite{gruening2018}) should be established by all software packages.
-Otherwise, the burden of the software installation might result in scientists ignoring good tools.
-
-Another important feature of software is a comprehensive documentation, which needs to be up-to-date and maintained.
-Software authors should constantly improve the usability\todo{ich bin nicht sicher ob ich das so hart sagen würde}, and be open to suggestions from the users.
-
-Finally, all tools should improve their integrated guessing of default parameters, as many users avoid fine tuning of those, especially, for larger screening approaches.
-Last, as sequencing technology is developing fast ( eg.\ PacBio or nanopore), tools need to be updated to not become obsolete.
-But the hope would be that with ongoing software development and improved sequencing technologies, the generation of whole chloroplast assemblies from any species will become a routine technique.
-
-\section*{Conclusion}
-%\ff{Conclusion}
-%Short summary of clear guidelines and future development (might not be necessary as these are the last two sections of the Discussion anyway, so we might elect to skip this).
-%\todo{sollten wir lobend erwähnen, dass alle auf github/gitlab sind?}
-The main assumption for our study to benchmark different chloroplast assembly tools, is that whole genome sequencing data are also a promising source for chlorplast assemblies.
-Our benchmark shows that ~\SI{60}{\percent} of the data sets without available chloroplast genome, have been assembled by at least one of the tools we analysed.
-Still, even with simulated (aka``perfect'') data, not all tools succeeded in generating complete chloroplast assemblies.
-Therefore, we determined the strengths and weaknesses of the specific tools and provided guidelines for the users.
-However, it might be necessary, to combine different methods or manually explore the parameter space, to obtain reliable results if a single run seems not sufficient.
-Ultimately, large scale studies reconstructing hundreds or thousands of chloroplast genomes are now feasible using the currently available tools. 
-%Outlook: next step in the pipeline is annotation. There is a similar problem: many tools, which one to use? 
-%A large scale study reconstructing chloroplasts throughout SRA (or \num{1001} genome project) is feasible and promising using the existing tools (estimated runtime, number of novel chloroplasts).
-%A meta-tool that automatically combines the different programs could be developed.
-%The benchmarking study could be augmented to automatically select the closest reference from the database and provide that to any tool that can take advantage of references.
 
@@
 JF, NT, and MJA are affiliated with the for-profit organization AnaLife Data Science.
-\ak{and I think we should mention Analife as competing interest, normally people list all non-academic shareholder whatever stuff, just to be sure}\todo{Ich weiß nicht ob das so passt}
 
@@
 
-\section*{Acknowledgements}
-Text for this section\todo{haben wir da jemanden oder etwas? funding?} \ldots
+%\section*{Acknowledgements}
+%Text for this section \ldots
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %% Do not use \listoffigures as most will included as separate files
-\ak{figures und tables gehen noch etwas durcheinander}
-\ak{teilweise fehlen noch figure legends}
 \section*{Figures}
-  \begin{figure}[h!]
-  \includegraphics[width=\textwidth]{plots/swarm.pdf}
-  \caption{\csentence{Results of scoring of the seven assemblers}
-  The box- and swarplots depict the results of the scoring algorithm we used. For the different assemblers. The whiskers of boxplots indicate the 1.5 x interquartile range. 
-    }
-      \label{fig:swarmplot}
-      \end{figure}
-
 \begin{figure}[h!]
@@
   \begin{figure}[h!]
-  \includegraphics[width=\textwidth]{plots/repro.pdf}
-  \caption{\csentence{Scores between two repeated runs for reproducibility testing}
-  The scatter plots depicts the scores of the 1. runs x-axis versus the scores of the 2. run y-axis of the data sets that were selected for re-evaluation. 
+  \includegraphics[width=\textwidth]{plots/swarm.pdf}
+  \caption{\csentence{Results of scoring of the seven assemblers}
+  The box- and swarplots depict the results of the scoring algorithm we used. For the different assemblers. The whiskers of boxplots indicate the 1.5 x interquartile range. 
     }
-      \label{fig:reproducibility}
+      \label{fig:swarmplot}
       \end{figure}
@@
 \begin{figure}[h!]
+  \includegraphics[width=\textwidth]{plots/repro.pdf}
+  \caption{\csentence{Scores between two repeated runs for consistency testing}
+  The scatter plots depicts the scores of the 1. runs x-axis versus the scores of the 2. run y-axis of the data sets that were selected for re-evaluation. 
+      }
+      \label{fig:consistency}
+      \end{figure}
+
+\begin{figure}[h!]
   \includegraphics[width=\textwidth]{plots/real_datasets_tree.pdf}
-  \caption{\csentence{Success of assemblers on real data sets on tree derived from NCBI taxonomy \cite{ncbi2011}}
+  \caption{\csentence{Success of assemblers on real data sets on tree derived from NCBI taxonomy \cite{ncbi2011}. Plot was prepared using \cite{Letunic2019}}
        }
       \label{fig:tree}
-      \end{figure}\todo{cite itol}
+      \end{figure}
 
@@
 
-\begin{table}[h!]
-\caption{Docker images used in our benchmark setup.}
-\label{tab:dockerimages}
-\centering
-      \resizebox{\textwidth}{!}{\begin{tabular}{ccc}
-        \hline
-          Tool & Image name and tag & SHA256 Checksum   \\ \hline
-          \ce & \dockerce & \dockercesha \\
-          \cassp & \dockercassp & \dockercasspsha \\
-          \fp & \dockerfp & \dockerfpsha \\
-          \go & \dockergo & \dockergosha \\
-          \ioga & \dockerioga & \dockeriogasha \\
-          \np & \dockernp & \dockernpsha \\
-          \oa & \dockeroa & \dockeroasha \\ \hline
-      \end{tabular}}
-\end{table}
-
 \begin{table}[ht]
 \caption{Scores of assemblies of simulated data}
-\label{tab:scores}
+\label{tab:scores_simulated}
 \centering
@@
 \caption{Mean scores of chloroplast genome assemblers}
-\label{tab:scores}
+\label{tab:scores_real}
 \centering
@@
 
-\include{sets_re_runs.tex}
-
-\begin{table}[ht]
-\caption{Performance metrics input size 25K}
-\label{tab:perform25K}
+\begin{table}[h!]
+\caption{Docker images used in our benchmark setup.}
+\label{tab:dockerimages}
 \centering
-\begin{tabular}{rlrrrr}
+      \resizebox{\textwidth}{!}{\begin{tabular}{ccc}
         \hline
- & program & threads & Peak CPU usage & Peak memeory & Peak disk usage (GB) \\ 
-  \hline
-1 & CAP &   1 & 113.32 & 0.31 & 0.06 \\ 
-  2 & CAP &   2 & 166.60 & 0.26 & 0.05 \\ 
-  3 & CAP &   4 & 305.99 & 0.26 & 0.05 \\ 
-  4 & CAP &   8 & 569.12 & 0.37 & 0.06 \\ 
-  5 & CE &   1 & 111.49 & 3.41 & 0.07 \\ 
-  6 & CE &   2 & 199.12 & 3.41 & 0.07 \\ 
-  7 & CE &   4 & 343.22 & 3.41 & 0.07 \\ 
-  8 & CE &   8 & 509.51 & 3.41 & 0.07 \\ 
-  9 & Fast-Plast &   1 & 118.31 & 0.77 & 0.30 \\ 
-  10 & Fast-Plast &   2 & 213.57 & 0.77 & 0.31 \\ 
-  11 & Fast-Plast &   4 & 379.27 & 0.77 & 0.32 \\ 
-  12 & Fast-Plast &   8 & 657.20 & 0.77 & 0.35 \\ 
-  13 & GetOrganelle &   1 & 111.39 & 0.38 & 0.05 \\ 
-  14 & GetOrganelle &   2 & 170.30 & 0.32 & 0.05 \\ 
-  15 & GetOrganelle &   4 & 242.27 & 0.31 & 0.06 \\ 
-  16 & GetOrganelle &   8 & 346.98 & 0.31 & 0.07 \\ 
-  17 & IOGA &   1 & 118.12 & 18.61 & 6.25 \\ 
-  18 & IOGA &   2 & 224.74 & 17.88 & 6.26 \\ 
-  19 & IOGA &   4 & 394.98 & 16.62 & 5.60 \\ 
-  20 & IOGA &   8 & 733.11 & 21.76 & 11.13 \\ 
-  21 & NOVOPlasty &   1 & 78.38 & 0.04 & 0.00 \\ 
-  22 & NOVOPlasty &   2 & 86.64 & 0.04 & 0.00 \\ 
-  23 & NOVOPlasty &   4 & 86.50 & 0.04 & 0.00 \\ 
-  24 & NOVOPlasty &   8 & 87.32 & 0.04 & 0.00 \\ 
-  25 & org.ASM &   1 & 112.08 & 0.79 & 0.03 \\ 
-  26 & org.ASM &   2 & 115.44 & 0.79 & 0.03 \\ 
-  27 & org.ASM &   4 & 105.09 & 0.79 & 0.03 \\ 
-  28 & org.ASM &   8 & 105.78 & 0.79 & 0.03 \\ 
-   \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[ht]
-\caption{Performance metrics input size 250K}
-\label{tab:perform250K}
-\centering
-\begin{tabular}{rlrrrr}
-  \hline
- & program & threads & Peak CPU usage & Peak memeory & Peak disk usage (GB) \\ 
-  \hline
-1 & CAP &   1 & 114.38 & 0.90 & 0.65 \\ 
-  2 & CAP &   2 & 204.39 & 0.93 & 0.65 \\ 
-  3 & CAP &   4 & 337.09 & 0.97 & 0.65 \\ 
-  4 & CAP &   8 & 652.75 & 1.08 & 0.65 \\ 
-  5 & CE &   1 & 117.57 & 3.96 & 0.63 \\ 
-  6 & CE &   2 & 230.35 & 3.96 & 0.63 \\ 
-  7 & CE &   4 & 414.25 & 3.96 & 0.63 \\ 
-  8 & CE &   8 & 755.76 & 3.97 & 0.63 \\ 
-  9 & Fast-Plast &   1 & 118.81 & 1.40 & 0.78 \\ 
-  10 & Fast-Plast &   2 & 234.12 & 2.25 & 0.78 \\ 
-  11 & Fast-Plast &   4 & 425.89 & 2.32 & 0.79 \\ 
-  12 & Fast-Plast &   8 & 845.94 & 2.52 & 0.79 \\ 
-  13 & GetOrganelle &   1 & 117.94 & 1.07 & 0.40 \\ 
-  14 & GetOrganelle &   2 & 227.05 & 1.13 & 0.40 \\ 
-  15 & GetOrganelle &   4 & 403.35 & 1.08 & 0.40 \\ 
-  16 & GetOrganelle &   8 & 747.20 & 1.03 & 0.39 \\ 
-  17 & IOGA &   1 & 118.62 & 12.03 & 4.01 \\ 
-  18 & IOGA &   2 & 234.09 & 9.71 & 4.01 \\ 
-  19 & IOGA &   4 & 420.77 & 10.09 & 3.48 \\ 
-  20 & IOGA &   8 & 842.57 & 19.21 & 9.45 \\ 
-  21 & NOVOPlasty &   1 & 111.97 & 0.32 & 0.00 \\ 
-  22 & NOVOPlasty &   2 & 115.07 & 0.32 & 0.00 \\ 
-  23 & NOVOPlasty &   4 & 116.42 & 0.31 & 0.00 \\ 
-  24 & NOVOPlasty &   8 & 115.86 & 0.31 & 0.00 \\ 
-  25 & org.ASM &   1 & 118.10 & 0.93 & 0.06 \\ 
-  26 & org.ASM &   2 & 161.76 & 0.93 & 0.06 \\ 
-  27 & org.ASM &   4 & 163.01 & 0.93 & 0.06 \\ 
-  28 & org.ASM &   8 & 160.74 & 0.93 & 0.06 \\ 
-   \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[ht]
-\caption{Performance metrics input size 2.5M}
-\label{tab:perform2.5M  }
-\centering
-\begin{tabular}{rlrrrr}
-  \hline
- & program & threads & Peak CPU usage & Peak memeory & Peak disk usage (GB) \\ 
- \hline
-1 & CAP &   1 & 118.80 & 6.83 & 6.59 \\ 
-  2 & CAP &   2 & 209.22 & 7.58 & 6.59 \\ 
-  3 & CAP &   4 & 357.36 & 7.25 & 6.59 \\ 
-  4 & CAP &   8 & 683.71 & 6.99 & 6.59 \\ 
-  5 & CE &   1 & 118.78 & 5.34 & 2.01 \\ 
-  6 & CE &   2 & 234.82 & 5.34 & 2.01 \\ 
-  7 & CE &   4 & 415.74 & 5.28 & 2.09 \\ 
-  8 & CE &   8 & 844.95 & 5.34 & 2.01 \\ 
-  9 & Fast-Plast &   1 & 119.24 & 6.80 & 5.80 \\ 
-  10 & Fast-Plast &   2 & 237.34 & 6.98 & 5.82 \\ 
-  11 & Fast-Plast &   4 & 443.27 & 8.02 & 5.69 \\ 
-  12 & Fast-Plast &   8 & 872.07 & 8.87 & 5.69 \\ 
-  13 & GetOrganelle &   1 & 118.91 & 5.25 & 3.31 \\ 
-  14 & GetOrganelle &   2 & 235.18 & 5.26 & 3.31 \\ 
-  15 & GetOrganelle &   4 & 420.10 & 5.44 & 3.31 \\ 
-  16 & GetOrganelle &   8 & 845.13 & 6.07 & 3.31 \\ 
-  17 & IOGA &   1 & 119.46 & 18.64 & 8.83 \\ 
-  18 & IOGA &   2 & 237.22 & 21.24 & 10.19 \\ 
-  19 & IOGA &   4 & 425.50 & 18.71 & 10.56 \\ 
-  20 & IOGA &   8 & 857.29 & 25.23 & 16.51 \\ 
-  21 & NOVOPlasty &   1 & 112.67 & 2.69 & 0.00 \\ 
-  22 & NOVOPlasty &   2 & 117.77 & 2.58 & 0.00 \\ 
-  23 & NOVOPlasty &   4 & 117.40 & 2.74 & 0.00 \\ 
-  24 & NOVOPlasty &   8 & 117.28 & 2.74 & 0.00 \\ 
-  25 & org.ASM &   1 & 118.73 & 2.63 & 0.37 \\ 
-  26 & org.ASM &   2 & 184.53 & 2.63 & 0.37 \\ 
-  27 & org.ASM &   4 & 177.03 & 2.63 & 0.37 \\ 
-  28 & org.ASM &   8 & 176.25 & 2.63 & 0.37 \\ 
-   \hline
-\end{tabular}
+          Tool & Image name and tag & SHA256 Checksum   \\ \hline
+          \ce & \dockerce & \dockercesha \\
+          \cassp & \dockercassp & \dockercasspsha \\
+          \fp & \dockerfp & \dockerfpsha \\
+          \go & \dockergo & \dockergosha \\
+          \ioga & \dockerioga & \dockeriogasha \\
+          \np & \dockernp & \dockernpsha \\
+          \oa & \dockeroa & \dockeroasha \\ \hline
+      \end{tabular}}
 \end{table}

### 2019-06-06 bmc_article.tex
Update on Overleaf.

@@
 
-\subsubsection*{Reproducibility}
-\todo{lieber Consistency?}To ensure reproducibility of the obtained results, we randomly chose  \num{100} data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
+\subsubsection*{Consistency}
+\todo{lieber Consistency?}To ensure consistency of the obtained results, we randomly chose  \num{100} data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
 The resulting assemblies were scored again as described and the scores of the first and the second run were compared to each other
@@
 \subsection*{Qualitative}
-The user experience of most tools was evaluated as mainly \good{} (see table \ref{tab:resultsQual}). However, a few critique points remained.
+The user experience of most tools was evaluated as mainly \good{} (\cref{tab:resultsQual}). However, a few critique points remained.
 Two minor dependencies were missing in the \go{} installation instructions and there was no test data available.
@@
 
-\subsubsection*{Reproducibility}
-Reproducibility was tested as described above, by re-running assemblies and comparison of the scores of two assemblies (\cref{fig:reproducibility}).
+\subsubsection*{Consistency}
+Consistency was tested by re-running assemblies and comparison of the scores of two assemblies (\cref{fig:consistency}).
 Replicates that did not produce an output were manually scored as \num{0}. 
@@
 Another important feature of software is a comprehensive documentation, which needs to be up-to-date and maintained.
-Software authors should constantly improve the usability\todo{ich bin nicht sicher ob ich das so hart sagen würde}, and be open to suggestions from the users.
+Additionally, software authors could improve the usability based on suggestions from their users.
 
 Finally, all tools should improve their integrated guessing of default parameters, as many users avoid fine tuning of those, especially, for larger screening approaches.
-Last, as sequencing technology is developing fast ( eg.\ PacBio or nanopore), tools need to be updated to not become obsolete.
+Last, as sequencing technology is developing fast (eg.\ PacBio or nanopore), tools need to be updated to not become obsolete.
 But the hope would be that with ongoing software development and improved sequencing technologies, the generation of whole chloroplast assemblies from any species will become a routine technique.
@@
 \section*{Conclusion}
-%\ff{Conclusion}
-%Short summary of clear guidelines and future development (might not be necessary as these are the last two sections of the Discussion anyway, so we might elect to skip this).
-%\todo{sollten wir lobend erwähnen, dass alle auf github/gitlab sind?}
 The main assumption for our study to benchmark different chloroplast assembly tools, is that whole genome sequencing data are also a promising source for chlorplast assemblies.
@@
 \begin{figure}[h!]
+  \includegraphics[width=\textwidth]{plots/repro.pdf}
+  \caption{\csentence{Scores between two repeated runs for consistency testing}
+  The scatter plots depicts the scores of the 1. runs x-axis versus the scores of the 2. run y-axis of the data sets that were selected for re-evaluation. 
+      }
+      \label{fig:consistency}
+      \end{figure}
+
+\begin{figure}[h!]
   \includegraphics[width=\textwidth]{plots/real_datasets_tree.pdf}
@@
 \section*{Tables}
+\begin{table}[h!]
+\caption{Docker images used in our benchmark setup.}
+\label{tab:dockerimages}
+\centering
+      \resizebox{\textwidth}{!}{\begin{tabular}{ccc}
+        \hline
+          Tool & Image name and tag & SHA256 Checksum   \\ \hline
+          \ce & \dockerce & \dockercesha \\
+          \cassp & \dockercassp & \dockercasspsha \\
+          \fp & \dockerfp & \dockerfpsha \\
+          \go & \dockergo & \dockergosha \\
+          \ioga & \dockerioga & \dockeriogasha \\
+          \np & \dockernp & \dockernpsha \\
+          \oa & \dockeroa & \dockeroasha \\ \hline
+      \end{tabular}}
+\end{table}
+
 \begin{table}[]
@@
     could score \good{}, \ok{} or \bad{} in each of the categories.}
-    \label{tab:resultsQual}
+    \label{tab:resultsqual}
 \begin{tabular}{p{3cm}cccccc}   
@@
 \end{tabular}      
-\end{table}
-
-\begin{table}[h!]
-\caption{Docker images used in our benchmark setup.}
-\label{tab:dockerimages}
-\centering
-      \resizebox{\textwidth}{!}{\begin{tabular}{ccc}
-        \hline
-          Tool & Image name and tag & SHA256 Checksum   \\ \hline
-          \ce & \dockerce & \dockercesha \\
-          \cassp & \dockercassp & \dockercasspsha \\
-          \fp & \dockerfp & \dockerfpsha \\
-          \go & \dockergo & \dockergosha \\
-          \ioga & \dockerioga & \dockeriogasha \\
-          \np & \dockernp & \dockernpsha \\
-          \oa & \dockeroa & \dockeroasha \\ \hline
-      \end{tabular}}
 \end{table}

### 2019-06-06 bmc_article.tex
Update on Overleaf.

@@
 \subsection*{Data availability}
-Source code for all methods used is available at \url{https://github.com/chloroExtractorTeam/benchmark} and archived in zenodo under \zenodorepo{}.
-All docker images are published on \url{https://cloud.docker.com/u/chloroextractorteam/} and are named with a leading \texttt{benchmark\_} (\cref{tab:dockerimages}).
+Source code for all methods used is available at \cite{github-benchmark-repo} and archived in zenodo under \zenodorepo{}.
+All docker images are published on \cite{dockerhub-benchmark} and are named with a leading \texttt{benchmark\_} (\cref{tab:dockerimages}).
 
@@
 \subsubsection*{Consistency}
-\todo{lieber Consistency?}To ensure consistency of the obtained results, we randomly chose  \num{100} data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
+To ensure consistency of the obtained results, we randomly chose  \num{100} data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
 The resulting assemblies were scored again as described and the scores of the first and the second run were compared to each other
@@
 The observed run times varied from a few minutes to several hours (\cref{fig:performance_runtime}).
-%\ak{did I miss Figure 1 ?, need to check figure numbering in the end}
+
 Some assemblies failed to finish within the time-limit we set (\SI{48}{\hour}). 
@@
 \np{} performed second best with scores above \num{80} for all data sets, only failing to resolve the contigs into one single circular chloroplast assembly.
-The overall performance \ak{of all assemblers ?} is best, when the input data consists purely of chloroplast reads.
+The overall performance is best, when the input data consists purely of chloroplast reads.
 Only \ioga{} and \cassp{} failed to deliver any results under this scenario once.
@@
 \go{} was the only tool that succeeded in obtaining similar scores for all assemblies, without producing and completely unsuccessful assemblies for this subset of data.
-Except for \fp{} all the other tools had at least one assembly that was unsuccessful in one run, but produced an output in the other.\ak{oben steht \go{} war als einziges immer gut, dann kommt except for \fp{} ??
-does not seem to be consistent}
+Except for \fp{} all the other tools had at least one assembly that was unsuccessful in one run, but produced an output in the other.
+%\ak{oben steht \go{} war als einziges immer gut, dann kommt except for \fp{} ?? does not seem to be consistent}
 Notably \ioga{} appears to have a tendency to perform differently in independent runs.
@@
 
-Both \fp{} and \np{} tend to have minor changes in the assembly when the overall performance is comparably well, leading to the arrow-shaped scatter plots.\ak{link to figure scatter plots is missing}
+Both \fp{} and \np{} tend to have minor changes in the assembly when the overall performance is comparably well, leading to the arrow-shaped scatter plots.
+%\ak{link to figure scatter plots is missing}
 \ce{} and \cassp{} appear to be the most robust assemblers, having only few deviations between the two runs.
@@
 \subsection*{Guidelines for the end-user}
-Given these results, our recommendation is to use \go{} as default option, and in case of failure \fp{} as backup solution.\ak{what if both lead to qualitative different results?, always trust \go{} , or could one compute a high-confidence assembly by combining different results ?, might be a point for future directions.}
+Given these results, our recommendation is to use \go{} as default option, and in case of failure \fp{} as backup solution.
+%\ak{what if both lead to qualitative different results?, always trust \go{} , or could one compute a high-confidence assembly by combining different results ?, might be a point for future directions.}
 If both programs fail, it is sensible to re-run \fp{} and additionally try \np{} and \oa{}.
@@
 For an automated approach, running \go{} and \fp{} in parallel appears to be a good trade-off between success rate and use of resources.
-%\todo{Does the decision depend on some parameter of the data (read length, amount, taxonomic group, ...)?}
 
 \subsection*{Ideas for future development}
-%\ff{this section (lower priority)}
 For further experiments, combining different components from different tools might be a promising approach.
@@
 JF, NT, and MJA are affiliated with the for-profit organization AnaLife Data Science.
-\ak{and I think we should mention Analife as competing interest, normally people list all non-academic shareholder whatever stuff, just to be sure}\todo{Ich weiß nicht ob das so passt}
+\ak{and I think we should mention Analife as competing interest, normally people list all non-academic shareholder whatever stuff, just to be sure}
+\todo{Ich weiß nicht ob das so passt}
 

### 2019-06-06 bmc_article.tex
Update on Overleaf.

@@
 
+\section*{Results}
+\subsection*{Performance metrics}
+%\subsection*{Computational Resources}
+%Table and figure of performance evaluation.
+Including RAM, I/O, runtime, parallelization ability, CPU usage.
+Free text description of results, range, mean/median, effect of input size, threads parameter, ...
+
+\subsubsection*{Time requirements}
+In terms of run time, massive differences between the different tools have been observed.
+Apart from tool-specific differences, input data and number of threads had huge impact.
+The observed run times varied from a few minutes to several hours (\cref{fig:performance_runtime}).
+
+Some assemblies failed to finish within the time-limit we set (\SI{48}{\hour}). 
+On average the longest time to generate the assemblies was taken by \ioga{} and \fp{} followed by \oa{} and \go{} the most time efficient tool was \ce{}, which on average is a little faster than \np{} and \cassp{}.
+%% multithreading
+
+Not all the tools were able to benefit from having access to multiple threads.
+Both \np{} and \oa{} take about the same time independent of being able to utilize \numlist[list-final-separator={, or }]{1;2;4;8} threads.
+\cassp{}, \ce{}, \go  and \fp{} all profit from multi-threading (\cref{fig:performance_runtime,fig:performance_memory_cpu}).
+
+\subsubsection*{Memory and CPU Usage }
+The peak and mean CPU usage, as well as peak memory and disk usage have been recorded for all assemblers based on the same input data set and number of threads to use (\cref{fig:performance_memory_cpu}).
+Mainly, the size of the input data influenced the peak memory usage with the exception of \ce{} and \ioga{}.
+Those two assemblers seems to have a memory usage pattern, which is less influenced by the size of the data.
+The number of allowed threads had only a limited impact on the peak memory usage.
+Nevertheless, all programs profit by a higher number of threads, if the size of the input data was increased.
+In contrast, the disk usage is independent from input size and number of threads for all assemblers.
+%but the factor between the programs exceeds a factor of \num{100}.
+
+\subsection*{Qualitative}
+The user experience of most tools was evaluated as mainly \good{} (\cref{tab:resultsQual}). However, a few critique points remained.
+Two minor dependencies were missing in the \go{} installation instructions and there was no test data available.
+Additionally, an issue occurred when running it on a \plant{At} data set.
+We are currently in the process of resolving this with the authors.
+
+The \fp{} installation instructions were missing some dependencies.
+Like \go{}, \fp{} does not offer a test data set or a tutorial, except for some example commands.
+
+The \oa{} installation instructions did not work.
+We found some issues, which are probably related to the requirement of \texttt{Python~3.7}.
+There is a tutorial where sample data is available.
+However, following the instructions resulted in a segmentation fault.
+We found a workaround for this bug and contacted the authors.
+
+The main critique point of \np{} was the lack of a test data set with instructions.
+This was fixed by the authors after we contacted them.
+Additionally, \np{} uses a custom license, where an OSI approved license would be preferred.
+
+The \ce{} does come with a test data set and a short tutorial.
+However, it is currently not possible to evaluate the results of the test run.
+
+The \ioga{} installation instructions were missing many dependencies.
+Also, there was no test data or tutorial available and there is no license assigned to it.
+Since there was no update to the GitHub repository for the last three years, the project can be seen as inactive.
+After contacting the authors, they promised to resolve the mentioned issues.
+
+As many of the other tools, the installation instructions for the \cassp{} were missing some dependencies.
+The list was updated after we contacted the authors.
+This tool does come with a test data set, however a note about the expected outcome is missing.
+A more extensive tutorial is provided.
+The description about the parameter is short, but sufficient.
+
+\subsection*{Quantitative}
+\subsubsection*{Simulated data}
+The only assembler obtaining perfect results according to our score for the simulated data sets is \go{} (\cref{fig:simulated,tab:scores_simulated}).
+\ioga{} and \cassp{} showed the worst performance, being unable to fully assemble a single chloroplast out of \num{14} runs.
+\np{} performed second best with scores above \num{80} for all data sets, only failing to resolve the contigs into one single circular chloroplast assembly.
+The overall performance is best, when the input data consists purely of chloroplast reads.
+Only \ioga{} and \cassp{} failed to deliver any results under this scenario once.
+In general, no clear correlation between either length of the input reads or the ratio of core vs chloroplast reads and the performance of the different assemblers can be observed.
+
+\subsubsection*{Real data sets}
+Concerning the performance of the assemblers on the real data sets, we were able to observe considerable differences in the median score (\cref{fig:swarmplot}).
+The highest scores were achieved by \go{} with a median of \num{99.7} and \num{199} circular assemblies out of a total of 356 assemblies that resulted in an output (\cref{tab:scores_real}).
+The performance of \go{} is followed by \fp{}, \np{}, \oa{}, and \ce{}.
+\fp{} is outperforming the latter two slightly in terms of score, with twice as much \num{114} perfectly assembled chloroplast genomes (\np{} produced \num{66} and \oa{} \num{55} circular genomes).
+\ioga{} and \cassp{} were both not able to assemble a circular, single-contig genome (\cref{tab:scores}), consequently resulting in the lowest mean and median scores (\cref{fig:upset}).
+
+%\textit{swarm plot goes here}
+%% Den upset plot eventuell erst in die Discussion reinbringen ? Da wir davon ableiten welche tools wir empfehlen?
+
+\subsubsection*{Consistency}
+Consistency was tested by re-running assemblies and comparison of the scores of two assemblies (\cref{fig:consistency}).
+Replicates that did not produce an output were manually scored as \num{0}. 
+\go{} was the only tool that succeeded in obtaining similar scores for all assemblies, without producing and completely unsuccessful assemblies for this subset of data.
+Except for \fp{} all the other tools had at least one assembly that was unsuccessful in one run, but produced an output in the other.
+%\ak{oben steht \go{} war als einziges immer gut, dann kommt except for \fp{} ?? does not seem to be consistent}
+Notably \ioga{} appears to have a tendency to perform differently in independent runs.
+Here, more than \SI{10}{\percent} of the assemblies failed in one run only.
+
+Both \fp{} and \np{} tend to have minor changes in the assembly when the overall performance is comparably well, leading to the arrow-shaped scatter plots.
+%\ak{link to figure scatter plots is missing}
+\ce{} and \cassp{} appear to be the most robust assemblers, having only few deviations between the two runs.
+
+\section*{Discussion}
+We aimed to generate an overall performance score for the different chloroplast assemblers, but depending on distinct downstream applications, the different criteria assessed in this work need to be weighted differently.
+For example, ease of installation and use might not be a big concern if the tool is installed once and integrated in an automated pipeline.
+On the other hand this factor alone might prevent other users from being able to use the tool in the first place.
+Similarly, computational requirements or run time might be less relevant, if the goal is to assemble a single chloroplast for further analysis, but it is essential if hundreds or thousands of samples should be processed in parallel for a large scale study.
+Eventually, both ease of use and run time are irrelevant if the tool is not able to successfully accomplish its task.
+Also the scope of this study needs to be considered when interpreting the guidelines below.
+In particular, we evaluated all tools under the assumption that they are used in the most basic form (default parameters, no hand selected reference, no pre-processing of the data or post-processing of the result, restricted run time).
+It is important to note that any tool might perform significantly different, if the above mentioned parameters are fine-tuned for a specific data set.
+
+The overall best success rate, both on simulated and real data, was achieved by \go{} followed by \fp{}.
+Both tools complement each other, as each is able to successfully reconstruct a full chloroplasts in cases where the other tool fails. 
+In rare cases \np{} or \oa{} are the only tool to succeed.
+The tools \fp{}, \np{}, and \oa{} produce the most variable results, thus re-running the tool after a failed attempt might be successful.
+\ce{} yields only few complete chloroplast assemblies, but requires also only few resources.
+It is easy to install and use and thus could be considered as a good option for a quick first try.
+Both \ioga{} and \cassp{} have the worst performance of all tools tested and fail to return reliable chloroplast assemblies.
+
+\subsection*{Guidelines for the end-user}
+Given these results, our recommendation is to use \go{} as default option, and in case of failure \fp{} as backup solution.
+%\ak{what if both lead to qualitative different results?, always trust \go{} , or could one compute a high-confidence assembly by combining different results ?, might be a point for future directions.}
+If both programs fail, it is sensible to re-run \fp{} and additionally try \np{} and \oa{}.
+This procedure maximizes the chance to effectively and efficiently recover the circular chloroplast genome from mixed genomic data.
+If none of these four assemblers produce sensible results, a reference guided approach and tweaking of the default parameters, might be the solution.
+Here, it is not possible to provide general guidelines, as the procedure will differ for different data sets.
+For an automated approach, running \go{} and \fp{} in parallel appears to be a good trade-off between success rate and use of resources.
+
+\subsection*{Ideas for future development}
+For further experiments, combining different components from different tools might be a promising approach.
+For example, read scaling from \ce{} followed by an assembly by \go{} and finally the structural resolution with \fp{} could be a promising approach, combing the respective strength of the different tools.
+
+Moreover, the installation issues need to be mitigated by modern software.
+Therefore, either containerization (docker, singularity, etc.) or install workflows (eg. bioconda \cite{gruening2018}) should be established by all software packages.
+Otherwise, the burden of the software installation might result in scientists ignoring good tools.
+
+Another important feature of software is a comprehensive documentation, which needs to be up-to-date and maintained.
+Additionally, software authors could improve the usability based on suggestions from their users.
+
+Finally, all tools should improve their integrated guessing of default parameters, as many users avoid fine tuning of those, especially, for larger screening approaches.
+Last, as sequencing technology is developing fast (eg.\ PacBio or nanopore), tools need to be updated to not become obsolete.
+But the hope would be that with ongoing software development and improved sequencing technologies, the generation of whole chloroplast assemblies from any species will become a routine technique.
+
+\section*{Conclusion}
+The main assumption for our study to benchmark different chloroplast assembly tools, is that whole genome sequencing data are also a promising source for chlorplast assemblies.
+Our benchmark shows that ~\SI{60}{\percent} of the data sets without available chloroplast genome, have been assembled by at least one of the tools we analysed.
+Still, even with simulated (aka``perfect'') data, not all tools succeeded in generating complete chloroplast assemblies.
+Therefore, we determined the strengths and weaknesses of the specific tools and provided guidelines for the users.
+However, it might be necessary, to combine different methods or manually explore the parameter space, to obtain reliable results if a single run seems not sufficient.
+Ultimately, large scale studies reconstructing hundreds or thousands of chloroplast genomes are now feasible using the currently available tools. 
+%Outlook: next step in the pipeline is annotation. There is a similar problem: many tools, which one to use? 
+%A large scale study reconstructing chloroplasts throughout SRA (or \num{1001} genome project) is feasible and promising using the existing tools (estimated runtime, number of novel chloroplasts).
+%A meta-tool that automatically combines the different programs could be developed.
+%The benchmarking study could be augmented to automatically select the closest reference from the database and provide that to any tool that can take advantage of references.
+
 \section*{Methods}
@@
 
-\section*{Results}
-\subsection*{Performance metrics}
-%\subsection*{Computational Resources}
-%Table and figure of performance evaluation.
-Including RAM, I/O, runtime, parallelization ability, CPU usage.
-Free text description of results, range, mean/median, effect of input size, threads parameter, ...
-
-\subsubsection*{Time requirements}
-In terms of run time, massive differences between the different tools have been observed.
-Apart from tool-specific differences, input data and number of threads had huge impact.
-The observed run times varied from a few minutes to several hours (\cref{fig:performance_runtime}).
-
-Some assemblies failed to finish within the time-limit we set (\SI{48}{\hour}). 
-On average the longest time to generate the assemblies was taken by \ioga{} and \fp{} followed by \oa{} and \go{} the most time efficient tool was \ce{}, which on average is a little faster than \np{} and \cassp{}.
-%% multithreading
-
-Not all the tools were able to benefit from having access to multiple threads.
-Both \np{} and \oa{} take about the same time independent of being able to utilize \numlist[list-final-separator={, or }]{1;2;4;8} threads.
-\cassp{}, \ce{}, \go  and \fp{} all profit from multi-threading (\cref{fig:performance_runtime}, \cref{fig:performance_memory_cpu}).
-
-\subsubsection*{Memory and CPU Usage }
-The peak and mean CPU usage, as well as peak memory and disk usage have been recorded for all assemblers based on the same input data set and number of threads to use (\cref{fig:performance_memory_cpu}).
-Mainly, the size of the input data influenced the peak memory usage with the exception of \ce{} and \ioga{}.
-Those two assemblers seems to have a memory usage pattern, which is less influenced by the size of the data.
-The number of allowed threads had only a limited impact on the peak memory usage.
-Nevertheless, all programs profit by a higher number of threads, if the size of the input data was increased.
-In contrast, the disk usage is independent from input size and number of threads for all assemblers.
-%but the factor between the programs exceeds a factor of \num{100}.
-
-\subsection*{Qualitative}
-The user experience of most tools was evaluated as mainly \good{} (\cref{tab:resultsQual}). However, a few critique points remained.
-Two minor dependencies were missing in the \go{} installation instructions and there was no test data available.
-Additionally, an issue occurred when running it on a \plant{At} data set.
-We are currently in the process of resolving this with the authors.
-
-The \fp{} installation instructions were missing some dependencies.
-Like \go{}, \fp{} does not offer a test data set or a tutorial, except for some example commands.
-
-The \oa{} installation instructions did not work.
-We found some issues, which are probably related to the requirement of \texttt{Python~3.7}.
-There is a tutorial where sample data is available.
-However, following the instructions resulted in a segmentation fault.
-We found a workaround for this bug and contacted the authors.
-
-The main critique point of \np{} was the lack of a test data set with instructions.
-This was fixed by the authors after we contacted them.
-Additionally, \np{} uses a custom license, where an OSI approved license would be preferred.
-
-The \ce{} does come with a test data set and a short tutorial.
-However, it is currently not possible to evaluate the results of the test run.
-
-The \ioga{} installation instructions were missing many dependencies.
-Also, there was no test data or tutorial available and there is no license assigned to it.
-Since there was no update to the GitHub repository for the last three years, the project can be seen as inactive.
-After contacting the authors, they promised to resolve the mentioned issues.
-
-As many of the other tools, the installation instructions for the \cassp{} were missing some dependencies.
-The list was updated after we contacted the authors.
-This tool does come with a test data set, however a note about the expected outcome is missing.
-A more extensive tutorial is provided.
-The description about the parameter is short, but sufficient.
-
-\subsection*{Quantitative}
-\subsubsection*{Simulated data}
-The only assembler obtaining perfect results according to our score for the simulated data sets is \go{} (\cref{fig:simulated}).
-\ioga{} and \cassp{} showed the worst performance, being unable to fully assemble a single chloroplast out of \num{14} runs.
-\np{} performed second best with scores above \num{80} for all data sets, only failing to resolve the contigs into one single circular chloroplast assembly.
-The overall performance is best, when the input data consists purely of chloroplast reads.
-Only \ioga{} and \cassp{} failed to deliver any results under this scenario once.
-In general, no clear correlation between either length of the input reads or the ratio of core vs chloroplast reads and the performance of the different assemblers can be observed.
-
-\subsubsection*{Real data sets}
-Concerning the performance of the assemblers on the real data sets, we were able to observe considerable differences in the median score (\cref{fig:swarmplot}).
-The highest scores were achieved by \go{} with a median of \num{99.7} and \num{199} circular assemblies out of a total of 356 assemblies that resulted in an output (\cref{tab:scores}).
-The performance of \go{} is followed by \fp{}, \np{}, \oa{}, and \ce{}.
-\fp{} is outperforming the latter two slightly in terms of score, with twice as much \num{114} perfectly assembled chloroplast genomes (\np{} produced \num{66} and \oa{} \num{55} circular genomes).
-\ioga{} and \cassp{} were both not able to assemble a circular, single-contig genome (\cref{tab:scores}), consequently resulting in the lowest mean and median scores (\cref{fig:upset}).
-
-%\textit{swarm plot goes here}
-%% Den upset plot eventuell erst in die Discussion reinbringen ? Da wir davon ableiten welche tools wir empfehlen?
-
-\subsubsection*{Consistency}
-Consistency was tested by re-running assemblies and comparison of the scores of two assemblies (\cref{fig:consistency}).
-Replicates that did not produce an output were manually scored as \num{0}. 
-\go{} was the only tool that succeeded in obtaining similar scores for all assemblies, without producing and completely unsuccessful assemblies for this subset of data.
-Except for \fp{} all the other tools had at least one assembly that was unsuccessful in one run, but produced an output in the other.
-%\ak{oben steht \go{} war als einziges immer gut, dann kommt except for \fp{} ?? does not seem to be consistent}
-Notably \ioga{} appears to have a tendency to perform differently in independent runs.
-Here, more than \SI{10}{\percent} of the assemblies failed in one run only.
-
-Both \fp{} and \np{} tend to have minor changes in the assembly when the overall performance is comparably well, leading to the arrow-shaped scatter plots.
-%\ak{link to figure scatter plots is missing}
-\ce{} and \cassp{} appear to be the most robust assemblers, having only few deviations between the two runs.
-
-\section*{Discussion}
-We aimed to generate an overall performance score for the different chloroplast assemblers, but depending on distinct downstream applications, the different criteria assessed in this work need to be weighted differently.
-For example, ease of installation and use might not be a big concern if the tool is installed once and integrated in an automated pipeline.
-On the other hand this factor alone might prevent other users from being able to use the tool in the first place.
-Similarly, computational requirements or run time might be less relevant, if the goal is to assemble a single chloroplast for further analysis, but it is essential if hundreds or thousands of samples should be processed in parallel for a large scale study.
-Eventually, both ease of use and run time are irrelevant if the tool is not able to successfully accomplish its task.
-Also the scope of this study needs to be considered when interpreting the guidelines below.
-In particular, we evaluated all tools under the assumption that they are used in the most basic form (default parameters, no hand selected reference, no pre-processing of the data or post-processing of the result, restricted run time).
-It is important to note that any tool might perform significantly different, if the above mentioned parameters are fine-tuned for a specific data set.
-
-The overall best success rate, both on simulated and real data, was achieved by \go{} followed by \fp{}.
-Both tools complement each other, as each is able to successfully reconstruct a full chloroplasts in cases where the other tool fails. 
-In rare cases \np{} or \oa{} are the only tool to succeed.
-The tools \fp{}, \np{}, and \oa{} produce the most variable results, thus re-running the tool after a failed attempt might be successful.
-\ce{} yields only few complete chloroplast assemblies, but requires also only few resources.
-It is easy to install and use and thus could be considered as a good option for a quick first try.
-Both \ioga{} and \cassp{} have the worst performance of all tools tested and fail to return reliable chloroplast assemblies.
-
-\subsection*{Guidelines for the end-user}
-Given these results, our recommendation is to use \go{} as default option, and in case of failure \fp{} as backup solution.
-%\ak{what if both lead to qualitative different results?, always trust \go{} , or could one compute a high-confidence assembly by combining different results ?, might be a point for future directions.}
-If both programs fail, it is sensible to re-run \fp{} and additionally try \np{} and \oa{}.
-This procedure maximizes the chance to effectively and efficiently recover the circular chloroplast genome from mixed genomic data.
-If none of these four assemblers produce sensible results, a reference guided approach and tweaking of the default parameters, might be the solution.
-Here, it is not possible to provide general guidelines, as the procedure will differ for different data sets.
-For an automated approach, running \go{} and \fp{} in parallel appears to be a good trade-off between success rate and use of resources.
-
-\subsection*{Ideas for future development}
-For further experiments, combining different components from different tools might be a promising approach.
-For example, read scaling from \ce{} followed by an assembly by \go{} and finally the structural resolution with \fp{} could be a promising approach, combing the respective strength of the different tools.
-
-Moreover, the installation issues need to be mitigated by modern software.
-Therefore, either containerization (docker, singularity, etc.) or install workflows (eg. bioconda \cite{gruening2018}) should be established by all software packages.
-Otherwise, the burden of the software installation might result in scientists ignoring good tools.
-
-Another important feature of software is a comprehensive documentation, which needs to be up-to-date and maintained.
-Additionally, software authors could improve the usability based on suggestions from their users.
-
-Finally, all tools should improve their integrated guessing of default parameters, as many users avoid fine tuning of those, especially, for larger screening approaches.
-Last, as sequencing technology is developing fast (eg.\ PacBio or nanopore), tools need to be updated to not become obsolete.
-But the hope would be that with ongoing software development and improved sequencing technologies, the generation of whole chloroplast assemblies from any species will become a routine technique.
-
-\section*{Conclusion}
-The main assumption for our study to benchmark different chloroplast assembly tools, is that whole genome sequencing data are also a promising source for chlorplast assemblies.
-Our benchmark shows that ~\SI{60}{\percent} of the data sets without available chloroplast genome, have been assembled by at least one of the tools we analysed.
-Still, even with simulated (aka``perfect'') data, not all tools succeeded in generating complete chloroplast assemblies.
-Therefore, we determined the strengths and weaknesses of the specific tools and provided guidelines for the users.
-However, it might be necessary, to combine different methods or manually explore the parameter space, to obtain reliable results if a single run seems not sufficient.
-Ultimately, large scale studies reconstructing hundreds or thousands of chloroplast genomes are now feasible using the currently available tools. 
-%Outlook: next step in the pipeline is annotation. There is a similar problem: many tools, which one to use? 
-%A large scale study reconstructing chloroplasts throughout SRA (or \num{1001} genome project) is feasible and promising using the existing tools (estimated runtime, number of novel chloroplasts).
-%A meta-tool that automatically combines the different programs could be developed.
-%The benchmarking study could be augmented to automatically select the closest reference from the database and provide that to any tool that can take advantage of references.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \includegraphics[width=\textwidth]{plots/real_datasets_tree.pdf}
-  \caption{\csentence{Success of assemblers on real data sets on tree derived from NCBI taxonomy \cite{ncbi2011}}
+  \caption{\csentence{Success of assemblers on real data sets on tree derived from NCBI taxonomy \cite{ncbi2011}. Plot was prepared using \cite{Letunic2019}}
        }
       \label{fig:tree}
-      \end{figure}\todo{cite itol}
+      \end{figure}
 
@@
 \section*{Tables}
-\begin{table}[h!]
-\caption{Docker images used in our benchmark setup.}
-\label{tab:dockerimages}
-\centering
-      \resizebox{\textwidth}{!}{\begin{tabular}{ccc}
-        \hline
-          Tool & Image name and tag & SHA256 Checksum   \\ \hline
-          \ce & \dockerce & \dockercesha \\
-          \cassp & \dockercassp & \dockercasspsha \\
-          \fp & \dockerfp & \dockerfpsha \\
-          \go & \dockergo & \dockergosha \\
-          \ioga & \dockerioga & \dockeriogasha \\
-          \np & \dockernp & \dockernpsha \\
-          \oa & \dockeroa & \dockeroasha \\ \hline
-      \end{tabular}}
-\end{table}
-
 \begin{table}[]
@@
     could score \good{}, \ok{} or \bad{} in each of the categories.}
-    \label{tab:resultsqual}
+    \label{tab:resultsQual}
 \begin{tabular}{p{3cm}cccccc}   
@@
 \caption{Scores of assemblies of simulated data}
-\label{tab:scores}
+\label{tab:scores_simulated}
 \centering
@@
 
+\begin{table}[h!]
+\caption{Docker images used in our benchmark setup.}
+\label{tab:dockerimages}
+\centering
+      \resizebox{\textwidth}{!}{\begin{tabular}{ccc}
+        \hline
+          Tool & Image name and tag & SHA256 Checksum   \\ \hline
+          \ce & \dockerce & \dockercesha \\
+          \cassp & \dockercassp & \dockercasspsha \\
+          \fp & \dockerfp & \dockerfpsha \\
+          \go & \dockergo & \dockergosha \\
+          \ioga & \dockerioga & \dockeriogasha \\
+          \np & \dockernp & \dockernpsha \\
+          \oa & \dockeroa & \dockeroasha \\ \hline
+      \end{tabular}}
+\end{table}
+
 \begin{table}[ht]
 \caption{Mean scores of chloroplast genome assemblers}
-\label{tab:scores}
+\label{tab:scores_real}
 \centering

### 2019-06-09 manuscript/sra_ref.tex
Add scripts for generation of sra_table

\textit{Abelmoschus esculentus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5812498}{SRR5812498} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035234}{NC\_035234} & \num{9028889} & \num{2726724478} & \num{151} & Yes \\
\textit{Abies sibirica} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR268415}{ERR268415} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035067}{NC\_035067} & \num{157369451} & \num{31473890200} & \num{100} & NO \\
\textit{Actinidia chinensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR083750}{DRR083750} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_026690}{NC\_026690} & \num{1974014} & \num{574124022} & \num{145} & Yes \\
\textit{Aegilops sharonensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR359708}{ERR359708} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024816}{NC\_024816} & \num{179478974} & \num{36254752748} & \num{101} & NO \\
\textit{Aegilops speltoides} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR424849}{ERR424849} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_022135}{NC\_022135} & \num{173225639} & \num{34991579078} & \num{101} & NO \\
\textit{Aegilops tauschii} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR091633}{SRR091633} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_022133}{NC\_022133} & \num{114178484} & \num{23064053768} & \num{101} & NO \\
\textit{Ajuga reptans} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6940062}{SRR6940062} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023102}{NC\_023102} & \num{16864855} & \num{5059456500} & \num{150} & NO \\
\textit{Aldrovanda vesiculosa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7072768}{SRR7072768} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035416}{NC\_035416} & \num{3510392} & \num{1060138384} & \num{151} & Yes \\
\textit{Allium cepa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1686960}{SRR1686960} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024813}{NC\_024813} & \num{90042453} & \num{27099552373} & \num{150} & Yes \\
\textit{Allium sativum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602598}{SRR5602598} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_031829}{NC\_031829} & \num{1270060} & \num{748290736} & \num{295} & NO \\
\textit{Alloteropsis angusta} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7528995}{SRR7528995} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027951}{NC\_027951} & \num{18695483} & \num{9347741500} & \num{250} & NO \\
\textit{Alloteropsis cimicina} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7529015}{SRR7529015} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027952}{NC\_027952} & \num{118496918} & \num{59248459000} & \num{250} & Yes \\
\textit{Alloteropsis paniculata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR4051980}{SRR4051980} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_032078}{NC\_032078} & \num{4048486} & \num{796542955} & \num{98} & NO \\
\textit{Alloteropsis semialata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7528994}{SRR7528994} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027824}{NC\_027824} & \num{26426678} & \num{13213339000} & \num{250} & Yes \\
\textit{Aloysia citrodora} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602597}{SRR5602597} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034695}{NC\_034695} & \num{1423723} & \num{844386488} & \num{297} & NO \\
\textit{Althaea officinalis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602596}{SRR5602596} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034701}{NC\_034701} & \num{1409711} & \num{833584333} & \num{296} & NO \\
\textit{Amaranthus hypochondriacus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3399331}{SRR3399331} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030770}{NC\_030770} & \num{6509} & \num{3113188} & \num{239} & NO \\
\textit{Ammopiptanthus nanus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6175451}{SRR6175451} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034743}{NC\_034743} & \num{189485569} & \num{56845670700} & \num{150} & NO \\
\textit{Anacardium occidentale} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5812497}{SRR5812497} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035235}{NC\_035235} & \num{27997137} & \num{7055278524} & \num{126} & NO \\
\textit{Apostasia odorata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6037860}{SRR6037860} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030722}{NC\_030722} & \num{48546649} & \num{14563994700} & \num{150} & Yes \\
\textit{Arabidopsis arenicola} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR054584}{DRR054584} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030346}{NC\_030346} & \num{31543276} & \num{6371741752} & \num{101} & Yes \\
\textit{Arabidopsis arenosa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR4128972}{SRR4128972} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029334}{NC\_029334} & \num{129638900} & \num{38891670000} & \num{150} & Yes \\
\textit{Arabidopsis cebennensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2040775}{SRR2040775} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029335}{NC\_029335} & \num{20358302} & \num{4112377004} & \num{101} & Yes \\
\textit{Arabidopsis croatica} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7637319}{SRR7637319} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030347}{NC\_030347} & \num{14265071} & \num{3573463604} & \num{125} & NO \\
\textit{Arabidopsis halleri} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8040824}{SRR8040824} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034366}{NC\_034366} & \num{128303531} & \num{38747666362} & \num{151} & Yes \\
\textit{Arabidopsis lyrata subsp. lyrata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1705621}{SRR1705621} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034379}{NC\_034379} & \num{16771948} & \num{4796683328} & \num{143} & NO \\
\textit{Arabidopsis lyrata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8157563}{SRR8157563} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034365}{NC\_034365} & \num{46678588} & \num{9429074776} & \num{101} & NO \\
\textit{Arabidopsis neglecta} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2040831}{SRR2040831} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030348}{NC\_030348} & \num{52410983} & \num{10482196600} & \num{100} & Yes \\
\textit{Arabidopsis pedemontana} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2040802}{SRR2040802} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029336}{NC\_029336} & \num{28098774} & \num{5675952348} & \num{101} & NO \\
\textit{Arabidopsis petrogena} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2040807}{SRR2040807} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030349}{NC\_030349} & \num{32189424} & \num{6502263648} & \num{101} & Yes \\
\textit{Arabidopsis suecica} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2084154}{SRR2084154} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030350}{NC\_030350} & \num{158377327} & \num{31675465400} & \num{100} & NO \\
\textit{Arabidopsis thaliana} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3340908}{SRR3340908} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_000932}{NC\_000932} & \num{6829274} & \num{4097564400} & \num{300} & NO \\
\textit{Arabidopsis umezawana} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2040810}{SRR2040810} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030351}{NC\_030351} & \num{24335095} & \num{4915689190} & \num{101} & NO \\
\textit{Arabis alpina} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7880736}{SRR7880736} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023367}{NC\_023367} & \num{12603925} & \num{3126123117} & \num{124} & Yes \\
\textit{Artemisia annua} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602595}{SRR5602595} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034683}{NC\_034683} & \num{665200} & \num{330541594} & \num{248} & Yes \\
\textit{Arundo plinii} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR4319202}{SRR4319202} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034652}{NC\_034652} & \num{10180635} & \num{6099219728} & \num{300} & Yes \\
\textit{Asclepias nivea} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR934044}{SRR934044} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_022431}{NC\_022431} & \num{1637178} & \num{311063820} & \num{95} & NO \\
\textit{Asclepias syriaca} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR934060}{SRR934060} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_022432}{NC\_022432} & \num{46704483} & \num{9434305566} & \num{101} & NO \\
\textit{Asparagus officinalis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR056675}{DRR056675} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034777}{NC\_034777} & \num{83276068} & \num{16821765736} & \num{101} & Yes \\
\textit{Astragalus mongholicus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3938254}{SRR3938254} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029828}{NC\_029828} & \num{7500181} & \num{1514903465} & \num{101} & Yes \\
\textit{Avena sativa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6056489}{SRR6056489} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027468}{NC\_027468} & \num{115104823} & \num{57552411500} & \num{250} & NO \\
\textit{Averrhoa carambola} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR2799539}{ERR2799539} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_033350}{NC\_033350} & \num{1023284} & \num{309031768} & \num{151} & NO \\
\textit{Betula nana} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR2026268}{ERR2026268} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_033978}{NC\_033978} & \num{45426355} & \num{13797661576} & \num{152} & NO \\
\textit{Boswellia sacra} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602594}{SRR5602594} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029420}{NC\_029420} & \num{2012947} & \num{1199195198} & \num{298} & Yes \\
\textit{Botryococcus braunii} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3721649}{SRR3721649} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_025545}{NC\_025545} & \num{137313108} & \num{41193932400} & \num{150} & NO \\
\textit{Brachypodium distachyon} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR4159530}{SRR4159530} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_011032}{NC\_011032} & \num{51410001} & \num{15525820302} & \num{151} & Yes \\
\textit{Brassica juncea} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2057910}{SRR2057910} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028272}{NC\_028272} & \num{54890460} & \num{11087872920} & \num{101} & NO \\
\textit{Brassica napus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6856349}{SRR6856349} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_016734}{NC\_016734} & \num{34913922} & \num{10544004444} & \num{151} & NO \\
\textit{Brassica nigra} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2054762}{SRR2054762} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030450}{NC\_030450} & \num{57198732} & \num{11554143864} & \num{101} & Yes \\
\textit{Bupleurum latissimum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6048019}{SRR6048019} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_033346}{NC\_033346} & \num{5702505} & \num{3432908010} & \num{301} & Yes \\
\textit{Cajanus cajan} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR073338}{SRR073338} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_031429}{NC\_031429} & \num{132406303} & \num{26746073206} & \num{101} & Yes \\
\textit{Camelina sativa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2082664}{SRR2082664} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029337}{NC\_029337} & \num{10643512} & \num{2149989424} & \num{101} & Yes \\
\textit{Camellia sinensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5894861}{SRR5894861} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_020019}{NC\_020019} & \num{4975058} & \num{2985034800} & \num{300} & NO \\
\textit{Cannabis sativa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7285294}{SRR7285294} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_026562}{NC\_026562} & \num{162968810} & \num{42761008291} & \num{131} & Yes \\
\textit{Capsella bursa-pastoris} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5412136}{SRR5412136} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_009270}{NC\_009270} & \num{15148015} & \num{9391769300} & \num{310} & NO \\
\textit{Capsella grandiflora} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1508428}{SRR1508428} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028517}{NC\_028517} & \num{98396864} & \num{19679372800} & \num{100} & NO \\
\textit{Capsella rubella} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR636124}{ERR636124} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027693}{NC\_027693} & \num{40236079} & \num{12151295858} & \num{151} & NO \\
\textit{Capsicum annuum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1982881}{SRR1982881} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_018552}{NC\_018552} & \num{10804729} & \num{1966460678} & \num{91} & Yes \\
\textit{Carica papaya} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR019500}{DRR019500} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_010323}{NC\_010323} & \num{103259953} & \num{22510669754} & \num{109} & Yes \\
\textit{Carnegiea gigantea} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5036293}{SRR5036293} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027618}{NC\_027618} & \num{12642777} & \num{7585666200} & \num{300} & NO \\
\textit{Carthamus tinctorius} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2154065}{SRR2154065} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030783}{NC\_030783} & \num{9648870} & \num{1949071740} & \num{101} & NO \\
\textit{Castanea mollissima} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8731963}{SRR8731963} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_014674}{NC\_014674} & \num{118123542} & \num{35437062600} & \num{150} & Yes \\
\textit{Catharanthus roseus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5217671}{SRR5217671} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_021423}{NC\_021423} & \num{23799598} & \num{7139879400} & \num{150} & Yes \\
\textit{Cenchrus americanus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5204424}{SRR5204424} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024171}{NC\_024171} & \num{149257429} & \num{36289690596} & \num{122} & Yes \\
\textit{Centaurea diffusa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2729212}{SRR2729212} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024286}{NC\_024286} & \num{69630024} & \num{13926004800} & \num{100} & Yes \\
\textit{Chenopodium quinoa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5938314}{SRR5938314} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034949}{NC\_034949} & \num{41331617} & \num{20748471734} & \num{251} & NO \\
\textit{Chlamydomonas reinhardtii} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR4235199}{SRR4235199} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_005353}{NC\_005353} & \num{4795246} & \num{1448164292} & \num{151} & Yes \\
\textit{Chlorella sorokiniana} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR4292644}{SRR4292644} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023835}{NC\_023835} & \num{24148422} & \num{4877981244} & \num{101} & NO \\
\textit{Chlorella variabilis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7012756}{SRR7012756} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_015359}{NC\_015359} & \num{16059428} & \num{4837652469} & \num{151} & NO \\
\textit{Chromochloris zofingiensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5310953}{SRR5310953} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029672}{NC\_029672} & \num{63205006} & \num{12641001200} & \num{100} & Yes \\
\textit{Chrysobalanus icaco} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1179655}{SRR1179655} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024061}{NC\_024061} & \num{5544469} & \num{1119982738} & \num{101} & Yes \\
\textit{Cicer arietinum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5183095}{SRR5183095} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_011163}{NC\_011163} & \num{37577869} & \num{6764016420} & \num{90} & Yes \\
\textit{Cinnamomum verum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5812493}{SRR5812493} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035236}{NC\_035236} & \num{4931460} & \num{1489300920} & \num{151} & NO \\
\textit{Citrullus lanatus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8523014}{SRR8523014} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_032008}{NC\_032008} & \num{27574511} & \num{16544706600} & \num{300} & Yes \\
\textit{Citrus aurantiifolia} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6188466}{SRR6188466} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024929}{NC\_024929} & \num{132426000} & \num{26485200000} & \num{100} & NO \\
\textit{Citrus limon} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602593}{SRR5602593} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034690}{NC\_034690} & \num{1362792} & \num{666398607} & \num{244} & NO \\
\textit{Citrus maxima} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3407098}{SRR3407098} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034290}{NC\_034290} & \num{149418786} & \num{47814011520} & \num{160} & NO \\
\textit{Citrus reticulata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3747540}{SRR3747540} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034671}{NC\_034671} & \num{53225257} & \num{15967577100} & \num{150} & Yes \\
\textit{Citrus sinensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3927459}{SRR3927459} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_008334}{NC\_008334} & \num{46781458} & \num{14034437400} & \num{150} & NO \\
\textit{Coffea arabica} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602572}{SRR5602572} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_008535}{NC\_008535} & \num{2532608} & \num{1494738062} & \num{295} & NO \\
\textit{Coffea canephora} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR321701}{ERR321701} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030053}{NC\_030053} & \num{33362762} & \num{7206356592} & \num{108} & Yes \\
\textit{Corymbia torelliana} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR4063804}{SRR4063804} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028410}{NC\_028410} & \num{66804809} & \num{20041442700} & \num{150} & Yes \\
\textit{Couepia guianensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1179648}{SRR1179648} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024063}{NC\_024063} & \num{7411159} & \num{1497054118} & \num{101} & Yes \\
\textit{Cucumis melo subsp. melo} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR246536}{ERR246536} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_015983}{NC\_015983} & \num{33207205} & \num{10094990320} & \num{152} & NO \\
\textit{Cucumis sativus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6490504}{SRR6490504} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_007144}{NC\_007144} & \num{35348114} & \num{10646772194} & \num{151} & Yes \\
\textit{Cunninghamia lanceolata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR2799542}{ERR2799542} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_021437}{NC\_021437} & \num{1062614} & \num{320909428} & \num{151} & Yes \\
\textit{Cymbidium ensifolium} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6117755}{SRR6117755} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028525}{NC\_028525} & \num{12766736} & \num{7685575072} & \num{301} & Yes \\
\textit{Cymbidium kanran} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6117756}{SRR6117756} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029711}{NC\_029711} & \num{5534224} & \num{3331602848} & \num{301} & NO \\
\textit{Cymbidium lancifolium} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6117757}{SRR6117757} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029712}{NC\_029712} & \num{5856776} & \num{3525779152} & \num{301} & NO \\
\textit{Cymbidium macrorhizon} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6117754}{SRR6117754} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029713}{NC\_029713} & \num{5777841} & \num{3478260282} & \num{301} & NO \\
\textit{Cynodon dactylon} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5457035}{SRR5457035} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034680}{NC\_034680} & \num{121672} & \num{65496192} & \num{269} & Yes \\
\textit{Cytinus hypocistis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR964904}{ERR964904} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_031150}{NC\_031150} & \num{8664415} & \num{1750211830} & \num{101} & NO \\
\textit{Dactylis glomerata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5236602}{SRR5236602} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027473}{NC\_027473} & \num{131404213} & \num{39421263900} & \num{150} & NO \\
\textit{Daucus carota} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7601255}{SRR7601255} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_008325}{NC\_008325} & \num{208788541} & \num{63054139382} & \num{151} & Yes \\
\textit{Dendrobium aphyllum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3932123}{SRR3932123} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035322}{NC\_035322} & \num{24390720} & \num{7317216000} & \num{150} & Yes \\
\textit{Dendrobium chrysanthum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3932147}{SRR3932147} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035336}{NC\_035336} & \num{12371613} & \num{3711483900} & \num{150} & Yes \\
\textit{Dendrobium chrysotoxum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3932141}{SRR3932141} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028549}{NC\_028549} & \num{12969805} & \num{3890941500} & \num{150} & Yes \\
\textit{Dendrobium crepidatum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3932124}{SRR3932124} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035331}{NC\_035331} & \num{10220355} & \num{3066106500} & \num{150} & NO \\
\textit{Dendrobium denneanum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3932144}{SRR3932144} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035324}{NC\_035324} & \num{11765400} & \num{3529620000} & \num{150} & Yes \\
\textit{Dendrobium falconeri} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3932139}{SRR3932139} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035326}{NC\_035326} & \num{11326112} & \num{3397833600} & \num{150} & NO \\
\textit{Dendrobium nobile} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3932122}{SRR3932122} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029456}{NC\_029456} & \num{11410037} & \num{3423011100} & \num{150} & Yes \\
\textit{Dendrobium parishii} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3932128}{SRR3932128} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035339}{NC\_035339} & \num{14183700} & \num{4255110000} & \num{150} & NO \\
\textit{Dendrobium pendulum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3932138}{SRR3932138} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029705}{NC\_029705} & \num{11357541} & \num{3407262300} & \num{150} & Yes \\
\textit{Dendrobium primulinum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3932120}{SRR3932120} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035321}{NC\_035321} & \num{10864205} & \num{3259261500} & \num{150} & NO \\
\textit{Dendrobium wardianum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3932135}{SRR3932135} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035329}{NC\_035329} & \num{9367500} & \num{2810250000} & \num{150} & Yes \\
\textit{Deschampsia antarctica} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1158316}{SRR1158316} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023533}{NC\_023533} & \num{153346825} & \num{30976058650} & \num{101} & Yes \\
\textit{Digitalis lanata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602573}{SRR5602573} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034688}{NC\_034688} & \num{1257524} & \num{730269772} & \num{290} & NO \\
\textit{Dionaea muscipula} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7072324}{SRR7072324} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035417}{NC\_035417} & \num{16215933} & \num{4897211766} & \num{151} & NO \\
\textit{Dioscorea rotundata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR063110}{DRR063110} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024170}{NC\_024170} & \num{18637125} & \num{9295053322} & \num{249} & NO \\
\textit{Dioscorea villosa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602590}{SRR5602590} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034686}{NC\_034686} & \num{1447023} & \num{858275557} & \num{297} & Yes \\
\textit{Diospyros lotus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1560932}{SRR1560932} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030786}{NC\_030786} & \num{8240803} & \num{1648160600} & \num{100} & Yes \\
\textit{Drosera erythrorhiza} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7072766}{SRR7072766} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035241}{NC\_035241} & \num{5832398} & \num{1761384196} & \num{151} & NO \\
\textit{Drosera regia} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7072322}{SRR7072322} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035415}{NC\_035415} & \num{1341304} & \num{405073808} & \num{151} & NO \\
\textit{Dunaliella salina} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3923695}{SRR3923695} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_016732}{NC\_016732} & \num{164049728} & \num{49214918400} & \num{150} & Yes \\
\textit{Echinacea angustifolia} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602579}{SRR5602579} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034324}{NC\_034324} & \num{1669371} & \num{878253310} & \num{263} & Yes \\
\textit{Echinacea atrorubens} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602578}{SRR5602578} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034323}{NC\_034323} & \num{961923} & \num{472814810} & \num{246} & NO \\
\textit{Echinacea laevigata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602581}{SRR5602581} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034322}{NC\_034322} & \num{1099311} & \num{545173423} & \num{248} & NO \\
\textit{Echinacea pallida} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602580}{SRR5602580} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034321}{NC\_034321} & \num{2039307} & \num{832368111} & \num{204} & Yes \\
\textit{Echinacea paradoxa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602575}{SRR5602575} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034320}{NC\_034320} & \num{3101240} & \num{1692835034} & \num{273} & NO \\
\textit{Echinacea purpurea} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602574}{SRR5602574} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034327}{NC\_034327} & \num{5197414} & \num{2531457606} & \num{244} & Yes \\
\textit{Echinacea sanguinea} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602577}{SRR5602577} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034328}{NC\_034328} & \num{4911880} & \num{2224965457} & \num{226} & Yes \\
\textit{Echinacea speciosa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602576}{SRR5602576} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034325}{NC\_034325} & \num{970715} & \num{483247492} & \num{249} & NO \\
\textit{Echinacea tennesseensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602587}{SRR5602587} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034326}{NC\_034326} & \num{907178} & \num{434759190} & \num{240} & NO \\
\textit{Echinochloa crus-galli} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5920285}{SRR5920285} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028719}{NC\_028719} & \num{203467365} & \num{50866841250} & \num{125} & NO \\
\textit{Echinochloa oryzicola} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5902661}{SRR5902661} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024643}{NC\_024643} & \num{129112810} & \num{32278202500} & \num{125} & Yes \\
\textit{Elaeis guineensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR276848}{ERR276848} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_017602}{NC\_017602} & \num{143340222} & \num{28954724844} & \num{101} & Yes \\
\textit{Eleutherococcus senticosus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602586}{SRR5602586} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_016430}{NC\_016430} & \num{424930} & \num{211982751} & \num{249} & NO \\
\textit{Epimedium koreanum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8534306}{SRR8534306} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029943}{NC\_029943} & \num{8308432} & \num{1262881664} & \num{76} & NO \\
\textit{Epimedium sagittatum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8275049}{SRR8275049} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029428}{NC\_029428} & \num{4141262} & \num{629471824} & \num{76} & NO \\
\textit{Eragrostis tef} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1463402}{SRR1463402} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029413}{NC\_029413} & \num{85023843} & \num{14454053310} & \num{85} & NO \\
\textit{Eriobotrya japonica} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602604}{SRR5602604} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034639}{NC\_034639} & \num{1852832} & \num{918799928} & \num{248} & Yes \\
\textit{Erodium chrysanthum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR576525}{SRR576525} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027065}{NC\_027065} & \num{31570835} & \num{6314167000} & \num{100} & NO \\
\textit{Erodium texanum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR2799526}{ERR2799526} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_014569}{NC\_014569} & \num{1158815} & \num{349962130} & \num{151} & Yes \\
\textit{Erythranthe lutea} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5307620}{SRR5307620} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030212}{NC\_030212} & \num{10000000} & \num{2000000000} & \num{100} & Yes \\
\textit{Eucalyptus grandis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1392700}{SRR1392700} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_014570}{NC\_014570} & \num{327608152} & \num{98282445600} & \num{150} & Yes \\
\textit{Euphorbia esula} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6355713}{SRR6355713} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_033910}{NC\_033910} & \num{65533012} & \num{13106602400} & \num{100} & NO \\
\textit{Fagopyrum tataricum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5433722}{SRR5433722} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027161}{NC\_027161} & \num{15222050} & \num{6981058500} & \num{229} & Yes \\
\textit{Festuca arundinacea} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6885354}{SRR6885354} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_011713}{NC\_011713} & \num{6197329} & \num{3085916062} & \num{249} & NO \\
\textit{Ficus carica} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5678803}{SRR5678803} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035237}{NC\_035237} & \num{26827466} & \num{15073339221} & \num{281} & NO \\
\textit{Ficus racemosa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1405699}{SRR1405699} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028185}{NC\_028185} & \num{31025867} & \num{4715931784} & \num{76} & NO \\
\textit{Foeniculum vulgare} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8690417}{SRR8690417} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029469}{NC\_029469} & \num{3715298} & \num{750490196} & \num{101} & NO \\
\textit{Fragaria chiloensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1612828}{SRR1612828} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_019601}{NC\_019601} & \num{43583617} & \num{10460068080} & \num{120} & NO \\
\textit{Fragaria vesca subsp. bracteata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR866156}{SRR866156} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_018766}{NC\_018766} & \num{4311362} & \num{819158780} & \num{95} & Yes \\
\textit{Fragaria virginiana} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602605}{SRR5602605} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_019602}{NC\_019602} & \num{1199457} & \num{708866398} & \num{295} & Yes \\
\textit{Francoa sonchifolia} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR576529}{SRR576529} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_021101}{NC\_021101} & \num{32806903} & \num{6561380600} & \num{100} & NO \\
\textit{Geranium maderense} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR2799530}{ERR2799530} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029999}{NC\_029999} & \num{1031538} & \num{311524476} & \num{151} & Yes \\
\textit{Ginkgo biloba} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3089810}{SRR3089810} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_016986}{NC\_016986} & \num{10164078} & \num{2541019500} & \num{125} & NO \\
\textit{Glycine dolichocarpa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1174380}{SRR1174380} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_021648}{NC\_021648} & \num{44850853} & \num{9059872306} & \num{101} & NO \\
\textit{Glycine max} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6796784}{SRR6796784} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_007942}{NC\_007942} & \num{70339371} & \num{21242490042} & \num{151} & NO \\
\textit{Glycine soja} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7725010}{SRR7725010} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_022868}{NC\_022868} & \num{131827844} & \num{39548353200} & \num{150} & Yes \\
\textit{Glycine syndetika} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1176843}{SRR1176843} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_021650}{NC\_021650} & \num{51528078} & \num{10408671756} & \num{101} & NO \\
\textit{Glycine tomentella} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6823488}{SRR6823488} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_021636}{NC\_021636} & \num{265989287} & \num{131814519905} & \num{248} & NO \\
\textit{Glycyrrhiza glabra} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8690419}{SRR8690419} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024038}{NC\_024038} & \num{4940810} & \num{998043620} & \num{101} & Yes \\
\textit{Glyptostrobus pensilis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR2799543}{ERR2799543} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_031354}{NC\_031354} & \num{1061851} & \num{320679002} & \num{151} & NO \\
\textit{Gnetum gnemon} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR268420}{ERR268420} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_026301}{NC\_026301} & \num{146146748} & \num{29229349600} & \num{100} & NO \\
\textit{Gossypium anomalum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3560153}{SRR3560153} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023213}{NC\_023213} & \num{152611035} & \num{30827429070} & \num{101} & NO \\
\textit{Gossypium arboreum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2012734}{SRR2012734} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_016712}{NC\_016712} & \num{8946554} & \num{5385825508} & \num{301} & NO \\
\textit{Gossypium aridum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8136263}{SRR8136263} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_033396}{NC\_033396} & \num{158194517} & \num{31638903400} & \num{100} & Yes \\
\textit{Gossypium armourianum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8136258}{SRR8136258} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_033400}{NC\_033400} & \num{155005858} & \num{31001171600} & \num{100} & NO \\
\textit{Gossypium barbadense} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8627357}{SRR8627357} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_008641}{NC\_008641} & \num{159103409} & \num{79869911318} & \num{251} & NO \\
\textit{Gossypium bickii} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3560187}{SRR3560187} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023214}{NC\_023214} & \num{179898006} & \num{35979601200} & \num{100} & Yes \\
\textit{Gossypium darwinii} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8545538}{SRR8545538} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_016670}{NC\_016670} & \num{440216228} & \num{132945300856} & \num{151} & NO \\
\textit{Gossypium davidsonii} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6334584}{SRR6334584} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_033395}{NC\_033395} & \num{117719642} & \num{35315892600} & \num{150} & NO \\
\textit{Gossypium gossypioides} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3560148}{SRR3560148} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_017894}{NC\_017894} & \num{153288210} & \num{30657642000} & \num{100} & NO \\
\textit{Gossypium harknessii} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8136257}{SRR8136257} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_033333}{NC\_033333} & \num{183115691} & \num{36431624874} & \num{99} & NO \\
\textit{Gossypium herbaceum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2012721}{SRR2012721} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023215}{NC\_023215} & \num{12440256} & \num{7489034112} & \num{301} & NO \\
\textit{Gossypium hirsutum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3560152}{SRR3560152} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_007944}{NC\_007944} & \num{4487735} & \num{2205113705} & \num{246} & Yes \\
\textit{Gossypium klotzschianum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8136264}{SRR8136264} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_033394}{NC\_033394} & \num{161773353} & \num{32354670600} & \num{100} & NO \\
\textit{Gossypium longicalyx} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR617704}{SRR617704} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023216}{NC\_023216} & \num{534258839} & \num{107920285478} & \num{101} & Yes \\
\textit{Gossypium mustelinum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8727328}{SRR8727328} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_016711}{NC\_016711} & \num{158115596} & \num{79374029192} & \num{251} & NO \\
\textit{Gossypium raimondii} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR1449077}{ERR1449077} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_016668}{NC\_016668} & \num{21720967} & \num{6559732034} & \num{151} & NO \\
\textit{Gossypium somalense} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3560160}{SRR3560160} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_018110}{NC\_018110} & \num{69625198} & \num{13925039600} & \num{100} & Yes \\
\textit{Gossypium sturtianum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3560184}{SRR3560184} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023218}{NC\_023218} & \num{95466009} & \num{19093201800} & \num{100} & NO \\
\textit{Gossypium thurberi} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8076131}{SRR8076131} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_015204}{NC\_015204} & \num{181003659} & \num{36200731800} & \num{100} & Yes \\
\textit{Gossypium tomentosum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6334536}{SRR6334536} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_016690}{NC\_016690} & \num{138849836} & \num{41654950800} & \num{150} & NO \\
\textit{Gossypium trilobum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3560157}{SRR3560157} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_033397}{NC\_033397} & \num{52816676} & \num{10563335200} & \num{100} & NO \\
\textit{Gossypium turneri} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8136254}{SRR8136254} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_026835}{NC\_026835} & \num{124131681} & \num{37239504300} & \num{150} & NO \\
\textit{Haberlea rhodopensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR4428742}{SRR4428742} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_031852}{NC\_031852} & \num{8365536} & \num{1673107200} & \num{100} & NO \\
\textit{Haplostachys haplostachya} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3170741}{SRR3170741} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029819}{NC\_029819} & \num{251836} & \num{76054472} & \num{151} & NO \\
\textit{Helianthus annuus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR825830}{SRR825830} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_007977}{NC\_007977} & \num{57562191} & \num{13124179548} & \num{114} & Yes \\
\textit{Helianthus argophyllus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2155086}{SRR2155086} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030275}{NC\_030275} & \num{12784471} & \num{2582463142} & \num{101} & NO \\
\textit{Helianthus debilis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5907791}{SRR5907791} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030173}{NC\_030173} & \num{7323836} & \num{1464767200} & \num{100} & NO \\
\textit{Helianthus divaricatus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3492253}{SRR3492253} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023109}{NC\_023109} & \num{13246221} & \num{2649244200} & \num{100} & NO \\
\textit{Helianthus giganteus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5907716}{SRR5907716} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023107}{NC\_023107} & \num{20626828} & \num{4125365600} & \num{100} & NO \\
\textit{Helianthus grosseserratus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5907715}{SRR5907715} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023108}{NC\_023108} & \num{23480167} & \num{4696033400} & \num{100} & Yes \\
\textit{Heteropogon triticeus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5446059}{SRR5446059} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035025}{NC\_035025} & \num{14302809} & \num{4290842700} & \num{150} & Yes \\
\textit{Hibiscus syriacus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1265942}{SRR1265942} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_026909}{NC\_026909} & \num{25909841} & \num{5233787882} & \num{101} & NO \\
\textit{Hirtella physophora} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1179646}{SRR1179646} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024066}{NC\_024066} & \num{18840660} & \num{3768132000} & \num{100} & Yes \\
\textit{Hirtella racemosa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1179649}{SRR1179649} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024060}{NC\_024060} & \num{8044385} & \num{1624965770} & \num{101} & Yes \\
\textit{Hordeum vulgare subsp. vulgare} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR490932}{SRR490932} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_008590}{NC\_008590} & \num{262845212} & \num{65711303000} & \num{125} & NO \\
\textit{Humulus lupulus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8690418}{SRR8690418} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028032}{NC\_028032} & \num{6541057} & \num{1321293514} & \num{101} & Yes \\
\textit{Hydrastis canadensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602606}{SRR5602606} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034702}{NC\_034702} & \num{1356811} & \num{671823274} & \num{248} & Yes \\
\textit{Hyoscyamus niger} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1508958}{SRR1508958} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024261}{NC\_024261} & \num{21000000} & \num{4200000000} & \num{100} & Yes \\
\textit{Hypseocharis bilobata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR576531}{SRR576531} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023260}{NC\_023260} & \num{32280852} & \num{6456170400} & \num{100} & NO \\
\textit{Illicium anisatum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602608}{SRR5602608} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034703}{NC\_034703} & \num{3195974} & \num{961644484} & \num{150} & NO \\
\textit{Illicium floridanum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602609}{SRR5602609} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034685}{NC\_034685} & \num{1929116} & \num{1141799529} & \num{296} & NO \\
\textit{Illicium henryi} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602610}{SRR5602610} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034699}{NC\_034699} & \num{1240196} & \num{611286832} & \num{246} & NO \\
\textit{Illicium verum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602607}{SRR5602607} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034689}{NC\_034689} & \num{2752799} & \num{828427309} & \num{150} & NO \\
\textit{Ipomoea batatas} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7868503}{SRR7868503} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_026703}{NC\_026703} & \num{55433003} & \num{27827367506} & \num{251} & NO \\
\textit{Ipomoea nil} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR013917}{DRR013917} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_031159}{NC\_031159} & \num{149492354} & \num{44847706200} & \num{150} & NO \\
\textit{Ipomoea trifida} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6667669}{SRR6667669} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034670}{NC\_034670} & \num{148892802} & \num{47645696640} & \num{160} & NO \\
\textit{Jasminum sambac} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602611}{SRR5602611} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034694}{NC\_034694} & \num{4487750} & \num{2661867968} & \num{297} & NO \\
\textit{Jasminum tortuosum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602601}{SRR5602601} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034691}{NC\_034691} & \num{1468745} & \num{726257599} & \num{247} & NO \\
\textit{Jatropha curcas} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR001794}{DRR001794} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_012224}{NC\_012224} & \num{99881947} & \num{15182055944} & \num{76} & NO \\
\textit{Juglans regia} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2057822}{SRR2057822} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028617}{NC\_028617} & \num{111991280} & \num{33821366560} & \num{151} & Yes \\
\textit{Juniperus cedrus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1145775}{SRR1145775} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028190}{NC\_028190} & \num{46193335} & \num{9238667000} & \num{100} & Yes \\
\textit{Juniperus communis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR268423}{ERR268423} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035068}{NC\_035068} & \num{472881723} & \num{94576344600} & \num{100} & NO \\
\textit{Lactuca sativa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8736654}{SRR8736654} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_007578}{NC\_007578} & \num{267081494} & \num{80124448200} & \num{150} & Yes \\
\textit{Lathyrus sativus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR413118}{ERR413118} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_014063}{NC\_014063} & \num{3876258} & \num{783004116} & \num{101} & NO \\
\textit{Laurus nobilis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602602}{SRR5602602} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034700}{NC\_034700} & \num{1774932} & \num{880729409} & \num{248} & Yes \\
\textit{Lavandula angustifolia} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5757713}{SRR5757713} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029370}{NC\_029370} & \num{37808338} & \num{11418118076} & \num{151} & NO \\
\textit{Lens culinaris} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR413115}{ERR413115} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027152}{NC\_027152} & \num{6895415} & \num{1392873830} & \num{101} & Yes \\
\textit{Licania alba} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1179652}{SRR1179652} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024064}{NC\_024064} & \num{6960753} & \num{1406072106} & \num{101} & Yes \\
\textit{Licania sprucei} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1179651}{SRR1179651} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024065}{NC\_024065} & \num{6492846} & \num{1311554892} & \num{101} & NO \\
\textit{Lilium tsingtauense} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1265940}{SRR1265940} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027675}{NC\_027675} & \num{9313992} & \num{1881426384} & \num{101} & NO \\
\textit{Liriodendron tulipifera} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR4240953}{SRR4240953} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_008326}{NC\_008326} & \num{4000000} & \num{1208000000} & \num{151} & Yes \\
\textit{Litchi chinensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5812499}{SRR5812499} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035238}{NC\_035238} & \num{6720070} & \num{2029461140} & \num{151} & NO \\
\textit{Lotus japonicus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8115522}{SRR8115522} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_002694}{NC\_002694} & \num{175495827} & \num{52999739754} & \num{151} & Yes \\
\textit{Ludisia discolor} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3484539}{SRR3484539} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030540}{NC\_030540} & \num{14073966} & \num{8472527532} & \num{301} & Yes \\
\textit{Macadamia integrifolia} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR1397263}{ERR1397263} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_025288}{NC\_025288} & \num{28756805} & \num{8684555110} & \num{151} & Yes \\
\textit{Magnolia biondii} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602588}{SRR5602588} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034687}{NC\_034687} & \num{1600124} & \num{953606691} & \num{298} & NO \\
\textit{Magnolia denudata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602603}{SRR5602603} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_018357}{NC\_018357} & \num{1640979} & \num{978183192} & \num{298} & Yes \\
\textit{Magnolia officinalis subsp. biloba} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602589}{SRR5602589} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_020317}{NC\_020317} & \num{1744003} & \num{1040030660} & \num{298} & NO \\
\textit{Malus prunifolia} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3571175}{SRR3571175} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_031163}{NC\_031163} & \num{22532714} & \num{6804879628} & \num{151} & NO \\
\textit{Mangifera indica} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5812496}{SRR5812496} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035239}{NC\_035239} & \num{9989213} & \num{3016742326} & \num{151} & Yes \\
\textit{Manihot esculenta} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2847384}{SRR2847384} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_010433}{NC\_010433} & \num{121616638} & \num{54727487100} & \num{225} & Yes \\
\textit{Mankyua chejuensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7630500}{SRR7630500} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_017006}{NC\_017006} & \num{7279904} & \num{4382502208} & \num{301} & Yes \\
\textit{Marchantia polymorpha} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR396657}{SRR396657} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_001319}{NC\_001319} & \num{123055214} & \num{36916564200} & \num{150} & NO \\
\textit{Medicago truncatula} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1028837}{SRR1028837} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_003119}{NC\_003119} & \num{29663436} & \num{8958357672} & \num{151} & NO \\
\textit{Melianthus villosus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR576532}{SRR576532} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023256}{NC\_023256} & \num{31695892} & \num{6339178400} & \num{100} & Yes \\
\textit{Mentha longifolia} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3204556}{SRR3204556} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_032054}{NC\_032054} & \num{67215785} & \num{13577588570} & \num{101} & Yes \\
\textit{Miscanthus sacchariflorus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR559245}{SRR559245} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028720}{NC\_028720} & \num{73073855} & \num{22068304210} & \num{151} & NO \\
\textit{Miscanthus sinensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR4028761}{SRR4028761} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028721}{NC\_028721} & \num{34003586} & \num{10269082972} & \num{151} & Yes \\
\textit{Mitragyna speciosa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602600}{SRR5602600} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034698}{NC\_034698} & \num{1327534} & \num{658729522} & \num{248} & NO \\
\textit{Monsonia emarginata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR2799532}{ERR2799532} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029694}{NC\_029694} & \num{1089971} & \num{329171242} & \num{151} & Yes \\
\textit{Nelumbo lutea} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5115287}{SRR5115287} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_015605}{NC\_015605} & \num{45729480} & \num{11432370000} & \num{125} & Yes \\
\textit{Nelumbo nucifera} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7159815}{SRR7159815} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_025339}{NC\_025339} & \num{30517828} & \num{9155348400} & \num{150} & NO \\
\textit{Nicotiana otophora} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1171700}{SRR1171700} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_032724}{NC\_032724} & \num{67460219} & \num{13626964238} & \num{101} & NO \\
\textit{Nicotiana tabacum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR954964}{SRR954964} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_001879}{NC\_001879} & \num{792406088} & \num{160066029776} & \num{101} & Yes \\
\textit{Nicotiana undulata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8173251}{SRR8173251} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_016068}{NC\_016068} & \num{223212812} & \num{45088988024} & \num{101} & Yes \\
\textit{Ocimum basilicum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6940087}{SRR6940087} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035143}{NC\_035143} & \num{32031837} & \num{9609551100} & \num{150} & NO \\
\textit{Oenothera biennis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1771524}{SRR1771524} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_010361}{NC\_010361} & \num{13426811} & \num{2658508578} & \num{99} & Yes \\
\textit{Oenothera villaricae} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1771538}{SRR1771538} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030532}{NC\_030532} & \num{3055389} & \num{611077800} & \num{100} & NO \\
\textit{Olea europaea subsp. europaea} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR375848}{ERR375848} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_015401}{NC\_015401} & \num{27590779} & \num{16729938945} & \num{303} & NO \\
\textit{Oryza australiensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR056778}{DRR056778} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024608}{NC\_024608} & \num{69350090} & \num{20805027000} & \num{150} & NO \\
\textit{Oryza barthii} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7341625}{SRR7341625} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027460}{NC\_027460} & \num{55484960} & \num{27742480000} & \num{250} & Yes \\
\textit{Oryza brachyantha} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR053294}{DRR053294} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030596}{NC\_030596} & \num{10715682} & \num{3214704600} & \num{150} & Yes \\
\textit{Oryza glaberrima} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7341626}{SRR7341626} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024175}{NC\_024175} & \num{62571390} & \num{31285695000} & \num{250} & NO \\
\textit{Oryza glumipatula} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR057991}{DRR057991} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027461}{NC\_027461} & \num{23451341} & \num{7035402300} & \num{150} & Yes \\
\textit{Oryza longiglumis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR056658}{DRR056658} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034763}{NC\_034763} & \num{50656466} & \num{15196939800} & \num{150} & Yes \\
\textit{Oryza longistaminata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR058031}{DRR058031} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027462}{NC\_027462} & \num{17927163} & \num{5378148900} & \num{150} & Yes \\
\textit{Oryza meridionalis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR058012}{DRR058012} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_016927}{NC\_016927} & \num{19143143} & \num{5742942900} & \num{150} & NO \\
\textit{Oryza meyeriana} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR056670}{DRR056670} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034765}{NC\_034765} & \num{41115373} & \num{12334611900} & \num{150} & NO \\
\textit{Oryza minuta} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR385916}{ERR385916} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030298}{NC\_030298} & \num{28110596} & \num{6746543040} & \num{120} & Yes \\
\textit{Oryza officinalis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR000604}{DRR000604} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027463}{NC\_027463} & \num{25866032} & \num{5690527040} & \num{110} & Yes \\
\textit{Oryza punctata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1264539}{SRR1264539} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027676}{NC\_027676} & \num{8000000} & \num{1600000000} & \num{100} & NO \\
\textit{Oryza ridleyi} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR056663}{DRR056663} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034764}{NC\_034764} & \num{91020902} & \num{27306270600} & \num{150} & Yes \\
\textit{Oryza rufipogon} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6220521}{SRR6220521} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_017835}{NC\_017835} & \num{26511359} & \num{8006430418} & \num{151} & NO \\
\textit{Oryza sativa Indica Group} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR553489}{SRR553489} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027678}{NC\_027678} & \num{4956305} & \num{2488065110} & \num{251} & NO \\
\textit{Oryza sativa Japonica Group} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR547959}{SRR547959} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_001320}{NC\_001320} & \num{5918441} & \num{2971057382} & \num{251} & NO \\
\textit{Oryza sativa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR2696318}{ERR2696318} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_031333}{NC\_031333} & \num{6588721} & \num{3947278012} & \num{300} & Yes \\
\textit{Ostreococcus tauri} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR4020477}{SRR4020477} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_008289}{NC\_008289} & \num{89130001} & \num{17826000200} & \num{100} & NO \\
\textit{Ostrya rehderiana} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8302715}{SRR8302715} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028349}{NC\_028349} & \num{33211296} & \num{8145137640} & \num{123} & NO \\
\textit{Panax ginseng} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5533645}{SRR5533645} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_006290}{NC\_006290} & \num{105595137} & \num{37246922641} & \num{176} & Yes \\
\textit{Panax japonicus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6512791}{SRR6512791} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028703}{NC\_028703} & \num{71312188} & \num{21020452500} & \num{147} & NO \\
\textit{Panax notoginseng} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6512795}{SRR6512795} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_026447}{NC\_026447} & \num{7185943} & \num{2100564900} & \num{146} & NO \\
\textit{Panax quinquefolius} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6512793}{SRR6512793} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027456}{NC\_027456} & \num{20952746} & \num{6152880600} & \num{147} & NO \\
\textit{Panax stipuleanatus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6512796}{SRR6512796} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030598}{NC\_030598} & \num{13610275} & \num{3922500000} & \num{144} & Yes \\
\textit{Panicum capillare} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR485871}{SRR485871} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030493}{NC\_030493} & \num{219099842} & \num{43819968400} & \num{100} & Yes \\
\textit{Panicum miliaceum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6650558}{SRR6650558} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029732}{NC\_029732} & \num{159892965} & \num{80266268430} & \num{251} & Yes \\
\textit{Panicum virgatum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8440701}{SRR8440701} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_015990}{NC\_015990} & \num{92006218} & \num{46187121436} & \num{251} & NO \\
\textit{Papaver somniferum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6780757}{SRR6780757} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029434}{NC\_029434} & \num{480182430} & \num{252410803808} & \num{263} & NO \\
\textit{Parinari campestris} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1179645}{SRR1179645} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024067}{NC\_024067} & \num{5970365} & \num{1206013730} & \num{101} & NO \\
\textit{Paulownia tomentosa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6940033}{SRR6940033} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_031436}{NC\_031436} & \num{29457173} & \num{8837151900} & \num{150} & NO \\
\textit{Pelargonium citronellum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR576534}{SRR576534} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_031194}{NC\_031194} & \num{30750530} & \num{6150106000} & \num{100} & Yes \\
\textit{Pelargonium cotyledonis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR2799534}{ERR2799534} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028052}{NC\_028052} & \num{995842} & \num{300744284} & \num{151} & NO \\
\textit{Pelargonium x hortorum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR576536}{SRR576536} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_008454}{NC\_008454} & \num{31358909} & \num{6271781800} & \num{100} & NO \\
\textit{Perilla frutescens} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6940083}{SRR6940083} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030756}{NC\_030756} & \num{34758180} & \num{10427454000} & \num{150} & Yes \\
\textit{Phaseolus vulgaris} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5807695}{SRR5807695} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_009259}{NC\_009259} & \num{17399674} & \num{5289500896} & \num{152} & Yes \\
\textit{Phoenix dactylifera} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2518264}{SRR2518264} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_013991}{NC\_013991} & \num{89471372} & \num{16641675192} & \num{93} & NO \\
\textit{Phyllostachys edulis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8245858}{SRR8245858} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_015817}{NC\_015817} & \num{196487218} & \num{58946165400} & \num{150} & NO \\
\textit{Physcomitrella patens} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR1638191}{ERR1638191} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_005087}{NC\_005087} & \num{97932953} & \num{29379885900} & \num{150} & Yes \\
\textit{Picea abies} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR1727007}{ERR1727007} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_021456}{NC\_021456} & \num{2556898} & \num{644338296} & \num{126} & NO \\
\textit{Picea asperata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR1735493}{ERR1735493} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_032367}{NC\_032367} & \num{1862931} & \num{469458612} & \num{126} & Yes \\
\textit{Picea crassifolia} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR1735613}{ERR1735613} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_032366}{NC\_032366} & \num{1706374} & \num{430006248} & \num{126} & NO \\
\textit{Picea glauca} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR869482}{SRR869482} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028594}{NC\_028594} & \num{19568105} & \num{19568105000} & \num{500} & Yes \\
\textit{Picea jezoensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR1795324}{ERR1795324} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029374}{NC\_029374} & \num{2499244} & \num{629809488} & \num{126} & Yes \\
\textit{Picea sitchensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5028182}{SRR5028182} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_011152}{NC\_011152} & \num{28752590} & \num{14376295000} & \num{250} & Yes \\
\textit{Pimenta dioica} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602585}{SRR5602585} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034684}{NC\_034684} & \num{1821150} & \num{1068525583} & \num{293} & Yes \\
\textit{Pinus lambertiana} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2026990}{SRR2026990} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_011156}{NC\_011156} & \num{165888035} & \num{49959743872} & \num{151} & Yes \\
\textit{Pinus massoniana} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7666034}{SRR7666034} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_021439}{NC\_021439} & \num{6755123} & \num{2026536900} & \num{150} & NO \\
\textit{Pinus sylvestris} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR268429}{ERR268429} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035069}{NC\_035069} & \num{162706395} & \num{32541279000} & \num{100} & NO \\
\textit{Pinus taeda} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1049756}{SRR1049756} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_021440}{NC\_021440} & \num{4969100} & \num{2534241000} & \num{255} & NO \\
\textit{Piper auritum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602592}{SRR5602592} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034697}{NC\_034697} & \num{1951892} & \num{964587352} & \num{247} & NO \\
\textit{Piper nigrum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602591}{SRR5602591} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034692}{NC\_034692} & \num{1342936} & \num{797054024} & \num{297} & NO \\
\textit{Pistacia vera} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR4453367}{SRR4453367} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034998}{NC\_034998} & \num{62397980} & \num{18719394000} & \num{150} & Yes \\
\textit{Pisum sativum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6702454}{SRR6702454} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_014057}{NC\_014057} & \num{144850725} & \num{29259846450} & \num{101} & NO \\
\textit{Podococcus barteri} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR2120220}{SRR2120220} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027276}{NC\_027276} & \num{2453} & \num{671984} & \num{137} & Yes \\
\textit{Populus alba} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3678826}{SRR3678826} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_008235}{NC\_008235} & \num{40869133} & \num{8255564866} & \num{101} & Yes \\
\textit{Populus tremula x Populus alba} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1653109}{SRR1653109} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028504}{NC\_028504} & \num{9920342} & \num{2003909084} & \num{101} & NO \\
\textit{Populus tremula} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR1735633}{ERR1735633} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027425}{NC\_027425} & \num{3234148} & \num{815005296} & \num{126} & Yes \\
\textit{Populus trichocarpa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5467392}{SRR5467392} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_009143}{NC\_009143} & \num{298329746} & \num{149761532492} & \num{251} & NO \\
\textit{Premna microphylla} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6940036}{SRR6940036} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_026291}{NC\_026291} & \num{22624524} & \num{6787357200} & \num{150} & Yes \\
\textit{Primula veris} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1660449}{SRR1660449} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_031428}{NC\_031428} & \num{3263725} & \num{1599834089} & \num{245} & NO \\
\textit{Prunus dulcis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602582}{SRR5602582} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034696}{NC\_034696} & \num{1285872} & \num{631355142} & \num{245} & NO \\
\textit{Prunus kansuensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3138168}{SRR3138168} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023956}{NC\_023956} & \num{72248792} & \num{14449758400} & \num{100} & Yes \\
\textit{Prunus mume} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8240066}{SRR8240066} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023798}{NC\_023798} & \num{45570976} & \num{13671292800} & \num{150} & Yes \\
\textit{Prunus persica} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5073560}{SRR5073560} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_014697}{NC\_014697} & \num{9978569} & \num{4989866485} & \num{250} & NO \\
\textit{Psidium guajava} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5812495}{SRR5812495} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_033355}{NC\_033355} & \num{20356683} & \num{5129884116} & \num{126} & NO \\
\textit{Punica granatum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5812494}{SRR5812494} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035240}{NC\_035240} & \num{7814299} & \num{2359918298} & \num{151} & NO \\
\textit{Pyrus pyrifolia} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5196234}{SRR5196234} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_015996}{NC\_015996} & \num{33563581} & \num{9782203050} & \num{146} & Yes \\
\textit{Raphanus sativus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR014095}{DRR014095} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024469}{NC\_024469} & \num{513274067} & \num{103681361534} & \num{101} & NO \\
\textit{Rhazya stricta} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR351509}{ERR351509} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_024292}{NC\_024292} & \num{36920951} & \num{6645771180} & \num{90} & NO \\
\textit{Saccharum officinarum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7771854}{SRR7771854} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035224}{NC\_035224} & \num{91863015} & \num{46115233530} & \num{251} & Yes \\
\textit{Saccharum spontaneum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR486146}{SRR486146} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034802}{NC\_034802} & \num{63408401} & \num{19149337102} & \num{151} & Yes \\
\textit{Salix purpurea} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3927005}{SRR3927005} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_026722}{NC\_026722} & \num{191948456} & \num{57584536800} & \num{150} & Yes \\
\textit{Salix suchowensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8255647}{SRR8255647} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_026462}{NC\_026462} & \num{53495983} & \num{16048794900} & \num{150} & Yes \\
\textit{Salvia miltiorrhiza} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1735356}{SRR1735356} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_020431}{NC\_020431} & \num{215771972} & \num{43585938344} & \num{101} & NO \\
\textit{Sanionia uncinata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6440975}{SRR6440975} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_025668}{NC\_025668} & \num{3961386} & \num{2379651487} & \num{300} & NO \\
\textit{Schizachyrium scoparium} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6442327}{SRR6442327} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035032}{NC\_035032} & \num{1476472} & \num{442941600} & \num{150} & Yes \\
\textit{Sciadopitys verticillata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR2799544}{ERR2799544} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029734}{NC\_029734} & \num{1136673} & \num{343275246} & \num{151} & Yes \\
\textit{Scutellaria baicalensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6940088}{SRR6940088} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027262}{NC\_027262} & \num{27930422} & \num{8379126600} & \num{150} & Yes \\
\textit{Scutellaria lateriflora} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602584}{SRR5602584} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034693}{NC\_034693} & \num{1699048} & \num{843357767} & \num{248} & NO \\
\textit{Sequoia sempervirens} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1951920}{SRR1951920} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030372}{NC\_030372} & \num{2354579} & \num{1412747400} & \num{300} & NO \\
\textit{Sesamum indicum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3407090}{SRR3407090} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_016433}{NC\_016433} & \num{20637541} & \num{5159385250} & \num{125} & NO \\
\textit{Setaria italica} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR2696316}{ERR2696316} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_022850}{NC\_022850} & \num{65844392} & \num{19753317600} & \num{150} & Yes \\
\textit{Setaria viridis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR4063259}{SRR4063259} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028075}{NC\_028075} & \num{106716486} & \num{33508976604} & \num{157} & Yes \\
\textit{Silene latifolia} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7040334}{SRR7040334} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_016730}{NC\_016730} & \num{284434421} & \num{71108605250} & \num{125} & NO \\
\textit{Solanum berthaultii} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5349620}{SRR5349620} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034951}{NC\_034951} & \num{30261020} & \num{7565255000} & \num{125} & NO \\
\textit{Solanum commersonii} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5349609}{SRR5349609} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_028069}{NC\_028069} & \num{31268502} & \num{7817125500} & \num{125} & NO \\
\textit{Solanum habrochaites} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR098098}{DRR098098} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_026879}{NC\_026879} & \num{95529750} & \num{17768533500} & \num{93} & NO \\
\textit{Solanum lycopersicum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR022700}{DRR022700} & \href{https://www.ncbi.nlm.nih.gov/nuccore/AC_000188}{AC\_000188} & \num{4192871} & \num{2104821242} & \num{251} & Yes \\
\textit{Solanum melongena} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR014074}{DRR014074} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030207}{NC\_030207} & \num{173060640} & \num{34958249280} & \num{101} & NO \\
\textit{Solanum peruvianum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1291239}{SRR1291239} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_026881}{NC\_026881} & \num{12772339} & \num{2449431901} & \num{96} & Yes \\
\textit{Solanum pimpinellifolium} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR074949}{SRR074949} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_026882}{NC\_026882} & \num{195678316} & \num{39527019832} & \num{101} & Yes \\
\textit{Solanum tuberosum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR3148763}{ERR3148763} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_008096}{NC\_008096} & \num{806926} & \num{243691652} & \num{151} & NO \\
\textit{Sorghum bicolor} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3927127}{SRR3927127} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_008602}{NC\_008602} & \num{30065772} & \num{9079863144} & \num{151} & NO \\
\textit{Sorghum timorense} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR424217}{SRR424217} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023800}{NC\_023800} & \num{200900821} & \num{40180164200} & \num{100} & Yes \\
\textit{Spirodela polyrhiza} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7548934}{SRR7548934} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_015891}{NC\_015891} & \num{87602747} & \num{26401985035} & \num{151} & Yes \\
\textit{Sporobolus michauxianus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR4434178}{SRR4434178} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029416}{NC\_029416} & \num{183439649} & \num{55031894700} & \num{150} & NO \\
\textit{Stachys byzantina} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3170744}{SRR3170744} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029825}{NC\_029825} & \num{212918} & \num{64301236} & \num{151} & Yes \\
\textit{Stachys chamissonis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3170745}{SRR3170745} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029822}{NC\_029822} & \num{2570411} & \num{776264122} & \num{151} & Yes \\
\textit{Stachys coccinea} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3170746}{SRR3170746} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029823}{NC\_029823} & \num{292594} & \num{88363388} & \num{151} & Yes \\
\textit{Stachys sylvatica} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR3170747}{SRR3170747} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029824}{NC\_029824} & \num{592661} & \num{178983622} & \num{151} & NO \\
\textit{Taraxacum kok-saghyz} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR8185394}{SRR8185394} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_032057}{NC\_032057} & \num{21183799} & \num{11049748919} & \num{261} & NO \\
\textit{Taxodium distichum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR2799546}{ERR2799546} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034941}{NC\_034941} & \num{879574} & \num{265631348} & \num{151} & Yes \\
\textit{Taxus baccata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR268425}{ERR268425} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035066}{NC\_035066} & \num{172310721} & \num{34462144200} & \num{100} & Yes \\
\textit{Tectona grandis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6940065}{SRR6940065} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_020098}{NC\_020098} & \num{24194338} & \num{7258301400} & \num{150} & Yes \\
\textit{Tetradesmus obliquus} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR1683652}{ERR1683652} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_008101}{NC\_008101} & \num{100944122} & \num{20390712644} & \num{101} & NO \\
\textit{Themeda triandra} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7529014}{SRR7529014} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_035016}{NC\_035016} & \num{91131777} & \num{45565888500} & \num{250} & Yes \\
\textit{Theobroma cacao} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5602583}{SRR5602583} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_014676}{NC\_014676} & \num{470765} & \num{277504475} & \num{295} & NO \\
\textit{Thlaspi arvense} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1034659}{SRR1034659} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_034362}{NC\_034362} & \num{10761690} & \num{5402368380} & \num{251} & NO \\
\textit{Trifolium subterraneum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=DRR032042}{DRR032042} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_011828}{NC\_011828} & \num{25964880} & \num{15630857760} & \num{301} & Yes \\
\textit{Triticum aestivum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5893651}{SRR5893651} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_002762}{NC\_002762} & \num{197767716} & \num{104816889480} & \num{265} & NO \\
\textit{Triticum monococcum} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR384895}{SRR384895} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_021760}{NC\_021760} & \num{157945836} & \num{31905058872} & \num{101} & NO \\
\textit{Triticum urartu} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR4010671}{SRR4010671} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_021762}{NC\_021762} & \num{123772698} & \num{63619166772} & \num{257} & NO \\
\textit{Urochloa ruziziensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR6816710}{SRR6816710} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_030068}{NC\_030068} & \num{154533231} & \num{46669035762} & \num{151} & NO \\
\textit{Utricularia reniformis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5349713}{SRR5349713} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029719}{NC\_029719} & \num{2186073} & \num{1157291061} & \num{265} & NO \\
\textit{Vaccinium macrocarpon} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1276173}{SRR1276173} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_019616}{NC\_019616} & \num{30540329} & \num{9223179358} & \num{151} & NO \\
\textit{Vicia sativa} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR413103}{ERR413103} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027155}{NC\_027155} & \num{10232390} & \num{2046478000} & \num{100} & NO \\
\textit{Vigna unguiculata} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7125688}{SRR7125688} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_018051}{NC\_018051} & \num{30233396} & \num{9070018800} & \num{150} & Yes \\
\textit{Vitis aestivalis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5891909}{SRR5891909} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_029454}{NC\_029454} & \num{17094973} & \num{5128491900} & \num{150} & Yes \\
\textit{Vitis amurensis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5891950}{SRR5891950} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_031383}{NC\_031383} & \num{21559227} & \num{6467768100} & \num{150} & NO \\
\textit{Vitis rotundifolia} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5627788}{SRR5627788} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023790}{NC\_023790} & \num{49224878} & \num{14767463400} & \num{150} & NO \\
\textit{Vitis vinifera} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR7160359}{SRR7160359} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_007957}{NC\_007957} & \num{8416372} & \num{8416372000} & \num{500} & NO \\
\textit{Viviania marifolia} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=ERR2799536}{ERR2799536} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_023259}{NC\_023259} & \num{1050522} & \num{317257644} & \num{151} & NO \\
\textit{Wisteria floribunda} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1265941}{SRR1265941} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027677}{NC\_027677} & \num{9382854} & \num{1895336508} & \num{101} & Yes \\
\textit{Wollemia nobilis} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR1927951}{SRR1927951} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_027235}{NC\_027235} & \num{116590} & \num{59624823} & \num{256} & NO \\
\textit{Zea mays} & \href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=SRR5826129}{SRR5826129} & \href{https://www.ncbi.nlm.nih.gov/nuccore/NC_001666}{NC\_001666} & \num{172800442} & \num{89856229840} & \num{260} & Yes \\

### 2019-06-09 manuscript/supplement.tex
Add scripts for generation of sra_table

--- 2019-06-06 bmc_article.tex
@@
-    %% BioMed_Central_Tex_Template_v1.06
-%%                                      %
-%  bmc_article.tex            ver: 1.06 %
-%                                       %
-
-%%IMPORTANT: do not delete the first line of this template
-%%It must be present to enable the BMC Submission system to
-%%recognise this template!!
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                     %%
-%%  LaTeX template for BioMed Central  %%
-%%     journal article submissions     %%
-%%                                     %%
-%%          <8 June 2012>              %%
-%%                                     %%
-%%                                     %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                                                 %%
-%% For instructions on how to fill out this Tex template           %%
-%% document please refer to Readme.html and the instructions for   %%
-%% authors page on the biomed central website                      %%
-%% http://www.biomedcentral.com/info/authors/                      %%
-%%                                                                 %%
-%% Please do not use \input{...} to include other tex files.       %%
-%% Submit your LaTeX manuscript as one .tex document.              %%
-%%                                                                 %%
-%% All additional figures and files should be attached             %%
-%% separately and not embedded in the \TeX\ document itself.       %%
-%%                                                                 %%
-%% BioMed Central currently use the MikTex distribution of         %%
-%% TeX for Windows) of TeX and LaTeX.  This is available from      %%
-%% http://www.miktex.org                                           %%
-%%                                                                 %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%% additional documentclass options:
-%  [doublespacing]
-%  [linenumbers]   - put the line numbers on margins
-
-%%% loading packages, author definitions
-
-%\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
-\documentclass{bmcart}
+\documentclass[oneside,10pt,A4]{scrartcl}
 
@@
 %%% Put your definitions there:
-\startlocaldefs
 \newcommand{\formatprogramnames}[1]{\texttt{#1}}
@@
 
-% List of docker images
-\newcommand{\docker}[2]{\href{https://cloud.docker.com/u/chloroextractorteam/repository/docker/chloroextractorteam/#1}{chloroextracteam/#1:#2}}
-\newcommand{\dockerce}{\docker{benchmark\_chloroextractor}{v2.0.0}}
-\newcommand{\dockercesha}{\texttt{8f49e03424b37e699c5fea9391f79dbb9f2d0dc550ce86c4c700f39deec2dacd}}
-\newcommand{\dockeroa}{\docker{benchmark\_org-asm}{v2.0.0}}
-\newcommand{\dockeroasha}{\texttt{ff83677c97b7c4e346191b9e04a5162eeea2a8dfd9e60ff84067d33747868f60}}
-\newcommand{\dockerfp}{\docker{benchmark\_fastplast}{v2.0.0}}
-\newcommand{\dockerfpsha}{\texttt{a3d06a610f8340ba49c3ff3b27342534e2a5348b17caa4fd3c3f3d327243a272}}
-\newcommand{\dockerioga}{\docker{benchmark\_ioga}{v2.0.0}}
-\newcommand{\dockeriogasha}{\texttt{4698a21c343c60290bbf16811165a654ff01e8fddeb41cd75d0771b7f45968c0}}
-\newcommand{\dockernp}{\docker{benchmark\_novoplasty}{v2.0.0}}
-\newcommand{\dockernpsha}{\texttt{106387bad4e8e5c53fb9d4c3bdd60cdddf05a47b52a38697369eeabb947c547c}}
-\newcommand{\dockergo}{\docker{benchmark\_getorganelle}{v2.0.0}}
-\newcommand{\dockergosha}{\texttt{2ed3a464a82025a196ea56c649d0b0a3472cef76994bb065d56054d93298d956}}
-\newcommand{\dockercassp}{\docker{benchmark\_chloroplast\_assembly\_protocol}{v2.0.0}}
-\newcommand{\dockercasspsha}{\texttt{d10d2317103d91fadec4cb1d5466ac109f23176ad74b6f44f0179175f050155d}}
-\endlocaldefs
+\usepackage{longtable}
+\usepackage{pdflscape}
+\usepackage{capt-of}
 
+\renewcommand{\thetable}{S\arabic{table}}%
+\renewcommand{\thefigure}{S\arabic{figure}}
 %%% Begin ...
@@
 
-%%% Start of article front matter
-\begin{frontmatter}
+\title{The landscape of chloroplast genome assembly
+tools}
+\subtitle{Supplemental material}
+\author{\parbox{\textwidth}{\centering{}Jan A Freudenthal, Simon Pfaff, Niklas Terhoeven, Arthur Korte, Markus J Ankenbrand and Frank Förster}}
+\date{}
+\maketitle
+\listoftables
 
-\begin{fmbox}
-\dochead{Research}
+\begin{landscape}
+\setlength{\LTcapwidth}{1.5\textwidth}
+\begin{longtable}{cccrrcc}
+\caption[Summary real data set]{\textbf{Summary real data set.} List of real data sets used during our benchmark study.
+The tables was sorted by species name.
+Additionally, the table contains the accession for the Sequencing Read Archive (SRA Acc) and the accession of the used reference (Ref Acc).
+Moreover, the original number of read pairs (read pairs), the overall number of sequenced nucleotides (base pairs), and the mean read length (read len.) is given.
+Finally, the last column contains the information, if that data set was used for the check of the consistency.} \\
+\hline
+Taxon & SRA Acc & Ref Acc & read pairs & base pairs (bp) & read len. (bp) & Consistency check \\
+\hline
+\endfirsthead
+\multicolumn{7}{c}{\tablename\ \thetable\ -- \textit{Continued from previous page}}\\[0.5em]
+Taxon & SRA Acc & Ref Acc & read pairs & base pairs (bp) & read len. (bp) & Consistency check \\ \hline
+\endhead
+\hline
+\multicolumn{7}{r}{Continued on next page}\\
+\endfoot
+\endlastfoot
+\input{sra_ref.tex}
+\end{longtable}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Enter the title of your article here     %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\title{The landscape of chloroplast genome assembly tools}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Enter the authors here                   %%
-%%                                          %%
-%% Specify information, if available,       %%
-%% in the form:                             %%
-%%   <key>={<id1>,<id2>}                    %%
-%%   <key>=                                 %%
-%% Comment or delete the keys which are     %%
-%% not used. Repeat \author command as much %%
-%% as required.                             %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\author[
-    addressref={aff1,aff3},
-    noteref={n1},
-    email={jan.freudenthal@uni-wuerzburg.de}
-    ]{\inits{JAF}\fnm{Jan A} \snm{Freudenthal}}
-\author[
-    addressref={aff1,aff2},
-    noteref={n1},
-    email={simon-pfaff@gmx.de}
-    ]{\inits{SP}\fnm{Simon} \snm{Pfaff}}
-\author[
-   addressref={aff1,aff3},
-   email={niklas.terhoeven@uni-wuerzubrg.de}
-]{\inits{NT}\fnm{Niklas} \snm{Terhoeven}}
-\author[
-   addressref={aff1},
-   email={arthur.korte@uni-wuerzubrg.de}
-]{\inits{AK}\fnm{Arthur} \snm{Korte}}
-\author[
-   addressref={aff1,aff3,aff2 },
-   noteref={n2},
-   email={markus.ankenbrand@uni-wuerzubrg.de}
-]{\inits{MJA}\fnm{Markus J} \snm{Ankenbrand}}
-\author[
-   addressref={aff2,aff4},                   % id's of addresses, e.g. {aff1,aff2}
-   corref={aff1},                       % id of corresponding address, if any
-   noteref={n2},                        % id's of article notes, if any
-   email={frank.foerster@uni-wuerzburg.de}   % email address
-]{\inits{FF}\fnm{Frank} \snm{Förster}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Enter the authors' addresses here        %%
-%%                                          %%
-%% Repeat \address commands as much as      %%
-%% required.                                %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\address[id=aff1]{%
-  \orgname{Center for Computational and Theoretical Biology, University of W\"{u}rzburg},
-  \street{Campus Hubland Nord},
-  \postcode{97074}
-  \city{W\"{u}rzburg},
-  \cny{Germany}
-}
-
-\address[id=aff3]{%
-  \orgname{AnaLife Data Science},
-  \street{Friedrich-Bergius-Ring 15},
-  \postcode{97076}
-  \city{W\"{u}rzburg},
-  \cny{Germany}
-}
-\address[id=aff2]{%                           % unique id
-  \orgname{Department of Bioinformatics, University of W\"{u}rzburg}, % university, etc
-  \street{Biozentrum, Am Hubland},                     %
-  \postcode{97074},                                % post or zip code
-  \city{W\"{u}rzburg},                              % city
-  \cny{Germany}                                    % country
-}
-
-\address[id=aff4]{%
-  \orgname{Fraunhofer IME-BR},
-  \street{Winchester Str.\ 2},
-  \postcode{97076}
-  \city{Gie\ss{}en},
-  \cny{Germany}
-}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Enter short notes here                   %%
-%%                                          %%
-%% Short notes will be after addresses      %%
-%% on first page.                           %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{artnotes}
-%\note{Sample of title note}     % note to the article
-\note[id=n1]{Equal contributor} % note, connected to author
-\note[id=n2]{Corresponding author} % note, connected to author
-\end{artnotes}
-
-\end{fmbox}% comment this for two column layout
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% The Abstract begins here                 %%
-%%                                          %%
-%% Please refer to the Instructions for     %%
-%% authors on http://www.biomedcentral.com  %%
-%% and include the section headings         %%
-%% accordingly for your article type.       %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstractbox}
-\begin{abstract} % abstract
-%One or two sentences providing a basic introduction to the field, comprehensible to a scientist in any discipline.
-Chloroplasts are photosynthetic organelles in plant cells and contain their own genomic information.
-That genome can be utilized in different scientific fields like phylogenetics or biotechnology.
-%Two to three sentences of more detailed background, comprehensible to scientists in related disciplines.
-Thus, different assemblers have been developed specialized in chloroplast assemblies.
-Those assemblers often use the output of whole genome sequencing experiments as input.
-Such sequencing data usually contain the complete chloroplast genome information, even if the sequencing aims for the core genome.
-%One sentence clearly stating the general problem being addressed by this particular study.
-Different assembly tools have never been systematically compared. %to each other concerning success rate or computational requirements.
-%One sentence summarising the main result (with the words “here we show” or their equivalent).
-Here we present a benchmark of seven chloroplast assembly tools, capable to succeed in more than \SI{60}{\percent} of real data sets.
-%Two or three sentences explaining what the main result reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
-Our results show significant differences between the tested assemblers in terms of generating whole chloroplast genome sequences and computational requirements.
-Moreover, we suggest further development to improve user experience and success rate.
-%One or two sentences to put the results into a more general context. 
-In terms of reproducibility, we created docker images for each tested tool, which are available for the scientific community.
-Following the presented guidelines, users are able to analyse and screen data sets for chloroplast genomes using only standard computer infrastructure.
-%Two or three sentences to provide a broader perspective, readily comprehensible to a scientist in any discipline, may be included in the first paragraph if the editor considers that the accessibility of the paper is significantly enhanced by their inclusion.
-Thus large scale screening for chloroplasts as hidden treasures within genomic sequencing data is feasible.
-
-%\ff{Abstract}
-%Useful as always: \url{https://cbs.umn.edu/sites/cbs.umn.edu/files/public/downloads/Annotated_Nature_abstract.pdf}
-%The special issue will accept manuscripts presenting:
-%
-%- in-depth analyses of advantages
-%
-%-limitations of state-of-the-art methods
-%
-%-demonstration on a variety of representative datasets and simulations
-%
-%-clear guidelines/recommendations for the end-user
-%
-%-insight into future directions for methods
-%\parttitle{First part title} %if any
-%Text for this section.
-%
-%\parttitle{Second part title} %if any
-%Text for this section.
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% The keywords begin here                  %%
-%%                                          %%
-%% Put each keyword in separate \kwd{}.     %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{keyword}
-\kwd{Chloroplast}
-\kwd{Genome}
-\kwd{Assembly}
-\kwd{Software}
-\kwd{Benchmark}
-\end{keyword}
-
-% MSC classifications codes, if any
-%\begin{keyword}[class=AMS]
-%\kwd[Primary ]{}
-%\kwd{}
-%\kwd[; secondary ]{}
-%\end{keyword}
-
-\end{abstractbox}
-%
-%\end{fmbox}% uncomment this for twcolumn layout
-
-\end{frontmatter}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% The Main Body begins here                %%
-%%                                          %%
-%% Please refer to the instructions for     %%
-%% authors on:                              %%
-%% http://www.biomedcentral.com/info/authors%%
-%% and include the section headings         %%
-%% accordingly for your article type.       %%
-%%                                          %%
-%% See the Results and Discussion section   %%
-%% for details on how to create sub-sections%%
-%%                                          %%
-%% use \cite{...} to cite references        %%
-%%  \cite{koon} and                         %%
-%%  \cite{oreg,khar,zvai,xjon,schn,pond}    %%
-%%  \nocite{smith,marg,hunn,advi,koha,mouse}%%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%% start of article main body
-% <put your article body there>
-
-%%%%%%%%%%%%%%%%
-%% Background %%
-%%
-\section*{Introduction}
-\subsection*{General introduction and motivation}
-Chloroplasts are essential organelles present in plant cells and the cells of some protists.
-Chloroplasts enable the conversion of light energy into chemical energy via photosynthesis.
-They harbor their own ribosomes and a circular DNA genome usually with a size between \SIrange{120}{160}{\kilo\basepair} \cite{palmer_1985}.
-Because of this small size, the chloroplast genome has been an early target for sequencing.
-The first chloroplast genome sequences were obtained as early as 1986 \cite{ohyama_chloroplast_1986,shinozaki_complete_1986}.
-These early efforts elucidated the general genome organization and structure of the chloroplast DNA. 
-Chloroplast genome content and structure are reviewed for example in \cite{wicke_evolution_2011,green_chloroplast_2011}.
-Chloroplast genomes are widely used for evolutionary analyses \cite{martin_plastid_2010,xiao-ming_inferring_2017}, barcoding \cite{kress_use_2005,hollingsworth_dna_2009,de_vere_dna_2015}, and meta-barcoding \cite{bell_review_2016,deiner_environmental_2017}.
-Interesting aspects of chloroplast genomes are their small size (\SIrange{120}{160}{\kilo\basepair},\cite{palmer_1985}), caused through endosymbiotic gene transfer \cite{martin_evolutionary_2002,timmis_endosymbiotic_2004} and the low number of \numrange{100}{120} genes that are still encoded on the chloroplast genome \cite{wicke_evolution_2011}.
-Despite the overall high conservation of the genome sequence, there are striking differences in the gene content between different groups (e.g.
-the loss of the whole \genename{ndh} gene family in Droseraceae \cite{nevill_plastome-wide_2019}).
-Even more extreme evolutionary cases, where chloroplasts show a very low GC content and a modified genetic code are described \cite{su_novel_2019}.
-
-These differences call for comparative genomic approaches.
-Given the small size, it is much easier to decipher the complete chloroplast genome than the complete core genome.
-For example the \plant{At} core genome is approximately \SI{125}{\mega\basepair} in length \cite{schmuths2004,cao2011} while the size of the \plant{At} chloroplast genome with \SI{154}{\kilo\basepair} is more than \SI{800}{\times} smaller \cite{sato1999}.
-
-Even if only a single chloroplast is located inside a plant cell, several hundreds copies of the chloroplast genome exists in each cell \cite{kumar_2014,bendich_1987}.
-Therefore, many genome sequencing projects contain chloroplast reads as by-product.
-In some cases the chloroplast data is even considered contamination and experimental protocols for reducing their content have been developed \cite{lutz_isolation_2011}.
-An alternative approach to improve the assembly of the core genome would be to first resolve the chloroplast genome and afterwards use this information to remove those reads that map to the chloroplast genome.
-
-Structurally, two inverted repeats (IR\textsubscript{A} and IR\textsubscript{B}) of \SIrange{10}{76}{\kilo\basepair} divide the chloroplast genome into a large (LSC) and a small single copy (SSC) region \cite{palmer_1985}.
-Those large inverted repeats complicate automated resolution with short read technologies\cite{Wang2018}.
-Moreover, the existence of different chloroplasts within a single individual, and thus multiple different chloroplast genomes, have been described for different plants \cite{corriveau_1988,Chat2002,Scar2016}.
-Although the origin and evolutionary importance of this phenomena ---called heteroplasmy--- are only poorly understood, the assembly of whole chloroplast genomes might be hindered.
-
-Databases exist containing short read data for species where no reference chloroplast sequence is publicly available, eg.\ the Sequence Read Archive at NCBI \cite{sra2010}.
-The availability of whole chloroplast genomes would enable large scale comparative studies \cite{tonti-filippini_what_2017}.
-Additionally, reconstructed full chloroplast genomes have been used as super-barcodes \cite{coissac_barcodes_2016}, for biotechnology applications and genetic engineering \cite{daniell_chloroplast_2016}.
-
-\subsection*{Approaches to extracting chloroplasts from whole genome data}
-
-Different strategies have been developed to assemble chloroplast genomes \cite{twyford_strategies_2017}.
-In general, obtaining a chloroplast genome from WGS data requires two steps. First, the chloroplast reads have to be extracted from the mixed sequencing data. 
-The second step is the assembly and resolution of the special circular structure including the inverted repeats.
-The extraction of the reads can be achieved by mapping the reads to a reference chloroplast. \cite{Vinga2012}.
-A different approach that does not perform alignments, relies on the higher coverage of chloroplast data in the whole genome sequencing data set\cite{Chan2013}.
-Here, a $k$-mer analysis can be used to extract the most frequent reads.
-An example for this is implemented in \ce{} \cite{j_ankenbrand_chloroextractor:_2018}.
-%\todo{ce ist hier der einzig explizit genannte Assembler, das wirkt wie bias :) entfernen?
-Nope...
-Steht klar ein Beispiel und wir haben nun mal den angesehen...
-Würde ich jetzt einmal so drin lassen.
-Alternativ nehmen wir noch einen dazu}
-A third method combines both approaches by using a reference chloroplast as seed and simultaneously assembling the reads based on $k$-mers \cite{dierckxsens_novoplasty:_2017}.
-
-%\ak{e.g.
-HomBlocks: A multiple-alignment construction pipeline for organelle phylogenomics based on locally collinear block searching, aber ist nicht inkluded, also können wir zitieren, müssen aber nicht}
-
-\subsection*{Purpose and scope of this study}
-The goal of this study is to compare the effectiveness and efficiency of existing open source command-line tools to de-novo assemble whole chloroplast genomes from raw genomic data sets with minimal configuration.
-This includes no need for extensive data preparation, no need for a specific reference (apart from \plant{At}), no need to change default parameters, no manual finishing.
-We further restricted our benchmark to paired end Illumina data sets as these are routinely generated by modern sequencing platforms \cite{Goodwin2016}.
-
-In our opinion this reflects the most common use cases: (1) a user trying a tool quickly without digging into options for fine tuning and (2) large scale automatic applications.
-Still, we acknowledge that the performance of the tools might be significantly improved by optimizing parameters (and references if applicable) for each data set specifically.
-However, an exhaustive comparison - including tuning of all different possible parameters for each tool- was out of scope for this study.
-
-Our results will enable the discovery of novel chloroplast genomes as well as an assembly of inter/intra-individual differences in the respective chloroplast genomes.
-
-\section*{Methods}
-\subsection*{Data availability}
-Source code for all methods used is available at \cite{github-benchmark-repo} and archived in zenodo under \zenodorepo{}.
-All docker images are published on \cite{dockerhub-benchmark} and are named with a leading \texttt{benchmark\_} (\cref{tab:dockerimages}).
-
-To enable a fair comparison of all tools, we generated simulated sequencing data.
-Those simulated data sets are stored at \zenododataset{}.
-This study adheres to the guidelines for computational method benchmarking \cite{weber_essential_2018}.
-
-\subsection*{Tool Selection}
-We included tools designed for assembling chloroplasts from whole genome paired end Illumina sequencing data.
-As a requirement, all tools must be available as open source software and allow execution via a command line interface.
-As a graphical user interface is not suitable for automated comparisons, tools only providing a graphical interface have not been included.
-The following tools were determined to be within the scope of this study:
-\oa{} \cite{coissac_barcodes_2016}, 
-\ce{} \cite{j_ankenbrand_chloroextractor:_2018}, 
-\fp{} \cite{mckain__fast-plast_2017}, 
-\ioga{} \cite{bakker_herbarium_2016}, 
-\np{} \cite{dierckxsens_novoplasty:_2017}, 
-\go{} \cite{jin_getorganelle:_2018}, and
-\cassp{} \cite{sancho_comparative_2018}.
-
-Other related tools for assembling chloroplasts that did not meet our criteria and are therefore outside the scope of this study are for example:
-\texttt{Organelle PBA} \cite{Soorni2017}, \texttt{sestaton/Chloro} \cite{sestaton}, \texttt{Norgal}  \cite{Al-Nakeeb2017}, and \texttt{MitoBim} \cite{mitobim2013}.
-
-\texttt{Organelle PBA} is designed for PacBio data and does not work with paired Illumina data alone.
-\texttt{sestaton/Chloro} fits our criteria, but it is flagged as work in progress and development and support seem to have ended two years ago.
-\texttt{Norgal} is a tool to extract organellar DNA from whole genome data based on a \textit{k}-mer frequency approach.
-However the final output is a set of contigs of mixed mitochondrial and plastid origin.
-The suggested approach to get a finished chloroplast genome is to run \np{} on the ten longest contigs.
-Therefore we only included \np{} with the default settings and excluded \texttt{Norgal}.
-\texttt{MitoBim} is specifically designed for mitochondrial genomes.
-Even though there is a claim by the author that it can be used for chloroplasts as well, there is no further description on how to do that \cite{mitobim_issue16}.
-
-Additionally, there is a protocol for the \texttt{Geneious} \cite{geneious} software available \cite{geneious-protocol}.
-However, \texttt{Geneious} is closed source and GUI based, which is not in the scope of this study.
-There is also another publication describing a method for assembling chloroplasts \cite{method-description-paper}.
-However, the link to the software is not active anymore.
-
-\subsection*{Our Setup}
-We want to use a minimum of different parameter settings for all assembly programs to enable a fair comparison. 
-Therefore, we decided to specify that all programs have to work based on two input files, representing a data set's forward (\texttt{forward.fq}) and reverse  (\texttt{reverse.fq}) sequence file in FASTQ format.
-Depending on the assembler, output files with different names and locations are generated.
-Those different files are copied and renamed to ensure that each assembly approach produces the same output file (\texttt{output.fa}). 
-Additionally, we set an environment variable for all programs to control the number of allowed threads.
-All three requirements (defined input file names, defined output file name, thread number control via environment variable) are ensured by a simple wrapper script (\texttt{wrapper.sh}).
-Finally, for a maximum of reproducibility all programs have been bundled into individual docker images based on a central base image which provides all the required software.
-Those docker images were used for the recording of the consumption of computational resources.
-Furthermore, all our docker images have been converted into singularity containers for the quantitative measurement on simulated and real data sets.
-Singularity container were built from docker images for usage on a HPC-environment using Singularity v.2.5.2 \cite{kurtzer2017singularity}
-All singularity containers were run on %the Julia-HPC 
-Intel® Xeon® Gold \num{6140} Processors using a Slurm workload manager version 17.11.8 \cite{Jette02slurm}.
-Assemblies were run on \num{4} threads using \SI{10}{\gibi\byte} RAM with a time limit of \SI{48}{\hour}.
-\subsection*{Data}
-\subsubsection*{Simulated}
-To avoid suffering from sequencing errors and biological variances, we simulated perfect reads based on the \plant{At} (TAIR10) chloroplast assembly \cite{tair10}.
-We used a sliding window approach with \texttt{seqkit} \cite{seqkit}.
-The exact commands are documented in \href{https://github.com/chloroExtractorTeam/benchmark/blob/master/03_representative_datasets.md}{\texttt{03\_representative\_datasets.md}} in \zenododataset{}.
-For the final simulated data sets reads based on mixtures of the \plant{At} (TAIR10) core and chloroplast genome were generated with different ratios ( \num{0}:\num{1}, \num{1}:\num{10}, \num{1}:\num{100}, and \num{1}:\num{1000}).
-Additionally, we generated data with different read lengths (\SIlist{150;250}{\basepair}). All data simulated contain exactly 2 million read pairs.
-
-%(circular for chloro and mito). No errors, no insert size variation, perfect quality, equal coverage.
-
-\subsubsection*{Real}
-We selected real data deposited at SRA \cite{sra2010}.
-We searched all data that matched  \texttt{((((((("green plants"[orgn]) AND "wgs"[Strategy]) AND "illumina"[Platform]) AND "biomol dna"[Properties]) AND "paired"[Layout]) AND "random"[Selection])) AND "public"[Access]} \cite{sra_search_term}.
-For each species with a reference chloroplast in CpBase \cite{cpbase}, we selected one data set of those.
-In total, this accumulated to \num{369} data sets (see supplement for details).
-
-\subsection*{Evaluation Criteria}
-\subsubsection*{Computational Resources}
-%Due to computational resources are limited, we evaluated the effect of different input parameters.
-We recorded the mean and the peak CPU usage, the peak memory consumption, and the size of the assembly folder for each program. 
-As input data, we used different data sets comprising \numlist{25000;250000;2500000} read pairs sampled from  our simulated reads.
-%Therefore, the simulated perfect read files have been read repeatedly to achieve the required number of read pairs.
-We used our docker image setup (\cref{tab:dockerimages}) to run all assembly programs three times for each parameter setting.
-The different settings combined different input data and different number of threads to use (\numlist{1;2;4;8}).
-
-Some programs will use more CPU threads than specified, therefore, the number of CPUs available have been fixed using the CPU option while running the docker run command.
-For each assembly setting, we recorded the peak memory consumption, the CPU usage (mean and peak CPU usage) and the size of the folder where the assembly was calculated.
-The values of CPU and memory usage have been obtained by docker.
-The disk usage was estimated using the GNU tool \texttt{du}.
-We used \texttt{GNU parallel} for queuing of the different settings \cite{Tange2011a}.
-
-\subsubsection*{Qualitative}
-The qualitative evaluation is mainly based on the reviewer guidelines for the Journal of Open Source Software (JOSS) \cite{joss}.
-To create a standard environment, all tools were tested in a fresh default installation of Ubuntu 18.04.2 running in a virtual machine (VirtualBox Version 5.2.18\_Ubuntu r123745).
-We chose this setup instead of the docker container, because it resembles a typical user environment better than the minimal docker installation.
-The tools were installed according to their installation instructions and the provided tutorial or example usage was executed.
-During the evaluation, the following questions were asked:
-
-\begin{itemize}
-    \item Is the tool easy to install? 
-    \item Is there a way to test the installation or a tutorial on how to use the tool? 
-    \item Is there a good documentation on the parameter settings? 
-    \item Is the tool maintained (issues answered, implementation of new features)? 
-    \item Is the tool Open Source?
-\end{itemize}
-
-These questions were answered with \good{}, \ok{} or \bad{}, depending on the quality of the result. 
-For example, a \good{} installation utilizes an automated package or dependency management like \texttt{apt}, CRAN, docker, etc.
-An \ok{} installation procedure provides a custom script to install everything or at least lists all dependencies.
-A \bad{} installation procedure fails to list important dependencies or produces errors, that prevent a successful installation without exhaustive debugging.
-
-After an initial evaluation, we contacted all authors via their GitHub or GitLab issue tracking to communicate potential flaws we found.
-
-\subsubsection*{Quantitative}
-
-%We use continuity: number of contigs.
-%Completeness: Number of covered bases on reference (when aligning assembly).
-%Correctness: Number of covered bases in assembly (when aligning reference).
-%Repeat resolution: Difference between above two measures (indicates collapsed or expanded repeats)
-%
-%\nocite{oreg,schn,pond,smith,marg,hunn,advi,koha,mouse}
-
-%We want to quantify continuity, completeness, correctness and repeat resolution.
-
-For each data set and assembler the generated chloroplast genome was compared to the respective reference genome using a pairwise alignment obtained with \texttt{minimap2} v2.16 \cite{li2018minimap2}.
-Based on theses alignments a score is calculated as shown in \cref{eq:quantitative}
-The assemblies were scored on a scale from 0 to 100, with 100 being the best and 0 the worst possible score.
-Four different metrics were Incorporated, each contributing  $\frac{1}{4}$ to the total score: Completeness, correctness, repeat resolution and continuity.
-These metrics are similar in concept by those used in the Assemblathon 2 project: coverage, validity, multiplicity, and parsimony \cite{assemblathon2}.
-
-The completeness is estimated as the coverage of the assembled chloroplast genome versus the reference genome ($cov_{ref}$)
-It resembles how many bases of the query genome can be mapped to its respective reference genome.
-Secondly, we mapped the reference genome against the query.
-The coverage of the reference genome ($cov_{qry}$) is used as measurement for the correctness of the assembly.
-The repeat resolution is estimated from the size difference of the assembly and the reference genome ($min\left\{ \frac{cov_{qry}}{cov_{ref}}, \frac{cov_{ref}}{cov_{qry}}\right\}$), leading to values between 0 and 1.
-The fourth metric used is the continuity, represented by the number of contigs.
-A perfect score is achieved if one circular chromosome was assembled, while the score gets worse with the amount of contigs.
-
-\begin{equation}
-   score = \frac{1}{4} \cdot \left( cov_{ref} +  cov_{qry} + min\left\{ \frac{cov_{qry}}{cov_{ref}}, \frac{cov_{ref}}{cov_{qry}}\right\} + \frac{1}{n_{contigs} }\right) \cdot 100 
-   \label{eq:quantitative}
-\end{equation}
-
-\subsubsection*{Consistency}
-To ensure consistency of the obtained results, we randomly chose  \num{100} data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
-The resulting assemblies were scored again as described and the scores of the first and the second run were compared to each other
-This information is important to assess the robustness of the different programs.
-
-\section*{Results}
-\subsection*{Performance metrics}
-%\subsection*{Computational Resources}
-%Table and figure of performance evaluation.
-Including RAM, I/O, runtime, parallelization ability, CPU usage.
-Free text description of results, range, mean/median, effect of input size, threads parameter, ...
-
-\subsubsection*{Time requirements}
-In terms of run time, massive differences between the different tools have been observed.
-Apart from tool-specific differences, input data and number of threads had huge impact.
-The observed run times varied from a few minutes to several hours (\cref{fig:performance_runtime}).
-
-Some assemblies failed to finish within the time-limit we set (\SI{48}{\hour}). 
-On average the longest time to generate the assemblies was taken by \ioga{} and \fp{} followed by \oa{} and \go{} the most time efficient tool was \ce{}, which on average is a little faster than \np{} and \cassp{}.
-%% multithreading
-
-Not all the tools were able to benefit from having access to multiple threads.
-Both \np{} and \oa{} take about the same time independent of being able to utilize \numlist[list-final-separator={, or }]{1;2;4;8} threads.
-\cassp{}, \ce{}, \go  and \fp{} all profit from multi-threading (\cref{fig:performance_runtime}, \cref{fig:performance_memory_cpu}).
-
-\subsubsection*{Memory and CPU Usage }
-The peak and mean CPU usage, as well as peak memory and disk usage have been recorded for all assemblers based on the same input data set and number of threads to use (\cref{fig:performance_memory_cpu}).
-Mainly, the size of the input data influenced the peak memory usage with the exception of \ce{} and \ioga{}.
-Those two assemblers seems to have a memory usage pattern, which is less influenced by the size of the data.
-The number of allowed threads had only a limited impact on the peak memory usage.
-Nevertheless, all programs profit by a higher number of threads, if the size of the input data was increased.
-In contrast, the disk usage is independent from input size and number of threads for all assemblers.
-%but the factor between the programs exceeds a factor of \num{100}.
-
-\subsection*{Qualitative}
-The user experience of most tools was evaluated as mainly \good{} (\cref{tab:resultsQual}). However, a few critique points remained.
-Two minor dependencies were missing in the \go{} installation instructions and there was no test data available.
-Additionally, an issue occurred when running it on a \plant{At} data set.
-We are currently in the process of resolving this with the authors.
-
-The \fp{} installation instructions were missing some dependencies.
-Like \go{}, \fp{} does not offer a test data set or a tutorial, except for some example commands.
-
-The \oa{} installation instructions did not work.
-We found some issues, which are probably related to the requirement of \texttt{Python~3.7}.
-There is a tutorial where sample data is available.
-However, following the instructions resulted in a segmentation fault.
-We found a workaround for this bug and contacted the authors.
-
-The main critique point of \np{} was the lack of a test data set with instructions.
-This was fixed by the authors after we contacted them.
-Additionally, \np{} uses a custom license, where an OSI approved license would be preferred.
-
-The \ce{} does come with a test data set and a short tutorial.
-However, it is currently not possible to evaluate the results of the test run.
-
-The \ioga{} installation instructions were missing many dependencies.
-Also, there was no test data or tutorial available and there is no license assigned to it.
-Since there was no update to the GitHub repository for the last three years, the project can be seen as inactive.
-After contacting the authors, they promised to resolve the mentioned issues.
-
-As many of the other tools, the installation instructions for the \cassp{} were missing some dependencies.
-The list was updated after we contacted the authors.
-This tool does come with a test data set, however a note about the expected outcome is missing.
-A more extensive tutorial is provided.
-The description about the parameter is short, but sufficient.
-
-\subsection*{Quantitative}
-\subsubsection*{Simulated data}
-The only assembler obtaining perfect results according to our score for the simulated data sets is \go{} (\cref{fig:simulated}).
-\ioga{} and \cassp{} showed the worst performance, being unable to fully assemble a single chloroplast out of \num{14} runs.
-\np{} performed second best with scores above \num{80} for all data sets, only failing to resolve the contigs into one single circular chloroplast assembly.
-The overall performance is best, when the input data consists purely of chloroplast reads.
-Only \ioga{} and \cassp{} failed to deliver any results under this scenario once.
-In general, no clear correlation between either length of the input reads or the ratio of core vs chloroplast reads and the performance of the different assemblers can be observed.
-
-\subsubsection*{Real data sets}
-Concerning the performance of the assemblers on the real data sets, we were able to observe considerable differences in the median score (\cref{fig:swarmplot}).
-The highest scores were achieved by \go{} with a median of \num{99.7} and \num{199} circular assemblies out of a total of 356 assemblies that resulted in an output (\cref{tab:scores}).
-The performance of \go{} is followed by \fp{}, \np{}, \oa{}, and \ce{}.
-\fp{} is outperforming the latter two slightly in terms of score, with twice as much \num{114} perfectly assembled chloroplast genomes (\np{} produced \num{66} and \oa{} \num{55} circular genomes).
-\ioga{} and \cassp{} were both not able to assemble a circular, single-contig genome (\cref{tab:scores}), consequently resulting in the lowest mean and median scores (\cref{fig:upset}).
-
-%\textit{swarm plot goes here}
-%% Den upset plot eventuell erst in die Discussion reinbringen ? Da wir davon ableiten welche tools wir empfehlen?
-
-\subsubsection*{Consistency}
-Consistency was tested by re-running assemblies and comparison of the scores of two assemblies (\cref{fig:consistency}).
-Replicates that did not produce an output were manually scored as \num{0}. 
-\go{} was the only tool that succeeded in obtaining similar scores for all assemblies, without producing and completely unsuccessful assemblies for this subset of data.
-Except for \fp{} all the other tools had at least one assembly that was unsuccessful in one run, but produced an output in the other.
-%\ak{oben steht \go{} war als einziges immer gut, dann kommt except for \fp{} ?? does not seem to be consistent}
-Notably \ioga{} appears to have a tendency to perform differently in independent runs.
-Here, more than \SI{10}{\percent} of the assemblies failed in one run only.
-
-Both \fp{} and \np{} tend to have minor changes in the assembly when the overall performance is comparably well, leading to the arrow-shaped scatter plots.
-%\ak{link to figure scatter plots is missing}
-\ce{} and \cassp{} appear to be the most robust assemblers, having only few deviations between the two runs.
-
-\section*{Discussion}
-We aimed to generate an overall performance score for the different chloroplast assemblers, but depending on distinct downstream applications, the different criteria assessed in this work need to be weighted differently.
-For example, ease of installation and use might not be a big concern if the tool is installed once and integrated in an automated pipeline.
-On the other hand this factor alone might prevent other users from being able to use the tool in the first place.
-Similarly, computational requirements or run time might be less relevant, if the goal is to assemble a single chloroplast for further analysis, but it is essential if hundreds or thousands of samples should be processed in parallel for a large scale study.
-Eventually, both ease of use and run time are irrelevant if the tool is not able to successfully accomplish its task.
-Also the scope of this study needs to be considered when interpreting the guidelines below.
-In particular, we evaluated all tools under the assumption that they are used in the most basic form (default parameters, no hand selected reference, no pre-processing of the data or post-processing of the result, restricted run time).
-It is important to note that any tool might perform significantly different, if the above mentioned parameters are fine-tuned for a specific data set.
-
-The overall best success rate, both on simulated and real data, was achieved by \go{} followed by \fp{}.
-Both tools complement each other, as each is able to successfully reconstruct a full chloroplasts in cases where the other tool fails. 
-In rare cases \np{} or \oa{} are the only tool to succeed.
-The tools \fp{}, \np{}, and \oa{} produce the most variable results, thus re-running the tool after a failed attempt might be successful.
-\ce{} yields only few complete chloroplast assemblies, but requires also only few resources.
-It is easy to install and use and thus could be considered as a good option for a quick first try.
-Both \ioga{} and \cassp{} have the worst performance of all tools tested and fail to return reliable chloroplast assemblies.
-
-\subsection*{Guidelines for the end-user}
-Given these results, our recommendation is to use \go{} as default option, and in case of failure \fp{} as backup solution.
-%\ak{what if both lead to qualitative different results?, always trust \go{} , or could one compute a high-confidence assembly by combining different results ?, might be a point for future directions.}
-If both programs fail, it is sensible to re-run \fp{} and additionally try \np{} and \oa{}.
-This procedure maximizes the chance to effectively and efficiently recover the circular chloroplast genome from mixed genomic data.
-If none of these four assemblers produce sensible results, a reference guided approach and tweaking of the default parameters, might be the solution.
-Here, it is not possible to provide general guidelines, as the procedure will differ for different data sets.
-For an automated approach, running \go{} and \fp{} in parallel appears to be a good trade-off between success rate and use of resources.
-
-\subsection*{Ideas for future development}
-For further experiments, combining different components from different tools might be a promising approach.
-For example, read scaling from \ce{} followed by an assembly by \go{} and finally the structural resolution with \fp{} could be a promising approach, combing the respective strength of the different tools.
-
-Moreover, the installation issues need to be mitigated by modern software.
-Therefore, either containerization (docker, singularity, etc.) or install workflows (eg. bioconda \cite{gruening2018}) should be established by all software packages.
-Otherwise, the burden of the software installation might result in scientists ignoring good tools.
-
-Another important feature of software is a comprehensive documentation, which needs to be up-to-date and maintained.
-Additionally, software authors could improve the usability based on suggestions from their users.
-
-Finally, all tools should improve their integrated guessing of default parameters, as many users avoid fine tuning of those, especially, for larger screening approaches.
-Last, as sequencing technology is developing fast (eg.\ PacBio or nanopore), tools need to be updated to not become obsolete.
-But the hope would be that with ongoing software development and improved sequencing technologies, the generation of whole chloroplast assemblies from any species will become a routine technique.
-
-\section*{Conclusion}
-The main assumption for our study to benchmark different chloroplast assembly tools, is that whole genome sequencing data are also a promising source for chlorplast assemblies.
-Our benchmark shows that ~\SI{60}{\percent} of the data sets without available chloroplast genome, have been assembled by at least one of the tools we analysed.
-Still, even with simulated (aka``perfect'') data, not all tools succeeded in generating complete chloroplast assemblies.
-Therefore, we determined the strengths and weaknesses of the specific tools and provided guidelines for the users.
-However, it might be necessary, to combine different methods or manually explore the parameter space, to obtain reliable results if a single run seems not sufficient.
-Ultimately, large scale studies reconstructing hundreds or thousands of chloroplast genomes are now feasible using the currently available tools. 
-%Outlook: next step in the pipeline is annotation. There is a similar problem: many tools, which one to use? 
-%A large scale study reconstructing chloroplasts throughout SRA (or \num{1001} genome project) is feasible and promising using the existing tools (estimated runtime, number of novel chloroplasts).
-%A meta-tool that automatically combines the different programs could be developed.
-%The benchmarking study could be augmented to automatically select the closest reference from the database and provide that to any tool that can take advantage of references.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                                          %%
-%% Backmatter begins here                   %%
-%%                                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{backmatter}
-
-\section*{Competing interests}
-The authors disclose that SP, NT, FF, and MJA are developers of \ce{}, one of the tools benchmarked in this article.
-The authors exercised caution not to let this fact unfairly influence their judgment and recommendations.
-JF, NT, and MJA are affiliated with the for-profit organization AnaLife Data Science.
-\ak{and I think we should mention Analife as competing interest, normally people list all non-academic shareholder whatever stuff, just to be sure}
-\todo{Ich weiß nicht ob das so passt}
-
-\section*{Author's contributions}
-MJA and FF conceived of the presented idea and supervised the findings of this manuscript.
-SP and FF created the docker images.
-NT performed the qualitative analysis for all assemblers.
-MJA prepared the simulated and real data sets.
-JAF assembled the real data sets.
-FF ran the performance assemblies on the simulated data sets.
-All authors developed the score model.
-JAF and MJA implemented the score model and prepared the figures.
-All authors discussed the results and contributed to the final manuscript.
-
-\section*{Acknowledgements}
-Text for this section\todo{haben wir da jemanden oder etwas? funding?} \ldots
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                  The Bibliography                       %%
-%%                                                         %%
-%%  Bmc_mathpys.bst  will be used to                       %%
-%%  create a .BBL file for submission.                     %%
-%%  After submission of the .TEX file,                     %%
-%%  you will be prompted to submit your .BBL file.         %%
-%%                                                         %%
-%%                                                         %%
-%%  Note that the displayed Bibliography will not          %%
-%%  necessarily be rendered by Latex exactly as specified  %%
-%%  in the online Instructions for Authors.                %%
-%%                                                         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% if your bibliography is in bibtex format, use those commands:
-\bibliographystyle{bmc-mathphys} % Style BST file (bmc-mathphys, vancouver, spbasic).
-\bibliography{bmc_article}      % Bibliography file (usually '*.bib' )
-% for author-year bibliography (bmc-mathphys or spbasic)
-% a) write to bib file (bmc-mathphys only)
-% @settings{label, options="nameyear"}
-% b) uncomment next line
-%\nocite{label}
-
-% or include bibliography directly:
-% \begin{thebibliography}
-% \bibitem{b1}
-% \end{thebibliography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                               %%
-%% Figures                       %%
-%%                               %%
-%% NB: this is for captions and  %%
-%% Titles. All graphics must be  %%
-%% submitted separately and NOT  %%
-%% included in the Tex document  %%
-%%                               %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%
-%% Do not use \listoffigures as most will included as separate files
-\section*{Figures}
-\begin{figure}[h!]
-  \includegraphics[width=\textwidth]{plots/comp_time_log.pdf}
-  \caption{\csentence{Computation time depending on number of threads and size of input data}
-  The boxplots show the differences in demand of CPU time for different number of threads and input data size for the seven different assemblers
-  }
-        \label{fig:performance_runtime}
-      \end{figure}
-
-\begin{figure}[h!]
-  \includegraphics[width=\textwidth]{plots/usage_amount_threads.pdf}
-  \caption{\csentence{Performance metrics}
-      Boxplots depicting the demand of CPU and RAM and disk space needed depending on the assembler, input data size and number of threads}
-      \label{fig:performance_memory_cpu}
-      \end{figure}
-
-\begin{figure}[h!]
-  \includegraphics[width=\textwidth]{plots/sim_tiles.pdf}
-  \caption{\csentence{Score of assemblies on simulated data}
-      Results of assemblies from simulated data sets. Color scale of the tiles represents the score }
-      \label{fig:simulated}
-      \end{figure}
-
-  \begin{figure}[h!]
-  \includegraphics[width=\textwidth]{plots/swarm.pdf}
-  \caption{\csentence{Results of scoring of the seven assemblers}
-  The box- and swarplots depict the results of the scoring algorithm we used. For the different assemblers. The whiskers of boxplots indicate the 1.5 x interquartile range. 
-    }
-      \label{fig:swarmplot}
-      \end{figure}
-
-\begin{figure}[h!]
-  \includegraphics[width=\textwidth,page=2]{plots/upset.pdf}
-  \caption{\csentence{Upset plot \cite{lex2014upset} comparing success of assemblers on the real data sets}
-      The plot shows the intersection of success ($score > 99$) between assemblers.
-For \num{69} data sets only \go{} was able to obtain a complete chloroplast.
-\num{43} were successful with both \go{} and \fp{} and so on}
-            \label{fig:upset}
-      \end{figure}
-
-\begin{figure}[h!]
-  \includegraphics[width=\textwidth]{plots/repro.pdf}
-  \caption{\csentence{Scores between two repeated runs for consistency testing}
-  The scatter plots depicts the scores of the 1. runs x-axis versus the scores of the 2. run y-axis of the data sets that were selected for re-evaluation. 
-      }
-      \label{fig:consistency}
-      \end{figure}
-
-\begin{figure}[h!]
-  \includegraphics[width=\textwidth]{plots/real_datasets_tree.pdf}
-  \caption{\csentence{Success of assemblers on real data sets on tree derived from NCBI taxonomy \cite{ncbi2011}}
-       }
-      \label{fig:tree}
-      \end{figure}\todo{cite itol}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                               %%
-%% Tables                        %%
-%%                               %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Use of \listoftables is discouraged.
-%%
-\section*{Tables}
-\begin{table}[h!]
-\caption{Docker images used in our benchmark setup.}
-\label{tab:dockerimages}
+\newpage
+{\tiny
+\captionof{table}{Docker images used in our benchmark setup.}
+\label{tab:dockerimages_suppl}
 \centering
-      \resizebox{\textwidth}{!}{\begin{tabular}{ccc}
+\begin{tabular}{ccc}
         \hline
@@
           \oa & \dockeroa & \dockeroasha \\ \hline
-      \end{tabular}}
-\end{table}
-
-\begin{table}[]
-    \centering
-    \caption{Overview of the results of the qualitative usability evaluation. Each tool 
-    could score \good{}, \ok{} or \bad{} in each of the categories.}
-    \label{tab:resultsqual}
-\begin{tabular}{p{3cm}cccccc}   
-Tool & Installation & Test/Tutorial & Documentation & Maintenance & FLOSS\\                           \hline \ce{}     &  \good{}  &  \good{}  &  \good{}  &  \good{}  &  \good{} \\
-\cassp{}  &  \ok{}    &  \good{}  &  \ok{}    &  \good{}  &  \good{} \\
-\fp{}     &  \bad{}   &  \ok{}    &  \good{}  &  \good{}  &  \good{} \\
-\go{}     &  \ok{}    &  \ok{}    &  \good{}  &  \good{}  &  \good{} \\
-\ioga{}   &  \bad{}   &  \bad{}   &  \ok{}    &  \ok{}    &  \bad{}  \\
-\np{}     &  \good{}  &  \good{}  &  \good{}  &  \good{}  &  \ok{}   \\
-\oa{}     &  \bad{}   &  \bad{}   &  \ok{}    &  \good{}  &  \good{} \\ \hline
       \end{tabular}
-\end{table}
-
-\begin{table}[ht]
-\caption{Scores of assemblies of simulated data}
-\label{tab:scores}
-\centering
-\begin{tabular}{rlrrrrrrr}
-  \hline
- & data set & CAP & CE & Fast-Plast & GetOrganelle & IOGA & NOVOPlasty & org.ASM \\ 
-  \hline
-1 & sim\_150bp.0-1 & 79.10 & 100.00 & 99.72 & 100.00 &  & 91.52 & 100.00 \\ 
-  2 & sim\_150bp.1-10 &  & 56.44 &  & 100.00 &  & 91.52 & 78.00 \\ 
-  3 & sim\_150bp.1-10.2M &  &  & 99.97 & 100.00 &  & 100.00 & 82.72 \\ 
-  4 & sim\_150bp.1-100 &  & 100.00 &  & 100.00 &  & 91.52 & 91.50 \\ 
-  5 & sim\_150bp.1-100.2M &  & 100.00 & 99.47 & 100.00 & 74.82 & 100.00 & 100.00 \\ 
-  6 & sim\_150bp.1-1000 & 79.10 &  &  & 100.00 &  & 91.52 & 91.50 \\ 
-  7 & sim\_150bp.1-1000.2M & 79.10 & 100.00 & 99.72 & 100.00 &  & 91.52 & 100.00 \\ 
-  8 & sim\_250bp.0-1 & 79.10 & 100.00 & 93.83 & 100.00 &  & 91.52 & 100.00 \\ 
-  9 & sim\_250bp.1-10 &  & 54.98 & 68.45 & 100.00 &  & 91.52 & 40.20 \\ 
-  10 & sim\_250bp.1-10.2M &  &  & 93.00 & 100.00 &  & 87.40 & 40.20 \\ 
-  11 & sim\_250bp.1-100 &  & 100.00 & 93.83 & 100.00 & 65.81 & 91.52 & 100.00 \\ 
-  12 & sim\_250bp.1-100.2M &  & 100.00 & 93.83 & 100.00 & 75.73 & 87.40 & 100.00 \\ 
-  13 & sim\_250bp.1-1000 & 79.10 & 21.30 &  & 100.00 &  & 91.52 & 91.50 \\ 
-  14 & sim\_250bp.1-1000.2M & 79.10 & 100.00 & 93.83 & 100.00 &  & 87.40 & 100.00 \\ 
-   \hline
-\end{tabular}
-\end{table}
-
-\begin{table}[ht]
-\caption{Mean scores of chloroplast genome assemblers}
-\label{tab:scores}
-\centering
-\begin{tabular}{rlrrrr}
-  \hline
- & assembler & Mean & SD & N\_perfect & N\_tot \\ 
-  \hline
-  1 & CAP & 51.26 & 8.42 &   0 & 221 \\ 
-  2 & CE & 69.99 & 12.33 &  14 & 205 \\ 
-  3 & Fast-Plast & 86.96 & 15.33 & 114 & 352 \\ 
-  4 & GetOrganelle & 89.13 & 15.30 & 199 & 356 \\ 
-  5 & IOGA & 68.74 & 11.69 &   0 & 296 \\ 
-  6 & NOVOPlasty & 82.78 & 16.55 &  66 & 270 \\ 
-  7 & org.ASM & 82.77 & 16.38 &  55 & 228 \\ 
-   \hline
-\end{tabular}
-\end{table}
-
-\include{sets_re_runs.tex}
+}
+\end{landscape}
 
@@
 
-% \begin{table}[h!]
-% \caption{Sample table title. This is where the description of the table should go.}
-%       \begin{tabular}{cccc}
-%         \hline
-%           & B1  &B2   & B3\\ \hline
-%         A1 & 0.1 & 0.2 & 0.3\\
-%         A2 & ... & ..  & .\\
-%         A3 & ..  & .   & .\\ \hline
-%       \end{tabular}
-% \end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                               %%
-%% Additional Files              %%
-%%                               %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Additional Files}
-  \subsection*{Additional file 1 --- Sample additional file title}
-\todo{Supplement description}
-    Additional file descriptions text (including details of how to
-    view the file, if it is in a non-standard format or the file extension).  This might
-    refer to a multi-page table or a figure.
-
-  \subsection*{Additional file 2 --- Sample additional file title}
-    Additional file descriptions text.
-
-\end{backmatter}
 \end{document}

### 2019-06-09 manuscript/sra_table_generation/generate_sra_ref.sh

@@ -1,0 +1,11 @@
+#!/bin/bash
+
+# Get the data from NCBI
+for i in $(sed '1d' ../sets_re_runs.csv | tr -d '"' | cut -f 2 -d ","); do sra-stat --quick ${i}; done | tee sets_sra-info.txt
+
+# Create a temporary file with combined information
+perl -ne 'chomp; my ($id, $tag, $reads, $rest) = split(/\|/, $_); my ($readnumber, $basenumber, undef) = split(":", $reads); $h{$id}{reads}+=$readnumber; $h{$id}{bases}+=$basenumber; END{ foreach my $id (sort keys %h) { printf "%s\t%d\t%d\t%.0f\n", $id, $h{$id}{reads}, $h{$id}{bases}, ($h{$id}{bases}/$h{$id}{reads}/2); }}' sets_sra-info.txt >blub.txt
+
+wget https://raw.githubusercontent.com/chloroExtractorTeam/benchmark/master/data/real/real_datasets.t
+
+join blub.txt <( join <(awk -F"," '{printf "%s\t%s\n", $2,$3}' sets_re_runs.csv | sed '/Re-eval/d' | sort | tr -d '"') <(sort real_datasets.tsv))  | perl generate_tab.pl | tee ../sra_ref.tex

### 2019-06-09 manuscript/bmc_article.tex
Update on Overleaf.

@@
 \newcommand{\good}{\textsc{Good}}
+
+\usepackage{xr}
+\externaldocument{supplement}
 
@@
 \fp{} is outperforming the latter two slightly in terms of score, with twice as much \num{114} perfectly assembled chloroplast genomes (\np{} produced \num{66} and \oa{} \num{55} circular genomes).
-\ioga{} and \cassp{} were both not able to assemble a circular, single-contig genome (\cref{tab:scores}), consequently resulting in the lowest mean and median scores (\cref{fig:upset}).
-
+\ioga{} and \cassp{} were both not able to assemble a circular, single-contig genome (\cref{tab:scores_real}), consequently resulting in the lowest mean and median scores (\cref{fig:upset}).
 %\textit{swarm plot goes here}
@@
 Both \ioga{} and \cassp{} have the worst performance of all tools tested and fail to return reliable chloroplast assemblies.
+
+Additionally, we observed no phylogenetic pattern in the success rate of the assemblers (\cref{fig:tree}).
+This indicates that the tools are generally able to reconstruct chloroplasts across the plant kingdom even without or with fixed \plant{At} as reference.
 
@@
 Those docker images were used for the recording of the consumption of computational resources.
+Those docker images have been used for the performance benchmarking on a four Intel CPU-E7 8867 v3 system offering \SI{1}{\tera\byte} of RAM.
 Furthermore, all our docker images have been converted into singularity containers for the quantitative measurement on simulated and real data sets.
@@
 For each species with a reference chloroplast in CpBase \cite{cpbase}, we selected one data set of those.
-In total, this accumulated to \num{369} data sets (see supplement for details).
+In total, this accumulated to \num{369} data sets (\cref{tab:real_dataset_details}) representing a broad spectrum of the green plants (\cref{fig:tree}).
 
@@
   \includegraphics[width=\textwidth]{plots/real_datasets_tree.pdf}
-  \caption{\csentence{Success of assemblers on real data sets on tree derived from NCBI taxonomy \cite{ncbi2011}. Plot was prepared using \cite{Letunic2019}}
+  \caption{\csentence{Success for chloroplast assembly shows no taxonomic bias} Success of assemblers on real data sets on tree derived from NCBI taxonomy \cite{ncbi2011}.
+Plot was prepared using \cite{Letunic2019}
        }
@@
 \section*{Tables}
-\begin{table}[]
+\begin{table}[h!]
     \centering
-    \caption{Overview of the results of the qualitative usability evaluation. Each tool 
+    \caption{\textbf{Overview of the results of the qualitative usability evaluation} Each tool 
     could score \good{}, \ok{} or \bad{} in each of the categories.}
@@
 
-\begin{table}[ht]
-\caption{Scores of assemblies of simulated data}
+\begin{table}[h!]
+\caption{\textbf{Scores of assemblies of simulated data}}
 \label{tab:scores_simulated}
@@
 
-\begin{table}[ht]
-\caption{Mean scores of chloroplast genome assemblers}
+\begin{table}[h!]
+\caption{\textbf{Mean scores of chloroplast genome assemblers}}
 \label{tab:scores_real}
@@
 \begin{table}[h!]
-\caption{Docker images used in our benchmark setup.}
+\caption{\textbf{Docker images used in our benchmark setup} SHA256 checksums are stated in \cref{tab:dockerimages_suppl}}
 \label{tab:dockerimages}
@@
         \hline
-          Tool & Image name and tag & SHA256 Checksum   \\ \hline
-          \ce & \dockerce & \dockercesha \\
-          \cassp & \dockercassp & \dockercasspsha \\
-          \fp & \dockerfp & \dockerfpsha \\
-          \go & \dockergo & \dockergosha \\
-          \ioga & \dockerioga & \dockeriogasha \\
-          \np & \dockernp & \dockernpsha \\
-          \oa & \dockeroa & \dockeroasha \\ \hline
+          Tool & Image name and tag\\ \hline
+          \ce & \dockerce \\
+          \cassp & \dockercassp \\
+          \fp & \dockerfp \\
+          \go & \dockergo \\
+          \ioga & \dockerioga \\
+          \np & \dockernp \\
+          \oa & \dockeroa \\ \hline
       \end{tabular}}
@@
 \section*{Additional Files}
-  \subsection*{Additional file 1 --- Sample additional file title}
-\todo{Supplement description}
-    Additional file descriptions text (including details of how to
-    view the file, if it is in a non-standard format or the file extension).  This might
-    refer to a multi-page table or a figure.
-
-  \subsection*{Additional file 2 --- Sample additional file title}
-    Additional file descriptions text.
+  \subsection*{Additional file 1 --- supplemental data}
+  Supplementary data contain a complete list of all real data sets used in this study.
+Additionally, a table with more details to the used docker images and the detailed results of the performance measurement are included.
+The file is available at \cite{supplement}.
 

### 2019-06-09 manuscript/bmc_article.tex
Update on Overleaf.

@@
 \usepackage{xr}
-\externaldocument{supplement}
+\makeatletter
+\newcommand*{\addFileDependency}[1]{% argument=file name and extension
+  \typeout{(#1)}
+  \@addtofilelist{#1}
+  \IfFileExists{#1}{}{\typeout{No file #1.}}
+}
+\makeatother
+
+\newcommand*{\myexternaldocument}[1]{%
+    \externaldocument{#1}%
+    \addFileDependency{#1.tex}%
+    \addFileDependency{#1.aux}%
+}
+\myexternaldocument{supplement}
 
@@
 Both \np{} and \oa{} take about the same time independent of being able to utilize \numlist[list-final-separator={, or }]{1;2;4;8} threads.
-\cassp{}, \ce{}, \go  and \fp{} all profit from multi-threading (\cref{fig:performance_runtime,fig:performance_memory_cpu}).
+\cassp{}, \ce{}, \go  and \fp{} all profit from multi-threading (\cref{fig:performance_runtime,fig:performance_memory_cpu,tab:perform25K_suppl,tab:perform250K_suppl,tab:perform2.5M_suppl}).
 
 \subsubsection*{Memory and CPU Usage }
-The peak and mean CPU usage, as well as peak memory and disk usage have been recorded for all assemblers based on the same input data set and number of threads to use (\cref{fig:performance_memory_cpu}).
+The peak and mean CPU usage, as well as peak memory and disk usage have been recorded for all assemblers based on the same input data set and number of threads to use (\cref{fig:performance_memory_cpu,tab:perform25K_suppl,tab:perform250K_suppl,tab:perform2.5M_suppl}).
 Mainly, the size of the input data influenced the peak memory usage with the exception of \ce{} and \ioga{}.
@@
 Additionally, a table with more details to the used docker images and the detailed results of the performance measurement are included.
-The file is available at \cite{supplement}.
+The file is available at \cite{zenodosupplement}.
 

### 2019-06-09 manuscript/bmc_article.tex
Update on Overleaf.

@@
 
+\section*{Availability of data and materials}
+The supplemental material is available from Zenodo \cite{zenodosupplement}.
+The simulated data set is available from Zenodo \cite{zenododataset}.
+All program code is available via Zenodo \cite{zenodorepo} or from Github \cite{github-benchmark-repo}.
+The input data sets can be generated using the raw reads from NCBI SRA (links for each data set in \cref{tab:real_dataset_details}).
+The resulting assemblies are avaiable from Zenodo \cite{zenodoassemblies}.
+
 %\section*{Acknowledgements}

### 2019-06-09 manuscript/supplement.tex
Update on Overleaf.

@@
 Moreover, the original number of read pairs (read pairs), the overall number of sequenced nucleotides (base pairs), and the mean read length (read len.) is given.
-Finally, the last column contains the information, if that data set was used for the check of the consistency.} \\
+Finally, the last column contains the information, if that data set was used for the check of the consistency.}\label{tab:real_dataset_details} \\
 \hline
@@
 \caption{Performance metrics input size 25K}
-\label{tab:perform25K}
+\label{tab:perform25K_suppl}
 \centering
@@
   \hline
- & program & threads & Peak CPU usage & Peak memeory & Peak disk usage (GB) \\ 
+ & program & threads & Peak CPU usage & Peak memory & Peak disk usage (GB) \\ 
   \hline
@@
 \caption{Performance metrics input size 250K}
-\label{tab:perform250K}
+\label{tab:perform250K_suppl}
 \centering
@@
 \caption{Performance metrics input size 2.5M}
-\label{tab:perform2.5M  }
+\label{tab:perform2.5M_suppl}
 \centering
@@
   \hline
- & program & threads & Peak CPU usage & Peak memeory & Peak disk usage (GB) \\ 
+ & program & threads & Peak CPU usage & Peak memory & Peak disk usage (GB) \\ 
  \hline

### 2019-07-22 code/eval_novel.sh
Create eval_novel.sh
Create a new evaluation file for novel dataset assemblies

@@ -1,0 +1,25 @@
+#!/usr/bin/env bash
+
+QRY=$1
+NAME=$2
+QRYF=$(tempfile)  
+cat $QRY | sed 's/>.*/>c/g' | seqkit rename  > $QRYF
+
+
+
+echo -ne "$NAME\t"
+
+blastn -query output.fa -subject output.fa -outfmt  '7 qseqid sseqid pident length qstart qend sstart send sstrand slen qlen' | grep minus | awk '$3 == "100.00" ' | awk '$1 == $2' |   sort -nr -k 4,4 | sed -n 1p | awk  '{print $4, $11}' | tr "\n" "\t"
+
+
+
+grep -c  "^>" $QRY
+
+rm ${NAME}_vs_ref.bam 
+rm ref_vs_${NAME}.bam
+
+### for the simulated data 
+#for i in */*/output.fa ; do echo -ne "$(dirname $(dirname $i))\t"  >> res.tsv ; ../evaluate_completeness.sh /home/maa62rb/sim/athaliana_chloro_sim/TAIR10_chrC.fas $i $(basename $(dirname $i)) >> res.tsv ; done
+
+## for the real datsets 
+#for i in */*/output.fa ; do dat=$(dirname $(dirname $i)); echo -ne "$dat\t"  >> res.tsv ; ../evaluate_completeness.sh ~maa62rb/real/references/$(cat /home/maa62rb/real/real_datasets.tsv   | grep $dat  | awk '{print $NF}').fa $i $(basename $(dirname $i)) >> res.tsv ; done

### 2019-07-22 code/eval_novel.sh
Update eval_novel.sh

@@ -2,21 +2,12 @@
 
 QRY=$1
 NAME=$2
-QRYF=$(tempfile)  
-cat $QRY | sed 's/>.*/>c/g' | seqkit rename  > $QRYF
-
-
-
 echo -ne "$NAME\t"
 
 blastn -query output.fa -subject output.fa -outfmt  '7 qseqid sseqid pident length qstart qend sstart send sstrand slen qlen' | grep minus | awk '$3 == "100.00" ' | awk '$1 == $2' |   sort -nr -k 4,4 | sed -n 1p | awk  '{print $4, $11}' | tr "\n" "\t"
 
-
-
 grep -c  "^>" $QRY
 
-rm ${NAME}_vs_ref.bam 
-rm ref_vs_${NAME}.bam
 
 ### for the simulated data 
 #for i in */*/output.fa ; do echo -ne "$(dirname $(dirname $i))\t"  >> res.tsv ; ../evaluate_completeness.sh /home/maa62rb/sim/athaliana_chloro_sim/TAIR10_chrC.fas $i $(basename $(dirname $i)) >> res.tsv ; done

### 2019-07-22 code/eval_novel.sh
Update eval_novel.sh

@@ -4,7 +4,7 @@ QRY=$1
 NAME=$2
 echo -ne "$NAME\t"
 
-blastn -query output.fa -subject output.fa -outfmt  '7 qseqid sseqid pident length qstart qend sstart send sstrand slen qlen' | grep minus | awk '$3 == "100.00" ' | awk '$1 == $2' |   sort -nr -k 4,4 | sed -n 1p | awk  '{print $4, $11}' | tr "\n" "\t"
+blastn -query $QRY -subject $QRY -outfmt  '7 qseqid sseqid pident length qstart qend sstart send sstrand slen qlen' | grep minus | awk '$3 == "100.00" ' | awk '$1 == $2' |   sort -nr -k 4,4 | sed -n 1p | awk  '{print $4, $11}' | tr "\n" "\t"
 
 grep -c  "^>" $QRY
 

### 2019-07-23 code/eval_novel.sh
Update eval_novel.sh

@@ -4,13 +4,9 @@ QRY=$1
 NAME=$2
 echo -ne "$NAME\t"
 
-blastn -query $QRY -subject $QRY -outfmt  '7 qseqid sseqid pident length qstart qend sstart send sstrand slen qlen' | grep minus | awk '$3 == "100.00" ' | awk '$1 == $2' |   sort -nr -k 4,4 | sed -n 1p | awk  '{print $4, $11}' | tr "\n" "\t"
+blastn -query $QRY -subject $QRY -outfmt  '7 qseqid sseqid pident length qstart qend sstart send sstrand slen qlen' | grep minus | awk '$3 ~ "100.00" ' | awk '$1 == $2' |   sort -nr -k 4,4 | sed -n 1p | awk  '{print $4, $11}' | tr "\n" "\t"
 
 grep -c  "^>" $QRY
 
-
-### for the simulated data 
-#for i in */*/output.fa ; do echo -ne "$(dirname $(dirname $i))\t"  >> res.tsv ; ../evaluate_completeness.sh /home/maa62rb/sim/athaliana_chloro_sim/TAIR10_chrC.fas $i $(basename $(dirname $i)) >> res.tsv ; done
-
-## for the real datsets 
-#for i in */*/output.fa ; do dat=$(dirname $(dirname $i)); echo -ne "$dat\t"  >> res.tsv ; ../evaluate_completeness.sh ~maa62rb/real/references/$(cat /home/maa62rb/real/real_datasets.tsv   | grep $dat  | awk '{print $NF}').fa $i $(basename $(dirname $i)) >> res.tsv ; done
+# Execute with : 
+# for i in */*/output.fa ; do echo $i ;  echo -ne "$(dirname $(dirname $i))\t"  >> res.tsv ; ./eval_novel.sh  $i $(basename $(dirname $i)) >> res.tsv ; done

### 2019-07-24 code/evaluate_completeness.sh
Update evaluate_completeness.sh

@@ -17,7 +17,8 @@ rm ${NAME}_vs_ref.bam
 rm ref_vs_${NAME}.bam
 
 ### for the simulated data 
-#for i in */*/output.fa ; do echo -ne "$(dirname $(dirname $i))\t"  >> res.tsv ; ../evaluate_completeness.sh /home/maa62rb/sim/athaliana_chloro_sim/TAIR10_chrC.fas $i $(basename $(dirname $i)) >> res.tsv ; done
+#for i in */*/output.fa ; do echo -ne "$(dirname $(dirname $i))\t"  >> res.tsv ; ../evaluate_completeness.sh ~maa62rb/chloroplast_benchmark/data/sim/TAIR10_chrC.fas $i $(basename $(dirname $i)) >> res.tsv ; done
+
 
 ## for the real datsets 
 #for i in */*/output.fa ; do dat=$(dirname $(dirname $i)); echo -ne "$dat\t"  >> res.tsv ; ../evaluate_completeness.sh ~maa62rb/real/references/$(cat /home/maa62rb/real/real_datasets.tsv   | grep $dat  | awk '{print $NF}').fa $i $(basename $(dirname $i)) >> res.tsv ; done

### 2020-05-19 manuscript/reviewer_response1.tex
Update to latest manuscript version

\documentclass[a4paper,10pt]{scrartcl}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\title{Response to Reviewers}
\author{Markus J. Ankenbrand and Frank F\"{o}rster for the authors}
\date{\today}
%
\begin{document}
\maketitle
\section{Editor}
We have now received reports from two referees, whose comments are available below.
As you will see from the reports, both referees raised serious concerns that the benchmark hasn't provided sufficient advance to be useful for the field.
At this stage, therefore, we are not persuaded that an offer of publication in Genome Biology would be justified.
Unless you can address all of the issues raised by the referees I am afraid that we would not be able to consider this work again.
In particular we ask that you provide additional analyses as requested by both referees to convince them of the advance.
The revised manuscript should address in full all the points raised by both referees; a separate list of the revisions made, specifying where in the manuscript the changes have been made, would also be helpful.
Please note that all data generated for the manuscript should be deposited in a relevant public repository, with accession codes listed in the manuscript's Availability of Data and Materials section.
All other supporting data should also be signposted.
If you decide to submit a revised version, you will need to  this as a new manuscript, although we would consider it in the same way as we do all revised manuscripts.
The exception is that we will take into account any work published in the intervening period.
For the time being, however, we hope that you will find our referees' comments helpful in deciding how to proceed.
Please feel free to contact us if you have any questions.

\section{Reviewer 1}
Methods are appropriate but same authors developed ChloroExtractor, an important tool used as a benchmark in this study.
Authors compare seven chloroplast genome assembly tools.
So, this reviewer is not sure of novelty of this manuscript.
So, authors haven't addressed the important question "Does the work represent a significant advance over previously published studies?".

\textbf{
Indeed the novelty in this article is not a new approach to the task of chloroplast genome assembly but rather a thourough benchmark of existing tools (including our tool ChloroExtractor).
This represents a substantial advance for the field as there are competing tools published for the same task without any information about their relative performances.
Currently, researchers have to do this evaluation of tools themselves to find the appropriate tool which leads to duplicated efforts as this is done by every group separately and without sharing results.
If this evaluation is neglected a suboptimal tool might be used which can lead to additional manual efforts in finishing or additional costs if more data is generated.
Thus, clear guidelines to the end user (and important directions for improvement to the developers) are novel, important and benficial for the research community.
}

User experience and success rate should be determined by users and documented through satisfaction surveys.
This is especially important when authors emphasize that program can be used using standard computer infrastructure.

\textbf{
We agree that this would be the best way to measure and quantify user experience.
However, this is not feasible with limited budget and time (TODO: is this excuse good enough?) while the main focus of the work was on quantitative performance measures, anyway.
We decided to include usability metrics that were obtainable in a defined and structured way using the JOSS reviewer guidelines.
}

There is >1,000 sequenced chloroplast genomes, with a large majority not fully assembled or annotated.
So, authors have plenty of opportunity to demonstrate use of these new assembly tools.

\textbf{
Thanks for pointing this out.
We now include as a proof of principle the application of these tools on more than 100 novel datasets.
We thus clearly demonstrate that the insights from this article can be used to produce further novel results that can lead to biological insight.
}

It is well known that intergenic spacer regions are not conserved and not even a single intergenic spacer region is conserved within chloroplasts genomes of the graminae or grass genomes.
Intergenic spacer region occupies >50\% of the genome.
So, how does reference genome help in genome assembly?

\textbf{
This is a very interesting question.
We don't think that this is within the scope of our publication as we compare de novo assembly tools.
TODO: some people use it, some programs use it, it seems to work often but actually your argument is justification why we restricted our analysis to de novo tools.
}

In order to have real life comparison, authors could have sequenced few chloroplast genomes and used that data to compare different assembly tools and time taken for each program, pros and cons.

\textbf{
We already tested the tools on real datasets downloaded from SRA which is equivalent to customly sequenced data.
But we now include additional 100+ novel data sets with no reference chloroplast in the database.
}

- Is the paper of broad interest to others in the field, or of outstanding interest to a broad audience of biologists?
This is of interest to evolutionary biologists to study phylogenetics or for chloroplast genetic engineering.

\section{Reviewer 2}
This study provides an systematically comparison of the chloroplast assembly tools at first and show significant differences between the tested assemblers in terms of generating whole chloroplast genome sequences and computational requirements.
Moreover, the authors created docker images for each tested tool, which are available for the scientific community and improved reproducibility, thus large scale screening for chloroplasts as hidden treasures within genomic sequencing data is feasible.
This topic of the review paper is knowledgeable and helpful for all the scientists who are working in the field of plant chloroplast assembly.
However, the overall manuscript is not well written and contains limited information about systematically comparison of the chloroplast assembly tools and docker images for assembled reproducibility.

\textbf{
Thanks for your thorough review and the pointers that helped us improve the overall readability of the manuscript.
In addition we received feedback and edits from a native English speaker to further improve readabilty.
TODO: how do we adress the "limited information" aspect. We could link to the github repo that contains all data and code we used including the dockerfiles.
}

Specific points: The number of lines on the edge does not correspond to the maintext.

The major concerns about this manuscript can be found below and major revision is suggested before publication in "Genome Biology".

\begin{itemize}
    \item Page1  part of "General introduction and motivation"
    \item Line 4: It should be quote recent article
    \item Line 11: It should be quote recent article
    \item Page2
    \item Line 16: It should be IRa and IRb
    \item Line 18: It should be quote recent article
    \item Line 24-27: Re-write sentence
    \item Part of "Approaches to extracting chloroplasts from whole genome data"
    \item Line 6: Delete the dot before the quote
    \item Lines 7-9: Re-write sentence
    \item Part of "Purpose and scope of this study"
    \item Line 2: It should be in italic type
    \item Line 2: It should be genome
    \item Line 3: Raw genomic data sets should be filter out low-quality reads by quality control
    \item Lines 4 and 5: Many command-line tools of de novo assemble for chloroplast genome have all of these features, e.g., MITObim.
    \item Part of "Time requirements"
    \item Line 1: It should be among
    \item Line 4: Different tools with more than 1 gigabyte data sets should be tested, and Figure1 can`t give valuable information as no significant difference for time-consuming. The same question for Part of "Memory and CPU Usage". Why these seven assemblers were chosen to test? Figure should be "Fig." and table as "Table".
    \item Part of "Qualitative"
    \item Line 3: NGS data for crop genomes can`t be used for GetOrganelle? In this part, the same data set should be used to test for every assemblers better.
    \item Part of "Quantitative"  
    \item Part of "Simulated data"
    \item Line 1: Why not show the result for different data sets with every assemblers in Fig.3 and Table 2? Fig.3 and table 2 show no regular pattern in scores except the assembler GetOrganelle obtaining perfect.
    \item Part of "Real data sets"
    \item Line 3: The performance of GetOrganelle was bad, as only 199 circular assemblies out of a total of 356 assemblies that resulted in an output, the percent is 55.9\%, however it achieved a median scores of 99.7. The number "99.7" should to be "89.13", as show in table 3? The SD value of GetOrganelle is too large than the other three tools but it achieved the highest scores.
    \item Part of "Consistency"
    \item Line 3: As shown in the Fig.6, only two tools achieved R2  not equal 1 by re-running assemblies and comparison of the scores of two assemblers, however, GetOrganelle defined as the only tool that succeed in obtaining similar score for all assemblers, this conclusion is not rigorous.
\end{itemize}
\end{document}

### 2020-05-19 manuscript/bmc_article.tex
Update to latest manuscript version

@@
 
-\usepackage[noabbrev]{cleveref}
 \usepackage{siunitx}
@@
 
-\usepackage{todonotes}
-\setlength{\marginparwidth}{3cm}
-
-\newcounter{todocounter}
-\newcommand{\ff}[1]
-{\stepcounter{todocounter}
- \todo[color=blue!40,author=For Frank]{\thetodocounter: #1}
- }
-\newcommand{\ak}[1]
-{\stepcounter{todocounter}
- \todo[color=green!40,author=Arthur]{\thetodocounter: #1}
- }
+% \usepackage{todonotes}
+% \setlength{\marginparwidth}{3cm}
+
+% \newcounter{todocounter}
+% \newcommand{\ff}[1]
+% {\stepcounter{todocounter}
+%  \todo[color=blue!40,author=For Frank]{\thetodocounter: #1}
+%  }
+% \newcommand{\ak}[1]
+% {\stepcounter{todocounter}
+%  \todo[color=green!40,author=Arthur]{\thetodocounter: #1}
+%  }
+\newcommand{\todo}[1]{\textcolor{red}{\bfseries(ToDO: #1})}
 
@@
 
+\usepackage[acronym,hyperfirst=false]{glossaries}
+\newacronym{joss}{JOSS}{Journal of Open Source Software}
+\newacronym{lsc}{LSC}{Large Single Copy}
+\newacronym{ssc}{SSC}{Small Single Copy}
+\newacronym{ir}{IR}{Inverted Repeat}
+\newacronym{gui}{GUI}{graphical user interface}
+
+\glsdisablehyper
+\makeglossaries
+
 % Niklas table
@@
 
+%\usepackage[noabbrev]{cleveref}
+\usepackage{cleveref}
+\crefname{figure}{Figure}{Figures}
+\crefname{table}{Table}{Tables}
+
 % List of docker images
@@
     addressref={aff1,aff3},
-    noteref={n1},
+    %noteref={n1},
     email={jan.freudenthal@uni-wuerzburg.de}
@@
     addressref={aff1,aff2},
-    noteref={n1},
     email={simon-pfaff@gmx.de}
@@
    addressref={aff1,aff3},
-   email={niklas.terhoeven@uni-wuerzubrg.de}
+   email={niklas.terhoeven@uni-wuerzburg.de}
 ]{\inits{NT}\fnm{Niklas} \snm{Terhoeven}}
@@
    addressref={aff1},
-   email={arthur.korte@uni-wuerzubrg.de}
+   email={arthur.korte@uni-wuerzburg.de}
 ]{\inits{AK}\fnm{Arthur} \snm{Korte}}
 \author[
-   addressref={aff1,aff3,aff2 },
+   addressref={aff1,aff3,aff4 },
    noteref={n2},
-   email={markus.ankenbrand@uni-wuerzubrg.de}
+   email={markus.ankenbrand@uni-wuerzburg.de}
 ]{\inits{MJA}\fnm{Markus J} \snm{Ankenbrand}}
 \author[
-   addressref={aff1,aff2,aff4},                   % id's of addresses, e.g. {aff1,aff2}
+   addressref={aff1,aff2,aff5},                   % id's of addresses, e.g. {aff1,aff2}
    corref={aff1},                       % id of corresponding address, if any
@@
   \orgname{AnaLife Data Science},
-  \street{Friedrich-Bergius-Ring 15},
-  \postcode{97076}
+  \street{Wiesengrund 16},
+  \postcode{97295 Waldbrunn}
   \city{W\"{u}rzburg},
@@
 }
-
 \address[id=aff4]{%
+  \orgname{Chair of Cellular and Molecular Imaging, Comprehensive Heart Failure Center, University Hospital W\"{u}rzburg},
+  \street{Josef-Schneider-Str.\ 2},
+  \postcode{97080}
+  \city{W\"{u}rzburg},
+  \cny{Germany}
+}
+
+\address[id=aff5]{%
   \orgname{Fraunhofer IME-BR},
   \street{Winchester Str.\ 2},
-  \postcode{97076}
+  \postcode{35394}
   \city{Gie\ss{}en},
@@
 %\note{Sample of title note}     % note to the article
-\note[id=n1]{Equal contributor} % note, connected to author
+%\note[id=n1]{Equal contributor} % note, connected to author
 \note[id=n2]{Corresponding author} % note, connected to author
@@
 %One or two sentences providing a basic introduction to the field, comprehensible to a scientist in any discipline.
-Chloroplasts are photosynthetic organelles in plant cells and contain their own genomic information.
-That genome can be utilized in different scientific fields like phylogenetics or biotechnology.
+Chloroplasts are intracellular organelles that enable plants to conduct photosynthesis.
+They arose through the symbiotic integration of a prokaryotic cell into an eukaryotic host cell and still contain their own genomes with distinct genomic information.
+Plastid genomes accommodate essential genes and are regularly utilized in biotechnology or phylogenetics.
 %Two to three sentences of more detailed background, comprehensible to scientists in related disciplines.
-Thus, different assemblers have been developed specialized in chloroplast assemblies.
-Those assemblers often use the output of whole genome sequencing experiments as input.
-Such sequencing data usually contain the complete chloroplast genome information, even if the sequencing aims for the core genome.
+Different assemblers that are able to asses the plastid genome, have been developed.
+These assemblers often use data of whole genome sequencing experiments, which usually contain reads from the complete chloroplast genome as well, as input.
+
 %One sentence clearly stating the general problem being addressed by this particular study.
-Different assembly tools have never been systematically compared. %to each other concerning success rate or computational requirements.
+The performance of different assembly tools has never been systematically compared. %to each other concerning success rate or computational requirements.
 %One sentence summarising the main result (with the words “here we show” or their equivalent).
-Here we present a benchmark of seven chloroplast assembly tools, capable to succeed in more than \SI{60}{\percent} of real data sets.
+Here we present a benchmark of seven chloroplast assembly tools, capable to succeed in more than \SI{60}{\percent} of known real data sets.
 %Two or three sentences explaining what the main result reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
 Our results show significant differences between the tested assemblers in terms of generating whole chloroplast genome sequences and computational requirements.
-Moreover, we suggest further development to improve user experience and success rate.
+The examination of more than \num{100} data sets with unknown plastid genomes led to the assembly of novel chloroplast genomes in almost \SI{50}{\percent} of the cases.
+%\todo{on the novel set we only have 49/105 which is roughly 47 percent}
 %One or two sentences to put the results into a more general context. 
-In terms of reproducibility, we created docker images for each tested tool, which are available for the scientific community.
-Following the presented guidelines, users are able to analyze and screen data sets for chloroplast genomes using only standard computer infrastructure.
+We created docker images for each tested tool that are freely available for the scientific community and ensure reproducibility of the analyses.
+These containers allow to analyze and screen data sets for chloroplast genomes using standard computational infrastructure.
 %Two or three sentences to provide a broader perspective, readily comprehensible to a scientist in any discipline, may be included in the first paragraph if the editor considers that the accessibility of the paper is significantly enhanced by their inclusion.
-Thus large scale screening for chloroplasts as hidden treasures within genomic sequencing data is feasible.
+Thus, large scale screening for chloroplasts as hidden treasures within genomic sequencing data is feasible.
 
@@
 \subsection*{General introduction and motivation}
-Chloroplasts are essential organelles present in plant cells and the cells of some protists.
-Chloroplasts enable the conversion of light energy into chemical energy via photosynthesis.
-They harbor their own ribosomes and a circular DNA genome usually with a size between \SIrange{120}{160}{\kilo\basepair} \cite{palmer_1985}.
-Because of this small size, the chloroplast genome has been an early target for sequencing.
-The first chloroplast genome sequences were obtained as early as 1986 \cite{ohyama_chloroplast_1986,shinozaki_complete_1986}.
-These early efforts elucidated the general genome organization and structure of the chloroplast DNA. 
-Chloroplast genome content and structure are reviewed for example in \cite{wicke_evolution_2011,green_chloroplast_2011}.
+Chloroplasts are essential organelles present in the cells of plants and autotrophic protists, which enable the conversion of light energy into chemical energy via photosynthesis.
+They harbor their own prokaryotic type of ribosomes and a circular DNA genome that varies in size between \SIrange{120}{160}{\kilo\basepair} \cite{palmer_1985}.
+Because of their small size, chloroplast genomes were one of the first targets for sequencing projects.
+The first chloroplast genome sequences were obtained in 1986 \cite{ohyama_chloroplast_1986,shinozaki_complete_1986}.
+These early efforts elucidated the general genome organization and structure of the chloroplast DNA and have been reviewed previously \cite{wicke_evolution_2011,green_chloroplast_2011}.
 Chloroplast genomes are widely used for evolutionary analyses \cite{martin_plastid_2010,xiao-ming_inferring_2017}, barcoding \cite{kress_use_2005,hollingsworth_dna_2009,de_vere_dna_2015}, and meta-barcoding \cite{bell_review_2016,deiner_environmental_2017}.
-Interesting aspects of chloroplast genomes are their small size (\SIrange{120}{160}{\kilo\basepair},\cite{palmer_1985}), caused through endosymbiotic gene transfer \cite{martin_evolutionary_2002,timmis_endosymbiotic_2004} and the low number of \numrange{100}{120} genes that are still encoded on the chloroplast genome \cite{wicke_evolution_2011}.
-Despite the overall high conservation of the genome sequence, there are striking differences in the gene content between different groups (e.g.
-the loss of the whole \genename{ndh} gene family in Droseraceae \cite{nevill_plastome-wide_2019}).
-Even more extreme evolutionary cases, where chloroplasts show a very low GC content and a modified genetic code are described \cite{su_novel_2019}.
-
-These differences call for comparative genomic approaches.
-Given the small size, it is much easier to decipher the complete chloroplast genome than the complete core genome.
-For example the \plant{At} core genome is approximately \SI{125}{\mega\basepair} in length \cite{schmuths2004,cao2011} while the size of the \plant{At} chloroplast genome with \SI{154}{\kilo\basepair} is more than \SI{800}{\times} smaller \cite{sato1999}.
-
-Even if only a single chloroplast is located inside a plant cell, several hundreds copies of the chloroplast genome exists in each cell \cite{kumar_2014,bendich_1987}.
-Therefore, many genome sequencing projects contain chloroplast reads as by-product.
-In some cases the chloroplast data is even considered contamination and experimental protocols for reducing their content have been developed \cite{lutz_isolation_2011}.
-An alternative approach to improve the assembly of the core genome would be to first resolve the chloroplast genome and afterwards use this information to remove those reads that map to the chloroplast genome.
-
-Structurally, two inverted repeats (IR\textsubscript{A} and IR\textsubscript{B}) of \SIrange{10}{76}{\kilo\basepair} divide the chloroplast genome into a large (LSC) and a small single copy (SSC) region \cite{palmer_1985}.
-Those large inverted repeats complicate automated resolution with short read technologies\cite{Wang2018}.
-Moreover, the existence of different chloroplasts within a single individual, and thus multiple different chloroplast genomes, have been described for different plants \cite{corriveau_1988,Chat2002,Scar2016}.
-Although the origin and evolutionary importance of this phenomena ---called heteroplasmy--- are only poorly understood, the assembly of whole chloroplast genomes might be hindered.
-
-Databases exist containing short read data for species where no reference chloroplast sequence is publicly available, eg.\ the Sequence Read Archive at NCBI \cite{sra2010}.
-The availability of whole chloroplast genomes would enable large scale comparative studies \cite{tonti-filippini_what_2017}.
-Additionally, reconstructed full chloroplast genomes have been used as super-barcodes \cite{coissac_barcodes_2016}, for biotechnology applications and genetic engineering \cite{daniell_chloroplast_2016}.
-
-\subsection*{Approaches to extracting chloroplasts from whole genome data}
+Interesting features of chloroplast genomes include their small size (\SIrange{120}{160}{\kilo\basepair},\cite{palmer_1985}), due to endosymbiotic gene transfer \cite{martin_evolutionary_2002,timmis_endosymbiotic_2004}, and the low number of \numrange{100}{120} genes that are encoded within the genome \cite{wicke_evolution_2011}.
+Despite the overall high sequence conservation of the chloroplast genome, there are striking differences in the gene content between different autotroph groups, exemplified by the loss of the whole \genename{ndh} gene family in Droseraceae \cite{nevill_plastome-wide_2019}).
+Even more extreme evolutionary cases, where chloroplasts show a very low GC content and a modified genetic code have been described \cite{su_novel_2019}.
+
+Structurally, two inverted repeats (\glspl{ir}) named \gls{ir}\textsubscript{A} and \gls{ir}\textsubscript{B} of \SIrange{10}{76}{\kilo\basepair} divide the chloroplast genome into a 
+%long single copy (\gls{lsc}) and a short single copy (\gls{ssc}) region
+\gls{lsc} and a \gls{ssc} region
+\cite{palmer_1985}, which complicates genome assembly with short read technologies\cite{Wang2018}.
+Moreover, the existence of different chloroplasts within a single individual, and thus multiple different chloroplast genomes, have been described for various plants \cite{corriveau_1988,Chat2002,Scar2016}.
+This phenomenon - called heteroplasmy - is only poorly understood in terms of its origin and evolutionary importance, but it impacts the assembly of whole chloroplast genomes.
+
+Nonetheless, given its small size, it is still much easier to decipher a complete chloroplast genome than a complete core genome.
+Consequently, many comparative genomic approaches target the chloroplast genome.
+For example the \plant{At} core genome is approximately \SI{125}{\mega\basepair} in length \cite{schmuths2004,cao2011} while the size of the \plant{At} chloroplast genome at \SI{154}{\kilo\basepair} is more than \SI{800} times smaller \cite{sato1999}.
+
+Each single chloroplast contains several hundred copies of its genome \cite{kumar_2014,bendich_1987}.
+Therefore, many plant core genome sequencing projects contain reads that originate from chloroplasts as a by-product and permit the assembly of chloroplast genomes.
+Such sequences are available from databases such as the Sequence Read Archive at NCBI \cite{sra2010}.
+
+Complete chloroplast genomes can be used as super-barcodes \cite{coissac_barcodes_2016}, both for biotechnology applications and genetic engineering \cite{daniell_chloroplast_2016}.
+Furthermore, the availability of whole chloroplast genomes would enable large scale comparative studies \cite{tonti-filippini_what_2017}.
+
+\subsection*{Approaches to extracting chloroplasts sequences from whole genome data}
 
 Different strategies have been developed to assemble chloroplast genomes \cite{twyford_strategies_2017}.
-In general, obtaining a chloroplast genome from WGS data requires two steps. First, the chloroplast reads have to be extracted from the mixed sequencing data. 
-The second step is the assembly and resolution of the special circular structure including the inverted repeats.
-The extraction of the reads can be achieved by mapping the reads to a reference chloroplast. \cite{Vinga2012}.
-A different approach that does not perform alignments, relies on the higher coverage of chloroplast data in the whole genome sequencing data set\cite{Chan2013}.
+In general, obtaining a chloroplast genome from whole genome sequencing (WGS) data requires two steps: (1) extraction of chloroplast reads from the sequencing data;  
+(2) assembly and resolution of the special circular structure including the \glspl{ir}.
+The extraction of chloroplast reads can be achieved by mapping the reads to a reference chloroplast. \cite{Vinga2012}.
+%\todo{gibt es dazu ein beispiel in unserem set? (niklas)}
+A different approach that does not depend on the availability of a reference chloroplast, uses the higher coverage of reads originating from the chloroplast \cite{Chan2013}.
 Here, a $k$-mer analysis can be used to extract the most frequent reads.
@@
 Alternativ nehmen wir noch einen dazu}
-A third method combines both approaches by using a reference chloroplast as seed and simultaneously assembling the reads based on $k$-mers \cite{dierckxsens_novoplasty:_2017}.
+%Arthur : Ich würds so lassen.
+A third method, which is for example used by \np{} \cite{dierckxsens_novoplasty:_2017}, combines both approaches by using a reference chloroplast as seed and simultaneously assembling the reads based on $k$-mers.
 
@@
 \subsection*{Purpose and scope of this study}
-The goal of this study is to compare the effectiveness and efficiency of existing open source command-line tools to de-novo assemble whole chloroplast genomes from raw genomic data sets with minimal configuration.
-This includes no need for extensive data preparation, no need for a specific reference (apart from \plant{At}), no need to change default parameters, no manual finishing.
-We further restricted our benchmark to paired end Illumina data sets as these are routinely generated by modern sequencing platforms \cite{Goodwin2016}.
-
-In our opinion this reflects the most common use cases: (1) a user trying a tool quickly without digging into options for fine tuning and (2) large scale automatic applications.
-Still, we acknowledge that the performance of the tools might be significantly improved by optimizing parameters (and references if applicable) for each data set specifically.
-However, an exhaustive comparison - including tuning of all different possible parameters for each tool- was out of scope for this study.
-
-Our results will enable the discovery of novel chloroplast genomes as well as an assembly of inter/intra-individual differences in the respective chloroplast genomes.
+The goal of this study was to compare the effectiveness and efficiency of existing open source command-line tools to perform a de-novo assembly of whole chloroplast genomes from raw genomic data.
+We only compared tools that require minimal configuration, which includes no need for extensive data preparation, no need for a specific reference (apart from \plant{At}), no need to change default parameters, and no manual finishing.
+We further restricted our benchmark to paired end Illumina data as the sole input, as  these are routinely generated by modern sequencing platforms \cite{Goodwin2016}.
+
+Thus our analyses reflect the most common use cases: (1) trying a tool quickly without digging into options for fine tuning; (2) large scale automatic applications.
+We tested all tools on more than \num{100} real data sets for species without published chloroplast genomes.
+The performance of most tools might be significantly improved by optimizing parameters for each data set specifically, but this exhaustive comparison - including tuning of all different possible parameters for each tool- was out of the scope of this study.
+
+To summarize, we provide new chloroplast genome sequences for many species and demonstrated the ability to discover and assemble novel chloroplast genomes as well as asses inter/intra-individual differences in the respective chloroplast genomes.
 
@@
 Free text description of results, range, mean/median, effect of input size, threads parameter, ...
+All described tools have been tested with regard to their assembly time, memory and CPU utilization.
 
 \subsubsection*{Time requirements}
-In terms of run time, massive differences between the different tools have been observed.
-Apart from tool-specific differences, input data and number of threads had huge impact.
+Massive differences between the different tools were observed in terms of the run time for the assembly.
+Apart from tool-specific differences, input data and number of threads used had a huge impact on the time requirement.
 The observed run times varied from a few minutes to several hours (\cref{fig:performance_runtime}).
 
-Some assemblies failed to finish within the time-limit we set (\SI{48}{\hour}). 
-On average the longest time to generate the assemblies was taken by \ioga{} and \fp{} followed by \oa{} and \go{} the most time efficient tool was \ce{}, which on average is a little faster than \np{} and \cassp{}.
+Some assemblies failed to finish within our time limit of \SI{48}{\hour}. 
+On average, the longest time to generate an assembly was taken by \ioga{} and \fp{} followed by \oa{} and \go{}.
+The most time efficient tool was \ce{}, which was a little faster than \np{} and \cassp{}.
 %% multithreading
 
-Not all the tools were able to benefit from having access to multiple threads.
-Both \np{} and \oa{} take about the same time independent of being able to utilize \numlist[list-final-separator={, or }]{1;2;4;8} threads.
-\cassp{}, \ce{}, \go  and \fp{} all profit from multi-threading (\cref{fig:performance_runtime,fig:performance_memory_cpu,tab:perform25K_suppl,tab:perform250K_suppl,tab:perform2.5M_suppl}).
+Not all tested tools were able to benefit from having access to multiple threads.
+Both \np{} and \oa{} required almost the same time independent of being allowed to utilize \numlist[list-final-separator={, or }]{1;2;4;8} threads.
+In contrast, \cassp{}, \ce{}, \go  and \fp{} all profited from multi-threading settings  (\cref{fig:performance_runtime,fig:performance_memory_cpu,tab:perform25K_suppl,tab:perform250K_suppl,tab:perform2.5M_suppl}).
 
 \subsubsection*{Memory and CPU Usage }
-The peak and mean CPU usage, as well as peak memory and disk usage have been recorded for all assemblers based on the same input data set and number of threads to use (\cref{fig:performance_memory_cpu,tab:perform25K_suppl,tab:perform250K_suppl,tab:perform2.5M_suppl}).
-Mainly, the size of the input data influenced the peak memory usage with the exception of \ce{} and \ioga{}.
-Those two assemblers seems to have a memory usage pattern, which is less influenced by the size of the data.
+The peak and mean CPU usage, as well as peak memory and disk usage were recorded for all assemblers based on the same input data set and number of threads  (\cref{fig:performance_memory_cpu,tab:perform25K_suppl,tab:perform250K_suppl,tab:perform2.5M_suppl}).
+In general, the size of the input data influenced the peak memory usage with the exception of \ce{} and \ioga{}.
+Those two assemblers showed a memory usage pattern, which was less influenced by the size of the data.
 The number of allowed threads had only a limited impact on the peak memory usage.
-Nevertheless, all programs profit by a higher number of threads, if the size of the input data was increased.
-In contrast, the disk usage is independent from input size and number of threads for all assemblers.
+All programs profited from a higher number of threads, if the size of the input data was increased concerning their memory and CPU usage footprint.
+%\todo{oben steht nicht alle? (niklas)}
+% Frank: Hier geht es um Memory und CPU-Usage... Oben nur um Runtime
+In contrast, the disk usage was independent of the size of the input data and the number of threads for all assemblers.
+
 %but the factor between the programs exceeds a factor of \num{100}.
@@
 \subsection*{Qualitative}
-The user experience of most tools was evaluated as mainly \good{} (\cref{tab:resultsQual}). However, a few critique points remained.
-Two minor dependencies were missing in the \go{} installation instructions and there was no test data available.
-Additionally, an issue occurred when running it on a \plant{At} data set.
-We are currently in the process of resolving this with the authors.
-
-The \fp{} installation instructions were missing some dependencies.
-Like \go{}, \fp{} does not offer a test data set or a tutorial, except for some example commands.
+
+On average, the user experience in terms of installation and running the analyses was evaluated as \good{} for all tools (\cref{tab:resultsQual}).
+
+However, we discovered the following slight problems:
+
+Two minor dependencies were missing in the \go{} installation instructions and there were no test data available \cite{go_issue_10}.
+Additionally, an issue occurred when running it on one particular \plant{At} data set.
+This was resolved after contact with the authors via GitHub \cite{go_issue_11}.
+%
+
+The \fp{} installation instructions were missing some dependencies \cite{fp_issue_33}. 
+Like \go{}, \fp{} does not offer a test data set or a tutorial, except for some example commands \cite{go_issue_10}. 
+%
 
 The \oa{} installation instructions did not work.
-We found some issues, which are probably related to the requirement of \texttt{Python~3.7}.
-There is a tutorial where sample data is available.
-However, following the instructions resulted in a segmentation fault.
-We found a workaround for this bug and contacted the authors.
-
-The main critique point of \np{} was the lack of a test data set with instructions.
-This was fixed by the authors after we contacted them.
-Additionally, \np{} uses a custom license, where an OSI approved license would be preferred.
-
-The \ce{} does come with a test data set and a short tutorial.
-However, it is currently not possible to evaluate the results of the test run.
-
-The \ioga{} installation instructions were missing many dependencies.
-Also, there was no test data or tutorial available and there is no license assigned to it.
-Since there was no update to the GitHub repository for the last three years, the project can be seen as inactive.
-After contacting the authors, they promised to resolve the mentioned issues.
-
-As many of the other tools, the installation instructions for the \cassp{} were missing some dependencies.
-The list was updated after we contacted the authors.
-This tool does come with a test data set, however a note about the expected outcome is missing.
-A more extensive tutorial is provided.
-The description about the parameter is short, but sufficient.
+We found some issues, which were probably related to the requirement of \texttt{Python~3.7}
+\cite{oa_issue_59}.
+A tutorial including sample data was available, but following the instructions resulted in a segmentation fault.
+We found a workaround for this bug and contacted the authors \cite{oa_issue_57}.
+%
+
+The main critique point of \np{} was the lack of test data and instructions.
+This was fixed by the authors after we contacted them \cite{np_issue_82}.
+Additionally, \np{} uses a custom license, where an OSI approved license would be preferable.
+%
+
+The \ce{} does come with test data and a short tutorial.
+However, it is currently not possible to evaluate the results of the test run as the expected results are not available \cite{ce_issue_139}.
+%
+
+The \ioga{} installation instructions were missing many dependencies \cite{ioga_issue_12}. There was also no test data or tutorial available and no license assigned to it \cite{ioga_issue_13}.
+After contacting the authors, the AGPL-3.0 license was added \cite{ioga_issue_11}, as well as a note in the description explaining, that \ioga{} is no longer maintained.
+
+Installation instructions for \cassp{} were also missing some dependencies.
+The list was updated after we contacted the authors \cite{cassp_issue_5}.
+This tool does come with an extensive tutorial and test data, but the expected outcome is not provided.
 
 \subsection*{Quantitative}
+For a quantitative evaluation we tested the capacity of all programs to assemble chloroplasts based on different input data.
+Input data were either generated from existing chloroplast genomes or downloaded from sequencing repositories.
+
 \subsubsection*{Simulated data}
-The only assembler obtaining perfect results according to our score for the simulated data sets is \go{} (\cref{fig:simulated,tab:scores_simulated}).
-\ioga{} and \cassp{} showed the worst performance, being unable to fully assemble a single chloroplast out of \num{14} runs.
-\np{} performed second best with scores above \num{80} for all data sets, only failing to resolve the contigs into one single circular chloroplast assembly.
-The overall performance is best, when the input data consists purely of chloroplast reads.
-Only \ioga{} and \cassp{} failed to deliver any results under this scenario once.
-In general, no clear correlation between either length of the input reads or the ratio of core vs chloroplast reads and the performance of the different assemblers can be observed.
+The different simulated data were all based on the \plant{At} chloroplast and core genome sequence.
+Some general trends could be observed: a ratio of 1:10 genome to chloroplast reads,  contains too few chloroplastic reads for most tools (except \fp{} and \go{}).
+A good performance for all tools was observed at a ratio of 1:100.
+Increasing the ratio further had no additional benefit, even if pure chloroplast reads were used (\cref{fig:simulated}).
+Using \SI{250}{\basepair{}} paired read compared to \SI{150}{\basepair{}} paired reads, did not produce improved results (\cref{fig:simulated}).
+In the case of \fp{}, the performance was even worse with the longer read length as more than a single copy of the chloroplast genome was returned.
+
+Overall \go{} and \fp{} were the most successful tools on the simulated data while \cassp{} and \ioga{} were unable to successfully assemble any chloroplasts out of the \num{16} different data sets.
+%The only assembler obtaining perfect results according to our score for the simulated data sets is \go{} (\cref{fig:simulated,tab:scores_simulated}).
+%\ioga{} and \cassp{} showed the worst performance, being unable to fully assemble a single chloroplast out of \num{14} runs.
+%\np{} performed second best with scores above \num{80} for all data sets, only failing to resolve the contigs into one single circular chloroplast assembly.
+%The overall performance is best, when the input data consists purely of chloroplast reads.
+%Only \ioga{} and \cassp{} failed to deliver any results under this scenario once.
 
 \subsubsection*{Real data sets}
-Concerning the performance of the assemblers on the real data sets, we were able to observe considerable differences in the median score (\cref{fig:swarmplot}).
-The highest scores were achieved by \go{} with a median of \num{99.7} and \num{199} circular assemblies out of a total of 356 assemblies that resulted in an output (\cref{tab:scores_real}).
-The performance of \go{} is followed by \fp{}, \np{}, \oa{}, and \ce{}.
-\fp{} is outperforming the latter two slightly in terms of score, with twice as much \num{114} perfectly assembled chloroplast genomes (\np{} produced \num{66} and \oa{} \num{55} circular genomes).
-\ioga{} and \cassp{} were both not able to assemble a circular, single-contig genome (\cref{tab:scores_real}), consequently resulting in the lowest mean and median scores (\cref{fig:upset}).
+To evaluate the performance on real data, we used publicly available short read data from NCBI's SRA with existing reference chloroplasts.
+We observed considerable differences for the tested assemblers, if we compared the generated alignments against the reference chloroplasts (\cref{fig:swarmplot}).
+%\todo{hier ein halbsatz, was im score berücksichtigt wird? (niklas)}
+%\todo{Jan: are these values correct? is table 3 up to date? This whole section might need to be rewritten, Yes all the tables and plots are up to date and to my knowledge correct}
+The highest scores were achieved by \go{} with a median of \num{99.8} and \num{210} circular assemblies out of a total of 360 assemblies that resulted in an output (\cref{tab:scores_real}).
+The performance of \go{} was followed by \fp{}, \np{}, \ioga{}, and \oa{}.
+\fp{} outperformed \np{} and \oa{} in terms of score, producing twice as many \num{113} perfectly assembled chloroplast genomes (\np{} produced \num{58} and \oa{} \num{46} circular genomes).
+\ioga{} and \cassp{} were both unable to assemble a circular, single-contig genome (\cref{tab:scores_real}, \cref{fig:upset}).
 %\textit{swarm plot goes here}
@@
 \subsubsection*{Consistency}
-Consistency was tested by re-running assemblies and comparison of the scores of two assemblies (\cref{fig:consistency}).
-Replicates that did not produce an output were manually scored as \num{0}. 
-\go{} was the only tool that succeeded in obtaining similar scores for all assemblies, without producing and completely unsuccessful assemblies for this subset of data.
-Except for \fp{} all the other tools had at least one assembly that was unsuccessful in one run, but produced an output in the other.
-%\ak{oben steht \go{} war als einziges immer gut, dann kommt except for \fp{} ?? does not seem to be consistent}
-Notably \ioga{} appears to have a tendency to perform differently in independent runs.
-Here, more than \SI{10}{\percent} of the assemblies failed in one run only.
-
-Both \fp{} and \np{} tend to have minor changes in the assembly when the overall performance is comparably well, leading to the arrow-shaped scatter plots.
+Consistency was tested by re-running assemblies using the real data and comparison of the two assemblies (\cref{fig:consistency}).
+\ce{} was the only tool able to reproduce the same scores in all runs (\cref{fig:consistency}).
+%\todo{Frank or Jan: whoever wrote this sentence, what does it mean? \ce{} produced completely unsuccessful assemblies but consistently. Please re-write or remove! Dont think it was me}
+\go{}, \oa{}, \cassp{}, and \ioga{} generated some assemblies that were unsuccessful in one run, but produced an output in the other attempt.
+For these assemblers the scores were virtually identical if both runs were succesful. %\todo{Jan: identical? basically identical}.
+Both \fp{} and \np{} show only minor changes for the successful assemblies, leading to arrow-shaped scatter plots (\cref{fig:consistency}).
 %\ak{link to figure scatter plots is missing}
-\ce{} and \cassp{} appear to be the most robust assemblers, having only few deviations between the two runs.
+\ce{} appears to be the most robust assembler, showing no deviations between the two runs.
+
+\subsubsection*{Novel}
+Finally, the assembly of chloroplasts for species without a published chloroplast, was performed with the different tools.
+In total \num{49} out of \num{105} chloroplasts (\SI{46.7}{\percent}) with no reference sequence in CpBase were successfully assembled (\cref{fig:upset_novel}).
+
+Almost half (\SI{44.9}{\percent}) of the successful assembled chloroplasts, were assembled by three or more different tools, while the remaining ones were only successfully generated by one or two different assemblers.
+Here, \go{} showed the best performance and produced 15 distinct chloroplast genomes. 
+For the assemblies obtained from multiple assemblers, we kept the \go{} assemblies,
+after visually inspecting all assemblies using AliTV \cite{alitv}.
+
+%\todo{Markus/Frank: YES should we host a specific page on the alitv page for all the novels? Here: \url{https://alitvteam.github.io/AliTV/chloroplast_benchmark/})}%
+For two assemblies, that were obtained by different assemblers, but not by \go{}, we kept one assembly obtained by \np{} and one from \fp{}.
+\todo{@frank: please check, my dataset contains 45 GO, 3 FP, 1NP}
+The resulting \num{49} sequences have been annotated with GeSeq \cite{geseq} and uploaded to NCBI Genbank (\cref{tab:accessions_suppl}).
+The median number of distinct genes annotated were 80 for coding sequences, 4 for rRNA and 27 for tRNA (\cref{tab:feature_count_novel}, \cref{fig:feature_count_novel}). 
+%\todo{FRANK: more info about the taxonomic distribution of our novels and how we extended the coverage of the tol}.  %% STILL 2 DO
 
 \section*{Discussion}
-We aimed to generate an overall performance score for the different chloroplast assemblers, but depending on distinct downstream applications, the different criteria assessed in this work need to be weighted differently.
+We compared the overall performance of the different chloroplast assemblers.
+Depending on the type of downstream applications, the various assessment criteria, need to be weighted differently.
 For example, ease of installation and use might not be a big concern if the tool is installed once and integrated in an automated pipeline.
-On the other hand this factor alone might prevent other users from being able to use the tool in the first place.
-Similarly, computational requirements or run time might be less relevant, if the goal is to assemble a single chloroplast for further analysis, but it is essential if hundreds or thousands of samples should be processed in parallel for a large scale study.
-Eventually, both ease of use and run time are irrelevant if the tool is not able to successfully accomplish its task.
-Also the scope of this study needs to be considered when interpreting the guidelines below.
-In particular, we evaluated all tools under the assumption that they are used in the most basic form (default parameters, no hand selected reference, no pre-processing of the data or post-processing of the result, restricted run time).
-It is important to note that any tool might perform significantly different, if the above mentioned parameters are fine-tuned for a specific data set.
-
-The overall best success rate, both on simulated and real data, was achieved by \go{} followed by \fp{}.
-Both tools complement each other, as each is able to successfully reconstruct a full chloroplasts in cases where the other tool fails. 
-In rare cases \np{} or \oa{} are the only tool to succeed.
-The tools \fp{}, \np{}, and \oa{} produce the most variable results, thus re-running the tool after a failed attempt might be successful.
-\ce{} yields only few complete chloroplast assemblies, but requires also only few resources.
-It is easy to install and use and thus could be considered as a good option for a quick first try.
-Both \ioga{} and \cassp{} have the worst performance of all tools tested and fail to return reliable chloroplast assemblies.
-
-Additionally, we observed no phylogenetic pattern in the success rate of the assemblers (\cref{fig:tree}).
-This indicates that the tools are generally able to reconstruct chloroplasts across the plant kingdom even without or with fixed \plant{At} as reference.
+On the other hand this factor alone might prevent users from being able to use the respective tool in the first place.
+Similarly, computational requirements or run time might be less relevant, if the goal is to assemble a single chloroplast for further analysis, but are essential if hundreds or thousands of samples will be processed in parallel for a large scale study.
+Ultimately, both ease of use and computational requirements are irrelevant, if the tool is not able to successfully produce reliable assemblies.
+
+All tools were evaluated under the assumption that they are used in their most basic form (e.g. using default parameters, no pre-processing of the data or post-processing of the result).
+It is important to note that any tool might perform significantly differently, if distinct parameters are specifically fine-tuned for each data set.
+
+The best performance overall, both on simulated and real data, was achieved by \go{}. \fp{} performed nearly as well on most data.
+Both tools complement each other, as one tool can achieve successful assemblies of full chloroplasts in cases where the other tool fails. 
+This is highlighted by looking at the de-novo assemblies of chloroplasts, where \go{} managed to generate assemblies for 15 different data sets, where no other tool succeeded and \fp{} was able to assemble 3 plastid genomes that defeated all other tools.
+\np{} was the only other tool, that could produce an assembly that was not generated with any other assembler.
+\fp{}, \np{}, and \oa{} produced the most variable results, and therefore re-running the tool after a failed attempt might be a valid strategy.
+\ce{} yielded only few complete chloroplast assemblies, but requires few resources and is easy to install and use. 
+Thus \ce{} could be considered as a good option for a quick first try.
+Both \ioga{} and \cassp{} had unsatisfactory performances and failed to return reliable chloroplast assemblies.
+Nevertheless, multiple alignments of the assembled chloroplast genomes revealed some common challenges for the different tools. 
+Those challenges include fragmented assemblies, invertions of the \gls{ssc}, or a changed location of the \gls{ir} (\cref{fig:alitv}).
+
+%\todo{FRANK: Add discussion of novel}  %% STILL 2 DO
+% Yes, what have we leraned form the novel chloroplasts .. e.g. gene content 
+We observed no phylogenetic pattern in the success rate of the assemblers (\cref{fig:tree}).
+This indicates that the tools are generally able to reconstruct chloroplast genomes across the plant kingdom even without available reference genomes.
 
 \subsection*{Guidelines for the end-user}
-Given these results, our recommendation is to use \go{} as default option, and in case of failure \fp{} as backup solution.
+Given these results, our recommendation is to use \go{} as a default option for chloroplast assemblies. 
+If \go{} does not produce a use-able assembly, \fp{} is a valid back-up solution that might be successful. 
+This procedure maximizes the chance of effectively and efficiently recovering the circular chloroplast genome.
 %\ak{what if both lead to qualitative different results?, always trust \go{} , or could one compute a high-confidence assembly by combining different results ?, might be a point for future directions.}
-If both programs fail, it is sensible to re-run \fp{} and additionally try \np{} and \oa{}.
-This procedure maximizes the chance to effectively and efficiently recover the circular chloroplast genome from mixed genomic data.
-If none of these four assemblers produce sensible results, a reference guided approach and tweaking of the default parameters, might be the solution.
-Here, it is not possible to provide general guidelines, as the procedure will differ for different data sets.
+If both programs fail, it is recommended to try \np{} or manually fine-tune the parameters of the different tools.
+It is obviously not possible to provide general guidelines, as the exact procedure will differ for different data sets.
+
 For an automated approach, running \go{} and \fp{} in parallel appears to be a good trade-off between success rate and use of resources.
@@
 For further experiments, combining different components from different tools might be a promising approach.
-For example, read scaling from \ce{} followed by an assembly by \go{} and finally the structural resolution with \fp{} could be a promising approach, combing the respective strength of the different tools.
+For example, read scaling from \ce{} followed by an assembly by \go{} and finally structural resolution with \fp{} could be a promising approach, combing the respective strengths of the different tools.
 
 Moreover, the installation issues need to be mitigated by modern software.
-Therefore, either containerization (docker, singularity, etc.) or install workflows (eg. bioconda \cite{gruening2018}) should be established by all software packages.
-Otherwise, the burden of the software installation might result in scientists ignoring good tools.
-
-Another important feature of software is a comprehensive documentation, which needs to be up-to-date and maintained.
-Additionally, software authors could improve the usability based on suggestions from their users.
-
-Finally, all tools should improve their integrated guessing of default parameters, as many users avoid fine tuning of those, especially, for larger screening approaches.
-Last, as sequencing technology is developing fast (eg.\ PacBio or nanopore), tools need to be updated to not become obsolete.
-But the hope would be that with ongoing software development and improved sequencing technologies, the generation of whole chloroplast assemblies from any species will become a routine technique.
+Therefore, either containerization (docker, singularity, etc.) or install workflows (e.g. bioconda \cite{gruening2018}) should be established by all software packages.
+Otherwise, the burden of the software installation might result in a low level of uptake by the research community.
+
+A comprehensive documentation, which needs to be up-to-date and maintained, is another important feature of good tools.
+
+All tools should improve their integrated guessing of default parameters, as these are seldom fine-tuned by users, and especially for larger screening approaches.
+
+Finally, as sequencing technology is developing fast (e.g.\ PacBio or Nanopore), tools need to be updated to be able to handle this new generation of sequencing data and to not become obsolete.
+The hope would be that with ongoing software development and improved sequencing technologies, the generation of whole chloroplast assemblies from any species will become a routine technique.
 
 \section*{Conclusion}
-The main assumption for our study to benchmark different chloroplast assembly tools, is that whole genome sequencing data are also a promising source for chlorplast assemblies.
-Our benchmark shows that ~\SI{60}{\percent} of the data sets without available chloroplast genome, have been assembled by at least one of the tools we analysed.
-Still, even with simulated (aka``perfect'') data, not all tools succeeded in generating complete chloroplast assemblies.
-Therefore, we determined the strengths and weaknesses of the specific tools and provided guidelines for the users.
-However, it might be necessary, to combine different methods or manually explore the parameter space, to obtain reliable results if a single run seems not sufficient.
+
+WGS data are also a rich source for chlorplast assemblies.
+For nearly half of the analyzed data without available chloroplast genome, we could generate complete assemblies using at least one of the tools.
+%\todo{Frank: where do the 60 percent come from?, is it not more like 40?}
+
+Still, even with simulated (i.e. ``perfect'') data, not all tools succeeded in generating complete chloroplast assemblies.
+Therefore, we determined the strengths and weaknesses of the specific tools and have provided guidelines for users.
+It might however be necessary to combine different methods or manually explore the parameter space.
 Ultimately, large scale studies reconstructing hundreds or thousands of chloroplast genomes are now feasible using the currently available tools. 
@@
 Source code for all methods used is available at \cite{github-benchmark-repo} and archived in zenodo under \zenodorepo{}.
-All docker images are published on \cite{dockerhub-benchmark} and are named with a leading \texttt{benchmark\_} (\cref{tab:dockerimages}).
+All docker images are published on dockerhub \cite{dockerhub-benchmark} and are named with a leading \texttt{benchmark\_} (\cref{tab:dockerimages}).
 
 To enable a fair comparison of all tools, we generated simulated sequencing data.
-Those simulated data sets are stored at \zenododataset{}.
+Those simulated data sets are stored at zenodo \zenododataset{}.
 This study adheres to the guidelines for computational method benchmarking \cite{weber_essential_2018}.
@@
 We included tools designed for assembling chloroplasts from whole genome paired end Illumina sequencing data.
-As a requirement, all tools must be available as open source software and allow execution via a command line interface.
-As a graphical user interface is not suitable for automated comparisons, tools only providing a graphical interface have not been included.
+As a requirement, all tools had to be available as open source software and allow execution via a command line interface.
+As a \gls{gui} is not suitable for automated comparisons, tools that only provided a graphical interface were also excluded.
 The following tools were determined to be within the scope of this study:
@@
 
-Other related tools for assembling chloroplasts that did not meet our criteria and are therefore outside the scope of this study are for example:
-\texttt{Organelle PBA} \cite{Soorni2017}, \texttt{sestaton/Chloro} \cite{sestaton}, \texttt{Norgal}  \cite{Al-Nakeeb2017}, and \texttt{MitoBim} \cite{mitobim2013}.
+Some other related tools for assembling chloroplasts that did not meet our criteria and were therefore outside the scope of this study include:
+\texttt{Organelle PBA} \cite{Soorni2017}; \texttt{sestaton/Chloro} \cite{sestaton}; \texttt{Norgal}  \cite{Al-Nakeeb2017}; \texttt{MitoBim} \cite{mitobim2013}.
 
 \texttt{Organelle PBA} is designed for PacBio data and does not work with paired Illumina data alone.
-\texttt{sestaton/Chloro} fits our criteria, but it is flagged as work in progress and development and support seem to have ended two years ago.
+\texttt{sestaton/Chloro} fits our criteria, but is flagged as a work in progress and development and support seem to have ended two years ago.
 \texttt{Norgal} is a tool to extract organellar DNA from whole genome data based on a \textit{k}-mer frequency approach.
-However the final output is a set of contigs of mixed mitochondrial and plastid origin.
+The final output is a set of contigs of mixed mitochondrial and plastid origin, however.
 The suggested approach to get a finished chloroplast genome is to run \np{} on the ten longest contigs.
-Therefore we only included \np{} with the default settings and excluded \texttt{Norgal}.
+We therefore only included \np{} with the default settings and excluded \texttt{Norgal}.
 \texttt{MitoBim} is specifically designed for mitochondrial genomes.
-Even though there is a claim by the author that it can be used for chloroplasts as well, there is no further description on how to do that \cite{mitobim_issue16}.
+Even though there is a claim by the author that it can also be used for chloroplasts, there is no further description on how to do so \cite{mitobim_issue16}.
 
 Additionally, there is a protocol for the \texttt{Geneious} \cite{geneious} software available \cite{geneious-protocol}.
-However, \texttt{Geneious} is closed source and GUI based, which is not in the scope of this study.
+However, \texttt{Geneious} is closed source and \gls{gui} based, which was not in the scope of this study.
 There is also another publication describing a method for assembling chloroplasts \cite{method-description-paper}.
@@
 \subsection*{Our Setup}
-We want to use a minimum of different parameter settings for all assembly programs to enable a fair comparison. 
-Therefore, we decided to specify that all programs have to work based on two input files, representing a data set's forward (\texttt{forward.fq}) and reverse  (\texttt{reverse.fq}) sequence file in FASTQ format.
-Depending on the assembler, output files with different names and locations are generated.
-Those different files are copied and renamed to ensure that each assembly approach produces the same output file (\texttt{output.fa}). 
+We wanted to use a minimum of different parameter settings for all assembly programs to enable a fair comparison. 
+Therefore, we decided to specify that all programs had to work based on two input files, representing the forward (\texttt{forward.fq}) and reverse  (\texttt{reverse.fq}) sequence file of a data set in FASTQ format.
+Depending on the assembler, output files with different names and locations were generated.
+Those different files were copied and renamed to ensure that each assembly approach produced the same output file (\texttt{output.fa}). 
 Additionally, we set an environment variable for all programs to control the number of allowed threads.
-All three requirements (defined input file names, defined output file name, thread number control via environment variable) are ensured by a simple wrapper script (\texttt{wrapper.sh}).
-Finally, for a maximum of reproducibility all programs have been bundled into individual docker images based on a central base image which provides all the required software.
-Those docker images were used for the recording of the consumption of computational resources.
-Those docker images have been used for the performance benchmarking on a four Intel CPU-E7 8867 v3 system offering \SI{1}{\tera\byte} of RAM.
-Furthermore, all our docker images have been converted into singularity containers for the quantitative measurement on simulated and real data sets.
-Singularity container were built from docker images for usage on a HPC-environment using Singularity v.2.5.2 \cite{kurtzer2017singularity}
+All three requirements (defined input file names, defined output file name, thread number control via environment variable) were ensured by a simple wrapper script (\texttt{wrapper.sh}).
+Finally, for a maximum of reproducibility, all programs were bundled into individual docker images based on a central base image which provides all the required software.
+Those docker images were used for the recording of the consumption of computational resources on a four Intel CPU-E7 8867 v3 system offering \SI{1}{\tera\byte} of RAM.
+Furthermore, all our docker images have been converted into singularity containers for quantitative measurement on simulated and real data sets.
+Singularity container were built from docker images for usage on an HPC-environment using Singularity v.2.5.2 \cite{kurtzer2017singularity}.
 All singularity containers were run on %the Julia-HPC 
@@
 \subsection*{Data}
-\subsubsection*{Simulated}
-To avoid suffering from sequencing errors and biological variances, we simulated perfect reads based on the \plant{At} (TAIR10) chloroplast assembly \cite{tair10}.
+\subsubsection*{Simulated data}
+To avoid complications from sequencing errors and biological variation, we simulated perfect reads based on the \plant{At} (TAIR10) chloroplast and core genome assembly \cite{tair10}.
 We used a sliding window approach with \texttt{seqkit} \cite{seqkit}.
 The exact commands are documented in \href{https://github.com/chloroExtractorTeam/benchmark/blob/master/03_representative_datasets.md}{\texttt{03\_representative\_datasets.md}} in \zenododataset{}.
-For the final simulated data sets reads based on mixtures of the \plant{At} (TAIR10) core and chloroplast genome were generated with different ratios ( \num{0}:\num{1}, \num{1}:\num{10}, \num{1}:\num{100}, and \num{1}:\num{1000}).
-Additionally, we generated data with different read lengths (\SIlist{150;250}{\basepair}). All data simulated contain exactly 2 million read pairs.
+For the final simulated data sets reads are based on the TAIR10 reference genome.
+Different ratios between the \plant{At} core genome in combination with its mitochondrial sequence and the chloroplast sequence were generated (\num{0}:\num{1}, \num{1}:\num{10}, \num{1}:\num{100}, and \num{1}:\num{1000}).
+The final data contained \SI{30}{\times} genome coverage and \SI{300}{\times} mitochondrial coverage, except the \num{0}:\num{1} ratio.
+%\todo{Markus: mito ist richtig, oder?}
+% Frank nach Rücksprache mit Markus: Ja... Ist Mitochondrium!
+Additionally, we generated data with different read lengths (\SIlist{150;250}{\basepair}). We further sampled each data set to create another version containing exactly 2\,million read pairs.
 
@@
 
-\subsubsection*{Real}
+\subsubsection*{Real data}
 We selected real data deposited at SRA \cite{sra2010}.
 We searched all data that matched \texttt{((((((("green plants"[orgn]) AND "wgs"[Strategy]) AND "illumina"[Platform]) AND "biomol dna"[Properties]) AND "paired"[Layout]) AND "random"[Selection])) AND "public"[Access]} \cite{sra_search_term}.
-For each species with a reference chloroplast in CpBase \cite{cpbase}, we selected one data set of those.
-In total, this accumulated to \num{369} data sets (\cref{tab:real_dataset_details}) representing a broad spectrum of the green plants (\cref{fig:tree}).
+For each species with a reference chloroplast in CpBase \cite{cpbase}, we selected one data set.
+In total, this amounted to \num{369} data sets (\cref{tab:real_dataset_details}) representing a broad spectrum of the green plants (\cref{fig:tree}).
+%\todo{Frank: Nochmal was zum Baum schreiben und novels dort mit aufnehmen!}  %% STILL 2 DO
+
+\subsubsection*{Novel data}
+To evaluate the performance for chloroplasts without a reference in CpBase \cite{cpbase}, we sampled \num{105} data sets from the SRA \cite{sra2010} real data set described above (\cref{tab:novels_supp}).
+For each entry within that novel data set the number of lineage splits between the source taxon and the related references from CpBase was calculated according to NCBI Taxonomy \cite{ncbitaxonomy}.
+The final successful assembly of \num{49} new chloroplasts was manually inspected and rotated to follow the expected orientation and order of chloroplast genome parts.
+Due to a lack of a clear definition, we followed the definition of \fp{} \cite{fastplast_orientation_issue}.
+%\todo{Frank: Beschreibung des Submission prozesses und der Datenvorbereitung}
+%to the closest relative as well as the last common ancestor have been calculated \todo{see table X (Frank)}. \todo{further description of the method (Frank)}
 
@@
 
-Some programs will use more CPU threads than specified, therefore, the number of CPUs available have been fixed using the CPU option while running the docker run command.
+Some programs want to use more CPU threads than specified, therefore, the number of CPUs available was limited using the \texttt{--cpu} option of the corresponding \texttt{docker run} command.
 For each assembly setting, we recorded the peak memory consumption, the CPU usage (mean and peak CPU usage) and the size of the folder where the assembly was calculated.
-The values of CPU and memory usage have been obtained by docker.
+The values of CPU and memory usage were obtained from docker.
 The disk usage was estimated using the GNU tool \texttt{du}.
@@
 \subsubsection*{Qualitative}
-The qualitative evaluation is mainly based on the reviewer guidelines for the Journal of Open Source Software (JOSS) \cite{joss}.
+The qualitative evaluation was mainly based on the reviewer guidelines for the \gls{joss} \cite{joss}.
 To create a standard environment, all tools were tested in a fresh default installation of Ubuntu 18.04.2 running in a virtual machine (VirtualBox Version 5.2.18\_Ubuntu r123745).
@@
 During the evaluation, the following questions were asked:
-
-\begin{itemize}
-    \item Is the tool easy to install? 
-    \item Is there a way to test the installation or a tutorial on how to use the tool? 
-    \item Is there a good documentation on the parameter settings? 
-    \item Is the tool maintained (issues answered, implementation of new features)? 
-    \item Is the tool Open Source?
-\end{itemize}
-
-These questions were answered with \good{}, \ok{} or \bad{}, depending on the quality of the result. 
-For example, a \good{} installation utilizes an automated package or dependency management like \texttt{apt}, CRAN, docker, etc.
-An \ok{} installation procedure provides a custom script to install everything or at least lists all dependencies.
-A \bad{} installation procedure fails to list important dependencies or produces errors, that prevent a successful installation without exhaustive debugging.
+(1) Is the tool easy to install?
+(2) Is there a way to test the installation or a tutorial on how to use the tool?
+(3) Is there good documentation of the parameter settings? 
+(4) Is the tool maintained (issues answered, implementation of new features)?
+(5) Is the tool Open Source?
+%\begin{itemize}
+%    \item Is the tool easy to install? 
+%    \item Is there a way to test the installation or a tutorial on how to use the tool? 
+%    \item Is there a good documentation on the parameter settings? 
+%    \item Is the tool maintained (issues answered, implementation of new features)? 
+%    \item Is the tool Open Source?
+%\end{itemize}
+
+These questions were subjectively answered with \good{}, \ok{} or \bad{}, depending on the quality of the result. 
+For example, a \good{} installation utilized an automated package or dependency management like \texttt{apt}, CRAN, docker, etc.
+An \ok{} installation procedure provided a custom script to install everything or at least list all dependencies.
+A \bad{} installation procedure failed to list important dependencies or produced errors, that prevented a successful installation without extensive debugging.
 
@@
 For each data set and assembler the generated chloroplast genome was compared to the respective reference genome using a pairwise alignment obtained with \texttt{minimap2} v2.16 \cite{li2018minimap2}.
-Based on theses alignments a score is calculated as shown in \cref{eq:quantitative}
-The assemblies were scored on a scale from 0 to 100, with 100 being the best and 0 the worst possible score.
-Four different metrics were Incorporated, each contributing  $\frac{1}{4}$ to the total score: Completeness, correctness, repeat resolution and continuity.
-These metrics are similar in concept by those used in the Assemblathon 2 project: coverage, validity, multiplicity, and parsimony \cite{assemblathon2}.
-
-The completeness is estimated as the coverage of the assembled chloroplast genome versus the reference genome ($cov_{ref}$)
-It resembles how many bases of the query genome can be mapped to its respective reference genome.
+Based on theses alignments a score was calculated (\cref{Eq:score}).
+The assemblies were scored on a scale from \numrange{0}{100}, with \num{100} being the best and \num{0} the worst possible score.
+Four different metrics were incorporated, each contributing a quarter to the total score: completeness; correctness; repeat resolution; continuity.
+These metrics are similar in concept by those used in the Assemblathon\,2 project: coverage; validity; multiplicity; parsimony \cite{assemblathon2}.
+
+The completeness was estimated as the coverage of the assembled chloroplast genome versus the reference genome ($cov_{ref}$).
+It represents how many bases of the query genome can be mapped to its respective reference genome.
 Secondly, we mapped the reference genome against the query.
-The coverage of the reference genome ($cov_{qry}$) is used as measurement for the correctness of the assembly.
-The repeat resolution is estimated from the size difference of the assembly and the reference genome ($min\left\{ \frac{cov_{qry}}{cov_{ref}}, \frac{cov_{ref}}{cov_{qry}}\right\}$), leading to values between 0 and 1.
-The fourth metric used is the continuity, represented by the number of contigs.
-A perfect score is achieved if one circular chromosome was assembled, while the score gets worse with the amount of contigs.
-
+The coverage of the reference genome ($cov_{qry}$) was used as a measurement of the correctness of the assembly.
+The repeat resolution was estimated from the size difference of the assembly and the reference genome ($min\left\{ \frac{cov_{qry}}{cov_{ref}}, \frac{cov_{ref}}{cov_{qry}}\right\}$), leading to values between \num{0} and \num{1}.
+The fourth metric used was the continuity, represented by the number of contigs.
+A perfect score was achieved if one circular chromosome was assembled, while the score became worse as the number of contigs increased.
 \begin{equation}
    score = \frac{1}{4} \cdot \left( cov_{ref} +  cov_{qry} + min\left\{ \frac{cov_{qry}}{cov_{ref}}, \frac{cov_{ref}}{cov_{qry}}\right\} + \frac{1}{n_{contigs} }\right) \cdot 100 
-   \label{eq:quantitative}
+   \label{Eq:score}
 \end{equation}
 
+\subsubsection*{Success}
+For assemblies with reference sequence we defined success as reaching a score of 99 or higher.
+For the novel chloroplasts our score could not be calculated.
+The following criteria were instead selected to classify a novel chloroplast as success: single contig of length at least \SI{130}{\kilo\basepair{}} and an \gls{ir} region of at least \SI{17}{\kilo\basepair{}}.
+These cutoffs were selected as they produced the highest f-score on the real data set where true assignment (success/failure) was assumed based on the score (success if score \num{99} or higher).
+%\todo{Frank: should we add some supplementary figure from plots/novel\_cutoffs.pdf?}
+% Frank: Nicht notwendig
+
 \subsubsection*{Consistency}
-To ensure consistency of the obtained results, we randomly chose  \num{100} data sets, that in the previous runs resulted in outputs for most of the assemblers and run them again with the same parameters as before.
+To ensure consistency of the obtained results, we rerun and re-evaluated all the assemblies. %\todo{JAN: Das sind jetzt aber alle, oder? Comment: Ja das sind alle }
 The resulting assemblies were scored again as described and the scores of the first and the second run were compared to each other
-This information is important to assess the robustness of the different programs.
+This information was important to assess the robustness of the different programs.
 
@@
 \section*{Competing interests}
-The authors disclose that SP, NT, FF, and MJA are developers of \ce{}, one of the tools benchmarked in this article.
-The authors exercised caution not to let this fact unfairly influence their judgment and recommendations.
+Authors  SP, NT, FF, and MJA are developers of \ce{}, one of the tools benchmarked in this article.
 JF, NT, and MJA are affiliated with the for-profit organization AnaLife Data Science.
@@
 \section*{Author's contributions}
-MJA and FF conceived of the presented idea and supervised the findings of this manuscript.
+MJA and FF conceived the project and supervised the findings.
 SP and FF created the docker images.
@@
 
+\section*{Acknowledgement}
+We thank Brooke Morriswood for proof-reading and English editing of the manuscript
+
 \section*{Availability of data and materials}
@@
       \label{fig:tree}
+      \end{figure}
+
+\begin{figure}[h!]
+  \includegraphics[width=\textwidth]{manuscript/plots/upset_novel.pdf}
+  \caption{\csentence{Upset plot \cite{lex2014upset} comparing success of assemblers on the novel data sets}
+      The plot shows the intersection of success (single contig, $length \ge 130kbp$, $ir \ge 17kbp$) between assemblers.
+For \num{15} data sets only \go{} was able to obtain a complete chloroplast.
+\num{10} were successful with \go{}, \fp{}, \np{}, and \oa{} and so on}
+      \label{fig:upset_novel}
+      \end{figure}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.9\textwidth]{manuscript/plots/AliTV.png}
+  \caption{\csentence{AliTV plot \cite{alitv} showing alignments of the different assemblers compared to each other and the reference} Each blue bar in the plot corresponds to an assembly of the \plant{Ob} chloroplast (DRR053294).
+Regions in adjacent assemblies are connected with colored ribbons for similar regions in the alignment with identity coded as color from red to green.
+The purple arrows on the assemblies depict the \gls{ir} regions.
+This plot highlights some common problems with chloroplast assembly.
+\cassp{} only assembled small fragments mostly from the \gls{ir} region.
+\ioga{} returned three separate contigs corresponding to \gls{lsc}, \gls{ssc}, and IR.
+\fp{} and \go{} produced assemblies that were identical to the reference.
+\ce{} has the same structure but the \gls{lsc} is flipped compared to the reference (which is a biologically valid option).
+Both \np{} and \oa{} had the \gls{ssc} flipped compared to the reference and did not start with the \gls{lsc} but the \gls{ir} and \gls{ssc}, respectively (the start point is arbitrary in a circular sequence).%
+      }
+      \label{fig:alitv}
+      \end{figure}
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.9\textwidth]{manuscript/plots/feature_counts_distinct.png}
+  \caption{\csentence{Supplemental Figure. Number of distinct features in novel chloroplast genomes} The distribution of feature types tRNA, rRNA, and coding sequence (CDS) are shown separately.%
+      }
+      \label{fig:feature_count_novel}
       \end{figure}
@@
 \go{}     &  \ok{}    &  \ok{}    &  \good{}  &  \good{}  &  \good{} \\
-\ioga{}   &  \bad{}   &  \bad{}   &  \ok{}    &  \ok{}    &  \bad{}  \\
+\ioga{}   &  \bad{}   &  \bad{}   &  \ok{}    &  \bad{}    &  \good{}  \\
 \np{}     &  \good{}  &  \good{}  &  \good{}  &  \good{}  &  \ok{}   \\
@@
   \hline
-1 & sim\_150bp.0-1 & 79.10 & 100.00 & 99.72 & 100.00 &  & 91.52 & 100.00 \\ 
-  2 & sim\_150bp.1-10 &  & 56.44 &  & 100.00 &  & 91.52 & 78.00 \\ 
-  3 & sim\_150bp.1-10.2M &  &  & 99.97 & 100.00 &  & 100.00 & 82.72 \\ 
-  4 & sim\_150bp.1-100 &  & 100.00 &  & 100.00 &  & 91.52 & 91.50 \\ 
-  5 & sim\_150bp.1-100.2M &  & 100.00 & 99.47 & 100.00 & 74.82 & 100.00 & 100.00 \\ 
-  6 & sim\_150bp.1-1000 & 79.10 &  &  & 100.00 &  & 91.52 & 91.50 \\ 
-  7 & sim\_150bp.1-1000.2M & 79.10 & 100.00 & 99.72 & 100.00 &  & 91.52 & 100.00 \\ 
-  8 & sim\_250bp.0-1 & 79.10 & 100.00 & 93.83 & 100.00 &  & 91.52 & 100.00 \\ 
-  9 & sim\_250bp.1-10 &  & 54.98 & 68.45 & 100.00 &  & 91.52 & 40.20 \\ 
-  10 & sim\_250bp.1-10.2M &  &  & 93.00 & 100.00 &  & 87.40 & 40.20 \\ 
-  11 & sim\_250bp.1-100 &  & 100.00 & 93.83 & 100.00 & 65.81 & 91.52 & 100.00 \\ 
-  12 & sim\_250bp.1-100.2M &  & 100.00 & 93.83 & 100.00 & 75.73 & 87.40 & 100.00 \\ 
-  13 & sim\_250bp.1-1000 & 79.10 & 21.30 &  & 100.00 &  & 91.52 & 91.50 \\ 
-  14 & sim\_250bp.1-1000.2M & 79.10 & 100.00 & 93.83 & 100.00 &  & 87.40 & 100.00 \\ 
+ 1 & sim\_150bp.0-1 & 79.10 & 100.00 & 99.48 & 100.00 &  & 91.52 & 100.00 \\ 
+  2 & sim\_150bp.0-1.2M & 79.10 & 100.00 & 99.72 & 100.00 & 79.10 & 91.52 & 91.50 \\ 
+  3 & sim\_150bp.1-10 &  & 56.44 & 100.00 & 76.98 &  & 91.52 & 78.00 \\ 
+  4 & sim\_150bp.1-10.2M &  &  & 99.97 & 100.00 &  & 91.52 & 82.72 \\ 
+  5 & sim\_150bp.1-100 & 75.72 & 100.00 & 99.48 & 100.00 & 66.09 & 91.52 & 91.50 \\ 
+  6 & sim\_150bp.1-100.2M &  & 100.00 & 99.47 & 100.00 &  & 100.00 & 100.00 \\ 
+  7 & sim\_150bp.1-1000 & 79.10 &  & 99.72 & 100.00 &  & 91.52 & 100.00 \\ 
+  8 & sim\_150bp.1-1000.2M & 79.10 & 100.00 & 99.72 & 100.00 &  & 91.52 & 100.00 \\ 
+  9 & sim\_250bp.0-1 & 79.10 & 100.00 & 93.82 & 100.00 &  & 91.52 & 91.50 \\ 
+  10 & sim\_250bp.0-1.2M & 79.10 & 100.00 & 93.83 & 100.00 &  & 91.52 & 91.50 \\ 
+  11 & sim\_250bp.1-10 &  & 54.98 & 68.45 & 78.89 & 52.71 & 91.52 & 40.20 \\ 
+  12 & sim\_250bp.1-10.2M &  &  & 93.00 & 100.00 & 52.67 & 87.40 & 40.20 \\ 
+  13 & sim\_250bp.1-100 & 72.81 & 100.00 & 93.82 & 100.00 &  & 87.40 & 100.00 \\ 
+  14 & sim\_250bp.1-100.2M &  & 100.00 & 93.83 & 100.00 &  & 87.40 & 100.00 \\ 
+  15 & sim\_250bp.1-1000 & 79.10 & 21.30 & 93.83 & 100.00 & 76.96 & 91.52 & 91.50 \\ 
+  16 & sim\_250bp.1-1000.2M & 79.10 & 100.00 & 93.83 & 100.00 & 67.55 & 87.40 & 100.00 \\
    \hline
@@
   \hline
- & assembler & Mean & SD & N\_perfect & N\_tot \\ 
+ & assembler & Median & IQR & N\_perfect & N\_tot \\ 
   \hline
-  1 & CAP & 51.26 & 8.42 &   0 & 221 \\ 
-  2 & CE & 69.99 & 12.33 &  14 & 205 \\ 
-  3 & Fast-Plast & 86.96 & 15.33 & 114 & 352 \\ 
-  4 & GetOrganelle & 89.13 & 15.30 & 199 & 356 \\ 
-  5 & IOGA & 68.74 & 11.69 &   0 & 296 \\ 
-  6 & NOVOPlasty & 82.78 & 16.55 &  66 & 270 \\ 
-  7 & org.ASM & 82.77 & 16.38 &  55 & 228 \\ 
+1 & CAP & 45.25 & 50.19 &   0 & 369 \\ 
+  2 & CE & 56.55 & 71.50 &  14 & 369 \\ 
+  3 & Fast-Plast & 92.80 & 23.59 & 113 & 369 \\ 
+  4 & GetOrganelle & 99.83 & 20.94 & 210 & 360 \\ 
+  5 & IOGA & 71.10 & 11.21 &  0 & 338 \\ 
+  6 & NOVOPlasty & 75.95 & 48.69 &  58 & 369 \\ 
+  7 & org.ASM & 67.35 & 91.69 &  46 & 348 \\ 
    \hline
@@
 \caption{\textbf{Docker images used in our benchmark setup} SHA256 checksums are stated in \cref{tab:dockerimages_suppl}}
+%\todo{Frank: add software version column (maybe use git describe)} %% STILL 2 DO
 \label{tab:dockerimages}
@@
 
+\begin{table}[h!]
+\caption{\textbf{Supplemenatal Table.
+Number of distinct features in novel chloroplast genomes} The distribution (mean, standard deviation (SD), medain, interquartile range (IQR)) of feature types tRNA, rRNA, and coding sequence (CDS) are listed separately.}
+\label{tab:feature_count_novel}
+\centering
+      \resizebox{\textwidth}{!}{\begin{tabular}{crrrr}
+        \hline
+          Feature & Mean & SD & Median & IQR\\ \hline
+          CDS  &   79.1 & 3.45 &    80 &    2\\
+          rRNA &   4.2  & 0.37 &     4 &    0\\
+          tRNA &  26.7  & 0.97 &    27 &    0\\ \hline
+      \end{tabular}}
+\end{table}
+
 % \begin{table}[h!]
@@
   Supplementary data contain a complete list of all real data sets used in this study.
-Additionally, a table with more details to the used docker images and the detailed results of the performance measurement are included.
+Additionally, a table with more details on the used docker images and the detailed results of the performance measurement are included.
 The file is available at \cite{zenodosupplement}.

### 2020-05-19 manuscript/supplement.tex
Update to latest manuscript version

@@
 \usepackage{graphicx}
+
+\usepackage{tabularx}
+\usepackage{booktabs}
 
@@
 
+\begin{table}[ht]
+\caption{Sequencing Read Archive and Genbank accessions for novel chloroplast genomes}
+\label{tab:accessions_suppl}
+\centering
+\begin{tabular}{cccc}\toprule
+Species & SRA-Accession & Assembler & Genbank-Accession \\\midrule
+\plant{At} & AAAA & AAA & AAAA \\\bottomrule
+\end{tabular}
+\end{table}
+
 \begin{landscape}
@@
 Finally, the last column contains the information, if that data set was used for the check of the consistency.}\label{tab:real_dataset_details} \\
-\hline
-Taxon & SRA Acc & Ref Acc & read pairs & base pairs (bp) & read len. (bp) & Consistency check \\
-\hline
+\toprule
+Taxon & SRA Acc & Ref Acc & read pairs & base pairs (bp) & read len. (bp) & Consistency check \\\midrule
 \endfirsthead
 \multicolumn{7}{c}{\tablename\ \thetable\ -- \textit{Continued from previous page}}\\[0.5em]
-Taxon & SRA Acc & Ref Acc & read pairs & base pairs (bp) & read len. (bp) & Consistency check \\ \hline
+Taxon & SRA Acc & Ref Acc & read pairs & base pairs (bp) & read len. (bp) & Consistency check \\ \midrule
 \endhead
-\hline
+\bottomrule
 \multicolumn{7}{r}{Continued on next page}\\
@@
 \begin{tabular}{ccc}
-        \hline
-          Tool & Image name and tag & SHA256 Checksum   \\ \hline
+        \toprule
+          Tool & Image name and tag & SHA256 Checksum   \\ \midrule
           \ce & \dockerce & \dockercesha \\
@@
           \np & \dockernp & \dockernpsha \\
-          \oa & \dockeroa & \dockeroasha \\ \hline
+          \oa & \dockeroa & \dockeroasha \\ \bottomrule
       \end{tabular}
@@
 \begin{tabular}{rlrrrr}
-  \hline
+  \toprule
  & program & threads & Peak CPU usage & Peak memory & Peak disk usage (GB) \\ 
-  \hline
+  \midrule
 1 & CAP &   1 & 113.32 & 0.31 & 0.06 \\ 
@@
   28 & org.ASM &   8 & 105.78 & 0.79 & 0.03 \\ 
-   \hline
+   \bottomrule
 \end{tabular}
@@
 \begin{tabular}{rlrrrr}
-  \hline
+  \toprule
  & program & threads & Peak CPU usage & Peak memory & Peak disk usage (GB) \\ 
-  \hline
+  \midrule
 1 & CAP &   1 & 114.38 & 0.90 & 0.65 \\ 
@@
   28 & org.ASM &   8 & 160.74 & 0.93 & 0.06 \\ 
-   \hline
+   \bottomrule
 \end{tabular}
@@
 \begin{tabular}{rlrrrr}
-  \hline
+  \toprule
  & program & threads & Peak CPU usage & Peak memory & Peak disk usage (GB) \\ 
- \hline
+ \midrule
 1 & CAP &   1 & 118.80 & 6.83 & 6.59 \\ 
@@
   28 & org.ASM &   8 & 176.25 & 2.63 & 0.37 \\ 
-   \hline
+   \bottomrule
 \end{tabular}
@@
 
+\begin{landscape}
+\begin{longtable}{lcccp{7cm}c}
+\caption[Novel data set]{\textbf{Novel data set.}}\label{tab:novels_supp} \\
+  \toprule
+ SRA Accession & Depth & TaxID & Rank & Related References with Depth & Status \\
+ \midrule
+\endfirsthead
+\multicolumn{6}{c}{\tablename\ \thetable\ -- \textit{Continued from previous page}}\\[0.5em]
+ SRA Accession & Depth & TaxID & Rank & Related References with Depth & Status \\
+ \midrule
+\endhead
+\bottomrule
+\multicolumn{6}{r}{Continued on next page}\\
+\endfoot
+\endlastfoot
+DRR053713 & 3 & 71243 & order & NC\_033350(3) & success \\
+DRR057122 & 3 & 3650 & family & NC\_007144(3) NC\_023544(3) NC\_029484(3) NC\_031834(3) NC\_032008(3) NC\_033899(3) NC\_015983(4) & success \\
+DRR106816 & 5 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
+ERR1917165 & 5 & 4118 & family & NC\_009808(3) NC\_026703(3) NC\_031159(3) NC\_034670(3) & success \\
+ERR2003066 & 3 & 721789 & tribe & NC\_018767(3) NC\_019601(3) NC\_019602(3) NC\_034347(3) NC\_015206(4) NC\_018766(4) & success \\
+ERR2744401 & 5 & 156152 & family & NC\_028519(3) NC\_028520(3) NC\_031345(3) NC\_034688(3) NC\_031153(4) NC\_031344(4) & success \\
+ERR2744402 & 4 & 156152 & family & NC\_028519(3) NC\_028520(3) NC\_031345(3) NC\_034688(3) NC\_031153(4) NC\_031344(4) & success \\
+ERR3089127 & 4 & 102810 & tribe & NC\_020092(3) NC\_020320(3) NC\_020607(3) NC\_025910(3) NC\_030785(3) NC\_031399(3) NC\_031400(3) NC\_034683(3) NC\_034851(3) & success \\
+SRR2154064 & 4 & 4210 & family & NC\_027835(4) NC\_034648(4) NC\_007578(5) NC\_007977(5) NC\_010601(5) NC\_013553(5) NC\_015543(5) NC\_015621(5) NC\_020092(5) NC\_020320(5) NC\_020607(5) NC\_023107(5) NC\_023108(5) NC\_023109(5) NC\_023110(5) NC\_023111(5) NC\_023112(5) NC\_023113(5) NC\_023114(5) NC\_023833(5) NC\_024286(5) NC\_025910(5) NC\_027113(5) NC\_027434(5) NC\_028005(5) NC\_028006(5) NC\_028027(5) NC\_029465(5) NC\_030173(5) NC\_030275(5) NC\_030772(5) NC\_030773(5) NC\_030783(5) NC\_030785(5) NC\_031395(5) NC\_031396(5) NC\_031399(5) NC\_031400(5) NC\_031815(5) NC\_031816(5) NC\_031833(5) NC\_031853(5) NC\_031898(5) NC\_032056(5) NC\_032057(5) NC\_034320(5) NC\_034321(5) NC\_034322(5) NC\_034323(5) NC\_034324(5) NC\_034325(5) NC\_034326(5) NC\_034327(5) NC\_034328(5) NC\_034683(5) NC\_034810(5) NC\_034811(5) NC\_034812(5) NC\_034813(5) NC\_034814(5) NC\_034815(5) NC\_034816(5) NC\_034817(5) NC\_034818(5) NC\_034819(5) NC\_034820(5) NC\_034821(5) NC\_034822(5) NC\_034823(5) NC\_034824(5) NC\_034825(5) NC\_034827(5) NC\_034828(5) NC\_034829(5) NC\_034830(5) NC\_034831(5) NC\_034832(5) NC\_034847(5) NC\_034848(5) NC\_034849(5) NC\_034850(5) NC\_034851(5) NC\_034852(5) NC\_034853(5) NC\_034854(5) NC\_034856(5) NC\_034857(5) NC\_034858(5) NC\_034859(5) NC\_034860(5) NC\_034861(5) NC\_034862(5) NC\_034864(5) NC\_034865(5) NC\_034866(5) NC\_034867(5) NC\_034868(5) NC\_034869(5) NC\_034870(5) NC\_034871(5) NC\_034872(5) NC\_034873(5) NC\_034874(5) NC\_034875(5) NC\_034876(5) NC\_034877(5) NC\_034878(5) NC\_034879(5) NC\_034880(5) NC\_034881(5) NC\_034882(5) NC\_034883(5) NC\_034884(5) NC\_034885(5) NC\_034886(5) NC\_034887(5) NC\_034888(5) NC\_034889(5) NC\_034891(5) NC\_034892(5) NC\_034893(5) NC\_034894(5) NC\_034895(5) NC\_034896(5) NC\_034897(5) NC\_034898(5) NC\_034899(5) NC\_034900(5) NC\_034901(5) NC\_034902(5) NC\_034903(5) NC\_034996(5) & success \\
+SRR2176133 & 3 & 40550 & order & NC\_026786(3) NC\_027659(3) & success \\
+SRR2401791 & 4 & 91888 & no rank & NC\_016433(4) NC\_021449(4) NC\_023463(4) NC\_025652(4) NC\_025653(4) NC\_029719(4) NC\_030212(4) NC\_031435(4) NC\_031436(4) NC\_008407(5) NC\_009808(5) NC\_013707(5) NC\_020098(5) NC\_021111(5) NC\_022859(5) NC\_023102(5) NC\_023115(5) NC\_023131(5) NC\_023132(5) NC\_023464(5) NC\_023465(5) NC\_024845(5) NC\_025641(5) NC\_025642(5) NC\_025651(5) NC\_025787(5) NC\_026202(5) NC\_026291(5) NC\_026703(5) NC\_027262(5) NC\_027838(5) NC\_027955(5) NC\_028519(5) NC\_028520(5) NC\_028533(5) NC\_029700(5) NC\_031159(5) NC\_031345(5) NC\_031437(5) NC\_031441(5) NC\_031442(5) NC\_031443(5) NC\_031444(5) NC\_031445(5) NC\_033534(5) NC\_034308(5) NC\_034309(5) NC\_034310(5) NC\_034311(5) NC\_034312(5) NC\_034670(5) NC\_034688(5) NC\_034691(5) NC\_034693(5) NC\_034694(5) NC\_034695(5) NC\_035000(5) NC\_001879(6) NC\_004561(6) NC\_007500(6) NC\_007602(6) NC\_007943(6) NC\_008096(6) NC\_015401(6) NC\_015604(6) NC\_015608(6) NC\_015623(6) NC\_016068(6) NC\_018117(6) NC\_018552(6) NC\_022451(6) NC\_024261(6) NC\_024292(6) NC\_025657(6) NC\_026551(6) NC\_026563(6) NC\_026567(6) NC\_026570(6) NC\_026574(6) NC\_026694(6) NC\_026726(6) NC\_026906(6) NC\_027099(6) NC\_027177(6) NC\_027441(6) NC\_027442(6) NC\_028007(6) NC\_028009(6) NC\_028069(6) NC\_028070(6) NC\_028614(6) NC\_029370(6) NC\_029746(6) NC\_029817(6) NC\_029818(6) NC\_029819(6) NC\_029820(6) NC\_029821(6) NC\_029822(6) NC\_029823(6) NC\_029824(6) NC\_029825(6) NC\_029833(6) NC\_030044(6) NC\_030056(6) NC\_030167(6) NC\_030168(6) NC\_030171(6) NC\_030177(6) NC\_030178(6) NC\_030185(6) NC\_030207(6) NC\_030282(6) NC\_030319(6) NC\_030543(6) NC\_030755(6) NC\_030756(6) NC\_030757(6) NC\_031153(6) NC\_031155(6) NC\_031344(6) NC\_031433(6) NC\_031434(6) NC\_031805(6) NC\_031874(6) NC\_032054(6) NC\_032724(6) NC\_033354(6) NC\_033524(6) NC\_033525(6) NC\_033526(6) NC\_033527(6) NC\_034698(6) NC\_034951(6) NC\_035143(6) AC\_000188(7) NC\_007898(7) NC\_016468(7) NC\_020431(7) NC\_021423(7) NC\_022431(7) NC\_022432(7) NC\_025655(7) NC\_025656(7) NC\_025658(7) NC\_026876(7) NC\_026877(7) NC\_026878(7) NC\_026879(7) NC\_026880(7) NC\_026881(7) NC\_026882(7) NC\_027259(7) NC\_029459(7) NC\_029460(7) NC\_031852(7) NC\_034660(7) NC\_035233(7) NC\_008535(8) NC\_030053(8) & success \\
+SRR2531270 & 3 & 3650 & family & NC\_007144(3) NC\_023544(3) NC\_029484(3) NC\_031834(3) NC\_032008(3) NC\_033899(3) NC\_015983(4) & success \\
+SRR2531276 & 4 & 3650 & family & NC\_007144(3) NC\_023544(3) NC\_029484(3) NC\_031834(3) NC\_032008(3) NC\_033899(3) NC\_015983(4) & success \\
+SRR2531278 & 3 & 3650 & family & NC\_007144(3) NC\_023544(3) NC\_029484(3) NC\_031834(3) NC\_032008(3) NC\_033899(3) NC\_015983(4) & success \\
+SRR2531280 & 3 & 3650 & family & NC\_007144(3) NC\_023544(3) NC\_029484(3) NC\_031834(3) NC\_032008(3) NC\_033899(3) NC\_015983(4) & success \\
+SRR2531284 & 3 & 3650 & family & NC\_007144(3) NC\_023544(3) NC\_029484(3) NC\_031834(3) NC\_032008(3) NC\_033899(3) NC\_015983(4) & success \\
+SRR2531289 & 3 & 3650 & family & NC\_007144(3) NC\_023544(3) NC\_029484(3) NC\_031834(3) NC\_032008(3) NC\_033899(3) NC\_015983(4) & success \\
+SRR4124062 & 7 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
+SRR4124063 & 6 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
+SRR4124078 & 6 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
+SRR4124079 & 7 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
+SRR4457826 & 4 & 102809 & tribe & NC\_027434(3) NC\_034810(3) NC\_034811(3) NC\_034812(3) NC\_034813(3) NC\_034814(3) NC\_034815(3) NC\_034816(3) NC\_034817(3) NC\_034818(3) NC\_034819(3) NC\_034820(3) NC\_034821(3) NC\_034822(3) NC\_034823(3) NC\_034824(3) NC\_034825(3) NC\_034827(3) NC\_034828(3) NC\_034829(3) NC\_034830(3) NC\_034831(3) NC\_034832(3) NC\_034847(3) NC\_034848(3) NC\_034849(3) NC\_034850(3) NC\_034852(3) NC\_034853(3) NC\_034854(3) NC\_034856(3) NC\_034857(3) NC\_034858(3) NC\_034859(3) NC\_034860(3) NC\_034861(3) NC\_034862(3) NC\_034864(3) NC\_034865(3) NC\_034866(3) NC\_034867(3) NC\_034868(3) NC\_034869(3) NC\_034870(3) NC\_034871(3) NC\_034872(3) NC\_034873(3) NC\_034874(3) NC\_034875(3) NC\_034876(3) NC\_034877(3) NC\_034878(3) NC\_034879(3) NC\_034880(3) NC\_034881(3) NC\_034882(3) NC\_034883(3) NC\_034884(3) NC\_034885(3) NC\_034886(3) NC\_034887(3) NC\_034888(3) NC\_034889(3) NC\_034891(3) NC\_034892(3) NC\_034893(3) NC\_034894(3) NC\_034895(3) NC\_034896(3) NC\_034897(3) NC\_034898(3) NC\_034899(3) NC\_034900(3) NC\_034901(3) NC\_034902(3) NC\_034903(3) NC\_034996(3) & success \\
+SRR4457835 & 4 & 102809 & tribe & NC\_027434(3) NC\_034810(3) NC\_034811(3) NC\_034812(3) NC\_034813(3) NC\_034814(3) NC\_034815(3) NC\_034816(3) NC\_034817(3) NC\_034818(3) NC\_034819(3) NC\_034820(3) NC\_034821(3) NC\_034822(3) NC\_034823(3) NC\_034824(3) NC\_034825(3) NC\_034827(3) NC\_034828(3) NC\_034829(3) NC\_034830(3) NC\_034831(3) NC\_034832(3) NC\_034847(3) NC\_034848(3) NC\_034849(3) NC\_034850(3) NC\_034852(3) NC\_034853(3) NC\_034854(3) NC\_034856(3) NC\_034857(3) NC\_034858(3) NC\_034859(3) NC\_034860(3) NC\_034861(3) NC\_034862(3) NC\_034864(3) NC\_034865(3) NC\_034866(3) NC\_034867(3) NC\_034868(3) NC\_034869(3) NC\_034870(3) NC\_034871(3) NC\_034872(3) NC\_034873(3) NC\_034874(3) NC\_034875(3) NC\_034876(3) NC\_034877(3) NC\_034878(3) NC\_034879(3) NC\_034880(3) NC\_034881(3) NC\_034882(3) NC\_034883(3) NC\_034884(3) NC\_034885(3) NC\_034886(3) NC\_034887(3) NC\_034888(3) NC\_034889(3) NC\_034891(3) NC\_034892(3) NC\_034893(3) NC\_034894(3) NC\_034895(3) NC\_034896(3) NC\_034897(3) NC\_034898(3) NC\_034899(3) NC\_034900(3) NC\_034901(3) NC\_034902(3) NC\_034903(3) NC\_034996(3) & success \\
+SRR5195283 & 3 & 4055 & order & NC\_024292(5) NC\_025657(5) NC\_027441(5) NC\_027442(5) NC\_028009(5) NC\_028614(5) NC\_030319(5) NC\_031155(5) NC\_033354(5) NC\_034698(5) NC\_021423(6) NC\_022431(6) NC\_022432(6) NC\_025655(6) NC\_025656(6) NC\_025658(6) NC\_029459(6) NC\_029460(6) NC\_008535(7) NC\_030053(7) & success \\
+SRR5409224 & 5 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
+SRR5409225 & 4 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
+SRR5581778 & 4 & 3650 & family & NC\_007144(3) NC\_023544(3) NC\_029484(3) NC\_031834(3) NC\_032008(3) NC\_033899(3) NC\_015983(4) & success \\
+SRR5586278 & 5 & 1521262 & subclass & NC\_012818(4) NC\_022136(4) NC\_022137(4) NC\_024157(4) NC\_024158(4) NC\_004766(6) NC\_014348(6) NC\_014592(6) NC\_028542(6) NC\_028543(6) NC\_028705(6) & success \\
+SRR5880481 & 3 & 41945 & order & NC\_020019(3) NC\_021121(3) NC\_022264(3) NC\_022459(3) NC\_022460(3) NC\_022461(3) NC\_022462(3) NC\_022463(3) NC\_023084(3) NC\_024541(3) NC\_024543(3) NC\_024659(3) NC\_024660(3) NC\_024661(3) NC\_024662(3) NC\_024663(3) NC\_026197(3) NC\_026690(3) NC\_026691(3) NC\_030180(3) NC\_030539(3) NC\_030609(3) NC\_030784(3) NC\_030786(3) NC\_030787(3) NC\_030789(3) NC\_031186(3) NC\_031187(3) NC\_031428(3) NC\_031892(3) NC\_033502(3) NC\_034331(3) NC\_034371(3) NC\_034640(3) NC\_034641(3) NC\_034677(3) NC\_034678(3) NC\_034913(3) NC\_034914(3) NC\_034915(3) NC\_035418(3) NC\_033501(4) NC\_019616(5) NC\_029704(5) & success \\
+SRR6331521 & 3 & 4149 & family & NC\_026202(3) NC\_031437(3) & success \\
+SRR6425047 & 5 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
+SRR6425048 & 5 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
+SRR6425049 & 5 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
+SRR6425628 & 4 & 167487 & subfamily & NC\_024292(3) NC\_033354(3) NC\_021423(4) & success \\
+SRR6425646 & 4 & 167487 & subfamily & NC\_024292(3) NC\_033354(3) NC\_021423(4) & success \\
+SRR6425647 & 4 & 167487 & subfamily & NC\_024292(3) NC\_033354(3) NC\_021423(4) & success \\
+SRR6425648 & 4 & 167487 & subfamily & NC\_024292(3) NC\_033354(3) NC\_021423(4) & success \\
+SRR6425651 & 4 & 167483 & subfamily & NC\_025657(3) NC\_025655(4) NC\_025656(4) NC\_025658(4) & success \\
+SRR6513658 & 3 & 3814 & subfamily & NC\_009259(6) NC\_013843(6) NC\_016708(6) NC\_018051(6) NC\_021091(6) NC\_023090(6) NC\_025909(6) NC\_027677(6) NC\_029406(6) NC\_031429(6) NC\_034742(6) NC\_034743(6) NC\_034774(6) NC\_002694(7) NC\_003119(7) NC\_007942(7) NC\_011163(7) NC\_011828(7) NC\_014057(7) NC\_014063(7) NC\_021636(7) NC\_021645(7) NC\_021646(7) NC\_021647(7) NC\_021648(7) NC\_021649(7) NC\_021650(7) NC\_022868(7) NC\_024034(7) NC\_024035(7) NC\_024036(7) NC\_024038(7) NC\_024166(7) NC\_025743(7) NC\_025744(7) NC\_025745(7) NC\_027073(7) NC\_027074(7) NC\_027075(7) NC\_027076(7) NC\_027077(7) NC\_027078(7) NC\_027079(7) NC\_027080(7) NC\_027148(7) NC\_027149(7) NC\_027150(7) NC\_027151(7) NC\_027152(7) NC\_027153(7) NC\_027154(7) NC\_027155(7) NC\_029828(7) NC\_030329(7) NC\_032066(7) NC\_032691(7) NC\_034229(7) NC\_035228(7) NC\_035229(7) NC\_028171(8) & success \\
+SRR6821984 & 3 & 3700 & family & NC\_000932(3) NC\_009265(3) NC\_009266(3) NC\_009267(3) NC\_009268(3) NC\_009269(3) NC\_009270(3) NC\_009271(3) NC\_009272(3) NC\_009273(3) NC\_009274(3) NC\_009275(3) NC\_016734(3) NC\_018565(3) NC\_021102(3) NC\_023367(3) NC\_024469(3) NC\_026445(3) NC\_026446(3) NC\_027693(3) NC\_028170(3) NC\_028272(3) NC\_028415(3) NC\_028517(3) NC\_028726(3) NC\_028727(3) NC\_028728(3) NC\_029253(3) NC\_029254(3) NC\_029331(3) NC\_029332(3) NC\_029333(3) NC\_029334(3) NC\_029335(3) NC\_029336(3) NC\_029337(3) NC\_029378(3) NC\_029379(3) NC\_030346(3) NC\_030347(3) NC\_030348(3) NC\_030349(3) NC\_030350(3) NC\_030351(3) NC\_030450(3) NC\_030515(3) NC\_030516(3) NC\_030775(3) NC\_033499(3) NC\_033500(3) NC\_034287(3) NC\_034299(3) NC\_034357(3) NC\_034359(3) NC\_034360(3) NC\_034361(3) NC\_034362(3) NC\_034363(3) NC\_034365(3) NC\_034366(3) NC\_034367(3) NC\_035303(3) NC\_034286(4) NC\_034379(4) & success \\
+SRR6940055 & 3 & 4136 & family & NC\_020098(3) NC\_023102(3) NC\_026291(3) NC\_027262(3) NC\_028533(3) NC\_034693(3) NC\_029370(4) NC\_029817(4) NC\_029818(4) NC\_029819(4) NC\_029820(4) NC\_029821(4) NC\_029822(4) NC\_029823(4) NC\_029824(4) NC\_029825(4) NC\_030755(4) NC\_030756(4) NC\_030757(4) NC\_031433(4) NC\_031434(4) NC\_031874(4) NC\_032054(4) NC\_035143(4) NC\_020431(5) NC\_027259(5) NC\_035233(5) & success \\
+SRR6940081 & 3 & 4136 & family & NC\_020098(3) NC\_023102(3) NC\_026291(3) NC\_027262(3) NC\_028533(3) NC\_034693(3) NC\_029370(4) NC\_029817(4) NC\_029818(4) NC\_029819(4) NC\_029820(4) NC\_029821(4) NC\_029822(4) NC\_029823(4) NC\_029824(4) NC\_029825(4) NC\_030755(4) NC\_030756(4) NC\_030757(4) NC\_031433(4) NC\_031434(4) NC\_031874(4) NC\_032054(4) NC\_035143(4) NC\_020431(5) NC\_027259(5) NC\_035233(5) & success \\
+SRR7223704 & 3 & 3700 & family & NC\_000932(3) NC\_009265(3) NC\_009266(3) NC\_009267(3) NC\_009268(3) NC\_009269(3) NC\_009270(3) NC\_009271(3) NC\_009272(3) NC\_009273(3) NC\_009274(3) NC\_009275(3) NC\_016734(3) NC\_018565(3) NC\_021102(3) NC\_023367(3) NC\_024469(3) NC\_026445(3) NC\_026446(3) NC\_027693(3) NC\_028170(3) NC\_028272(3) NC\_028415(3) NC\_028517(3) NC\_028726(3) NC\_028727(3) NC\_028728(3) NC\_029253(3) NC\_029254(3) NC\_029331(3) NC\_029332(3) NC\_029333(3) NC\_029334(3) NC\_029335(3) NC\_029336(3) NC\_029337(3) NC\_029378(3) NC\_029379(3) NC\_030346(3) NC\_030347(3) NC\_030348(3) NC\_030349(3) NC\_030350(3) NC\_030351(3) NC\_030450(3) NC\_030515(3) NC\_030516(3) NC\_030775(3) NC\_033499(3) NC\_033500(3) NC\_034287(3) NC\_034299(3) NC\_034357(3) NC\_034359(3) NC\_034360(3) NC\_034361(3) NC\_034362(3) NC\_034363(3) NC\_034365(3) NC\_034366(3) NC\_034367(3) NC\_035303(3) NC\_034286(4) NC\_034379(4) & success \\
+SRR7223710 & 3 & 3700 & family & NC\_000932(3) NC\_009265(3) NC\_009266(3) NC\_009267(3) NC\_009268(3) NC\_009269(3) NC\_009270(3) NC\_009271(3) NC\_009272(3) NC\_009273(3) NC\_009274(3) NC\_009275(3) NC\_016734(3) NC\_018565(3) NC\_021102(3) NC\_023367(3) NC\_024469(3) NC\_026445(3) NC\_026446(3) NC\_027693(3) NC\_028170(3) NC\_028272(3) NC\_028415(3) NC\_028517(3) NC\_028726(3) NC\_028727(3) NC\_028728(3) NC\_029253(3) NC\_029254(3) NC\_029331(3) NC\_029332(3) NC\_029333(3) NC\_029334(3) NC\_029335(3) NC\_029336(3) NC\_029337(3) NC\_029378(3) NC\_029379(3) NC\_030346(3) NC\_030347(3) NC\_030348(3) NC\_030349(3) NC\_030350(3) NC\_030351(3) NC\_030450(3) NC\_030515(3) NC\_030516(3) NC\_030775(3) NC\_033499(3) NC\_033500(3) NC\_034287(3) NC\_034299(3) NC\_034357(3) NC\_034359(3) NC\_034360(3) NC\_034361(3) NC\_034362(3) NC\_034363(3) NC\_034365(3) NC\_034366(3) NC\_034367(3) NC\_035303(3) NC\_034286(4) NC\_034379(4) & success \\
+SRR8082590 & 3 & 3646 & order & NC\_024060(3) NC\_024061(3) NC\_024062(3) NC\_024063(3) NC\_024064(3) NC\_024065(3) NC\_024066(3) NC\_024067(3) NC\_026986(3) NC\_030517(3) NC\_030534(3) NC\_030544(3) NC\_030545(3) NC\_030546(3) NC\_030547(3) NC\_030548(3) NC\_030549(3) NC\_030550(3) NC\_030551(3) NC\_030552(3) NC\_030553(3) NC\_030554(3) NC\_030555(3) NC\_030556(3) NC\_030557(3) NC\_030558(3) NC\_030559(3) NC\_030560(3) NC\_030561(3) NC\_030562(3) NC\_030563(3) NC\_030564(3) NC\_030565(3) NC\_030566(3) NC\_030567(3) NC\_030568(3) NC\_030569(3) NC\_030570(3) NC\_030571(3) NC\_030572(3) NC\_030573(3) NC\_030574(3) NC\_030575(3) NC\_030576(3) NC\_030577(3) NC\_030578(3) NC\_030579(3) NC\_030580(3) NC\_030581(3) NC\_030582(3) NC\_030583(3) NC\_030601(3) NC\_034285(3) NC\_008235(4) NC\_009143(4) NC\_024681(4) NC\_024734(4) NC\_024735(4) NC\_024747(4) NC\_026462(4) NC\_026722(4) NC\_027425(4) NC\_028350(4) NC\_028504(4) NC\_031371(4) NC\_031398(4) NC\_032060(4) NC\_032368(4) NC\_032717(4) NC\_033876(4) NC\_010433(5) NC\_012224(5) NC\_015308(5) NC\_016736(5) NC\_034803(5) NC\_033910(7) & success \\
+SRR8481357 & 5 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
+SRR8481359 & 5 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
+SRR8784049 & 7 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
+SRR8784093 & 5 & 2231393 & no rank & NC\_009259(5) NC\_013843(5) NC\_016708(5) NC\_018051(5) NC\_021091(5) NC\_023090(5) NC\_025909(5) NC\_027677(5) NC\_029406(5) NC\_031429(5) NC\_034742(5) NC\_034743(5) NC\_034774(5) NC\_002694(6) NC\_003119(6) NC\_007942(6) NC\_011163(6) NC\_011828(6) NC\_014057(6) NC\_014063(6) NC\_021636(6) NC\_021645(6) NC\_021646(6) NC\_021647(6) NC\_021648(6) NC\_021649(6) NC\_021650(6) NC\_022868(6) NC\_024034(6) NC\_024035(6) NC\_024036(6) NC\_024038(6) NC\_024166(6) NC\_025743(6) NC\_025744(6) NC\_025745(6) NC\_027073(6) NC\_027074(6) NC\_027075(6) NC\_027076(6) NC\_027077(6) NC\_027078(6) NC\_027079(6) NC\_027080(6) NC\_027148(6) NC\_027149(6) NC\_027150(6) NC\_027151(6) NC\_027152(6) NC\_027153(6) NC\_027154(6) NC\_027155(6) NC\_029828(6) NC\_030329(6) NC\_032066(6) NC\_032691(6) NC\_034229(6) NC\_035228(6) NC\_035229(6) NC\_028171(7) & success \\
+\end{longtable}
+\end{landscape}
 \end{document}

### 2020-05-20 code/geseq_gff_2_feature_table.pl
Add a script to convert a multi sequence geseq gff3 into feature file for bankit submission

@@ -1,0 +1,42 @@
+#!/usr/bin/env perl
+
+use strict;
+use warnings;
+
+my %dat = ();
+
+while (<>)
+{
+    chomp;
+    my @fields = split(/\t/, $_);
+
+    next unless (defined $fields[1] && $fields[1] && $fields[1] eq "ogdraw");
+
+    # get the sequence ID
+    $fields[0] =~ /^(\S+)--organism/;
+
+    my $set = { id => $1 };
+
+    # get the coords
+    $set->{start} = $fields[3]+0;
+    $set->{end}   = $fields[4]+0;
+
+    # get the type
+    # ;gbkey=repeat_region;Note=inverted_repeat_B_(IRB)%2C
+    $fields[8] =~ /gbkey=([^;]+)/;
+    $set->{key} = $1;
+    $fields[8] =~ /Note=([^;]+?)%2C/;
+    $set->{note} = $1;
+    $set->{note} =~ s/_/ /g;
+    
+    push(@{$dat{$set->{id}}}, \%{$set});
+}
+
+foreach my $key (keys %dat)
+{
+    printf ">Feature %s\n", $key;
+    foreach my $set (@{$dat{$key}})
+    {
+	printf "%d\t%d\t%s\n\t\t\t%s\t%s\n", $set->{start}, $set->{end}, $set->{key}, "note", $set->{note};
+    }
+}

### 2020-05-21 manuscript/reviewer_response1.tex
Update manuscript folder for resubmission

@@
 \maketitle
-\section{Editor}
-We have now received reports from two referees, whose comments are available below.
-As you will see from the reports, both referees raised serious concerns that the benchmark hasn't provided sufficient advance to be useful for the field.
-At this stage, therefore, we are not persuaded that an offer of publication in Genome Biology would be justified.
-Unless you can address all of the issues raised by the referees I am afraid that we would not be able to consider this work again.
-In particular we ask that you provide additional analyses as requested by both referees to convince them of the advance.
-The revised manuscript should address in full all the points raised by both referees; a separate list of the revisions made, specifying where in the manuscript the changes have been made, would also be helpful.
-Please note that all data generated for the manuscript should be deposited in a relevant public repository, with accession codes listed in the manuscript's Availability of Data and Materials section.
-All other supporting data should also be signposted.
-If you decide to submit a revised version, you will need to  this as a new manuscript, although we would consider it in the same way as we do all revised manuscripts.
-The exception is that we will take into account any work published in the intervening period.
-For the time being, however, we hope that you will find our referees' comments helpful in deciding how to proceed.
-Please feel free to contact us if you have any questions.
-
+% \section{Editor}
+% We have now received reports from two referees, whose comments are available below.
+% As you will see from the reports, both referees raised serious concerns that the benchmark hasn't provided sufficient advance to be useful for the field.
+% At this stage, therefore, we are not persuaded that an offer of publication in Genome Biology would be justified.
+% Unless you can address all of the issues raised by the referees I am afraid that we would not be able to consider this work again.
+% In particular we ask that you provide additional analyses as requested by both referees to convince them of the advance.
+% The revised manuscript should address in full all the points raised by both referees; a separate list of the revisions made, specifying where in the manuscript the changes have been made, would also be helpful.
+% Please note that all data generated for the manuscript should be deposited in a relevant public repository, with accession codes listed in the manuscript's Availability of Data and Materials section.
+% All other supporting data should also be signposted.
+% If you decide to submit a revised version, you will need to  this as a new manuscript, although we would consider it in the same way as we do all revised manuscripts.
+% The exception is that we will take into account any work published in the intervening period.
+% For the time being, however, we hope that you will find our referees' comments helpful in deciding how to proceed.
+% Please feel free to contact us if you have any questions.
 \section{Reviewer 1}
@@
 \textbf{
-Indeed the novelty in this article is not a new approach to the task of chloroplast genome assembly but rather a thourough benchmark of existing tools (including our tool ChloroExtractor).
+Indeed the novelty in this article is not a new approach to the task of chloroplast genome assembly but rather a thorough benchmark of existing tools (including our tool ChloroExtractor).
 This represents a substantial advance for the field as there are competing tools published for the same task without any information about their relative performances.
 Currently, researchers have to do this evaluation of tools themselves to find the appropriate tool which leads to duplicated efforts as this is done by every group separately and without sharing results.
-If this evaluation is neglected a suboptimal tool might be used which can lead to additional manual efforts in finishing or additional costs if more data is generated.
-Thus, clear guidelines to the end user (and important directions for improvement to the developers) are novel, important and benficial for the research community.
+If this evaluation is neglected a non optimal tool might be used which can lead to additional manual efforts in finishing or additional costs if more data is generated.
+Thus, clear guidelines to the end user (and important directions for improvement to the developers) are novel, important and beneficial for the research community.
 }
@@
 We agree that this would be the best way to measure and quantify user experience.
-However, this is not feasible with limited budget and time (TODO: is this excuse good enough?) while the main focus of the work was on quantitative performance measures, anyway.
-We decided to include usability metrics that were obtainable in a defined and structured way using the JOSS reviewer guidelines.
+However, the main focus of the work was on quantitative performance measures. 
+Nevertheless, we decided to include usability metrics that were obtainable in a defined and structured way using the reviewer guidelines of the ``Journal of Open Source Software'' (JOSS).
 }
@@
 Thanks for pointing this out.
-We now include as a proof of principle the application of these tools on more than 100 novel datasets.
-We thus clearly demonstrate that the insights from this article can be used to produce further novel results that can lead to biological insight.
+We now include as a proof of principle the application of these tools on 105 novel data sets.
+The assembly of 49 of those 105 data sets returned chloroplast genomes.
+After further screening against NCBI databases, still 20 data sets remained.
+That sets contained new chloroplast genomes for species without a reported plastid genome.
+We thus clearly demonstrate that the insights from this article can be used to produce further novel results that can lead to further biological insight.
 }
@@
 This is a very interesting question.
-We don't think that this is within the scope of our publication as we compare de novo assembly tools.
-TODO: some people use it, some programs use it, it seems to work often but actually your argument is justification why we restricted our analysis to de novo tools.
+But due to we are comparing de novo assembly tools, we think answering this question is outside the scope of our publication.
+Nevertheless, using reference plastid genomes, is helpful to sort the huge amount of input data into potential plastid genome related sequences and non related sequences which need no longer to be considered for an assembly.
+%TODO: some people use it, some programs use it, it seems to work often but actually your argument is justification why we restricted our analysis to de novo tools.
 }
@@
 \textbf{
-We already tested the tools on real datasets downloaded from SRA which is equivalent to customly sequenced data.
-But we now include additional 100+ novel data sets with no reference chloroplast in the database.
+We already tested the tools on real data sets downloaded from NCBIs SRA which is equivalent to customly sequenced data.
+But we now include additional 105 novel data sets with no reference chloroplast in the database.
 }
@@
 Thanks for your thorough review and the pointers that helped us improve the overall readability of the manuscript.
-In addition we received feedback and edits from a native English speaker to further improve readabilty.
-TODO: how do we adress the "limited information" aspect. We could link to the github repo that contains all data and code we used including the dockerfiles.
+In addition we received feedback and edits from a native English speaker to further improve readability.
+We try to add more information about our systematically comparison into the manuscript, moreover, we provide all our script and even the docker container in our GitHub repository, DockerHub, and Zenodo to enable a maximum of reproducibility.
 }
@@
 \end{itemize}
+
+\textbf{We addressed the more specific issues within the manuscript.}
 \end{document}

### 2020-05-21 manuscript/bmc_article.tex
Update manuscript folder for resubmission

@@
 \author[
-   addressref={aff1,aff2,aff5},                   % id's of addresses, e.g. {aff1,aff2}
-   corref={aff1},                       % id of corresponding address, if any
+   addressref={aff1,aff2,aff5,aff6},                   % id's of addresses, e.g. {aff1,aff2}
+   corref={aff6},                       % id of corresponding address, if any
    noteref={n2},                        % id's of article notes, if any
-   email={frank.foerster@uni-wuerzburg.de}   % email address
+   email={frank.foerster@computational.bio.uni-giessen.de}   % email address
 ]{\inits{FF}\fnm{Frank} \snm{Förster}}
@@
 }
-
 \address[id=aff5]{%
@@
   \postcode{35394}
+  \city{Gie\ss{}en},
+  \cny{Germany}
+}
+\address[id=aff6]{%
+  \orgname{Bioinformatics Core Facility of the University of Gie\ss{}en},
+  \street{Heinrich-Buff-Ring 58},
+  \postcode{35392}
   \city{Gie\ss{}en},
@@
 Different assemblers that are able to asses the plastid genome, have been developed.
-These assemblers often use data of whole genome sequencing experiments, which usually contain reads from the complete chloroplast genome as well, as input.
+These assemblers often use data of whole genome sequencing experiments, which usually contain reads from the complete chloroplast genome.
 
@@
 Our results show significant differences between the tested assemblers in terms of generating whole chloroplast genome sequences and computational requirements.
-The examination of more than \num{100} data sets with unknown plastid genomes led to the assembly of novel chloroplast genomes in almost \SI{50}{\percent} of the cases.
+The examination of \num{105} data sets from species with unknown plastid genomes led to the assembly of \num{20} novel chloroplast genomes.
 %\todo{on the novel set we only have 49/105 which is roughly 47 percent}
@@
 
-%\todo{Markus/Frank: YES should we host a specific page on the alitv page for all the novels? Here: \url{https://alitvteam.github.io/AliTV/chloroplast_benchmark/})}%
-For two assemblies, that were obtained by different assemblers, but not by \go{}, we kept one assembly obtained by \np{} and one from \fp{}.
-\todo{@frank: please check, my dataset contains 45 GO, 3 FP, 1NP}
-The resulting \num{49} sequences have been annotated with GeSeq \cite{geseq} and uploaded to NCBI Genbank (\cref{tab:accessions_suppl}).
+For three assemblies, that were obtained by different assemblers, but not by \go{}, we kept one assembly obtained by \np{} and two from \fp{}.
+All resulting \num{49} sequences have been annotated with GeSeq \cite{geseq}. 
 The median number of distinct genes annotated were 80 for coding sequences, 4 for rRNA and 27 for tRNA (\cref{tab:feature_count_novel}, \cref{fig:feature_count_novel}). 
-%\todo{FRANK: more info about the taxonomic distribution of our novels and how we extended the coverage of the tol}.  %% STILL 2 DO
+All sequences were stored in our repository \zenodorepo{}.
+To avoid multi submissions of the same sequence to Genbank, all \num{49} sequences have been inspected against Genbank database via BLAST.
+Finally, \num{20} sequences were uploaded to NCBI TPA:inferential (\cref{tab:accessions_suppl}) as novel chloroplast genomes.
 
@@
 
-%\todo{FRANK: Add discussion of novel}  %% STILL 2 DO
-% Yes, what have we leraned form the novel chloroplasts .. e.g. gene content 
 We observed no phylogenetic pattern in the success rate of the assemblers (\cref{fig:tree}).
@@
 Source code for all methods used is available at \cite{github-benchmark-repo} and archived in zenodo under \zenodorepo{}.
-All docker images are published on dockerhub \cite{dockerhub-benchmark} and are named with a leading \texttt{benchmark\_} (\cref{tab:dockerimages}).
+All used assembly tools are hosted on GitHub (\cref{tab:toolsversions}) and are encapsulated in docker containers.
+That docker containers are published on dockerhub \cite{dockerhub-benchmark} and are named with a leading \texttt{benchmark\_} (\cref{tab:dockerimages_suppl}).
 
@@
 We selected real data deposited at SRA \cite{sra2010}.
-We searched all data that matched \texttt{((((((("green plants"[orgn]) AND "wgs"[Strategy]) AND "illumina"[Platform]) AND "biomol dna"[Properties]) AND "paired"[Layout]) AND "random"[Selection])) AND "public"[Access]} \cite{sra_search_term}.
+We searched all data that matched \texttt{((((((("green plants"[orgn]) AND "wgs"[Strategy]) AND "illumina"[Platform]) AND "biomol dna"[Properties]) AND "paired"[Layout]) AND "random"[Selection])) AND "public"[Access]}\cite{sra_search_term}.
 For each species with a reference chloroplast in CpBase \cite{cpbase}, we selected one data set.
 In total, this amounted to \num{369} data sets (\cref{tab:real_dataset_details}) representing a broad spectrum of the green plants (\cref{fig:tree}).
-%\todo{Frank: Nochmal was zum Baum schreiben und novels dort mit aufnehmen!}  %% STILL 2 DO
 
@@
 %Therefore, the simulated perfect read files have been read repeatedly to achieve the required number of read pairs.
-We used our docker image setup (\cref{tab:dockerimages}) to run all assembly programs three times for each parameter setting.
+We used our docker image setup (\cref{tab:dockerimages_suppl}) to run all assembly programs three times for each parameter setting.
 The different settings combined different input data and different number of threads to use (\numlist{1;2;4;8}).
@@
 \begin{table}[h!]
-\caption{\textbf{Docker images used in our benchmark setup} SHA256 checksums are stated in \cref{tab:dockerimages_suppl}}
-%\todo{Frank: add software version column (maybe use git describe)} %% STILL 2 DO
-\label{tab:dockerimages}
+\caption{\textbf{Tools and version information used in our benchmark setup} All tools are wrapped into docker containers and stored on dockerhub \cite{dockerhub-benchmark}.
+The corresponding tags and SHA256 checksums are reported in \cref{tab:dockerimages_suppl}}
+\label{tab:toolsversions}
 \centering
-      \resizebox{\textwidth}{!}{\begin{tabular}{ccc}
+      \resizebox{\textwidth}{!}{\begin{tabular}{llc}
         \hline
-          Tool & Image name and tag\\ \hline
-          \ce & \dockerce \\
-          \cassp & \dockercassp \\
-          \fp & \dockerfp \\
-          \go & \dockergo \\
-          \ioga & \dockerioga \\
-          \np & \dockernp \\
-          \oa & \dockeroa \\ \hline
+        Tool & Source Repository & Commit used for benchmarking \\ \hline
+        \go & \url{https://github.com/Kinggerm/GetOrganelle.git} & \texttt{587c1c51c34e270eb9178a42a77a5150157e6925} \\
+        \ioga & \url{https://github.com/holmrenser/IOGA.git} & \texttt{c460ea9d9fe176fec2bd76d369b0cbb36793b2bf} \\
+        \np & \url{https://github.com/ndierckx/NOVOPlasty.git} & \texttt{6af0894f8ea1d76a1b71df9cb762cf6e48dceac1} \\
+        \ce & \url{https://github.com/chloroExtractorTeam/chloroExtractor.git} & \texttt{87364e48ec84a3f6ee91fc8d995b0bda5a0fa82d} \\
+        \cassp & \url{https://github.com/eead-csic-compbio/chloroplast_assembly_protocol.git} & \texttt{250d16ac02005d6a5939bf182b3d2995d0e88229} \\
+        \fp & \url{https://github.com/mrmckain/Fast-Plast.git} & \texttt{7e32b2e797fd1f49d32d6559e8345afefbaff803} \\
+        \oa & \url{https://git.metabarcoding.org/org-asm/org-asm.git} & \texttt{830313acae3ca773b63f6bea9fc6d017e021bde5} \\ \hline
+%          Tool & Image name and tag\\ \hline
+%          \ce & \dockerce \\
+%          \cassp & \dockercassp \\
+%          \fp & \dockerfp \\
+%          \go & \dockergo \\
+%          \ioga & \dockerioga \\
+%          \np & \dockernp \\
+%          \oa & \dockeroa \\ \hline
       \end{tabular}}

### 2020-08-20 manuscript/bmc_article.tex
Preparation for revision submission

@@
 }
-\myexternaldocument{supplement}
+\myexternaldocument{additionalfile1}
 
@@
 
+\newcommand{\crefsupp}[1]{Additional file\,1: \cref{#1}}
+
 % List of docker images
@@
 
-\title{The landscape of chloroplast genome assembly tools}
+\title{A systematic comparison of  chloroplast genome assembly tools}
 
@@
 \author[
-   addressref={aff1,aff3,aff4 },
+   addressref={aff1,aff3,aff4,aff5},
    noteref={n2},
@@
 \author[
-   addressref={aff1,aff2,aff5,aff6},                   % id's of addresses, e.g. {aff1,aff2}
+   addressref={aff1,aff2,aff6,aff7,aff8},                   % id's of addresses, e.g. {aff1,aff2}
    corref={aff6},                       % id of corresponding address, if any
@@
 \address[id=aff5]{%
+  \orgname{@IIMOG}
+ }
+\address[id=aff6]{%
   \orgname{Fraunhofer IME-BR},
-  \street{Winchester Str.\ 2},
-  \postcode{35394}
+  \street{Ohlebergsweg 12},
+  \postcode{35392}
   \city{Gie\ss{}en},
@@
 }
-\address[id=aff6]{%
+\address[id=aff7]{%
   \orgname{Bioinformatics Core Facility of the University of Gie\ss{}en},
@@
 }
+\address[id=aff8]{%
+  \orgname{@frank\_foerster}
+ }
 
@@
 \begin{abstract} % abstract
-%One or two sentences providing a basic introduction to the field, comprehensible to a scientist in any discipline.
-Chloroplasts are intracellular organelles that enable plants to conduct photosynthesis.
+\parttitle{Background} Chloroplasts are intracellular organelles that enable plants to conduct photosynthesis.
 They arose through the symbiotic integration of a prokaryotic cell into an eukaryotic host cell and still contain their own genomes with distinct genomic information.
 Plastid genomes accommodate essential genes and are regularly utilized in biotechnology or phylogenetics.
-%Two to three sentences of more detailed background, comprehensible to scientists in related disciplines.
-Different assemblers that are able to asses the plastid genome, have been developed.
+Different assemblers that are able to assess the plastid genome have been developed.
 These assemblers often use data of whole genome sequencing experiments, which usually contain reads from the complete chloroplast genome.
 
-%One sentence clearly stating the general problem being addressed by this particular study.
-The performance of different assembly tools has never been systematically compared. %to each other concerning success rate or computational requirements.
-%One sentence summarising the main result (with the words “here we show” or their equivalent).
-Here we present a benchmark of seven chloroplast assembly tools, capable to succeed in more than \SI{60}{\percent} of known real data sets.
-%Two or three sentences explaining what the main result reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
+\parttitle{Results} The performance of different assembly tools has never been systematically compared.
+Here we present a benchmark of seven chloroplast assembly tools, capable of succeeding in more than \SI{60}{\percent} of known real data sets.
 Our results show significant differences between the tested assemblers in terms of generating whole chloroplast genome sequences and computational requirements.
-The examination of \num{105} data sets from species with unknown plastid genomes led to the assembly of \num{20} novel chloroplast genomes.
-%\todo{on the novel set we only have 49/105 which is roughly 47 percent}
-%One or two sentences to put the results into a more general context. 
-We created docker images for each tested tool that are freely available for the scientific community and ensure reproducibility of the analyses.
-These containers allow to analyze and screen data sets for chloroplast genomes using standard computational infrastructure.
-%Two or three sentences to provide a broader perspective, readily comprehensible to a scientist in any discipline, may be included in the first paragraph if the editor considers that the accessibility of the paper is significantly enhanced by their inclusion.
-Thus, large scale screening for chloroplasts as hidden treasures within genomic sequencing data is feasible.
-
-%\ff{Abstract}
-%Useful as always: \url{https://cbs.umn.edu/sites/cbs.umn.edu/files/public/downloads/Annotated_Nature_abstract.pdf}
-%The special issue will accept manuscripts presenting:
-%
-%- in-depth analyses of advantages
-%
-%-limitations of state-of-the-art methods
-%
-%-demonstration on a variety of representative datasets and simulations
-%
-%-clear guidelines/recommendations for the end-user
-%
-%-insight into future directions for methods
-%\parttitle{First part title} %if any
-%Text for this section.
-%
-%\parttitle{Second part title} %if any
-%Text for this section.
+The examination of \num{105}~data sets from species with unknown plastid genomes leads to the assembly of \num{20}~novel chloroplast genomes.
+
+\parttitle{Conclusions} We create docker images for each tested tool that are freely available for the scientific community and ensure reproducibility of the analyses.
+These containers allow the analysis and screening of data sets for chloroplast genomes using standard computational infrastructure.
+Thus, large scale screening for chloroplasts within genomic sequencing data is feasible.
 \end{abstract}
@@
 Structurally, two inverted repeats (\glspl{ir}) named \gls{ir}\textsubscript{A} and \gls{ir}\textsubscript{B} of \SIrange{10}{76}{\kilo\basepair} divide the chloroplast genome into a 
-%long single copy (\gls{lsc}) and a short single copy (\gls{ssc}) region
 \gls{lsc} and a \gls{ssc} region
@@
 The extraction of chloroplast reads can be achieved by mapping the reads to a reference chloroplast. \cite{Vinga2012}.
-%\todo{gibt es dazu ein beispiel in unserem set? (niklas)}
 A different approach that does not depend on the availability of a reference chloroplast, uses the higher coverage of reads originating from the chloroplast \cite{Chan2013}.
@@
 An example for this is implemented in \ce{} \cite{j_ankenbrand_chloroextractor:_2018}. 
-%\todo{ce ist hier der einzig explizit genannte Assembler, das wirkt wie bias :) entfernen?
-Nope...
-Steht klar ein Beispiel und wir haben nun mal den angesehen...
-Würde ich jetzt einmal so drin lassen.
-Alternativ nehmen wir noch einen dazu}
-%Arthur : Ich würds so lassen.
 A third method, which is for example used by \np{} \cite{dierckxsens_novoplasty:_2017}, combines both approaches by using a reference chloroplast as seed and simultaneously assembling the reads based on $k$-mers.
-
-%\ak{e.g.
-HomBlocks: A multiple-alignment construction pipeline for organelle phylogenomics based on locally collinear block searching, aber ist nicht inkluded, also können wir zitieren, müssen aber nicht}
 
@@
 \subsection*{Performance metrics}
-%\subsection*{Computational Resources}
-%Table and figure of performance evaluation.
-Including RAM, I/O, runtime, parallelization ability, CPU usage.
-Free text description of results, range, mean/median, effect of input size, threads parameter, ...
 All described tools have been tested with regard to their assembly time, memory and CPU utilization.
@@
 The most time efficient tool was \ce{}, which was a little faster than \np{} and \cassp{}.
-%% multithreading
 
@@
 Both \np{} and \oa{} required almost the same time independent of being allowed to utilize \numlist[list-final-separator={, or }]{1;2;4;8} threads.
-In contrast, \cassp{}, \ce{}, \go  and \fp{} all profited from multi-threading settings  (\cref{fig:performance_runtime,fig:performance_memory_cpu,tab:perform25K_suppl,tab:perform250K_suppl,tab:perform2.5M_suppl}).
+In contrast, \cassp{}, \ce{}, \go  and \fp{} all profited from multi-threading settings  (\cref{fig:performance_runtime,fig:performance_memory_cpu} and \crefsupp{tab:perform25K_suppl,tab:perform250K_suppl,tab:perform2.5M_suppl}).
 
 \subsubsection*{Memory and CPU Usage }
-The peak and mean CPU usage, as well as peak memory and disk usage were recorded for all assemblers based on the same input data set and number of threads  (\cref{fig:performance_memory_cpu,tab:perform25K_suppl,tab:perform250K_suppl,tab:perform2.5M_suppl}).
+The peak and mean CPU usage, as well as peak memory and disk usage were recorded for all assemblers based on the same input data set and number of threads  (\cref{fig:performance_memory_cpu} and \crefsupp{tab:perform25K_suppl,tab:perform250K_suppl,tab:perform2.5M_suppl}).
 In general, the size of the input data influenced the peak memory usage with the exception of \ce{} and \ioga{}.
@@
 All programs profited from a higher number of threads, if the size of the input data was increased concerning their memory and CPU usage footprint.
-%\todo{oben steht nicht alle? (niklas)}
-% Frank: Hier geht es um Memory und CPU-Usage... Oben nur um Runtime
 In contrast, the disk usage was independent of the size of the input data and the number of threads for all assemblers.
-
-%but the factor between the programs exceeds a factor of \num{100}.
 
@@
 Overall \go{} and \fp{} were the most successful tools on the simulated data while \cassp{} and \ioga{} were unable to successfully assemble any chloroplasts out of the \num{16} different data sets.
-%The only assembler obtaining perfect results according to our score for the simulated data sets is \go{} (\cref{fig:simulated,tab:scores_simulated}).
-%\ioga{} and \cassp{} showed the worst performance, being unable to fully assemble a single chloroplast out of \num{14} runs.
-%\np{} performed second best with scores above \num{80} for all data sets, only failing to resolve the contigs into one single circular chloroplast assembly.
-%The overall performance is best, when the input data consists purely of chloroplast reads.
-%Only \ioga{} and \cassp{} failed to deliver any results under this scenario once.
 
@@
 We observed considerable differences for the tested assemblers, if we compared the generated alignments against the reference chloroplasts (\cref{fig:swarmplot}).
-%\todo{hier ein halbsatz, was im score berücksichtigt wird? (niklas)}
-%\todo{Jan: are these values correct? is table 3 up to date? This whole section might need to be rewritten, Yes all the tables and plots are up to date and to my knowledge correct}
 The highest scores were achieved by \go{} with a median of \num{99.8} and \num{210} circular assemblies out of a total of 360 assemblies that resulted in an output (\cref{tab:scores_real}).
@@
 \ioga{} and \cassp{} were both unable to assemble a circular, single-contig genome (\cref{tab:scores_real}, \cref{fig:upset}).
-%\textit{swarm plot goes here}
-%% Den upset plot eventuell erst in die Discussion reinbringen ? Da wir davon ableiten welche tools wir empfehlen?
 
@@
 \ce{} was the only tool able to reproduce the same scores in all runs (\cref{fig:consistency}).
-%\todo{Frank or Jan: whoever wrote this sentence, what does it mean? \ce{} produced completely unsuccessful assemblies but consistently. Please re-write or remove! Dont think it was me}
 \go{}, \oa{}, \cassp{}, and \ioga{} generated some assemblies that were unsuccessful in one run, but produced an output in the other attempt.
-For these assemblers the scores were virtually identical if both runs were succesful. %\todo{Jan: identical? basically identical}.
+For these assemblers the scores were virtually identical if both runs were succesful.
 Both \fp{} and \np{} show only minor changes for the successful assemblies, leading to arrow-shaped scatter plots (\cref{fig:consistency}).
-%\ak{link to figure scatter plots is missing}
 \ce{} appears to be the most robust assembler, showing no deviations between the two runs.
@@
 To avoid multi submissions of the same sequence to Genbank, all \num{49} sequences have been inspected against Genbank database via BLAST.
-Finally, \num{20} sequences were uploaded to NCBI TPA:inferential (\cref{tab:accessions_suppl}) as novel chloroplast genomes.
+Finally, \num{20} sequences were uploaded to NCBI TPA:inferential (\crefsupp{tab:accessions_suppl}) as novel chloroplast genomes.
+Moreover, a search for the species name unveiled that \num{7} of the \num{20} sequences are used as ornamental plant, in folk medicine, or as crop plant.
 
@@
 This procedure maximizes the chance of effectively and efficiently recovering the circular chloroplast genome.
-%\ak{what if both lead to qualitative different results?, always trust \go{} , or could one compute a high-confidence assembly by combining different results ?, might be a point for future directions.}
 If both programs fail, it is recommended to try \np{} or manually fine-tune the parameters of the different tools.
@@
 For nearly half of the analyzed data without available chloroplast genome, we could generate complete assemblies using at least one of the tools.
-%\todo{Frank: where do the 60 percent come from?, is it not more like 40?}
 
@@
 Ultimately, large scale studies reconstructing hundreds or thousands of chloroplast genomes are now feasible using the currently available tools.
-%Outlook: next step in the pipeline is annotation. There is a similar problem: many tools, which one to use? 
-%A large scale study reconstructing chloroplasts throughout SRA (or \num{1001} genome project) is feasible and promising using the existing tools (estimated runtime, number of novel chloroplasts).
-%A meta-tool that automatically combines the different programs could be developed.
-%The benchmarking study could be augmented to automatically select the closest reference from the database and provide that to any tool that can take advantage of references.
 
@@
 \subsection*{Data availability}
-Source code for all methods used is available at \cite{github-benchmark-repo} and archived in zenodo under \zenodorepo{}.
+Source code for all methods used is available at \cite{github-benchmark-repo} and archived in Zenodo under \zenodorepo{}.
 All used assembly tools are hosted on GitHub (\cref{tab:toolsversions}) and are encapsulated in docker containers.
-That docker containers are published on dockerhub \cite{dockerhub-benchmark} and are named with a leading \texttt{benchmark\_} (\cref{tab:dockerimages_suppl}).
+That docker containers are published on dockerhub \cite{dockerhub-benchmark} and are named with a leading \texttt{benchmark\_} (\crefsupp{tab:dockerimages_suppl}).
 
 To enable a fair comparison of all tools, we generated simulated sequencing data.
-Those simulated data sets are stored at zenodo \zenododataset{}.
+Those simulated data sets are stored at Zenodo \zenododataset{}.
+All resulting assemblies are available from Zenodo \cite{zenodoassemblies}.
 This study adheres to the guidelines for computational method benchmarking \cite{weber_essential_2018}.
@@
 Singularity container were built from docker images for usage on an HPC-environment using Singularity v.2.5.2 \cite{kurtzer2017singularity}.
-All singularity containers were run on %the Julia-HPC 
-Intel® Xeon® Gold \num{6140} Processors using a Slurm workload manager version 17.11.8 \cite{Jette02slurm}.
+All singularity containers were run on Intel® Xeon® Gold \num{6140} Processors using a Slurm workload manager version 17.11.8 \cite{Jette02slurm}.
 Assemblies were run on \num{4} threads using \SI{10}{\gibi\byte} RAM with a time limit of \SI{48}{\hour}.
@@
 The final data contained \SI{30}{\times} genome coverage and \SI{300}{\times} mitochondrial coverage, except the \num{0}:\num{1} ratio.
-%\todo{Markus: mito ist richtig, oder?}
-% Frank nach Rücksprache mit Markus: Ja... Ist Mitochondrium!
 Additionally, we generated data with different read lengths (\SIlist{150;250}{\basepair}). We further sampled each data set to create another version containing exactly 2\,million read pairs.
-
-%(circular for chloro and mito). No errors, no insert size variation, perfect quality, equal coverage.
 
@@
 \subsubsection*{Novel data}
-To evaluate the performance for chloroplasts without a reference in CpBase \cite{cpbase}, we sampled \num{105} data sets from the SRA \cite{sra2010} real data set described above (\cref{tab:novels_supp}).
+To evaluate the performance for chloroplasts without a reference in CpBase \cite{cpbase}, we sampled \num{105} data sets from the SRA \cite{sra2010} real data set described above (\crefsupp{tab:novels_supp}).
 For each entry within that novel data set the number of lineage splits between the source taxon and the related references from CpBase was calculated according to NCBI Taxonomy \cite{ncbitaxonomy}.
@@
 Due to a lack of a clear definition, we followed the definition of \fp{} \cite{fastplast_orientation_issue}.
-%\todo{Frank: Beschreibung des Submission prozesses und der Datenvorbereitung}
-%to the closest relative as well as the last common ancestor have been calculated \todo{see table X (Frank)}. \todo{further description of the method (Frank)}
 
@@
 \subsubsection*{Computational Resources}
-%Due to computational resources are limited, we evaluated the effect of different input parameters.
 We recorded the mean and the peak CPU usage, the peak memory consumption, and the size of the assembly folder for each program. 
 As input data, we used different data sets comprising \numlist{25000;250000;2500000} read pairs sampled from  our simulated reads.
-%Therefore, the simulated perfect read files have been read repeatedly to achieve the required number of read pairs.
-We used our docker image setup (\cref{tab:dockerimages_suppl}) to run all assembly programs three times for each parameter setting.
+We used our docker image setup (\crefsupp{tab:dockerimages_suppl}) to run all assembly programs three times for each parameter setting.
 The different settings combined different input data and different number of threads to use (\numlist{1;2;4;8}).
@@
 (5) Is the tool Open Source?
-%\begin{itemize}
-%    \item Is the tool easy to install? 
-%    \item Is there a way to test the installation or a tutorial on how to use the tool? 
-%    \item Is there a good documentation on the parameter settings? 
-%    \item Is the tool maintained (issues answered, implementation of new features)? 
-%    \item Is the tool Open Source?
-%\end{itemize}
 
@@
 \subsubsection*{Quantitative}
-
-%We use continuity: number of contigs.
-%Completeness: Number of covered bases on reference (when aligning assembly).
-%Correctness: Number of covered bases in assembly (when aligning reference).
-%Repeat resolution: Difference between above two measures (indicates collapsed or expanded repeats)
-%
-%\nocite{oreg,schn,pond,smith,marg,hunn,advi,koha,mouse}
-
-%We want to quantify continuity, completeness, correctness and repeat resolution.
-
 For each data set and assembler the generated chloroplast genome was compared to the respective reference genome using a pairwise alignment obtained with \texttt{minimap2} v2.16 \cite{li2018minimap2}.
@@
 These cutoffs were selected as they produced the highest f-score on the real data set where true assignment (success/failure) was assumed based on the score (success if score \num{99} or higher).
-%\todo{Frank: should we add some supplementary figure from plots/novel\_cutoffs.pdf?}
-% Frank: Nicht notwendig
 
 \subsubsection*{Consistency}
-To ensure consistency of the obtained results, we rerun and re-evaluated all the assemblies. %\todo{JAN: Das sind jetzt aber alle, oder? Comment: Ja das sind alle }
+To ensure consistency of the obtained results, we rerun and re-evaluated all the assemblies. 
 The resulting assemblies were scored again as described and the scores of the first and the second run were compared to each other
@@
 
+\section*{Funding}
+Not applicable.
+
+\section*{Ethics approval}
+Not applicable.
+
 \section*{Availability of data and materials}
@@
 The input data sets can be generated using the raw reads from NCBI SRA (links for each data set in \cref{tab:real_dataset_details}).
-The resulting assemblies are avaiable from Zenodo \cite{zenodoassemblies}.
+The resulting assemblies are available from Zenodo \cite{zenodoassemblies}.
 
@@
   \includegraphics[width=0.9\textwidth]{manuscript/plots/feature_counts_distinct.png}
-  \caption{\csentence{Supplemental Figure. Number of distinct features in novel chloroplast genomes} The distribution of feature types tRNA, rRNA, and coding sequence (CDS) are shown separately.%
+  \caption{\csentence{Number of distinct features in novel chloroplast genomes} The distribution of feature types tRNA, rRNA, and coding sequence (CDS) are shown separately.%
       }
@@
 \caption{\textbf{Tools and version information used in our benchmark setup} All tools are wrapped into docker containers and stored on dockerhub \cite{dockerhub-benchmark}.
-The corresponding tags and SHA256 checksums are reported in \cref{tab:dockerimages_suppl}}
+The corresponding tags and SHA256 checksums are reported in \crefsupp{tab:dockerimages_suppl}}
 \label{tab:toolsversions}
@@
         \oa & \url{https://git.metabarcoding.org/org-asm/org-asm.git} & \texttt{830313acae3ca773b63f6bea9fc6d017e021bde5} \\ \hline
-%          Tool & Image name and tag\\ \hline
-%          \ce & \dockerce \\
-%          \cassp & \dockercassp \\
-%          \fp & \dockerfp \\
-%          \go & \dockergo \\
-%          \ioga & \dockerioga \\
-%          \np & \dockernp \\
-%          \oa & \dockeroa \\ \hline
       \end{tabular}}
@@
 \begin{table}[h!]
-\caption{\textbf{Supplemenatal Table.
-Number of distinct features in novel chloroplast genomes} The distribution (mean, standard deviation (SD), medain, interquartile range (IQR)) of feature types tRNA, rRNA, and coding sequence (CDS) are listed separately.}
+\caption{\textbf{Number of distinct features in novel chloroplast genomes} The distribution (mean, standard deviation (SD), medain, interquartile range (IQR)) of feature types tRNA, rRNA, and coding sequence (CDS) are listed separately.}
 \label{tab:feature_count_novel}

### 2020-08-21 manuscript/all/bmc_article.tex
Delete old manuscript directory

--- 2020-08-20 manuscript/bmc_article.tex
@@
 \begin{figure}[h!]
-  \includegraphics[width=\textwidth]{plots/comp_time_log.pdf}
+  \includegraphics[width=\textwidth]{comp_time_log.pdf}
   \caption{\csentence{Computation time depending on number of threads and size of input data}
@@
 \begin{figure}[h!]
-  \includegraphics[width=\textwidth]{plots/usage_amount_threads.pdf}
+  \includegraphics[width=\textwidth]{usage_amount_threads.pdf}
   \caption{\csentence{Performance metrics}
@@
 \begin{figure}[h!]
-  \includegraphics[width=\textwidth]{plots/sim_tiles.pdf}
+  \includegraphics[width=\textwidth]{sim_tiles.pdf}
   \caption{\csentence{Score of assemblies on simulated data}
@@
   \begin{figure}[h!]
-  \includegraphics[width=\textwidth]{plots/swarm.pdf}
+  \includegraphics[width=\textwidth]{swarm.pdf}
   \caption{\csentence{Results of scoring of the seven assemblers}
@@
 \begin{figure}[h!]
-  \includegraphics[width=\textwidth,page=2]{plots/upset.pdf}
+  \includegraphics[width=\textwidth,page=2]{upset.pdf}
   \caption{\csentence{Upset plot \cite{lex2014upset} comparing success of assemblers on the real data sets}
@@
 \begin{figure}[h!]
-  \includegraphics[width=\textwidth]{plots/repro.pdf}
+  \includegraphics[width=\textwidth]{repro.pdf}
   \caption{\csentence{Scores between two repeated runs for consistency testing}
@@
 \begin{figure}[h!]
-  \includegraphics[width=\textwidth]{plots/real_datasets_tree.pdf}
+  \includegraphics[width=\textwidth]{real_datasets_tree.pdf}
   \caption{\csentence{Success for chloroplast assembly shows no taxonomic bias} Success of assemblers on real data sets on tree derived from NCBI taxonomy \cite{ncbi2011}.
@@
 \begin{figure}[h!]
-  \includegraphics[width=\textwidth]{manuscript/plots/upset_novel.pdf}
+  \includegraphics[width=\textwidth]{upset_novel.pdf}
   \caption{\csentence{Upset plot \cite{lex2014upset} comparing success of assemblers on the novel data sets}
@@
   \centering
-  \includegraphics[width=0.9\textwidth]{manuscript/plots/AliTV.png}
+  \includegraphics[width=0.9\textwidth]{AliTV.png}
   \caption{\csentence{AliTV plot \cite{alitv} showing alignments of the different assemblers compared to each other and the reference} Each blue bar in the plot corresponds to an assembly of the \plant{Ob} chloroplast (DRR053294).
@@
   \centering
-  \includegraphics[width=0.9\textwidth]{manuscript/plots/feature_counts_distinct.png}
+  \includegraphics[width=0.9\textwidth]{feature_counts_distinct.png}
   \caption{\csentence{Number of distinct features in novel chloroplast genomes} The distribution of feature types tRNA, rRNA, and coding sequence (CDS) are shown separately.%

### 2020-08-21 manuscript/sra_table_generation/generate_sra_ref.sh

@@ -1,11 +1,0 @@
-#!/bin/bash
-
-# Get the data from NCBI
-for i in $(sed '1d' ../sets_re_runs.csv | tr -d '"' | cut -f 2 -d ","); do sra-stat --quick ${i}; done | tee sets_sra-info.txt
-
-# Create a temporary file with combined information
-perl -ne 'chomp; my ($id, $tag, $reads, $rest) = split(/\|/, $_); my ($readnumber, $basenumber, undef) = split(":", $reads); $h{$id}{reads}+=$readnumber; $h{$id}{bases}+=$basenumber; END{ foreach my $id (sort keys %h) { printf "%s\t%d\t%d\t%.0f\n", $id, $h{$id}{reads}, $h{$id}{bases}, ($h{$id}{bases}/$h{$id}{reads}/2); }}' sets_sra-info.txt >blub.txt
-
-wget https://raw.githubusercontent.com/chloroExtractorTeam/benchmark/master/data/real/real_datasets.t
-
-join blub.txt <( join <(awk -F"," '{printf "%s\t%s\n", $2,$3}' sets_re_runs.csv | sed '/Re-eval/d' | sort | tr -d '"') <(sort real_datasets.tsv))  | perl generate_tab.pl | tee ../sra_ref.tex

### 2020-08-21 manuscript/sra_table_generation/generate_tab.pl

@@ -1,38 +1,0 @@
-#!/usr/bin/env perl
-    
-use strict;
-use warnings;
-
-my @dat = ();
-
-while (<>)
-{
-   chomp;
-
-   my @fields = split(/\s+/, $_);
-   
-   my ($sra, $reads, $bases, $readlen, $used, $genus, $epithet, $spotlen, $nt);
-
-   $sra     = shift(@fields);
-   $reads   = shift(@fields);
-   $bases   = shift(@fields);
-   $readlen = shift(@fields);
-   $used    = shift(@fields);
-   $genus   = shift(@fields);
-   $nt      = pop(@fields);
-   $spotlen = pop(@fields);
-   $epithet = join(" ", @fields);
-   
-   my $taxon = '\textit{'.$genus." ".$epithet.'}';
-   $sra = sprintf '\href{https://trace.ncbi.nlm.nih.gov/Traces/sra/?run=%s}{%s}', $sra, $sra;
-   my $nt2 = $nt;
-   $nt2 =~ s/_/\\_/g;
-   $nt  = sprintf '\href{https://www.ncbi.nlm.nih.gov/nuccore/%s}{%s}', $nt, $nt2;
-
-   push(@dat, join(" & ", $taxon, $sra, $nt, '\num{'.$reads.'}', '\num{'.$bases.'}', '\num{'.$readlen.'}', $used)." \\\\\n");
-}
-
-foreach (sort @dat)
-{
-   print $_;
-}

### 2020-08-21 manuscript/additionalfile1.tex
State for resubmission 2

--- 2020-05-19 manuscript/supplement.tex
@@
 
-\title{The landscape of chloroplast genome assembly
-tools}
+\title{A systematic comparison of  chloroplast genome assembly tools}
 \subtitle{Supplemental material}
@@
 
+\begin{landscape}
+\setlength{\LTcapwidth}{1.5\textwidth}
 \begin{table}[ht]
@@
 \centering
-\begin{tabular}{cccc}\toprule
-Species & SRA-Accession & Assembler & Genbank-Accession \\\midrule
-\plant{At} & AAAA & AAA & AAAA \\\bottomrule
+\begin{tabular}{lcccc}\toprule
+Species & SRA-Accession & Assembler & Uses & Genbank-Accession \\\midrule
+\emph{Antirrhinum majus \emph{subsp.} Striatum} & ERR2744402 & \go{} & ornamental plant & - \\
+\emph{Antirrhinum majus \emph{var.} pseudomajus} & ERR2744401 & \go{} & ornamental plant & - \\
+\emph{Arachis magna} & SRR8481359 & \go{} & - & - \\
+\emph{Boechera stricta} & SRR6821984 & \np{} & - & - \\
+\emph{Buddleja globosa} & SRR6331521 & \go{} & folk medicine & - \\
+\emph{Congea tomentosa} & SRR6940055 & \go{} & - & - \\
+\emph{Cucurbita argyrosperma} & SRR2531270 & \go{} & crop plant & - \\
+\emph{Cucurbita ecuadorensis} & SRR2531278 & \go{} & - & - \\
+\emph{Cucurbita lundelliana} & SRR2531284 & \go{} & - & - \\
+\emph{Cucurbita okeechobeensis} & SRR2531280 & \go{} & - & - \\
+\emph{Cucurbita pedatifolia} & SRR2531289 & \go{} & - & - \\
+\emph{Cuscuta campestris} & ERR1917165 & \go{} & - & - \\
+\emph{Erysimum baeticum} & SRR7223704 & \go{} & - & - \\
+\emph{Erysimum nevadense} & SRR7223710 & \go{} & - & - \\
+\emph{Garrya flavescens} & SRR2401791 & \go{} & - & - \\
+\emph{Gerbera hybrid cultivar} & SRR2154064 & \go{} & - & -\\
+\emph{Leucanthemum vulgare} & ERR3089127 & \go{} & ornamental plant & - \\
+\emph{Petraeovitex bambusetorum} & SRR6940081 & \go{} & - & - \\
+\emph{Pityopsis graminifolia \emph{var.} Graminifolia} & SRR4457826 & \go{} & ornamental plant & - \\
+\emph{Pityopsis graminifolia \emph{var.} tenuifolia} & SRR4457835 & \go{} & ornamental plant & - \\
+\bottomrule
 \end{tabular}
 \end{table}
+\end{landscape}
 
